### 2014-03-02 src/article/article.tex
tex added

%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[twocolumn,english]{paper}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=2.65cm,bmargin=2.65cm,lmargin=2.65cm,rmargin=2.65cm}
\setlength{\parindent}{0bp}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{setspace}
\onehalfspacing

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% A simple dot to overcome graphicx limitations
\newcommand{\lyxdot}{.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\numberwithin{equation}{section}
\numberwithin{figure}{section}

\makeatother

\usepackage{babel}
\begin{document}

\title{This is Article}

\author{Christian Poveda Ruiz}
\maketitle
\begin{abstract}
FIXME: Write abstract
\end{abstract}

\section{Introduction}

FIXME: Multidark

FIXME: NFW profile

FIXME: MCMC

\section{State of Art}

\section{What did I do?}

FIXME: Which simulation? $m=1.7\times10^{11}\ M_{\odot}$

$ $

In order to obtain a mass profile for each halo in funcion of the
radius, the center of each halo must be calculated. However the center
of mass will not give an accurate position for the center because
some haloes are highly irregular, is more convenient to take the gravitational
potential for each particle

\[
\phi\left(\boldsymbol{r}_{n}\right)=-\sum_{j\neq i}\frac{1}{\left\Vert \boldsymbol{r}_{n}-\boldsymbol{r}_{j}\right\Vert }
\]
Take $\boldsymbol{r}_{0}=\min\left(\phi\left(\boldsymbol{r}_{n}\right)\right)$
as the center then define new coordinates $\boldsymbol{r}_{n}^{\prime}=\boldsymbol{r}_{0}-\boldsymbol{r}_{n}$,
this $\boldsymbol{r}_{0}$ will be in the most relevant region for
the dynamics of each halo. Organizing the $\left\{ \boldsymbol{r}_{n}^{\prime}\right\} $
in crescent order, the accumulated mass for each $\boldsymbol{r}_{n}^{\prime}$
will be $m_{n}=nm$.

$ $

FIXME: Mass profile of a halo

$ $

The last part of the process consists in fitting the NFW mass profile
to the $m_{n}$ data using the Metropolis-Hastings algorithm to sample
the Likelihood ${\cal L}\left(\rho_{0},r_{s}\right)=\exp\left(-\frac{1}{2}\chi^{2}\left(\rho_{0},r_{s}\right)\right)$,
where $\chi^{2}\left(\rho_{0},r_{s}\right)=\sum\limits _{n}\left|m_{n}-m\left(\boldsymbol{r}_{n}^{\prime},\rho_{0},r_{s}\right)\right|^{2}$,
and take the values of $\rho_{0}$ and $r_{s}$ where the Likelihood
is maximum.

\section{Results}

\subsection{Trial Problem with several Generated Halos }

FIXME: I tested it with HaloGenerator

\subsection{Results from the simulation}

FIXME: Plot with error bars

\begin{figure}
\begin{centering}
\includegraphics[scale=0.43]{/home/christian/Documentos/git/Montecarlo-NFW/data/results/results_2014-02-11-23:43:20/rs}
\par\end{centering}

\caption{}

\end{figure}

\subsection{What kind of implications (Low resolution simulations, other fitting
algorithms)}

\section{Conclusions}
\end{document}

### 2014-03-02 src/catalog.py
fixed some mistakes

@@ -1,5 +1,6 @@
 import numpy as np, pylab, sys, matplotlib, plotter
 from matplotlib.mlab import griddata
+from scipy.optimize import curve_fit
 
 def distance(x1,y1,z1,x2,y2,z2):
     return np.sqrt(((x1-x2)**2.0)+((y1-y2)**2.0)+((z1-z2)**2.0))
@@ -20,11 +21,14 @@ mcmc_rs_min = mcmc[:,9]
 mcmc_rvir = mcmc[:,10]
 mcmc_c = mcmc[:,11]
 
+pylab.plot(np.log10(mcmc_rho0),np.log10(f(mcmc_rho0,param[0],param[1],param[2])),'or')
+pylab.plot(np.log10(mcmc_rho0),np.log10(mcmc_rs),'.k')
+pylab.show()
+
 bdmv_id = bdmv[:,0]
 bdmv_x = bdmv[:,1]
 bdmv_y = bdmv[:,2]
 bdmv_z = bdmv[:,3]
-bdmv_rho0 = bdmv[:,7]
 bdmv_rvir = bdmv[:,7]
 bdmv_c = bdmv[:,8]
 bdmv_rs = bdmv_rvir/bdmv_c

### 2014-03-02 src/main.py

@@ -99,7 +99,6 @@ for filename in os.listdir('./'+str(sys.argv[1])):
         plotter.mass(radius, mass, parameters)
         plotter.logmass(radius, mass, parameters)
         plotter.logdensity(r_density, density, parameters)
-        plotter.random_walk(a_walk,b_walk,n_iterations)
         plotter.rainbow_likelihood(a_walk,b_walk,chi2)
 
         sys.stdout.write('Done\n')
@@ -115,7 +114,7 @@ for filename in os.listdir('./'+str(sys.argv[1])):
         c = r_vir/scale_radius
     else:
         r_vir = 0
-        c = 0
+        c = -99
 
     export = open('results_'+now+'.dat', 'a')
     rho_max, rho_min = np.exp(fit.error_bars(a_walk,a,'log'))

### 2014-04-13 data/test/test_stack_3/test.py
new test with concentration

@@ -1,0 +1,21 @@
+import numpy as np, pylab
+
+data = np.loadtxt('gets_center.csv',delimiter=',')
+orig = np.loadtxt('parameters.dat',delimiter=',')
+data = data[data[:,0].argsort()]
+print data
+c_bdmv = data[:,4]
+c_bdmw = data[:,7]
+
+r_bdmv = data[:,10]
+r_bdmw = data[:,11]
+
+rs_bdmv = r_bdmv/c_bdmv
+rs_bdmw = r_bdmw/c_bdmw
+
+rs = orig[:,1]
+
+pylab.plot(rs,rs,'-k')
+pylab.plot(rs,rs_bdmv,'ob')
+pylab.plot(rs,rs_bdmw,'or')
+pylab.show()

### 2014-04-14 data/test/test.py
new test

@@ -1,95 +1,125 @@
 import numpy as np, pylab
 
-real = np.loadtxt('parameters.dat',delimiter=',')
-auto = np.loadtxt('auto_center.csv',delimiter=',')
-gets = np.loadtxt('gets_center.csv',delimiter=',')
+data = np.loadtxt('gets_center.csv',delimiter=',')
 
-auto = auto[auto[:,0].argsort()]
-gets =gets[gets[:,0].argsort()]
+orig = np.loadtxt('parameters.dat',delimiter=',')
+data = data[data[:,0].argsort()]
 
-real_a = real[:,0]
-auto_a,auto_amin,auto_amax = auto[:,4],auto[:,5],auto[:,6]
-gets_a,gets_amin,gets_amax = gets[:,4],gets[:,5],gets[:,6]
-auto_asigma = np.array([auto_amax-auto_a,auto_a-auto_amin])
-gets_asigma = np.array([gets_amax-gets_a,gets_a-gets_amin])
+c_bdmv = data[:,4]
+c_bdmw = data[:,7]
 
-real_b = real[:,1]
-auto_b,auto_bmin,auto_bmax = auto[:,7],auto[:,8],auto[:,9]
-gets_b,gets_bmin,gets_bmax = gets[:,7],gets[:,8],gets[:,9]
-auto_bsigma = np.array([auto_bmax-auto_b,auto_b-auto_bmin])
-gets_bsigma = np.array([gets_bmax-gets_b,gets_b-gets_bmin])
+r_bdmv = data[:,10]
+r_bdmw = data[:,11]
 
+rs_bdmv = r_bdmv/c_bdmv
+rs_bdmw = r_bdmw/c_bdmw
 
-pylab.plot(real_a,real_a,'-k')
-pylab.errorbar(real_a,auto_a,yerr=auto_asigma,fmt='.r',elinewidth=1,capsize=2,capthick=1)
-pylab.xscale('log')
-pylab.yscale('log')
-pylab.xlabel('$Real$')
-pylab.ylabel('$Obtained$')
-pylab.title('$\\rho_0$ with center at 0')
-pylab.savefig('rho0_auto.png',dpi=300)
+rs = orig[:,1]
+
+pylab.title('$r_s$')
+pylab.plot(rs,rs,'-k')
+pylab.plot(rs,rs_bdmv,'ob')
[…]

### 2014-04-14 data/test/test_stack_3/test.py

@@ -1,32 +1,0 @@
-import numpy as np, pylab
-
-data = np.loadtxt('gets_center.csv',delimiter=',')
-orig = np.loadtxt('parameters.dat',delimiter=',')
-data = data[data[:,0].argsort()]
-
-c_bdmv = data[:,4]
-c_bdmw = data[:,7]
-
-r_bdmv = data[:,10]
-r_bdmw = data[:,11]
-
-rs_bdmv = r_bdmv/c_bdmv
-rs_bdmw = r_bdmw/c_bdmw
-
-rs = orig[:,1]
-
-pylab.title('$r_s$')
-pylab.plot(rs,rs,'-k')
-pylab.plot(rs,rs_bdmv,'ob')
-pylab.xlabel('Real')
-pylab.ylabel('BDMV')
-pylab.savefig('bdmv.png',dpi=300)
-pylab.close()
-
-pylab.title('$r_s$')
-pylab.plot(rs,rs,'-k')
-pylab.plot(rs,rs_bdmw,'or')
-pylab.xlabel('Real')
-pylab.ylabel('BDMW')
-pylab.savefig('bdmw.png',dpi=300)
-pylab.close()

### 2014-04-14 src/article/article.tex
new article

@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[twocolumn,english]{paper}
+\documentclass[english]{article}
 \usepackage[T1]{fontenc}
@@
 \setlength{\parindent}{0bp}
+\usepackage{float}
 \usepackage{amsthm}
 \usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{setspace}
-\onehalfspacing
 
 \makeatletter
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% A simple dot to overcome graphicx limitations
-\newcommand{\lyxdot}{.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
@@
 \author{Christian Poveda Ruiz}
+
 \maketitle
-\begin{abstract}
-FIXME: Write abstract
-\end{abstract}
 
@@
 
-FIXME: Multidark
+The Navarro-Frenk-White mass profile can be normalized respect to
+the virial mass and written in function of the normalized radius respect
+to the virial radius $r_{norm}$ and the concentration $c$
 
-FIXME: NFW profile
-
-FIXME: MCMC
+\[
+m_{nfw}\left(r_{norm},c\right)=A\left[\log\left(1+r_{norm}c\right)-\left(\frac{1}{r_{norm}c}+1\right)^{-1}\right]
+\]
+Where $A$ is a normalization constant such that $m_{nfw}\left(1,c\right)=1$
 
@@
 \section{What did I do?}
-
-FIXME: Which simulation? $m=1.7\times10^{11}\ M_{\odot}$
-
-$ $
 
@@
 \[
-\phi\left(\boldsymbol{r}_{n}\right)=-\sum_{j\neq i}\frac{1}{\left\Vert \boldsymbol{r}_{n}-\boldsymbol{r}_{j}\right\Vert }
+\phi\left(\boldsymbol{R}_{n}\right)=-\sum_{j\neq n}\frac{1}{\left\Vert \boldsymbol{R}_{n}-\boldsymbol{R}_{j}\right\Vert }
 \]
-Take $\boldsymbol{r}_{0}=\min\left(\phi\left(\boldsymbol{r}_{n}\right)\right)$
-as the center then define new coordinates $\boldsymbol{r}_{n}^{\prime}=\boldsymbol{r}_{0}-\boldsymbol{r}_{n}$,
-this $\boldsymbol{r}_{0}$ will be in the most relevant region for
-the dynamics of each halo. Organizing the $\left\{ \boldsymbol{r}_{n}^{\prime}\right\} $
-in crescent order, the accumulated mass for each $\boldsymbol{r}_{n}^{\prime}$
-will be $m_{n}=nm$.
+Take $\boldsymbol{R}_{0}=\min\left(\phi\left(\boldsymbol{R}_{n}\right)\right)$
+as the center then define new coordinates $\boldsymbol{R}_{n}^{\prime}=\boldsymbol{R}_{0}-\boldsymbol{R}_{n}$,
+this $\boldsymbol{R}_{0}$ will be in the most relevant region for
+the dynamics of each halo. Organizing the $\left\{ \boldsymbol{R}_{n}^{\prime}\right\} $
+in crescent order, the accumulated mass for each $\boldsymbol{R}_{n}^{\prime}$
+will be $M_{n}=nM$.
 
-$ $
+\begin{figure}[H]
+\caption{FIXME: Mass profile of a halo}
+\end{figure}
 
-FIXME: Mass profile of a halo
-
-$ $
-
-The last part of the process consists in fitting the NFW mass profile
-to the $m_{n}$ data using the Metropolis-Hastings algorithm to sample
-the Likelihood ${\cal L}\left(\rho_{0},r_{s}\right)=\exp\left(-\frac{1}{2}\chi^{2}\left(\rho_{0},r_{s}\right)\right)$,
-where $\chi^{2}\left(\rho_{0},r_{s}\right)=\sum\limits _{n}\left|m_{n}-m\left(\boldsymbol{r}_{n}^{\prime},\rho_{0},r_{s}\right)\right|^{2}$,
-and take the values of $\rho_{0}$ and $r_{s}$ where the Likelihood
-is maximum.
+Then the virial radius is obtained and the particles that are beyond
+the virial radius are removed. After that both the mass and the radius
+get normalized respect to the mass and virial radius, we will call
+these new variables $m_{n}$ and $r_{n}$. The last part of the process
+consists in fitting the normalized NFW mass profile to the $m_{n}$
+data using the Metropolis-Hastings algorithm to sample the Likelihood
+${\cal L}\left(c\right)=\exp\left(-\chi^{2}\left(c\right)\right)$
+where 
+\[
+\chi^{2}\left(c\right)=\sum\limits _{n}\left|m_{n}-m_{nfw}\left(r_{n},c\right)\right|^{2}
+\]
+And taking the values of $c$ where the Likelihood is maximum. Finally
+we compare this results with the values obtaned by BDM, since the
+number of halos obtained by FOF and BDM is different, each BDM halo
+gets related with the nearest halo in FOF. We compute two concentrations,
+one where the overdensity limit is $360\rho_{back}$ (like in BDMV)
+an other where the overdensity limit is $740\rho_{back}$ (like in
+BDMW).
 
@@
 
-\subsection{Trial Problem with several Generated Halos }
+\subsection{Trial Problem with several Generated Halos}
 
-FIXME: I tested it with HaloGenerator
+To be sure that the results are reasonable, several tests were performed
+generating halos from the Navarro-Frenk-White profile with known values
+for $\rho_{0}$ and $r_{s}.$ The center of the generated halos is
+$\boldsymbol{0}=\left(0,0,0\right)$ so we can determine how good
+estimate is the minimum of the potential at the center of each halo.
+Two types of tests were run: The first omitting the calculation of
+the center of each halo and assuming that is $\boldsymbol{0}$ and
+second by calculating the center as the minimum of the potential.
 
-\subsection{Results from the simulation}
+\begin{figure}[H]
+\caption{FIXME: Test results}
+\end{figure}
 
-FIXME: Plot with error bars
-
-\begin{figure}
-\begin{centering}
-\includegraphics[scale=0.43]{/home/christian/Documentos/git/Montecarlo-NFW/data/results/results_2014-02-11-23:43:20/rs}
-\par\end{centering}
-
-\caption{}
-
-\end{figure}
+\subsection{Results from the simulations}
 

### 2014-05-06 src/article/poster.tex
added poster

%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,spanish]{article}
\usepackage{fontspec}
\usepackage[landscape,paperwidth=60cm,paperheight=40cm]{geometry}
\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm}
\setlength{\parindent}{0bp}
\usepackage{graphicx}
\usepackage[numbers]{natbib}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% A simple dot to overcome graphicx limitations
\newcommand{\lyxdot}{.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\usepackage{enumitem}		% customizable list environments
\newlength{\lyxlabelwidth}      % auxiliary length

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{multicol}

\makeatother

\usepackage{xunicode}
\usepackage{polyglossia}
\setdefaultlanguage{spanish}
\begin{document}
\large

\title{\Huge{Navarro-Frenk-White en Simulaciones Cosmologicas Usando MCMC}}

\author{\huge{Christian Poveda}}

\date{\LARGE{Universidad de los Andes}}

\maketitle
\setlength{\columnsep}{1.5cm}
\begin{multicols}{3}
\thispagestyle{empty}

\section{Introducción}

\subsection{Perfil de Navarro-Frenk-White }

El perfil de Navarro-Frenk-White permite obtener la densidad de materia
oscura de un halo en función del radio y está dado por
\[
\rho\left(R;\rho_{0},R_{s}\right)=\frac{\rho_{0}}{\frac{R}{R_{s}}\left(1+\frac{R}{R_{s}}\right)^{2}}
\]
Integrando es posible obtener la masa contenida en función del radio
\[
M\left(R;\rho_{0},R_{s}\right)=4\pi\rho_{0}R_{s}^{3}\left[\log\left(1+\frac{R}{R_{s}}\right)-\frac{R}{R_{s}+R}\right]
\]
Adicionalmente se suele definir el radio virial de un halo $R_{vir}$
como el valor de $r$ tal que $\left\langle \rho\right\rangle \left(R_{vir}\right)=n\rho_{back}$
donde $n$ es el factor de sobredensidad y la concentración de cada
halo como $c:=R_{vir}/R_{s}$ \citep{NFW}. Así se puede normalizar
el perfil de masa 
\[
m\left(r;c\right)=A\left[\log\left(1+rc\right)-\frac{rc}{1+rc}\right]
\]
Donde $r=R/R_{vir}$. Y
\[
A=\left[\log\left(1+c\right)-\frac{c}{1+c}\right]^{-1}
\]
A continuación se muestra la masa normalizada con distintos valores
de la concentración

\begin{center}
\includegraphics[scale=0.6]{conc}
\par\end{center}

\subsection{Friend-Of-Friend}

Fue inventado en 1985 por Davis et al.\citep{FOF}. Este algoritmo
buscador de halos consiste en definir una longitud de enlace a partír
de un umbral de densidad. Si dos partículas están separadas por una
distancia menor a su longitud de enlace, pertenecen al mismo halo.

\begin{center}
\includegraphics[scale=0.9]{\lyxdot \lyxdot /Dropbox/Research/Seminario/FOFgroups-sub-linklength}
\par\end{center}

\subsection{Bound Density Maximum}

Fue inventado en 1997 por Klypin y Holtzman \citep{BDM}. Consiste
en buscar máximos locales de densidad, luego se recorta el halo donde
sea lo suficientemente denso ($r_{vir}$) y se remueven las partículas
que no estén ligadas. En MultiDark hay dos catálogos: BDMV ($\eta=360$)
y BDMW ($\eta=740$).

\begin{center}
\includegraphics[scale=0.9]{\lyxdot \lyxdot /Dropbox/Research/Seminario/BDMhalos-s}
\par\end{center}

\section{Muestreando con MCMC}

\subsection{Definiendo un Centro}

Se toma el centro de cada halo como su mínimo de potencial

\[
\phi\left(\vec{R}_{i}\right)=-\sum_{j\neq i}\frac{Gm^{2}}{\left\Vert \vec{R}_{i}-\vec{R}_{j}\right\Vert }
\]

Luego se redefinen las coordenadas de cada partícula respecto a este
nuevo centro

\[
\vec{R}_{i}^{\prime}=\vec{R}_{i}-\vec{R}_{c}
\]

Se cuenta el número de partículas dentro de cada radio. Despues de
esto se calcula el radio virial, se eliminan las partículas con un
radio mayor a este y se normalizan las distancias. En la siguiente
gráfica se muestra la proyección de un halo de la simulación MDR1
sobre el plano y-z con sus respectivos radios viriales

\begin{center}
\includegraphics[scale=0.6]{halo_yz}
\par\end{center}

\subsection{Algoritmo de Metropolis-Hastings }

Se utiliza el algoritmo de Metropolis-Hastings para muestrear la verosimilitud

\[
{\cal L}\left(c\right)=\exp\left(-\chi^{2}\left(c\right)\right)
\]

\[
\chi^{2}\left(c\right)=\sum_{i}\left(m_{i}-m_{NFW}\left(r_{i};c\right)\right)^{2}
\]

Luego se toma el valor de donde ${\cal L}\left(c\right)$ es máxima,
sin embargo se toma la reestricción $c\geq1$. Para el halo mostrado
anteriormente vemos que

\begin{center}
\includegraphics[scale=0.6]{chi2}
\par\end{center}

Tomando el valor de $c$ que corresponde al mínimo valor de $\chi^{2}$
para ambos casos, se obtienen las siguientes curvas

\begin{center}
\includegraphics[scale=0.6]{mass_norm_BDMV}
\par\end{center}

\begin{center}
\includegraphics[scale=0.6]{mass_norm_BDMW}
\par\end{center}

\section{Resultados}

Usando los datos de la simulación MDR1\citep{MULTIDARK} se compararon
los valores de la concentración obtenidos por BDM con los obtenidos
por este método usando el catalogo FOF como base. Sin embargo no existe
una correspondecia uno a uno entre estos dos catálogos, asi que se
le asigna a cada halo de BDM un compañero en FOF como los halos con
centros más cercanos, al tomar la mediana de la concentración contra
la masa de cada halo tenemos que

\begin{center}
\includegraphics[scale=0.6]{concentration}
\par\end{center}

\section{Discusión}

Cupcake ipsum dolor. Sit amet carrot cake cheesecake I love jelly
sugar plum. Liquorice candy gummi bears dessert icing cupcake. I love
macaroon cotton candy biscuit. Pudding candy canes I love candy canes.
Macaroon ice cream I love powder. Biscuit lemon drops sweet wafer
carrot cake. Apple pie pastry danish ice cream sweet pastry gummies
lemon drops. Cheesecake cheesecake marzipan.
\begin{thebibliography}{1}
\bibitem{NFW}The Structure of cold dark matter halos - Navarro, Julio
F. et al. Astrophys.J. 462 (1996) 563-575 astro-ph/9508025

\bibitem{MULTIDARK}MDR1 Database. En Multidark Database (sf). Recuperado
el 6 de mayo de 2014, de http://www.multidark.org/MultiDark/Help?
page=databases/mdr1/database

\bibitem{BDM}Particle mesh code for cosmological simulations - Klypin,
Anatoly et al. astro-ph/9712217.

\bibitem{FOF}The Evolution of Large Scale Structure in a Universe
Dominated by Cold Dark Matter - Davis, Marc et al. Astrophys.J. 292
(1985) 371-394 NSF-ITP-84-129.

\end{thebibliography}
\end{multicols} 
\end{document}

### 2014-05-06 src/article/poster.tex
corrections

@@
 \usepackage[landscape,paperwidth=60cm,paperheight=40cm]{geometry}
-\geometry{verbose,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2.5cm}
+\geometry{verbose,tmargin=2.5cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
 \setlength{\parindent}{0bp}
@@
 \makeatletter
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-%% A simple dot to overcome graphicx limitations
-\newcommand{\lyxdot}{.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
@@
 \]
-Donde $r=R/R_{vir}$. Y
+Donde $r=R/R_{vir}$ y
 \[
@@
 \begin{center}
-\includegraphics[scale=0.9]{\lyxdot \lyxdot /Dropbox/Research/Seminario/FOFgroups-sub-linklength}
+\includegraphics[scale=0.9]{FOFgroups-sub-linklength}
 \par\end{center}
@@
 \begin{center}
-\includegraphics[scale=0.9]{\lyxdot \lyxdot /Dropbox/Research/Seminario/BDMhalos-s}
+\includegraphics[scale=0.9]{BDMhalos-s}
 \par\end{center}
@@
 radio mayor a este y se normalizan las distancias. En la siguiente
-gráfica se muestra la proyección de un halo de la simulación MDR1
+gráfica se muestra la proyección de un halo deÑ catálogo FOF-MDR1
 sobre el plano y-z con sus respectivos radios viriales
@@
 los valores de la concentración obtenidos por BDM con los obtenidos
-por este método usando el catalogo FOF como base. Sin embargo no existe
+por este método usando el catálogo FOF como base. Sin embargo no existe
 una correspondecia uno a uno entre estos dos catálogos, asi que se

### 2014-05-07 src/catalog.py
now with multiprocessing

@@ -129,7 +129,7 @@ log_m_bdmw_mcmc = np.log10(used_n_bdmw)
 log_m_bdmv_orig = np.log10(bdmv_m)
 log_m_bdmw_orig = np.log10(bdmw_m)
 
-bins_bdmv_mcmc,median_c_bdmv_mcmc,quartile_c_bdmv_mcmc  = get_stats(log_m_bdmv_mcmc,used_c_bdmv)
+bins_bdmv_mcmc,median_c_bdmv_mcmc,quartile_c_bdmv_mcmc = get_stats(log_m_bdmv_mcmc,used_c_bdmv)
 bins_bdmw_mcmc,median_c_bdmw_mcmc,quartile_c_bdmw_mcmc = get_stats(log_m_bdmw_mcmc,used_c_bdmw)
 bins_bdmv_orig,median_c_bdmv_orig,quartile_c_bdmv_orig = get_stats(log_m_bdmv_orig,bdmv_c)
 bins_bdmw_orig,median_c_bdmw_orig,quartile_c_bdmw_orig = get_stats(log_m_bdmw_orig,bdmw_c)

### 2014-05-07 src/fit.py

@@ -22,9 +22,6 @@ def chi2(obs,mod):
 
 def metropolis_one(data,obs,mod,n_iterations):
 
-    sys.stdout.write('\rRunning Metropolis-Hastings Algorithm... ')
-    sys.stdout.flush()
-    
     guess = [np.log(10)]
     
     a_walk = np.empty((n_iterations+1))
@@ -62,8 +59,6 @@ def metropolis_one(data,obs,mod,n_iterations):
 
     best_a = a_walk[n]
 
-    sys.stdout.write('Done\n')
-
     return best_a,a_walk,chisq
 
 # Does a maximum-likelihood estimate using the Metropolis-Hastings algorithm for a model with two parameters.
@@ -77,9 +72,6 @@ def metropolis_one(data,obs,mod,n_iterations):
 
 def metropolis(data,obs,mod,n_iterations, maxi,mini):
 
-    sys.stdout.write('\rRunning Metropolis-Hastings Algorithm... ')
-    sys.stdout.flush()
-    
     guess = curve_fit(mod,data,obs,maxfev=n_iterations)[0]
 
     if guess[1] > maxi:
@@ -130,7 +122,6 @@ def metropolis(data,obs,mod,n_iterations, maxi,mini):
     best_a = a_walk[n]
     best_b = b_walk[n]
 
-    sys.stdout.write('Done\n')
 
     return best_a,best_b,a_walk,b_walk,chisq
 

### 2014-05-07 src/main.py

@@ -1,5 +1,6 @@
 import numpy as np, pylab, math, sys, timeit, os, random, datetime, nfw, fit, plotter
 from scipy.optimize import fsolve
+import multiprocessing
 
 # Gets the concentration and virial radius for several haloes
 # It must be executed with the following command line:
@@ -15,153 +16,420 @@ from scipy.optimize import fsolve
 # Have fun! 
 #
 # Done by: Christian Poveda (cn.poveda542@uniandes.edu.co)
+#
+# Thanks to Diva Martinez (dm.martinez831@uniandes.edu.co) for the multiprocessing idea
 
-totaltime = 0.0
+processes = 4
 now = datetime.datetime.now().strftime("%Y-%m-%d-%H:%M:%S")
-
+mass_element = 1.0   
 plt = 1
+total_list = os.listdir('./'+str(sys.argv[1]))
+len_list = len(total_list)
+lists = [total_list[i*len_list // processes: (i+1)*len_list //processes] for i in range(processes)]
+jobs = []
+
 try:
     if (sys.argv[6]=='noplot'):
         print 'No Plotting mode enabled'
         plt = 0
 except:
     plt = 1
-
+ 
 os.system('mkdir results_'+now)
-
 sys.stdout.write('\rCompiling the code used to calculate the center of each halo... ')
 sys.stdout.flush()
 os.system('cc potential.c -lm -o  potential.out')
 sys.stdout.write('Done\n')
 
+def run(directories,process_number):
+
+    process_number+=1
+    count = 0
+    filename_export = './results_'+now+'/results_'+str(process_number)+'.csv'
+    os.system('touch '+filename_export)
+
+    for filename in directories:
+
+        count = count + 1
+        sys.stdout.write('\rWorking with file '+str(count)+' of '+str(len(directories))+' in process '+str(process_number)+'... ')
+        sys.stdout.flush()
+
+        path = os.path.expanduser('./'+str(sys.argv[1])+'/'+filename)
+        data = np.loadtxt(open(path, 'r'), delimiter=",",skiprows=int(sys.argv[5]))
+
+        x = data[:,int(sys.argv[2])]
+        y = data[:,int(sys.argv[3])]
[…]

### 2014-05-07 src/plotter.py

@@ -12,8 +12,6 @@ angle = np.arange(0,2*np.pi,0.01)
 
 def halo(x,y,z,x_center,y_center,z_center,r_bdmv,r_bdmw):
     
-    sys.stdout.write('\rPlotting halo... ')
-    sys.stdout.flush()
     pylab.plot(x , y, 'k.')
     pylab.plot(x_center , y_center, 'ko')
     pylab.plot(r_bdmv*np.cos(angle)+x_center,r_bdmv*np.sin(angle)+y_center,'--b',label='BDMV')
@@ -46,8 +44,7 @@ def halo(x,y,z,x_center,y_center,z_center,r_bdmv,r_bdmw):
     pylab.title('Halo z-x')
     pylab.savefig('halo_zx.png',format='png',dpi=300)
     pylab.close()
-    sys.stdout.write('Done\n')
-
+   
 # Plots the NFW mass profile 
 # Requires:
 #     radius: array with the radial distances

### 2014-05-07 src/potential.c

@@ -7,6 +7,7 @@ int count_lines(char *filename);
 // Gives an array with the gravitational potential for each particle
 // Requires:
 //    argv[1]: name of the file with the positions of each particle in x,y and z
+//    argv[2]: name of the file to export the potential of each particle
 // Returns:
 //    a file with the potential for each particle
 
@@ -24,7 +25,7 @@ int main(int argc, char** argv){
  n_points = count_lines(argv[1]);
 
  rfile = fopen(argv[1], "r");
- cfile = fopen("potential.dat", "w");
+ cfile = fopen(argv[2], "w");
 
  x = malloc(n_points*sizeof(double));
  y = malloc(n_points*sizeof(double));

### 2014-05-07 src/main.py
removed line

@@ -1,6 +1,5 @@
-import numpy as np, pylab, math, sys, timeit, os, random, datetime, nfw, fit, plotter
+import numpy as np, pylab, math, sys, timeit, os, random, datetime, nfw, fit, plotter, multiprocessing
 from scipy.optimize import fsolve
-import multiprocessing
 
 # Gets the concentration and virial radius for several haloes
 # It must be executed with the following command line:

### 2014-05-07 src/main.py
removed lines

@@ -168,267 +168,6 @@ with export as outfile:
         with open(fname) as infile:
             for line in infile:
                 outfile.write(line)    
-
-
-sys.stdout.write('Done\n')
-
-def run(directories,process_number):
     
-    count = 0
-    filename_export = './results_'+now+'/results_'+str(process_number)+'.csv'
-    os.system('touch '+filename_export)
-
-    for filename in directories:
-
-        count = count + 1
-        sys.stdout.write('\rWorking with file '+str(count)+' of '+str(len(directories))+' in process '+str(process_number)+'... ')
-        sys.stdout.flush()
-
-        path = os.path.expanduser('./'+str(sys.argv[1])+'/'+filename)
-        data = np.loadtxt(open(path, 'r'), delimiter=",",skiprows=int(sys.argv[5]))
-
-        x = data[:,int(sys.argv[2])]
-        y = data[:,int(sys.argv[3])]
-        z = data[:,int(sys.argv[4])]
-
-        n_points = len(x)
-        results_folder ='./results_'+now+'/'+str(filename)
-        
-        file_id = int(filename.split('_')[1])
-        positions_name ='positions_'+str(file_id)+'.dat'
-        potential_name ='potential_'+str(file_id)+'.dat'
-        open(positions_name, "w").write('\n'.join('%lf,%lf,%lf' % (x[i],y[i],z[i]) for i in range(n_points)))
-
-        os.system('./potential.out '+positions_name+' '+potential_name)
-
-        potential = np.loadtxt(open(potential_name, 'r'))
-        maximum = np.argmax(potential)
-
-        x_center,y_center,z_center = x[maximum],y[maximum],z[maximum]
-        
-        os.system('rm '+potential_name+' '+positions_name)
-        
-        r_values = np.sort(np.sqrt((x-x_center)**2 + (y-y_center)**2 + (z-z_center)**2), kind='quicksort')
-        
-        mass = mass_element*np.arange(1,n_points,1)
-        radius = np.delete(r_values,0)
-
-        avg_density = mass/((4.0/3.0)*np.pi*(radius**3))
-        rho_back = mass_element*(2048.0/1000.0)**3
-
[…]

### 2014-05-07 src/main.py
now with sleep zZzZZ...

@@ -1,4 +1,4 @@
-import numpy as np, pylab, math, sys, timeit, os, random, datetime, nfw, fit, plotter, multiprocessing
+import numpy as np, pylab, math, sys, timeit, os, random, datetime, nfw, fit, plotter, multiprocessing, time
 from scipy.optimize import fsolve
 
 # Gets the concentration and virial radius for several haloes
@@ -19,6 +19,7 @@ from scipy.optimize import fsolve
 # Thanks to Diva Martinez (dm.martinez831@uniandes.edu.co) for the multiprocessing idea
 
 processes = 4
+dt = 10.0*60.0
 now = datetime.datetime.now().strftime("%Y-%m-%d-%H:%M:%S")
 mass_element = 1.0   
 plt = 1
@@ -155,10 +156,9 @@ for i in range(processes):
     jobs.append(p)
     p.start()
 
-
 for p in jobs: 
     while(p.is_alive()):
-        pass
+        time.sleep(dt) 
 
 export = open('./results_'+now+'/results_'+now+'.csv', 'w')
 

### 2014-05-08 src/catalog.py
now with quartiles

@@ -1,4 +1,4 @@
-import numpy as np, pylab, sys, matplotlib, plotter
+import numpy as np, pylab, sys, matplotlib
 from matplotlib.mlab import griddata
 from scipy.optimize import curve_fit
 
@@ -10,7 +10,8 @@ def get_stats(log_mass,conc):
     bins = np.arange(0,np.amax(log_mass)+0.5,0.5)
     bins_index = np.digitize(log_mass,bins)
     median = np.empty(len(bins))
-    quartile = np.empty(len(bins))
+    quar1 = np.empty(len(bins))
+    quar2 = np.empty(len(bins))
 
     for i in range(len(bins)):
         tempo = []
@@ -19,8 +20,11 @@ def get_stats(log_mass,conc):
                 tempo.append(conc[j])
         tempo = np.array(tempo)
         median[i] = np.median(tempo)
-        quartile[i] = 0
-    return bins,median,quartile
+        if (tempo.size):
+            quar1[i],quar2[i] = np.percentile(tempo,[25,75])            
+        else:
+            quar1[i],quar2[i]=0,0
+    return bins,median,quar1,quar2
 
 dm = 8.721e9
 
@@ -129,18 +133,21 @@ log_m_bdmw_mcmc = np.log10(used_n_bdmw)
 log_m_bdmv_orig = np.log10(bdmv_m)
 log_m_bdmw_orig = np.log10(bdmw_m)
 
-bins_bdmv_mcmc,median_c_bdmv_mcmc,quartile_c_bdmv_mcmc = get_stats(log_m_bdmv_mcmc,used_c_bdmv)
-bins_bdmw_mcmc,median_c_bdmw_mcmc,quartile_c_bdmw_mcmc = get_stats(log_m_bdmw_mcmc,used_c_bdmw)
-bins_bdmv_orig,median_c_bdmv_orig,quartile_c_bdmv_orig = get_stats(log_m_bdmv_orig,bdmv_c)
-bins_bdmw_orig,median_c_bdmw_orig,quartile_c_bdmw_orig = get_stats(log_m_bdmw_orig,bdmw_c)
[…]

### 2014-05-08 src/article/poster.tex
finished this sucker

@@
 
-Cupcake ipsum dolor. Sit amet carrot cake cheesecake I love jelly
-sugar plum. Liquorice candy gummi bears dessert icing cupcake. I love
-macaroon cotton candy biscuit. Pudding candy canes I love candy canes.
-Macaroon ice cream I love powder. Biscuit lemon drops sweet wafer
-carrot cake. Apple pie pastry danish ice cream sweet pastry gummies
-lemon drops. Cheesecake cheesecake marzipan.
+A diferencia del estimado de la concentración dada por \emph{BDM }este
+método permite obtener un estimado más directo. Sin embargo no se
+sabe a que se deben las discrepancias entre los resultados obtenidos,
+aun es necesario determinar si estas diferencias se deben al algorítmo
+utilizado en si o a la población de datos que se tomó.
 \begin{thebibliography}{1}

### 2014-05-12 paper/article.tex
new article structure

--- 2014-04-14 src/article/article.tex
@@
-%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-\documentclass[english]{article}
-\usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
-\usepackage[letterpaper]{geometry}
-\geometry{verbose,tmargin=2.65cm,bmargin=2.65cm,lmargin=2.65cm,rmargin=2.65cm}
-\setlength{\parindent}{0bp}
-\usepackage{float}
-\usepackage{amsthm}
+\documentclass[useAMS,usenatbib]{mn2e}
 \usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{graphics}
+\usepackage{graphicx}
+\usepackage{epsfig} 
+\usepackage{hyperref}
+\def\be{\begin{equation}}
+\def\ee{\end{equation}}
+\def\ba{\begin{eqnarray}}
+\def\ea{\end{eqnarray}}
 
-\makeatletter
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
-\numberwithin{equation}{section}
-\numberwithin{figure}{section}
+% To highlight comments
+\usepackage{color}
+\definecolor{red}{rgb}{1,0.0,0.0}
+\newcommand{\red}{\color{red}}
+\definecolor{blue}{rgb}{0.1,0.3,0.9}
+\newcommand{\blue}{\color{blue}}
 
-\makeatother
+\usepackage[normalem]{ulem}
+\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
 
-\usepackage{babel}
+\newcommand{\documentname}{paper~}
+\newcommand{\LCDM}{$\Lambda$CDM~}
+\newcommand{\beq}{\begin{eqnarray}} 
+\newcommand{\eeq}{\end{eqnarray}} 
+\newcommand{\zz}{$z\sim 3$}
+
+\newcommand{\apj}{ApJ} 
+\newcommand{\apjs}{ApJS} 
+\newcommand{\apjl}{ApJL} 
+\newcommand{\aj}{AJ} 
+\newcommand{\mnras}{MNRAS} 
+\newcommand{\mnrassub}{MNRAS accepted} 
+\newcommand{\aap}{A\&A} 
+\newcommand{\aaps}{A\&AS} 
+\newcommand{\araa}{ARA\&A} 
+\newcommand{\nat}{Nature} 
+\newcommand{\physrep}{PhR}
+\newcommand{\pasp}{PASP}   
+\newcommand{\pasj}{PASJ}   
+\newcommand{\avg}[1]{\langle{#1}\rangle} 
+\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
+\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}} 
+\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}} 
+\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}} 
+\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}
+\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
+        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$~}\fi}}  
+\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
+        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}} 
+\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}} 
+\newcommand{\lya}{{Lyman$\alpha$~}}
+\newcommand{\clara}{{\texttt{CLARA}}~}
+\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}} 
+\newcommand{\hs}{{\hspace{1mm}}}
+\newcommand{\muavg}{\vert\langle\cos\theta\rangle\vert}
+% definition to produce a "less than or similar to" symbol
+\def\lsim{~\rlap{$<$}{\lower 1.0ex\hbox{$\sim$}}}
+
+% definition to produce a "greater than or similar to" symbol
+
+% definition to produce a "greater than or similar to" symbol
+\def\gsim{~\rlap{$>$}{\lower 1.0ex\hbox{$\sim$}}}
+
 \begin{document}
 
-\title{This is Article}
-
-\author{Christian Poveda Ruiz}
-
+\title[Bayesian halo concentration]{Measurement of dark matter halo concentrations using a bayesian approach}
+\author[Poveda \& Forero-Romero]{
+\parbox[t]{\textwidth}{\raggedright
+  Christian Poveda$^{1}$ \&
+  Jaime E. Forero-Romero$^{1}$
+}
+\vspace*{6pt}\\
+$^{1}$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
+No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
+}
 \maketitle
 
+\begin{abstract}
+asd
+\end{abstract}
+\begin{keywords}
+methods: numerical, galaxies: haloes, cosmology: theory, dark
+matter
+\end{keywords}
+
 \section{Introduction}
+\label{sec:introduction}
+
+\citep{NFW}
+
+\section{Basics of the NFW profile}
+\label{sec:basics}
 
@@
 
-\section{State of Art}
-
-\section{What did I do?}
+\section{Bayesian Method}
+\label{sec:method}
 
@@
 
+\section{Mock Data and Simulations}
+\label{sec:data}
+
 \section{Results}
+\label{sec:results}
 
@@
 
+\section{Discussion}
+\label{sec:discussion}
+
 \section{Conclusions}
+\label{sec:conclusions}
+
+\bibliographystyle{mn2e}
+\bibliography{references}
+
 \end{document}

### 2014-05-15 paper/article.tex
working with the section 2

@@
 
-The Navarro-Frenk-White mass profile can be normalized respect to
-the virial mass and written in function of the normalized radius respect
-to the virial radius $r_{norm}$ and the concentration $c$
-
+The Navarro-Frenk-White mass profile can be normalized respect to the virial mass and written in function of the normalized radius respect to the virial radius $r=R/R_{vir}$ and the concentration $c$ 
 \[
-m_{nfw}\left(r_{norm},c\right)=A\left[\log\left(1+r_{norm}c\right)-\left(\frac{1}{r_{norm}c}+1\right)^{-1}\right]
+m_{nfw}\left(r;c\right)=A\left[\log\left(1+rc\right)-\left(\frac{rc}{rc+1}\right)\right]
 \]
-Where $A$ is a normalization constant such that $m_{nfw}\left(1,c\right)=1$
-
+Where
+\[
+A=\left[\log\left(1+c\right)-\left(\frac{c}{c+1}\right)\right]^{-1} 
+\]
 \section{Bayesian Method}
@@
 
-In order to obtain a mass profile for each halo in funcion of the
-radius, the center of each halo must be calculated. However the center
-of mass will not give an accurate position for the center because
-some haloes are highly irregular, is more convenient to take the gravitational
-potential for each particle
-
+In order to obtain a mass profile for each halo in funcion of the radius, the center of each halo must be calculated.
+However the center of mass will not give an accurate position for the center because some haloes are highly irregular, is more convenient to take the gravitational potential for each particle
 \[
@@
 \]
-Take $\boldsymbol{R}_{0}=\min\left(\phi\left(\boldsymbol{R}_{n}\right)\right)$
-as the center then define new coordinates $\boldsymbol{R}_{n}^{\prime}=\boldsymbol{R}_{0}-\boldsymbol{R}_{n}$,
-this $\boldsymbol{R}_{0}$ will be in the most relevant region for
-the dynamics of each halo. Organizing the $\left\{ \boldsymbol{R}_{n}^{\prime}\right\} $
-in crescent order, the accumulated mass for each $\boldsymbol{R}_{n}^{\prime}$
-will be $M_{n}=nM$.
+Take $\boldsymbol{R}_{0}=\min\left(\phi\left(\boldsymbol{R}_{n}\right)\right)$ as the center then define new coordinates $\boldsymbol{R}_{n}^{\prime}=\boldsymbol{R}_{0}-\boldsymbol{R}_{n}$, this $\boldsymbol{R}_{0}$ will be in the most relevant region for the dynamics of each halo.
+Organizing the $\left\{ \boldsymbol{R}_{n}^{\prime}\right\} $ in crescent order, the accumulated mass for each $\boldsymbol{R}_{n}^{\prime}$ will be $M_{n}=nM$.
 
@@
 
-Then the virial radius is obtained and the particles that are beyond
-the virial radius are removed. After that both the mass and the radius
-get normalized respect to the mass and virial radius, we will call
-these new variables $m_{n}$ and $r_{n}$. The last part of the process
-consists in fitting the normalized NFW mass profile to the $m_{n}$
-data using the Metropolis-Hastings algorithm to sample the Likelihood
-${\cal L}\left(c\right)=\exp\left(-\chi^{2}\left(c\right)\right)$
-where 
+Then the virial radius is obtained and the particles that are beyond the virial radius are removed.
+After that both the mass and the radius get normalized respect to the mass and virial radius, we will call these new variables $m_{n}$ and $r_{n}$.
+The last part of the process consists in fitting the normalized NFW mass profile to the $m_{n}$ data using the Metropolis-Hastings algorithm to sample the Likelihood ${\cal L}\left(c\right)=\exp\left(-\chi^{2}\left(c\right)\right)$ where
 \[
@@
 \]
-And taking the values of $c$ where the Likelihood is maximum. Finally
-we compare this results with the values obtaned by BDM, since the
-number of halos obtained by FOF and BDM is different, each BDM halo
-gets related with the nearest halo in FOF. We compute two concentrations,
-one where the overdensity limit is $360\rho_{back}$ (like in BDMV)
-an other where the overdensity limit is $740\rho_{back}$ (like in
-BDMW).
+And taking the values of $c$ where the Likelihood is maximum.
+Moreover, we can obtain a confidence interval for $c$ doing an histogram of the random walk done by the Metropolis-Hastings Algorithm.
+Finally we compare this results with the values obtaned by BDM, since the number of halos obtained by FOF and BDM is different, each BDM halo gets related with the nearest halo in FOF.
+We compute two concentrations, one where the overdensity limit is $360\rho_{back}$ (like in BDMV) an other where the overdensity limit is $740\rho_{back}$ (like in BDMW).
 
@@
 \label{sec:data}
-
 \section{Results}
@@
 
-To be sure that the results are reasonable, several tests were performed
-generating halos from the Navarro-Frenk-White profile with known values
-for $\rho_{0}$ and $r_{s}.$ The center of the generated halos is
-$\boldsymbol{0}=\left(0,0,0\right)$ so we can determine how good
-estimate is the minimum of the potential at the center of each halo.
-Two types of tests were run: The first omitting the calculation of
-the center of each halo and assuming that is $\boldsymbol{0}$ and
-second by calculating the center as the minimum of the potential.
-
+Several halos with known values of $c$ were generated.
+These halos were then processed to determine the acurracy of this method.
+The number of particles and value of $c$ for each halo were generated randomly.
 \begin{figure}[H]
@@
 
-\subsection{What kind of implications (Low resolution simulations, other fitting
-algorithms)}
+\subsection{What kind of implications (Low resolution simulations, other fitting algorithms)}
 

### 2014-05-15 src/fit.py
corrected percentiles

@@ -133,32 +133,10 @@ def metropolis(data,obs,mod,n_iterations, maxi,mini):
 # Returns:
 #     minimum and maximum boundary for the interval
 
-def error_bars(walk,parameter,opt):
-
-    n_iterations = len(walk)
-    n_bins = int(n_iterations/100)
+def error_bars(walk,opt):
 
     if (opt=='log'):
-        freq,bins = np.histogram(np.exp(walk), bins=n_bins)
-        index = np.argmin(np.abs(bins-np.exp(parameter)))
-
+        max,min = np.percentile(np.exp(walk),[13.6,86.4])
     else:
-        freq,bins = np.histogram(walk, bins=n_bins)
-        index = np.argmin(np.abs(bins-parameter))
-
-    max_c = [index+int(0.341*sum(freq)/n_bins),len(bins)-1]
-    min_c = [index-int(0.341*sum(freq)/n_bins),0]
-
-    M = max_c[np.argmin(max_c)]
-    m = min_c[np.argmax(min_c)]
-    
-    if (opt=='log'):
-
-        max = np.log(bins[M])
-        min = np.log(bins[m])
-
-    else:
-        max = bins[M]
-        min = bins[m]
-    
+        max,min = np.percentile(walk,[13.6,86.4])
     return max, min

### 2014-05-15 src/main.py
corrected parameters of get_errorbars

@@ -122,8 +122,8 @@ def run(directories,process_number):
         c_bdmv = np.exp(log_bdmv)
         c_bdmw = np.exp(log_bdmw)
     
-        bdmv_max, bdmv_min = np.exp(fit.error_bars(bdmv_walk,log_bdmv,'log'))
-        bdmw_max, bdmw_min = np.exp(fit.error_bars(bdmw_walk,log_bdmw,'log'))
+        bdmv_max, bdmv_min = np.exp(fit.error_bars(bdmv_walk,'log'))
+        bdmw_max, bdmw_min = np.exp(fit.error_bars(bdmw_walk,'log'))
     
         if (plt == 1):
 

### 2014-05-15 src/test.py

@@ -91,7 +91,7 @@ def run(directories,process_number):
 
         c = np.exp(log_c)
     
-        c_max, c_min = np.exp(fit.error_bars(c_walk,log_c,'log'))
+        c_max, c_min = np.exp(fit.error_bars(c_walk,'log'))
 
         export = open(filename_export, 'a')
         line = [[file_id,x_center,y_center,z_center,c,c_max,c_min]]

### 2014-05-15 src/fit.py
back to old version

@@ -132,11 +132,32 @@ def metropolis(data,obs,mod,n_iterations, maxi,mini):
 #     opt: need to put 'log' if the random walk is in logarithmic scale
 # Returns:
 #     minimum and maximum boundary for the interval
+def error_bars(walk,parameter,opt):
 
-def error_bars(walk,opt):
+    n_iterations = len(walk)
+    n_bins = int(n_iterations/100)
 
     if (opt=='log'):
-        max,min = np.percentile(np.exp(walk),[13.6,86.4])
+        freq,bins = np.histogram(np.exp(walk), bins=n_bins)
+        index = np.argmin(np.abs(bins-np.exp(parameter)))
+
     else:
-        max,min = np.percentile(walk,[13.6,86.4])
+        freq,bins = np.histogram(walk, bins=n_bins)
+        index = np.argmin(np.abs(bins-parameter))
+
+    max_c = [index+int(0.341*sum(freq)/n_bins),len(bins)-1]
+    min_c = [index-int(0.341*sum(freq)/n_bins),0]
+
+    M = max_c[np.argmin(max_c)]
+    m = min_c[np.argmax(min_c)]
+    
+    if (opt=='log'):
+
+        max = np.log(bins[M])
+        min = np.log(bins[m])
+
+    else:
+        max = bins[M]
+        min = bins[m]
+    
     return max, min

### 2014-05-15 src/main.py

@@ -122,8 +122,8 @@ def run(directories,process_number):
         c_bdmv = np.exp(log_bdmv)
         c_bdmw = np.exp(log_bdmw)
     
-        bdmv_max, bdmv_min = np.exp(fit.error_bars(bdmv_walk,'log'))
-        bdmw_max, bdmw_min = np.exp(fit.error_bars(bdmw_walk,'log'))
+        bdmv_max, bdmv_min = np.exp(fit.error_bars(bdmv_walk,log_bdmv,'log'))
+        bdmw_max, bdmw_min = np.exp(fit.error_bars(bdmw_walk,log_bdmw,'log'))
     
         if (plt == 1):
 
@@ -133,13 +133,24 @@ def run(directories,process_number):
             plotter.halo(x,y,z,x_center,y_center,z_center,r_bdmv,r_bdmw)
             plotter.mass_norm(bdmv_radius,bdmv_mass,c_bdmv,bdmv_max,bdmv_min,'BDMV')
             plotter.mass_norm(bdmw_radius,bdmw_mass,c_bdmw,bdmw_max,bdmw_min,'BDMW')
-
             pylab.scatter(np.exp(bdmv_walk),bdmv_chi2,label='BDMV')
             pylab.scatter(np.exp(bdmw_walk),bdmw_chi2,c='r',label='BDMW')
             pylab.legend(loc=4, borderaxespad=0.5)
-            pylab.xlabel('$log(c)$')
+            pylab.xlabel('$c$')
             pylab.ylabel('$\chi ^2$')
             pylab.savefig('chi2.png',dpi=300)
+            pylab.close()
+
+            pylab.hist(np.exp(bdmv_walk),1000,normed=True)
+            pylab.xlabel('c')
+            pylab.ylabel('P(c)')
+            pylab.savefig('bdmv_hist.png',dpi=300)
+            pylab.close()
+
+            pylab.hist(np.exp(bdmw_walk),1000,normed=True)
+            pylab.xlabel('c')
+            pylab.ylabel('P(c)')
+            pylab.savefig('bdmw_hist.png',dpi=300)
             pylab.close()
 
             os.chdir('../../')

### 2014-05-15 src/main.py
new likelihood plot

@@ -133,12 +133,21 @@ def run(directories,process_number):
             plotter.halo(x,y,z,x_center,y_center,z_center,r_bdmv,r_bdmw)
             plotter.mass_norm(bdmv_radius,bdmv_mass,c_bdmv,bdmv_max,bdmv_min,'BDMV')
             plotter.mass_norm(bdmw_radius,bdmw_mass,c_bdmw,bdmw_max,bdmw_min,'BDMW')
+
             pylab.scatter(np.exp(bdmv_walk),bdmv_chi2,label='BDMV')
             pylab.scatter(np.exp(bdmw_walk),bdmw_chi2,c='r',label='BDMW')
             pylab.legend(loc=4, borderaxespad=0.5)
             pylab.xlabel('$c$')
             pylab.ylabel('$\chi ^2$')
             pylab.savefig('chi2.png',dpi=300)
+            pylab.close()
+
+            pylab.scatter(np.exp(bdmv_walk),np.exp(-bdmv_chi2/2),label='BDMV')
+            pylab.scatter(np.exp(bdmw_walk),np.exp(-bdmw_chi2/2),c='r',label='BDMW')
+            pylab.legend(loc=4, borderaxespad=0.5)
+            pylab.xlabel('$c$')
+            pylab.ylabel('$\cal{L}$')
+            pylab.savefig('likelihood.png',dpi=300)
             pylab.close()
 
             pylab.hist(np.exp(bdmv_walk),1000,normed=True)

### 2014-05-21 src/glue.py
now working with cython

@@ -2,7 +2,7 @@ import sys, os
 
 directory = str(sys.argv[1])
 total_list = os.listdir(directory)
-filenames = [directory+'/'+element for element in total_list if 'result' in element]
+filenames = sorted([directory+'/'+element for element in total_list if 'result' in element])
 
 
 export = open(directory+'/results.csv', 'w')

### 2014-05-21 src/main.py

@@ -1,4 +1,4 @@
-import numpy as np, pylab, math, sys, timeit, os, random, datetime, nfw, fit, plotter, multiprocessing, time
+import numpy as np, pylab, math, sys, timeit, os, random, datetime, nfw, mcmc,fit , plotter, multiprocessing, time
 from scipy.optimize import fsolve
 
 # Gets the concentration and virial radius for several haloes
@@ -115,9 +115,26 @@ def run(directories,process_number):
         bdmw_mass = bdmw_mass/bdmw_mass[-1]
         bdmw_radius = bdmw_radius/bdmw_radius[-1]
 
-        n_iterations = 25000
-        log_bdmv,bdmv_walk,bdmv_chi2 = fit.metropolis_one(np.log(bdmv_radius),np.log(bdmv_mass),nfw.loglogmass_norm,n_iterations)
-        log_bdmw,bdmw_walk,bdmw_chi2 = fit.metropolis_one(np.log(bdmw_radius),np.log(bdmw_mass),nfw.loglogmass_norm,n_iterations)
+        n_iterations = 50000
+
+#        log_bdmv,bdmv_walk,bdmv_chi2 = fit.metropolis_one(np.log(bdmv_radius),np.log(bdmv_mass),nfw.loglogmass_norm,n_iterations)
+#        log_bdmw,bdmw_walk,bdmw_chi2 = fit.metropolis_one(np.log(bdmw_radius),np.log(bdmw_mass),nfw.loglogmass_norm,n_iterations)
+
+        step = np.array([np.log(1.03)])
+        guess = np.array([np.log(10)])
+        reest = [lambda x: x >= 0]
+
+        chi_bdmv = lambda p : mcmc.chi2(p,nfw.loglogmass_norm,np.log(bdmv_radius),np.log(bdmv_mass),np.ones(len(bdmv_radius)))
+        chi_bdmw = lambda p : mcmc.chi2(p,nfw.loglogmass_norm,np.log(bdmw_radius),np.log(bdmw_mass),np.ones(len(bdmw_radius)))
+    
+        bdmv_walk,bdmv_chi2 = mcmc.walker(chi_bdmv,guess,step,n_iterations,reest)
+        bdmw_walk,bdmw_chi2 = mcmc.walker(chi_bdmw,guess,step,n_iterations,reest)
+
+        bdmv_walk = bdmv_walk[0]
+        bdmw_walk = bdmw_walk[0]
[…]

### 2014-05-21 src/mcmc.pyx

@@ -1,0 +1,54 @@
+STUFF = "Hi"
+
+import numpy as np
+cimport numpy as np
+
+def chi2(np.ndarray p,model,np.ndarray x_obs,np.ndarray y_obs,np.ndarray sigma):
+    cdef float chi_sq = np.sum(((model(x_obs,p) - y_obs)/sigma)**2)
+    return chi_sq
+
+def walker(dist,np.ndarray state_0,np.ndarray step_size,n_iterations,reestrictions = None):
+
+    cdef int dims = len(state_0)
+    cdef np.ndarray walk = np.empty((dims,n_iterations))
+    cdef np.ndarray prob = np.empty(n_iterations)
+    cdef np.ndarray t_init
+    cdef np.ndarray t_prime
+    cdef float P_init
+    cdef float P_prime
+    cdef float a
+    cdef float b
+    walk[:,0] = state_0
+    prob[0] = dist(state_0)
+
+    if reestrictions == None:
+        reestrictions = [lambda x: True for i in range(dims)]
+        
+    for i in range(1,n_iterations):
+        
+        t_init = walk[:,i-1]
+        t_prime = np.empty(dims)
+        
+        for n in range(dims):
+            t_prime[n] = np.random.normal(t_init[n],step_size[n])
+            while reestrictions[n](t_prime[n]) == False:
+                t_prime[n] = np.random.normal(t_init[n],step_size[n])
+
+        P_init = dist(t_init)
+        P_prime = dist(t_prime)
+
+        a = -(P_prime-P_init)
+
+        if a > 0:
+            walk[:,i] = t_prime
+            prob[i] = P_prime
+        else:
+            b = np.log(np.random.random())
+            if a > b:
+                walk[:,i] = t_prime
+                prob[i] = P_prime
+            else:
+                walk[:,i] = t_init
+                prob[i] = P_init
+                
+    return walk,prob

### 2014-05-21 paper/article.tex
writing formulas in the introduction

@@
 
-\section{Basics of the NFW profile}
+\section{Basics of dark matter halos and the NFW profile}
 \label{sec:basics}
 
-The Navarro-Frenk-White mass profile can be normalized respect to the virial mass and written in function of the normalized radius respect to the virial radius $r=R/R_{vir}$ and the concentration $c$ 
-\[
-m_{nfw}\left(r;c\right)=A\left[\log\left(1+rc\right)-\left(\frac{rc}{rc+1}\right)\right]
-\]
+The Navarro-Frenk-White density profile can be written as
+
+\begin{equation}
+\rho(r) = \frac{\rho_c\delta_c}{r/R_s(1+r/R_s)^2}, 
+\end{equation}
+%
+where $\rho_c\equiv 3H^2/8\pi G$ is the Universe critical density,
+$\delta_c$ is the halo dimensionless characteristic density. is a
+normalization constant and $R_s$ is known as the scale radius, the
+radius that marks the transition between the two power law behaviour
+in the $\rho\propto r^{-1}$ for $r<R_s$ and $\rho\propto r^{-2}$ for
+$r>R_s$.
+
+One can define the scale radius as a fraction of the virial radius,
+$R_{vir}$,
+
+\begin{equation}
+R_s = R_{vir}/c,
+\end{equation}
+
+where $c>1$ is known as the concentration of the halo.
+
+Taking the virial radius as the radius that encloses 200 times the
+critical density, the concentration and the characteristic density are
+related by
+
+\begin{equation}
+\delta_c =\frac{200}{3}\frac{c^3}{[\ln(1+c)-c/(1+c)]}.
+\end{equation}
+
+Therefore, for a given value of the overdensity that defines a halo,
+the density profile has only one free parameter: the concentration.
+
+The total mass enclosed within a radius $r$ can be computed to be:
+
+\begin{equation}
+M(<r) = 4\pi\rho_c\delta_c  R_s^3\left[\ln \left
+  (\frac{R_s+r}{r})\right) - \frac{r}{R_s+r}\right].
+\end{equation}
+
+If we now define dimensionless variables $x\equiv r/R_{\rm vir}$ and
+$m\equiv M(<r)/M_{\rm vir}$...
+
+profile can be normalized respect to the
+virial mass and written in function of the normalized radius respect
+to the virial radius $r=R/R_{vir}$ and the concentration $c$
+
+\begin{equation}
+m_{\rm NFW}\left(r;c\right)=A\left[\log\left(1+rc\right)-\left(\frac{rc}{rc+1}\right)\right) 
+\end{equation}
 Where
-\[
+\begin{equation}
 A=\left[\log\left(1+c\right)-\left(\frac{c}{c+1}\right)\right]^{-1} 
-\]
+\end{equation}
+
 \section{Bayesian Method}
@@
 
-Several halos with known values of $c$ were generated.
-These halos were then processed to determine the acurracy of this method.
-The number of particles and value of $c$ for each halo were generated randomly.
+Several halos with known values of $c$ were generated. These halos
+were then processed to determine the acurracy of this method. The
+number of particles and value of $c$ for each halo were generated
+randomly.  
 \begin{figure}[H]

### 2014-05-23 paper/article.tex
adding text

--- 2014-05-15 paper/article.tex
@@
 
-\section{Basics of the NFW profile}
+\section{Basic properties of the NFW density profile}
 \label{sec:basics}
 
-The Navarro-Frenk-White mass profile can be normalized respect to the virial mass and written in function of the normalized radius respect to the virial radius $r=R/R_{vir}$ and the concentration $c$ 
-\[
-m_{nfw}\left(r;c\right)=A\left[\log\left(1+rc\right)-\left(\frac{rc}{rc+1}\right)\right]
-\]
-Where
-\[
-A=\left[\log\left(1+c\right)-\left(\frac{c}{c+1}\right)\right]^{-1} 
-\]
-\section{Bayesian Method}
-\label{sec:method}
+The Navarro-Frenk-White density profile can be written as
 
-In order to obtain a mass profile for each halo in funcion of the radius, the center of each halo must be calculated.
-However the center of mass will not give an accurate position for the center because some haloes are highly irregular, is more convenient to take the gravitational potential for each particle
-\[
-\phi\left(\boldsymbol{R}_{n}\right)=-\sum_{j\neq n}\frac{1}{\left\Vert \boldsymbol{R}_{n}-\boldsymbol{R}_{j}\right\Vert }
-\]
-Take $\boldsymbol{R}_{0}=\min\left(\phi\left(\boldsymbol{R}_{n}\right)\right)$ as the center then define new coordinates $\boldsymbol{R}_{n}^{\prime}=\boldsymbol{R}_{0}-\boldsymbol{R}_{n}$, this $\boldsymbol{R}_{0}$ will be in the most relevant region for the dynamics of each halo.
-Organizing the $\left\{ \boldsymbol{R}_{n}^{\prime}\right\} $ in crescent order, the accumulated mass for each $\boldsymbol{R}_{n}^{\prime}$ will be $M_{n}=nM$.
+\begin{equation}
+\rho(r) = \frac{\rho_c\delta_c}{r/r_s(1+r/r_s)^2}, 
+\end{equation}
+%
+where $\rho_c\equiv 3H^2/8\pi G$ is the Universe critical density,
+$\delta_c$ is the halo dimensionless characteristic density and $r_s$
+is known as the scale radius, the radius that marks the transition
+between the two power law behaviour in the $\rho\propto r^{-1}$ for
+$r<r_s$ and $\rho\propto r^{-2}$ for  $r>r_s$.
 
-\begin{figure}[H]
+We define the virial radius of a halo, $r_v$, as the boundary of the
+spherical volume that encloses an average density of $\Delta_v$ times
+the critical density of the Universe. The corresponding mass $M_{v}$
+can be thus expressed as $M_{v} = \frac{4\pi}{3}\rho_c\Delta_v r_v^3$.
+
+The total mass enclosed within a radius $r$ can be computed to be:
+\begin{equation}
+M(<r) = 4\pi\rho_c\delta_c  r_s^3\left[\ln \left
+  (\frac{r_s+r}{r}\right) - \frac{r}{r_s+r}\right].
+\end{equation}
+
+We can now define the concentration of the halo as $c=r_v/r_s$, the
+dimensioless variable $x\equiv r/r_v$ and $m\equiv M(<r)/M_v$, which
+allows us to express the total enclosed mass within a dimensionless
+radius $x$ as:
+
+\begin{equation}
+m(<x) =
+\frac{1}{A}\left[\ln\left(1+xc\right)-\left(\frac{xc}{xc+1}\right)\right],
+\label{eq:profile}
+\end{equation}
+%
+where 
+%
+\begin{equation}
+A=\left[\ln\left(1+c\right)-\left(\frac{c}{c+1}\right)\right],
+\end{equation}
+
+meaning that the concentration is the only free parameter to
+determine the density profile of the halo.
+
+\begin{figure}
 \caption{FIXME: Mass profile of a halo}
@@
 
-Then the virial radius is obtained and the particles that are beyond the virial radius are removed.
-After that both the mass and the radius get normalized respect to the mass and virial radius, we will call these new variables $m_{n}$ and $r_{n}$.
-The last part of the process consists in fitting the normalized NFW mass profile to the $m_{n}$ data using the Metropolis-Hastings algorithm to sample the Likelihood ${\cal L}\left(c\right)=\exp\left(-\chi^{2}\left(c\right)\right)$ where
-\[
-\chi^{2}\left(c\right)=\sum\limits _{n}\left|m_{n}-m_{nfw}\left(r_{n},c\right)\right|^{2}
-\]
-And taking the values of $c$ where the Likelihood is maximum.
-Moreover, we can obtain a confidence interval for $c$ doing an histogram of the random walk done by the Metropolis-Hastings Algorithm.
-Finally we compare this results with the values obtaned by BDM, since the number of halos obtained by FOF and BDM is different, each BDM halo gets related with the nearest halo in FOF.
-We compute two concentrations, one where the overdensity limit is $360\rho_{back}$ (like in BDMV) an other where the overdensity limit is $740\rho_{back}$ (like in BDMW).
+\section{A Bayesian Approach to Halo Fitting}
+\label{sec:method}
 
-\section{Mock Data and Simulations}
+We proceed to find the value of the concentration parameter that
+best describes the simulation data, following the model in
+Eq. (\ref{eq:profile}). We use the integrated mass profile because it
+allows us to use the data directly with the simulation without binning
+the particle positions and estimating a density.
+
+We construct the integrated mass profile by ranking the particles by
+their increasing distance to the center of the halo. Once they are ranked,
+the total mass at a radius $r_i$, increases by $m_p$, where $r_i$ is
+the position of the $i$-th particle and $m_p$ is the mass of the
+computational particle.  We define the center of the halo to be  at
+the position of the particle with the lowest gravitational
+potential. In the process of building the mass profile we discard the
+particle at the center.
+
+We stop the construction of the integrated mass profile once we arrive
+at an average density of $\Delta_h\rho_c$. This radius marks the
+virial radius and the virial mass. We divide the total mass enclosed
+mass $M_i$ and the radii $r_i$ by these values to obtaine the
+dimensionless variables $x_i$ and $m_i$.
+
+Using these positions and masses we define the following $\chi^2$ function
+
+\begin{equation}
+\chi^2(c) = \sum_{i}[m_i - m(< x_i;c)]^2, 
+\end{equation}
+%
+where $m(<x_i;c)$ corresponds to the values in Eq.(\ref{eq:profile}) at
+$x=x_i$ and a given value of the concentration parameter $c$.
+
+Finally we use a Metropolis-Hastings algorithm to sample the likelihood
+function distribution defined by ${\cal L}(c)=\exp(-\chi^2(c)/2)$ to
+find the optimum value of $c$ and its associated uncertainty
+$\sigma_c$.
+
+\section{Numerical Experiments}
+Finally we compare this results with the values obtaned by BDM, since
+the number of halos obtained by FOF and BDM is different, each BDM
+halo gets related with the nearest halo in FOF. We compute two
+concentrations, one where the overdensity limit is $360\rho_{back}$
+(like in BDMV) an other where the overdensity limit is
+$740\rho_{back}$ (like in BDMW).
+
+\subsection{Mock Data and Simulations}
 \label{sec:data}

### 2014-05-25 paper/article.tex
new title

@@
 
-\title[Bayesian halo concentration]{Measurement of dark matter halo concentrations using a bayesian approach}
+\title[Bayesian halo concentrations]{Dark matter halo
+  concentrations with a bayesian approach}
 \author[Poveda \& Forero-Romero]{
@@
 \begin{equation}
-\chi^2(c) = \sum_{i}[m_i - m(< x_i;c)]^2, 
+\chi^2(c) = \sum_{i}[\log m_i - \log m(< x_i;c)]^2, 
 \end{equation}
@@
 \section{Numerical Experiments}
+
+\subsection{Mock Halos}
+Several halos with known values of $c$ were generated. These halos
+were then processed to determine the acurracy of this method. The
+number of particles and value of $c$ for each halo were generated
+randomly.
+
+\subsection{Simulation Data}
+\label{sec:data}
+
+\section{Results}
+\label{sec:results}
+
 Finally we compare this results with the values obtaned by BDM, since
@@
 
-\subsection{Mock Data and Simulations}
-\label{sec:data}
-\section{Results}
-\label{sec:results}
-
-\subsection{Trial Problem with several Generated Halos}
-
-Several halos with known values of $c$ were generated. These halos
-were then processed to determine the acurracy of this method. The
-number of particles and value of $c$ for each halo were generated
-randomly.  
+\subsection{Mock Halos}
 \begin{figure}[H]
@@
 
-\subsection{Results from the simulations}
-
-\subsection{What kind of implications (Low resolution simulations, other fitting algorithms)}
+\subsection{Simulation Dat}
 
@@
 \label{sec:discussion}
+
+\subsection{Comparison against other methods}
+
+\subsection{Concentration as a function of halo mass}
+
+\subsection{Implication for comparison against observations}
 

### 2014-05-26 paper/article.tex
new references and updating procedure

@@
 We define the virial radius of a halo, $r_v$, as the boundary of the
-spherical volume that encloses an average density of $\Delta_v$ times
-the critical density of the Universe. The corresponding mass $M_{v}$
-can be thus expressed as $M_{v} = \frac{4\pi}{3}\rho_c\Delta_v r_v^3$.
+spherical volume that encloses an average density of $\Delta_h$ times
+the average density of the Universe. The corresponding mass $M_{v}$,
+the virial mass, can be thus expressed as $M_{v} =
+\frac{4\pi}{3}\bar{\rho}\Delta_h r_v^3$.
 
@@
 meaning that the concentration is the only free parameter to
-determine the density profile of the halo.
+determine the density profile of the halo. In Figure
+\ref{fig:profiles} we show the family of normalized integrated mass
+profiles for different values of the concentration in the range
+$1\leq c \leq 20$.
 
@@
 We stop the construction of the integrated mass profile once we arrive
-at an average density of $\Delta_h\rho_c$. This radius marks the
+at an average density of $\Delta_h\bar{\rho}$. This radius marks the
 virial radius and the virial mass. We divide the total mass enclosed
@@
 \subsection{Mock Halos}
-Several halos with known values of $c$ were generated. These halos
-were then processed to determine the acurracy of this method. The
-number of particles and value of $c$ for each halo were generated
-randomly.
+
+We generate $100$ mock halos with concentration values randomly
+placed in the range $1<c<10$. Each one of the halos is generated with
+four different total particle numbers: $20$, $200$, $2000$ and $20000$.
+
+The method we use to generate the halos is based on the integrated
+mass profile. {\bf Our algorithm works as follows...}
 
@@
 
-\section{Results}
-\label{sec:results}
+We use data from the MultiDark cosmological volume. This simulation
+follows the non-linear evolution of a dark matter density field
+sampled with $2048^3$ particles over a cubic box of $1000$ \hMpc on a
+side. The data is publicly available, more details about the structure
+of the database and the simulations can be found in
+\citep{2013AN....334..691R}.
+
+We select a sample of halos in a cubic sub-volumne of $XXX$ \hMpc on a
+side. We select first all the halos at $z=0$ detected with a
+Friends-of-Friends (FoF) algorithm with masses in the interval $10^{11}\leq
+M_{\rm FoF}/\hMsun \leq 10^{15}$. The FoF algorithm ran with a linking
+length of $0.17$ times the average interparticle distance. This choice
+translates into an overdensity $\Delta_h\sim 700$ that is dependent on
+the halo concentration \citep{More2011}.
+
+For each selected halo with the previous procedure we select from the database
+all the particles that belong to it. From the particles we follow the
+procedure spelled out in Section \ref{sec:method} with $\Delta_h=740$
+(corresponding to $200$ times the critical density) to find the
+halo concentration. Finally, we store the values obtained for the
+virial radius, virial mass and concentration.
 
@@
 $740\rho_{back}$ (like in BDMW).
+
+\section{Results}
+\label{sec:results}
 

### 2014-05-26 paper/article.tex
update on the data

@@
 
-We select a sample of halos in a cubic sub-volumne of $XXX$ \hMpc on a
-side. We select first all the halos at $z=0$ detected with a
-Friends-of-Friends (FoF) algorithm with masses in the interval $10^{11}\leq
-M_{\rm FoF}/\hMsun \leq 10^{15}$. The FoF algorithm ran with a linking
-length of $0.17$ times the average interparticle distance. This choice
-translates into an overdensity $\Delta_h\sim 700$ that is dependent on
-the halo concentration \citep{More2011}.
+We select a sample of halos in a cubic sub-volumne of $100$ \hMpc on a
+side centered on the most massive halo in the simulation at
+$z=0$\footnote{This corresponds to the \texttt{miniMDR1} database in
+  the MultiDark webpage}. We select first all the halos at $z=0$
+detected with a Friends-of-Friends (FoF) algorithm with masses in the
+interval $10^{11}\leq M_{\rm FoF}/\hMsun \leq 10^{15}$. The FoF
+algorithm ran with a linking length of $0.17$ times the average
+interparticle distance. This choice translates into an overdensity
+$\Delta_h\sim 700$ that is dependent on the halo concentration
+\citep{More2011}.
 

### 2014-05-26 src/main.py
just bdmw

@@ -85,17 +85,9 @@ def run(directories,process_number):
         avg_density = mass/((4.0/3.0)*np.pi*(radius**3))
         rho_back = mass_element*(2048.0/1000.0)**3
 
-        bdmv = 360.0
         bdmw = 740.0
 
-        bdmv_index = np.argmin(np.abs(avg_density-bdmv*rho_back))
         bdmw_index = np.argmin(np.abs(avg_density-bdmw*rho_back))
-
-        if np.argmin(np.abs(avg_density-bdmv*rho_back)) > 1:
-            r_bdmv = radius[bdmv_index]
-        else:
-            r_bdmv = radius[-1]
-            bdmv_index = len(avg_density)-1
 
         if np.argmin(np.abs(avg_density-bdmw*rho_back)) > 1:
             r_bdmw = radius[bdmw_index]
@@ -103,13 +95,7 @@ def run(directories,process_number):
             r_bdmw = radius[-1]
             bdmw_index = len(avg_density)-1
 
-        bdmv_mass = np.resize(mass,bdmv_index)
-        bdmv_radius = np.resize(radius,bdmv_index)
-        
-        bdmv_mass = bdmv_mass/bdmv_mass[-1]
-        bdmv_radius = bdmv_radius/bdmv_radius[-1]
-        
-        bdmw_mass = np.resize(mass,bdmw_index)
+            bdmw_mass = np.resize(mass,bdmw_index)
         bdmw_radius = np.resize(radius,bdmw_index)
 
         bdmw_mass = bdmw_mass/bdmw_mass[-1]
@@ -117,29 +103,20 @@ def run(directories,process_number):
 
         n_iterations = 50000
 
-#        log_bdmv,bdmv_walk,bdmv_chi2 = fit.metropolis_one(np.log(bdmv_radius),np.log(bdmv_mass),nfw.loglogmass_norm,n_iterations)
-#        log_bdmw,bdmw_walk,bdmw_chi2 = fit.metropolis_one(np.log(bdmw_radius),np.log(bdmw_mass),nfw.loglogmass_norm,n_iterations)
-
         step = np.array([np.log(1.03)])
         guess = np.array([np.log(10)])
         reest = [lambda x: x >= 0]
 
[…]

### 2014-05-26 src/plotter.py
just bdmw

@@ -10,13 +10,12 @@ angle = np.arange(0,2*np.pi,0.01)
 # Returns:
 #     Three files with graphics in the planes x-y, y-z and z-x of the halo
 
-def halo(x,y,z,x_center,y_center,z_center,r_bdmv,r_bdmw):
+def halo(x,y,z,x_center,y_center,z_center,r_vir):
     
     pylab.plot(x , y, 'k.')
     pylab.plot(x_center , y_center, 'ko')
-    pylab.plot(r_bdmv*np.cos(angle)+x_center,r_bdmv*np.sin(angle)+y_center,'--b',label='BDMV')
-    pylab.plot(r_bdmw*np.cos(angle)+x_center,r_bdmw*np.sin(angle)+y_center,'--r',label='BDMW')
-    pylab.legend(loc=4, borderaxespad=0.5)
+    pylab.plot(r_vir*np.cos(angle)+x_center,r_vir*np.sin(angle)+y_center,'--b')
+    
     pylab.xlabel('x (Mpc/H)')
     pylab.ylabel('y (Mpc/H)')
     pylab.title('Halo x-y')
@@ -25,9 +24,7 @@ def halo(x,y,z,x_center,y_center,z_center,r_bdmv,r_bdmw):
 
     pylab.plot(y , z, 'k.')
     pylab.plot(y_center , z_center, 'ko')
-    pylab.plot(r_bdmv*np.cos(angle)+y_center,r_bdmv*np.sin(angle)+z_center,'--b',label='BDMV')
-    pylab.plot(r_bdmw*np.cos(angle)+y_center,r_bdmw*np.sin(angle)+z_center,'--r',label='BDMW')
-    pylab.legend(loc=4, borderaxespad=0.5)
+    pylab.plot(r_vir*np.cos(angle)+y_center,r_vir*np.sin(angle)+z_center,'--b')
     pylab.xlabel('y (Mpc/H)')
     pylab.ylabel('z (Mpc/H)')
     pylab.title('Halo y-z')
@@ -36,9 +33,7 @@ def halo(x,y,z,x_center,y_center,z_center,r_bdmv,r_bdmw):
 
     pylab.plot(z , x, 'k.')
     pylab.plot(z_center , x_center, 'ko')
-    pylab.plot(r_bdmv*np.cos(angle)+z_center,r_bdmv*np.sin(angle)+x_center,'--b',label='BDMV')
[…]

### 2014-05-26 src/main.py
corrected identation mistake

@@ -95,7 +95,7 @@ def run(directories,process_number):
             r_bdmw = radius[-1]
             bdmw_index = len(avg_density)-1
 
-            bdmw_mass = np.resize(mass,bdmw_index)
+        bdmw_mass = np.resize(mass,bdmw_index)
         bdmw_radius = np.resize(radius,bdmw_index)
 
         bdmw_mass = bdmw_mass/bdmw_mass[-1]
@@ -138,7 +138,6 @@ def run(directories,process_number):
             pylab.ylabel('$\cal{L}$')
             pylab.savefig('likelihood.png',dpi=300)
             pylab.close()
-
 
             pylab.hist(np.exp(bdmw_walk),1000,normed=True)
             pylab.xlabel('c')

### 2014-05-26 src/main.py
corrected typos

@@ -23,7 +23,7 @@ processes = int(sys.argv[6])
 now = datetime.datetime.now().strftime("%Y-%m-%d-%H:%M:%S")
 mass_element = 1.0   
 plt = 1
-total_list = sorted(os.listdir('./'+str(sys.argv[1])))
+total_list = os.listdir('./'+str(sys.argv[1]))
 len_list = len(total_list)
 lists = [total_list[i*len_list // processes: (i+1)*len_list //processes] for i in range(processes)]
 jobs = []
@@ -124,9 +124,9 @@ def run(directories,process_number):
             os.system('mkdir '+results_folder)
             os.chdir(results_folder)
 
-            plotter.halo(x,y,z,x_center,y_center,z_center,r_bdmv,r_bdmw)
-            plotter.mass_norm(bdmw_radius,bdmw_mass,c_bdmw,bdmw_max,bdmw_min)
-            pylab.scatter(np.exp(bdmv_walk),bdmv_chi2)
+            plotter.halo(x,y,z,x_center,y_center,z_center,r_bdmw)
+            plotter.mass_norm(bdmw_radius,bdmw_mass,c_bdmw,bdmw_max,bdmw_min,'bdmw')
+            pylab.scatter(np.exp(bdmw_walk),bdmw_chi2)
             pylab.legend(loc=4, borderaxespad=0.5)
             pylab.xlabel('$c$')
             pylab.ylabel('$\chi ^2$')

### 2014-05-26 src/main.py
removed unused code

@@ -127,7 +127,6 @@ def run(directories,process_number):
             plotter.halo(x,y,z,x_center,y_center,z_center,r_bdmw)
             plotter.mass_norm(bdmw_radius,bdmw_mass,c_bdmw,bdmw_max,bdmw_min,'bdmw')
             pylab.scatter(np.exp(bdmw_walk),bdmw_chi2)
-            pylab.legend(loc=4, borderaxespad=0.5)
             pylab.xlabel('$c$')
             pylab.ylabel('$\chi ^2$')
             pylab.savefig('chi2.png',dpi=300)

### 2014-05-26 src/main.py
every plot in pdf

@@ -129,19 +129,19 @@ def run(directories,process_number):
             pylab.scatter(np.exp(bdmw_walk),bdmw_chi2)
             pylab.xlabel('$c$')
             pylab.ylabel('$\chi ^2$')
-            pylab.savefig('chi2.png',dpi=300)
+            pylab.savefig('chi2.pdf',dpi=300)
             pylab.close()
 
             pylab.scatter(np.exp(bdmw_walk),np.exp(-bdmw_chi2/2),c='r',label='BDMW')
             pylab.xlabel('$c$')
             pylab.ylabel('$\cal{L}$')
-            pylab.savefig('likelihood.png',dpi=300)
+            pylab.savefig('likelihood.pdf',dpi=300)
             pylab.close()
 
             pylab.hist(np.exp(bdmw_walk),1000,normed=True)
             pylab.xlabel('c')
             pylab.ylabel('P(c)')
-            pylab.savefig('histogram.png',dpi=300)
+            pylab.savefig('histogram.pdf',dpi=300)
             pylab.close()
 
             os.chdir('../../')

### 2014-05-26 src/plotter.py

@@ -19,7 +19,7 @@ def halo(x,y,z,x_center,y_center,z_center,r_vir):
     pylab.xlabel('x (Mpc/H)')
     pylab.ylabel('y (Mpc/H)')
     pylab.title('Halo x-y')
-    pylab.savefig('halo_xy.png',format='png',dpi=300)
+    pylab.savefig('halo_xy.pdf',format='pdf',dpi=300)
     pylab.close()
 
     pylab.plot(y , z, 'k.')
@@ -28,7 +28,7 @@ def halo(x,y,z,x_center,y_center,z_center,r_vir):
     pylab.xlabel('y (Mpc/H)')
     pylab.ylabel('z (Mpc/H)')
     pylab.title('Halo y-z')
-    pylab.savefig('halo_yz.png',format='png',dpi=300)
+    pylab.savefig('halo_yz.pdf',format='pdf',dpi=300)
     pylab.close()
 
     pylab.plot(z , x, 'k.')
@@ -37,7 +37,7 @@ def halo(x,y,z,x_center,y_center,z_center,r_vir):
     pylab.xlabel('z (Mpc/H)')
     pylab.ylabel('x (Mpc/H)')
     pylab.title('Halo z-x')
-    pylab.savefig('halo_zx.png',format='png',dpi=300)
+    pylab.savefig('halo_zx.pdf',format='pdf',dpi=300)
     pylab.close()
    
 # Plots the NFW mass profile 
@@ -56,7 +56,7 @@ def mass(radius, mass, parameters):
     pylab.xlabel('Radius (Mpc/H)')
     pylab.ylabel('Mass (10^11 Solar Masses)')
     pylab.title('Mass')
-    pylab.savefig('mass.png',format='png',dpi=300)
+    pylab.savefig('mass.pdf',format='pdf',dpi=300)
     pylab.close()
 
 # Plots the NFW mass profile in logarithmic scale 
@@ -81,7 +81,7 @@ def logmass(radius, mass, parameters,lims_a,lims_b):
     pylab.xlabel('Radius (Mpc/H)')
     pylab.ylabel('Mass (10^11 Solar Masses)')
     pylab.title('Mass (log-log)')
-    pylab.savefig('log_mass.png',format='png',dpi=300)
+    pylab.savefig('log_mass.pdf',format='pdf',dpi=300)
     pylab.close()
 
 def mass_norm(radius,mass,c,c_max,c_min,name):
[…]

### 2014-05-26 src/fit.py
removed emcee

@@ -1,6 +1,6 @@
-import numpy as np, sys, os, nfw, emcee
+import numpy as np, sys, os, nfw
 from scipy.optimize import curve_fit
-from emcee.utils import sample_ball
+
 # Returns the chi squared estimate given a prediction and the real data
 # Requires:
 #     obs: observed data

### 2014-05-26 paper/article.tex
minor updates
new paragaph

@@
 The method we use to generate the halos is based on the integrated
-mass profile. {\bf Our algorithm works as follows...}
+mass profile.
+Given the number of particles $n$ and the concentration $c$ we define the mass element as $\delta m = 1/n$ (this corresponds to the mass of each particle, such that the total mass is one).
+Then for each number $k$ from $1$ to $n$ we find the value of $r$ such that
+\begin{equation}
+m(<r;c)-k \cdot \delta m 
+\end{equation}
+is zero using Ridders' method.
+This value of $r$ will be the radius of the $k$th particle of the generated halo, then polar and azimuthal angles $\theta$ and $\phi$ are generated randomly.
+Finally these three coordinates are transformed into cartesian coordinates $(r,\theta,\phi) \rightarrow (x,y,z)$.
+This process is repeated $n$ times in order to generate the $x,y,z$ coordinates for each particle.
 
@@
 interparticle distance. This choice translates into an overdensity
-$\Delta_h\sim 700$ that is dependent on the halo concentration
+$\Delta_h\sim 400-700$ that is dependent on the halo concentration
 \citep{More2011}.
@@
 
-Finally we compare this results with the values obtaned by BDM, since
-the number of halos obtained by FOF and BDM is different, each BDM
-halo gets related with the nearest halo in FOF. We compute two
-concentrations, one where the overdensity limit is $360\rho_{back}$
-(like in BDMV) an other where the overdensity limit is
-$740\rho_{back}$ (like in BDMW).
-
 \section{Results}
@@
 \subsection{Mock Halos}
+\label{sec:results_mocks}
 \begin{figure}[H]
@@
 
-\subsection{Simulation Dat}
+\subsection{Simulation Data}
+\label{sec:results_mocks}
 
@@
 
-\subsection{Implication for comparison against observations}
+\subsection{Implication for comparisons against observations}
 

### 2014-05-27 src/glue_test.py
sorted results

@@ -6,7 +6,7 @@ filenames = sorted([directory+'/'+element for element in total_list if 'result' 
 
 
 export = open(directory+'/results.csv', 'w')
-head = 'Id,x_center,y_center,z_center,c_bdmv,c_bdmv_max,c_bdmv_min,c_bdmw,c_bdmw_max,c_bdmw_min,r_vir_bdmv,r_vir_bdmw,n_vir_bdmv,n_vir_bdmw,n_tot'
+head='Id,x_center,y_center,z_center,conc,c_max,c_min'
 
 with export as outfile:
     for fname in filenames:
@@ -17,4 +17,4 @@ with export as outfile:
 data = np.loadtxt(directory+'/results.csv',delimiter=',')
 data = data[data[:,0].argsort()]
 
-np.savetxt(directory+'/results.csv',data,fmt='%d,%f,%f,%f,%f,%f,%f,%f,%f,%f,%f,%f,%d,%d,%d',header=head)
+np.savetxt(directory+'/results.csv',data,fmt='%d,%f,%f,%f,%f,%f,%f',header=head)

### 2014-05-27 data/test/catalog.py
sorted results

@@ -4,8 +4,8 @@ expected = np.loadtxt('parameters.csv',delimiter = ',')
 obtained = np.loadtxt('results.csv',delimiter = ',')
 
 c_exp = expected[:,0]
-r_vir = expected[:,1]
-m_vir = expected[:,2]
+r_vir = np.ones(len(expected[:,0]))
+m_vir = expected[:,1]
 c_obt = obtained[:,4]
 c_max = obtained[:,5]
 c_min = obtained[:,6]

### 2014-05-27 paper/article.tex
removed comma

@@
 mass profile.
-Given the number of particles $n$ and the concentration $c$ we define the mass element as $\delta m = 1/n$ (this corresponds to the mass of each particle, such that the total mass is one).
+Given the number of particles $n$ and the concentration $c$ we define the mass element as $\delta m = 1/n$ (this corresponds to the mass of each particle such that the total mass is one).
 Then for each number $k$ from $1$ to $n$ we find the value of $r$ such that

### 2014-05-27 paper/article.tex
new figure + new paragraph

@@
 The method we use to generate the halos is based on the integrated
-mass profile.
-Given the number of particles $n$ and the concentration $c$ we define the mass element as $\delta m = 1/n$ (this corresponds to the mass of each particle such that the total mass is one).
-Then for each number $k$ from $1$ to $n$ we find the value of $r$ such that
+mass profile. Given the number of particles $n$ and the concentration
+$c$ we define the mass element as $\delta m = 1/n$ (this corresponds
+to the mass of each particle such that the total mass is one). Then
+for each number $k$ from $1$ to $n$ we find the value of $r$ such that
+the difference 
+%
 \begin{equation}
@@
 \end{equation}
-is zero using Ridders' method.
-This value of $r$ will be the radius of the $k$th particle of the generated halo, then polar and azimuthal angles $\theta$ and $\phi$ are generated randomly.
-Finally these three coordinates are transformed into cartesian coordinates $(r,\theta,\phi) \rightarrow (x,y,z)$.
-This process is repeated $n$ times in order to generate the $x,y,z$ coordinates for each particle.
+%
+is zero using Ridders' method. This value of $r$ is the radius of
+the $k$th particle of the generated halo, then polar and azimuthal
+angles $\theta$ and $\phi$ are randomly generated. Finally these three
+coordinates are transformed into cartesian coordinates
+$(r,\theta,\phi) \rightarrow (x,y,z)$. This process is repeated $n$
+times in order to generate the $x,y,z$ coordinates for each particle.
 
@@
 \label{sec:results_mocks}
-\begin{figure}[H]
-\caption{FIXME: Test results}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{percentual_diff.pdf}
+\end{center}
+\caption{Cumulative distribution of the fractional difference between
+  the input concentration in the mock halo generator, $c_{in}$ and the
+  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
+  halos generated with a different number of particles, $N$.
+    \label{fig:results_mocks}}
 \end{figure}
+
+In Figure \ref{fig:results_mocks} we show the integrated distribution
+percentual difference between the concentration measured with our
+fitting method $c_{out}$ in comparison with the concentration used to
+generate the mock halos, $c_{in}$, $D=(c_{in}-c_{out})/c_{in}$.
 

### 2014-05-27 src/table.py
table generator tool created

@@ -1,0 +1,18 @@
+import numpy as np
+
+data = np.loadtxt('results.csv',delimiter=',')
+orig = np.loadtxt('parameters.csv',delimiter=',')
+
+conc = orig[:,0]
+
+n = int(len(conc)/4)
+print n
+conc = conc[0:n]
+c_20 = data[0:n,4]
+c_200 = data[n:2*n,4]
+c_2000 = data[2*n:3*n,4]
+c_20000 = data[3*n:4*n,4]
+print len(conc),len(c_20),len(c_200),len(c_2000),len(c_20000)
+export = np.dstack((conc,c_20,c_200,c_2000,c_20000))[0]
+head = 'c,c_20,c_200,c_2000,c_20000'
+np.savetxt('table.csv',export,fmt='%f,%f,%f,%f,%f',header=head)

### 2014-07-31 paper/article.tex
new plots

@@
 \begin{figure}
-\caption{FIXME: Mass profile of a halo}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{nfw_normalized.pdf}
+\end{center}
+\caption{Mass profiles of several haloes with different concentrations
+    \label{fig:profiles}}
 \end{figure}
@@
 generate the mock halos, $c_{in}$, $D=(c_{in}-c_{out})/c_{in}$.
+Then we can see that as the number of particles increases, the curve becomes more pronounced at 0.
+Showing that for most of the halos $c_{in}$ is very similar to $c_{out}$.
 
@@
 \subsection{Comparison against other methods}
-
+FIXME: Ask to Jaime, Differences with BDM
 \subsection{Concentration as a function of halo mass}
-
+FIXME: Add plots and interpretation, Matches with BDM
 \subsection{Implication for comparisons against observations}
+FIXME: Ask to Jaime
 
@@
 \label{sec:conclusions}
+FIXME: Ask to Jaime
 

### 2014-07-31 src/plotting.py

@@ -1,0 +1,16 @@
+import pylab, numpy as np, nfw, matplotlib
+
+r = np.arange(0,1,0.001)
+C = np.linspace(1,20,6)
+
+for c in C:
+    pylab.plot(r,nfw.mass_norm(r,c),color='black',lw= np.log(c+1)/2,label="$c="+str(c)+"$")
+pylab.legend(loc=0, scatterpoints=1, prop={'size':20})
+filename = 'nfw_normalized'
+matplotlib.rcParams.update({'font.size': 18})
+pylab.xlabel('$r_{norm}$',fontsize=20)
+pylab.ylabel('$m_{norm}$',fontsize=20)
+pylab.savefig(filename+'.eps',transparent=True)
+pylab.savefig(filename+'.pdf',transparent=True)
+pylab.savefig(filename+'.png',transparent=True)
+pylab.close()

### 2014-08-21 data/results/miniMD/compare.py
new results

@@ -1,0 +1,47 @@
+import numpy as np, pylab,sys
+
+mcmc = np.loadtxt(sys.argv[1],delimiter=',')
+vel = np.loadtxt(sys.argv[2],delimiter=',')
+dens = np.loadtxt(sys.argv[3],delimiter=',')
+
+id_mcmc = mcmc[:,0]
+id_dens = dens[:,0]
+
+c_mcmc = mcmc[:,4]
+c_vel = vel[:,4]
+c_dens = dens[:,4]
+
+c_mcmc_dens = np.empty(0)
+c_vel_dens = np.empty(0)
+
+for id in id_dens:
+    index = np.where(id_mcmc == id)
+    c_mcmc_dens = np.append(c_mcmc_dens,c_mcmc[index])
+    c_vel_dens = np.append(c_vel_dens,c_vel[index])
+
+pylab.scatter(c_vel,c_mcmc)
+pylab.plot(c_vel,c_vel,'-r')
+pylab.xscale('log')
+pylab.yscale('log')
+pylab.xlabel("$Velocity\ Method$")
+pylab.ylabel("$Mass\ Method$")
+pylab.savefig('velocity-mass.png',dpi=200)
+pylab.close()
+
+pylab.scatter(c_dens,c_mcmc_dens)
+pylab.plot(c_dens,c_dens,'-r')
+pylab.xscale('log')
+pylab.yscale('log')
+pylab.xlabel("$Density\ Method$")
+pylab.ylabel("$Mass\ Method$")
+pylab.savefig('density-mass.png',dpi=200)
+pylab.close()
+
+pylab.scatter(c_dens,c_vel_dens)
+pylab.plot(c_dens,c_dens,'-r')
+pylab.xscale('log')
+pylab.yscale('log')
+pylab.xlabel("$Density\ Method$")
+pylab.ylabel("$Velocity\ Method$")
+pylab.savefig('density-velocity.png',dpi=200)
+pylab.close()

### 2014-08-21 src/nfw.py

@@ -54,5 +54,5 @@ def loglogdensity(logr,loga,logb):
 def loglogmass_norm(logr_norm,logc):
     return np.log((np.log(1.0+np.exp(logr_norm+logc))-np.exp(logr_norm+logc)/(1.0+np.exp(logr_norm+logc)))/(np.log(1.0+np.exp(logc))-np.exp(logc)/(1.0+np.exp(logc))))
 
-def loglogdensity_norm(logr_norm,logc):
-    return (2.0*(np.log(1.0+np.exp(logc))-np.log(1.0+np.exp(logr_norm+logc)))-logr_norm)
+def loglogdensity_norm(logr_norm,logc):    
+    return 2.0*(np.log(1.0+np.exp(logc))-np.log(1.0+np.exp(logr_norm+logc)))-logr_norm

### 2014-08-25 data/results/miniMD/compare.py
new plot

@@ -1,5 +1,26 @@
 import numpy as np, pylab,sys
 
+def get_stats(log_mass,conc):
+
+    bins = np.arange(0,np.amax(log_mass)+0.5,0.5)
+    bins_index = np.digitize(log_mass,bins)
+    median = np.empty(len(bins))
+    quar1 = np.empty(len(bins))
+    quar2 = np.empty(len(bins))
+
+    for i in range(len(bins)):
+        tempo = []
+        for j in range(len(bins_index)):
+            if (i == bins_index[j]):
+                tempo.append(conc[j])
+        tempo = np.array(tempo)
+        if (tempo.size):
+            median[i] = np.median(tempo)
+            quar1[i],quar2[i] = np.percentile(tempo,[25,75])
+        else:
+            median[i],quar1[i],quar2[i]=0,0,0
+    return bins,median,quar1,quar2
+
 mcmc = np.loadtxt(sys.argv[1],delimiter=',')
 vel = np.loadtxt(sys.argv[2],delimiter=',')
 dens = np.loadtxt(sys.argv[3],delimiter=',')
@@ -11,8 +32,40 @@ c_mcmc = mcmc[:,4]
 c_vel = vel[:,4]
 c_dens = dens[:,4]
 
+m_mcmc = mcmc[:,8]
+m_vel = vel[:,7]
+m_dens = dens[:,8]
+
 c_mcmc_dens = np.empty(0)
 c_vel_dens = np.empty(0)
+
+'''
+pylab.scatter(m_mcmc,c_mcmc,c='b')
+pylab.scatter(m_vel,c_vel,c='y')
+pylab.scatter(m_dens,c_dens,c='r')
+pylab.xscale('log')
+pylab.yscale('log')
+pylab.show()
+'''
+
+bins_mcmc,median_mcmc,quar1_mcmc,quar2_mcmc = get_stats(np.log10(m_mcmc),c_mcmc)
+bins_vel,median_vel,quar1_vel,quar2_vel = get_stats(np.log10(m_vel),c_vel)
+bins_dens,median_dens,quar1_dens,quar2_dens = get_stats(np.log10(m_dens),c_dens)
+
+pylab.plot(10**(bins_mcmc),median_mcmc,'-g',lw=2,label='Mass')
+pylab.fill_between(10**(bins_mcmc),quar1_mcmc,quar2_mcmc,color='g',alpha=0.4)
[…]

### 2014-08-25 src/velocity.py
i forgot an square root

@@ -86,7 +86,7 @@ def run(directories,process_number):
 	v_max = np.max(velocity)
 	v_vir = velocity[-1]
 	def f(c):
-		return (v_max/v_vir) - 0.216*c/(np.log(1+c)-c/(1+c)) 
+		return (v_max/v_vir) - np.sqrt(0.216*c/(np.log(1+c)-c/(1+c))) 
 	
 	c = fsolve(f,10.0)
         export = open(filename_export, 'a')

### 2014-08-25 paper/article.tex
new results
wrote a word

@@
 \subsection{Comparison against other methods}
-FIXME: Ask to Jaime, Differences with BDM
+We compared this method against two methods: The first one consists in using shells for estimating the density in function of the radius and using the same MCMC method for fitting and the second one consists in using the circular velocity $V(r)=\sqrt{GM(<r)/r}$ and the relation for the NFW profile
+\begin{equation}
+\frac{V_{max}}{V(r_{vir})} = \sqrt{\frac{0.216c}{M(r_{vir})}}
+\end{equation}
+Where $V_{max}$ is the maximum velocity, to find the value of the concentration. We obtained the following results
+
+Fixme: RESULTS!
 \subsection{Concentration as a function of halo mass}
-FIXME: Add plots and interpretation, Matches with BDM
+Aditionally we compared those three methods plotting the concentration as a function of halo mass
+
+Fixme: Plot!
+
+The bold lines in Figure ?? corresponds to the median and the thinner lines corresponds to the quartiles.
 \subsection{Implication for comparisons against observations}

### 2014-08-26 paper/article.tex
added plot

@@
 \begin{equation}
-\frac{V_{max}}{V(r_{vir})} = \sqrt{\frac{0.216c}{M(r_{vir})}}
+\frac{V_{max}}{V(r_{v})} = \sqrt{\frac{0.216c}{M(r_{v};c)}}
 \end{equation}
-Where $V_{max}$ is the maximum velocity, to find the value of the concentration. We obtained the following results
+Where $V_{max}$ is the maximum velocity, to find the value of the concentration.
 
-Fixme: RESULTS!
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{density-mass.pdf}
+\end{center}
+\caption{Concentration obtained from the mass method against the one obtained in the density method
+    \label{fig:density-mass}}
+\end{figure}
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{density-velocity.pdf}
+\end{center}
+\caption{Concentration obtained from the velocity method against the one obtained in the density method
+    \label{fig:density-velocity}}
+\end{figure}
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{velocity-mass.pdf}
+\end{center}
+\caption{Concentration obtained from the mass method against the one obtained in the velocity method
+    \label{fig:velocity-mass}}
+\end{figure}
 \subsection{Concentration as a function of halo mass}
-Aditionally we compared those three methods plotting the concentration as a function of halo mass
+Aditionally we compared those three methods plotting the concentration as a function of the number of particles of each halo
 
-Fixme: Plot!
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{concentration.pdf}
+\end{center}
+\caption{Concentration against number of particles
+    \label{fig:concentrations}}
+\end{figure}
 
-The bold lines in Figure ?? corresponds to the median and the thinner lines corresponds to the quartiles.
+The bold lines in Figure \ref{fig:concentrations} corresponds to the median and the thinner lines corresponds to the quartiles.
+As we can see the velocity method has a greater dispersion compared to the other two.
 \subsection{Implication for comparisons against observations}

### 2014-09-05 data/test/mock_100/error.py
plots are ready

@@ -7,14 +7,14 @@ dens = np.loadtxt('mock_100_density/table.csv',delimiter=',')
 orig = vlct[:,0]
 
 def chi2(x_obs,x_org):
-    return np.sum((x_obs-x_org)**2)
+    return np.sum(np.abs((x_obs-x_org)/x_org))/len(x_obs)
 
 pylab.title('$Velocity$')
 pylab.plot(orig,orig,label='$real$')
-pylab.plot(orig,vlct[:,1],label='$n=20$')
-pylab.plot(orig,vlct[:,2],label='$n=200$')
-pylab.plot(orig,vlct[:,3],label='$n=2000$')
-pylab.plot(orig,vlct[:,4],label='$n=20000$')
+pylab.plot(orig,vlct[:,1],'.',label='$n=20$')
+pylab.plot(orig,vlct[:,2],'.',label='$n=200$')
+pylab.plot(orig,vlct[:,3],'.',label='$n=2000$')
+pylab.plot(orig,vlct[:,4],'.',label='$n=20000$')
 pylab.xlabel('$Original$')
 pylab.ylabel('$Obtained$')
 pylab.legend(loc=4, borderaxespad=0.5)
@@ -28,9 +28,9 @@ orig = dens[:,0]
 
 pylab.title('$Density$')
 pylab.plot(orig,orig,label='$real$')
-pylab.plot(orig,dens[:,1],label='$n=20$')
-pylab.plot(orig,dens[:,2],label='$n=200$')
-pylab.plot(orig,dens[:,3],label='$n=2000$')
+pylab.plot(orig,dens[:,1],'.',label='$n=20$')
+pylab.plot(orig,dens[:,2],'.',label='$n=200$')
+pylab.plot(orig,dens[:,3],'.',label='$n=2000$')
 pylab.xscale('log')
 pylab.yscale('log')
 pylab.xlabel('$Original$')
@@ -45,10 +45,10 @@ orig = mass[:,0]
 
 pylab.title('$Mass$')
 pylab.plot(orig,orig,label='$real$')
-pylab.plot(orig,mass[:,1],label='$n=20$')
-pylab.plot(orig,mass[:,2],label='$n=200$')
-pylab.plot(orig,mass[:,3],label='$n=2000$')
-pylab.plot(orig,mass[:,4],label='$n=20000$')
+pylab.plot(orig,mass[:,1],'.',label='$n=20$',)
[…]

### 2014-09-05 data/results/miniMD/compare.py
plots ready

@@ -72,28 +72,31 @@ for id in id_dens:
     c_mcmc_dens = np.append(c_mcmc_dens,c_mcmc[index])
     c_vel_dens = np.append(c_vel_dens,c_vel[index])
 
-pylab.scatter(c_vel,c_mcmc)
-pylab.plot(c_vel,c_vel,'-r')
+pylab.scatter(c_vel,c_mcmc,c='k',alpha=0.1)
 pylab.xscale('log')
 pylab.yscale('log')
+pylab.xlim(xmin=np.amin(c_vel))
+pylab.ylim(ymin=np.amin(c_mcmc))
 pylab.xlabel("$Velocity\ Method$")
 pylab.ylabel("$Mass\ Method$")
 pylab.savefig('velocity-mass.png',dpi=200)
 pylab.close()
 
-pylab.scatter(c_dens,c_mcmc_dens)
-pylab.plot(c_dens,c_dens,'-r')
+pylab.scatter(c_dens,c_mcmc_dens,c='k',alpha=0.1)
 pylab.xscale('log')
 pylab.yscale('log')
+pylab.xlim(xmin=np.amin(c_dens))
+pylab.ylim(ymin=np.amin(c_mcmc_dens))
 pylab.xlabel("$Density\ Method$")
 pylab.ylabel("$Mass\ Method$")
 pylab.savefig('density-mass.png',dpi=200)
 pylab.close()
 
-pylab.scatter(c_dens,c_vel_dens)
-pylab.plot(c_dens,c_dens,'-r')
+pylab.scatter(c_dens,c_vel_dens,c='k',alpha=0.1)
 pylab.xscale('log')
 pylab.yscale('log')
+pylab.xlim(xmin=np.amin(c_dens))
+pylab.ylim(ymin=np.amin(c_vel_dens))
 pylab.xlabel("$Density\ Method$")
 pylab.ylabel("$Velocity\ Method$")
 pylab.savefig('density-velocity.png',dpi=200)

### 2014-09-05 data/results/miniMD/compare.py
changed format to .pdf

@@ -79,7 +79,7 @@ pylab.xlim(xmin=np.amin(c_vel))
 pylab.ylim(ymin=np.amin(c_mcmc))
 pylab.xlabel("$Velocity\ Method$")
 pylab.ylabel("$Mass\ Method$")
-pylab.savefig('velocity-mass.png',dpi=200)
+pylab.savefig('velocity-mass.pdf',dpi=200)
 pylab.close()
 
 pylab.scatter(c_dens,c_mcmc_dens,c='k',alpha=0.1)
@@ -89,7 +89,7 @@ pylab.xlim(xmin=np.amin(c_dens))
 pylab.ylim(ymin=np.amin(c_mcmc_dens))
 pylab.xlabel("$Density\ Method$")
 pylab.ylabel("$Mass\ Method$")
-pylab.savefig('density-mass.png',dpi=200)
+pylab.savefig('density-mass.pdf',dpi=200)
 pylab.close()
 
 pylab.scatter(c_dens,c_vel_dens,c='k',alpha=0.1)
@@ -99,5 +99,5 @@ pylab.xlim(xmin=np.amin(c_dens))
 pylab.ylim(ymin=np.amin(c_vel_dens))
 pylab.xlabel("$Density\ Method$")
 pylab.ylabel("$Velocity\ Method$")
-pylab.savefig('density-velocity.png',dpi=200)
+pylab.savefig('density-velocity.pdf',dpi=200)
 pylab.close()

### 2014-09-05 paper/article.tex
added plots

@@
 \end{figure}
+
+We tested the three methods using the same data from the Mock Halos test. In order to see the accuracy of each method depending on the number of particles we define
+
+\begin{equation}
+\xi=\frac{1}{N}\sum\left|\frac{c_{org}-c_{obt}}{c_{org}}\right|
+\end{equation}
+
+Where $c_{org}$ and $c_{obt}$ are the original and obtained concentrations respectively and $N$ the number of haloes with a certain number of particles.
+Then we calculate $\xi$ for each number of particles (20, 200, 2000 and 20000).
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{error.pdf}
+\end{center}
+\caption{Relative error Against number of Particles
+    \label{fig:error}}
+\end{figure}
+
+In Figure \ref{fig:error} we plotted $\xi$ for the three methods.
+We consider that $\xi$ is a good estimate because it is standardized, giving equal weight to all errors regardless of the magnitude of the concentrations or the number of halos.
+On the other hand we have that $\xi$ decreases quite fast with the number of particles and is more precise in any case that the other methods.
+
 \subsection{Concentration as a function of halo mass}
@@
 The bold lines in Figure \ref{fig:concentrations} corresponds to the median and the thinner lines corresponds to the quartiles.
-As we can see the velocity method has a greater dispersion compared to the other two.
 \subsection{Implication for comparisons against observations}

### 2014-09-05 paper/article.tex
better explanation for the relative error

@@
 \begin{equation}
-\xi=\frac{1}{N}\sum\left|\frac{c_{org}-c_{obt}}{c_{org}}\right|
+\xi(n)=\frac{1}{\left|{\cal{H}}_n\right|}\sum_{{\cal{H}}_n}\left|\frac{c_{org}-c_{obt}}{c_{org}}\right|
 \end{equation}
 
-Where $c_{org}$ and $c_{obt}$ are the original and obtained concentrations respectively and $N$ the number of haloes with a certain number of particles.
+Where ${\cal{H}}_n$ corresponds to the set of haloes with $n$ particles, $c_{org}$ and $c_{obt}$ are the original and obtained concentrations respectively for each halo in ${\cal{H}}_n$ and $\left|{\cal{H}}_n\right|$ the number of haloes in ${\cal{H}}_n$.
 Then we calculate $\xi$ for each number of particles (20, 200, 2000 and 20000).

### 2014-09-08 paper/article.tex
corrected mistake in mock haloes
added correction

@@
 We generate $100$ mock halos with concentration values randomly
-placed in the range $1<c<10$. Each one of the halos is generated with
+placed in the range $1<c<20$. Each one of the halos is generated with
 four different total particle numbers: $20$, $200$, $2000$ and $20000$.
@@
 We consider that $\xi$ is a good estimate because it is standardized, giving equal weight to all errors regardless of the magnitude of the concentrations or the number of halos.
-On the other hand we have that $\xi$ decreases quite fast with the number of particles and is more precise in any case that the other methods.
+On the other hand we have that $\xi$ decreases quite fast with the number of particles for our method and is more precise in any case that the other methods.
 

### 2014-09-09 paper/article.tex
some edits

@@
 between the two power law behaviour in the $\rho\propto r^{-1}$ for
-$r<r_s$ and $\rho\propto r^{-2}$ for  $r>r_s$.
+$r<r_s$ and $\rho\propto r^{-3}$ for  $r>r_s$.
 
@@
 the average density of the Universe. The corresponding mass $M_{v}$,
-the virial mass, can be thus expressed as $M_{v} =
+the virial mass, can be written as $M_{v} =
 \frac{4\pi}{3}\bar{\rho}\Delta_h r_v^3$.
 
-The total mass enclosed within a radius $r$ can be computed to be:
+\subsection{Integrated Mass}
+From these definitions we can compute the total mass enclosed inside a
+radius $r$:
 \begin{equation}
@@
 
-We can now define the concentration of the halo as $c=r_v/r_s$, the
-dimensioless variable $x\equiv r/r_v$ and $m\equiv M(<r)/M_v$, which
-allows us to express the total enclosed mass within a dimensionless
-radius $x$ as:
-
+We can now express the same quantity in terms of dimensionless the
+variables $x\equiv r/r_v$ and $m\equiv M(<r)/M_v$,
+%
 \begin{equation}
@@
 \end{equation}
+%
+and the parameter $c$ is known as the concentration $c\equiv r_v/r_s$.
 
-meaning that the concentration is the only free parameter to
-determine the density profile of the halo. In Figure
-\ref{fig:profiles} we show the family of normalized integrated mass
-profiles for different values of the concentration in the range
+The most interesting feature of Eq. (\ref{eq:profile}) is that the
+concentration is the only free parameter to describe the shape of the
+halo densitry profile. In Figure \ref{fig:profiles} we show $m(<x)$ as
+a function of $x$ for different values of the concentration in the range
 $1\leq c \leq 20$.
@@
 \end{center}
-\caption{Mass profiles of several haloes with different concentrations
+\caption{Dimensionless mass profiles as a function of the
+  dimensionless radius for different concentration values.
     \label{fig:profiles}}
 \end{figure}
+
+\subsection{Circular velocity}
+
+It is also customary to express the mass of the halo inte terms of the
+circular velocity $V_{c}=sqrt{GM(<r)/r}$. From this we can
+define a new dimensionless circular velocity $v(<x)\equiv
+V_{c}(<r)/V_{c}(<r_v)$, using the result in Equation \ref{eq:profile}
+to have:
+
+\begin{equation}
+v(<x)=\sqrt{\frac{1}{A}\left[\frac{\ln\left(1+xc\right)}{x}-\frac{c}{xc+1}\right]},
+\end{equation}
 

### 2014-09-09 src/main.py
now with explanation

@@ -53,40 +53,47 @@ def run(directories,process_number):
         count = count + 1
         print '\rWorking with file '+str(count)+' of '+str(len(directories))+' in process '+str(process_number)
 
+    # Creates the "data" array with the information from the file in "path"
         path = os.path.expanduser('./'+str(sys.argv[1])+'/'+filename)
         data = np.loadtxt(open(path, 'r'), delimiter=",",skiprows=int(sys.argv[5]))
 
+    # Gets the cartesian coordinates for each particle in the halo and the number of particles
         x = data[:,int(sys.argv[2])]
         y = data[:,int(sys.argv[3])]
         z = data[:,int(sys.argv[4])]
-
         n_points = len(x)
-        
+
+    # Exports a file with the cartesian coordinates of each particle
         file_id = int(filename.split('_')[1])
         positions_name ='positions_'+str(file_id)+'.dat'
         potential_name ='potential_'+str(file_id)+'.dat'
         results_folder ='./results_'+now+'/'+str(file_id)
         open(positions_name, "w").write('\n'.join('%lf,%lf,%lf' % (x[i],y[i],z[i]) for i in range(n_points)))
 
+    # Runs the executable "potential.out" that will get the potential energy for each particle
         os.system('./potential.out '+positions_name+' '+potential_name)
 
+    # Finds the particle with the lowest potential and puts it as the new origin
         potential = np.loadtxt(open(potential_name, 'r'))
         maximum = np.argmax(potential)
-
         x_center,y_center,z_center = x[maximum],y[maximum],z[maximum]
-        
-        os.system('rm '+potential_name+' '+positions_name)
-    
+
+    # Gets the radial distance from the new origin to each particle and sorts it
         r_values = np.sort(np.sqrt((x-x_center)**2 + (y-y_center)**2 + (z-z_center)**2), kind='quicksort')
-        
+    
+    # Removes the files used by "potential.out"
+        os.system('rm '+potential_name+' '+positions_name)
+
+    # Gets the mass for each radius and removes the particle in the origin
         mass = mass_element*np.arange(1,n_points,1)
         radius = np.delete(r_values,0)
 
+    # Gets the average density in function of the radius
         avg_density = mass/((4.0/3.0)*np.pi*(radius**3))
         rho_back = mass_element*(2048.0/1000.0)**3
 
[…]

### 2014-09-09 src/configure.py
added configuration generator

@@ -1,0 +1,16 @@
+export = open('config.div','w')
+conf_file = open('config.div','r')
+data = conf_file.readlines()
+conf_file.close()
+
+directory = '../../TrainingHalos/particle_ID/MDmini'
+x,y,z =  '2','3','4'
+skip_lines = '16'
+processes = '4'
+plot = 'False'
+test = 'False'
+
+line =  directory+' '+x+' '+y+' '+z+' '+skip_lines+' '+processes+' '+plot+' '+test+'\n'
+
+export.write(line)
+export.close()

### 2014-09-09 src/configure.py
added new parameters

@@ -3,14 +3,15 @@ conf_file = open('config.div','r')
 data = conf_file.readlines()
 conf_file.close()
 
-directory = '../../TrainingHalos/particle_ID/MDmini'
+directory = '../../TrainingHalos/data/particle_ID/MDmini'
 x,y,z =  '2','3','4'
 skip_lines = '16'
 processes = '4'
+steps = '50000'
 plot = 'False'
 test = 'False'
 
-line =  directory+' '+x+' '+y+' '+z+' '+skip_lines+' '+processes+' '+plot+' '+test+'\n'
+line =  directory+' '+x+' '+y+' '+z+' '+skip_lines+' '+processes+' '+steps+' '+plot+' '+test+'\n'
 
 export.write(line)
 export.close()

### 2014-09-09 src/main.py
easy run

@@ -2,37 +2,22 @@ import numpy as np, pylab, math, sys, timeit, os, random, datetime, nfw, mcmc,fi
 from scipy.optimize import fsolve
 
 # Gets the concentration and virial radius for several haloes
-# It must be executed with the following command line:
-#
-#      python main.py directory #x #y #x skip processes noplot*
-#
-# Where:
-#      directory: is the path of the directory with the files with the positions of the haloes
-#      #x, #y, #z: are the column position of each coordinate in the files (for Multidark is 2 3 4)
-#      skip: number of rows to skip (For Multidark is 16) 
-#      processes: number of child processes
-#      noplot: is an optional parameter, if it is added the code will not make any graphics
-#
-# Have fun! 
-#
-# Done by: Christian Poveda (cn.poveda542@uniandes.edu.co)
-#
-# Thanks to Diva Martinez (dm.martinez831@uniandes.edu.co) for the multiprocessing idea
 
-processes = int(sys.argv[6])
+config = open('config.div','r').readline().split()
+print config
+processes = int(config[5])
 now = datetime.datetime.now().strftime("%Y-%m-%d-%H:%M:%S")
 mass_element = 1.0   
 plt = 1
-total_list = os.listdir('./'+str(sys.argv[1]))
+total_list = os.listdir('./'+str(config[0]))
 len_list = len(total_list)
 lists = [total_list[i*len_list // processes: (i+1)*len_list //processes] for i in range(processes)]
 jobs = []
 
-try:
-    if (sys.argv[7]=='noplot'):
-        print 'No Plotting mode enabled'
-        plt = 0
-except:
+if (config[7]=='False'):
+    print 'No Plotting mode enabled'
+    plt = 0
+else:
     plt = 1
  
 os.system('mkdir results_'+now)
@@ -54,13 +39,13 @@ def run(directories,process_number):
         print '\rWorking with file '+str(count)+' of '+str(len(directories))+' in process '+str(process_number)
 
     # Creates the "data" array with the information from the file in "path"
-        path = os.path.expanduser('./'+str(sys.argv[1])+'/'+filename)
-        data = np.loadtxt(open(path, 'r'), delimiter=",",skiprows=int(sys.argv[5]))
+        path = os.path.expanduser('./'+str(config[0])+'/'+filename)
+        data = np.loadtxt(open(path, 'r'), delimiter=",",skiprows=int(config[4]))
 
     # Gets the cartesian coordinates for each particle in the halo and the number of particles
[…]

### 2014-09-10 src/configure.py
new interface

@@ -1,17 +1,69 @@
-export = open('config.div','w')
-conf_file = open('config.div','r')
-data = conf_file.readlines()
-conf_file.close()
+import Tkinter as tk, tkFileDialog, tkMessageBox
+    
+root = tk.Tk()
 
-directory = '../../TrainingHalos/data/particle_ID/MDmini'
-x,y,z =  '2','3','4'
-skip_lines = '16'
-processes = '4'
-steps = '50000'
-plot = 'False'
-test = 'False'
+directory = tk.StringVar()
+x = tk.StringVar()
+y = tk.StringVar()
+z = tk.StringVar()
+skip = tk.StringVar()
+proc = tk.StringVar()
+step = tk.StringVar()
+plot = tk.BooleanVar()
+test = tk.BooleanVar()
 
-line =  directory+' '+x+' '+y+' '+z+' '+skip_lines+' '+processes+' '+steps+' '+plot+' '+test+'\n'
+tk.Entry(root,textvariable=directory).grid(row=0,column=1)
+tk.Entry(root,textvariable=x).grid(row=1,column=1)
+tk.Entry(root,textvariable=y).grid(row=2,column=1)
+tk.Entry(root,textvariable=z).grid(row=3,column=1)
+tk.Entry(root,textvariable=skip).grid(row=4,column=1)
+tk.Entry(root,textvariable=proc).grid(row=5,column=1)
+tk.Entry(root,textvariable=step).grid(row=6,column=1)
 
-export.write(line)
-export.close()
+try:
+    params = open('config.div','r').readline().split()    
+    directory.set(params[0])
+    x.set(params[1])
+    y.set(params[2])
+    z.set(params[3])
+    skip.set(params[4])
+    proc.set(params[5])
+    step.set(params[6])
+    plot.set((params[7] == 'True'))
+    test.set((params[8] == 'True'))
+    print 'El archivin existe :D'
+except:
+    print 'El archivin no existe D:'
+
+tk.Label(root, text='Path').grid(row=0)
+tk.Label(root, text='X Column').grid(row=1)
+tk.Label(root, text='Y Column').grid(row=2)
+tk.Label(root, text='Z Column').grid(row=3)
+tk.Label(root, text='Lines to Skip').grid(row=4)
+tk.Label(root, text='Proceses').grid(row=5)
+tk.Label(root, text='MCMC Steps').grid(row=6)
+tk.Label(root, text='Plotting Mode').grid(row=7)
[…]

### 2014-09-10 src/main.py
corrected path

@@ -9,7 +9,7 @@ processes = int(config[5])
 now = datetime.datetime.now().strftime("%Y-%m-%d-%H:%M:%S")
 mass_element = 1.0   
 plt = 1
-total_list = os.listdir('./'+str(config[0]))
+total_list = os.listdir(str(config[0]))
 len_list = len(total_list)
 lists = [total_list[i*len_list // processes: (i+1)*len_list //processes] for i in range(processes)]
 jobs = []

### 2014-09-10 src/configure.py
changed format

@@ -21,7 +21,7 @@ tk.Entry(root,textvariable=proc).grid(row=5,column=1)
 tk.Entry(root,textvariable=step).grid(row=6,column=1)
 
 try:
-    params = open('config.div','r').readline().split()    
+    params = open('config.div','r').readline().split(',')    
     directory.set(params[0])
     x.set(params[1])
     y.set(params[2])
@@ -50,7 +50,7 @@ def change_path():
     
 def save():
     export = open('config.div','w')
-    line =  directory.get()+' '+x.get()+' '+y.get()+' '+z.get()+' '+skip.get()+' '+proc.get()+' '+step.get()+' '+('%r' % (plot.get()))+' '+('%r' % (test.get()))+'\n'
+    line =  directory.get()+','+x.get()+','+y.get()+','+z.get()+','+skip.get()+','+proc.get()+','+step.get()+','+('%r' % (plot.get()))+','+('%r' % (test.get()))+'\n'
     export.write(line)
     export.close()
     tkMessageBox.showinfo('Save', 'Configuration file was saved successfully')

### 2014-09-10 src/configure.py
small corrections

@@ -50,7 +50,7 @@ def change_path():
     
 def save():
     export = open('config.div','w')
-    line =  directory.get()+','+x.get()+','+y.get()+','+z.get()+','+skip.get()+','+proc.get()+','+step.get()+','+('%r' % (plot.get()))+','+('%r' % (test.get()))+'\n'
+    line =  directory.get()+','+x.get()+','+y.get()+','+z.get()+','+skip.get()+','+proc.get()+','+step.get()+','+('%r' % (plot.get()))+','+('%r' % (test.get()))
     export.write(line)
     export.close()
     tkMessageBox.showinfo('Save', 'Configuration file was saved successfully')

### 2014-09-12 paper/article.tex
corrected mistake
new plots

@@
 It is also customary to express the mass of the halo inte terms of the
-circular velocity $V_{c}=sqrt{GM(<r)/r}$. From this we can
+circular velocity $V_{c}=\sqrt{GM(<r)/r}$. From this we can
 define a new dimensionless circular velocity $v(<x)\equiv
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{density-mass.pdf}
+  \includegraphics[width=0.48\textwidth]{mass-density.pdf}
 \end{center}
-\caption{Concentration obtained from the mass method against the one obtained in the density method
+\caption{Concentration obtained from the density method against the one obtained in the mass method
     \label{fig:density-mass}}

### 2014-09-12 data/results/MDmini/compare.py
updated tool

@@ -55,13 +55,15 @@ pylab.fill_between(10**(bins_vel),quar1_vel,quar2_vel,color='b',alpha=0.4)
 
 pylab.legend(loc=1, borderaxespad=0.5)
 pylab.xscale('log')
-pylab.xlim([1E3,1E5])
+pylab.xlim([1E2,1E5])
+pylab.ylim([0,10])
 pylab.xlabel('$Number\ of\ Particles$')
 pylab.ylabel('$Concentration$')
 pylab.savefig('concentration.pdf',dpi=300)
 pylab.close()
 
 pylab.scatter(c_vel,c_mcmc,c='k',alpha=0.1)
+pylab.plot(c_vel,c_vel,'-r',alpha=0.4)
 pylab.xscale('log')
 pylab.yscale('log')
 pylab.xlim(xmin=np.amin(c_vel),xmax=np.amax(c_vel))
@@ -72,6 +74,7 @@ pylab.savefig('velocity-mass.pdf',dpi=200)
 pylab.close()
 
 pylab.scatter(c_mcmc,c_dens,c='k',alpha=0.1)
+pylab.plot(c_mcmc,c_mcmc,'-r',alpha=0.4)
 pylab.xscale('log')
 pylab.yscale('log')
 pylab.xlim(xmin=np.amin(c_dens),xmax=np.amax(c_mcmc))
@@ -82,10 +85,11 @@ pylab.savefig('mass-density.pdf',dpi=200)
 pylab.close()
 
 pylab.scatter(c_dens,c_vel,c='k',alpha=0.1)
+pylab.plot(c_vel,c_vel,'-r',alpha=0.4)
 pylab.xscale('log')
 pylab.yscale('log')
-pylab.xlim(xmin=np.amin(c_dens),xmax=np.amax(c_vel))
-pylab.ylim(ymin=np.amin(c_dens),ymax=np.amax(c_vel))
+pylab.xlim(xmin=np.amin(c_vel),xmax=np.amax(c_vel))
+pylab.ylim(ymin=np.amin(c_vel),ymax=np.amax(c_vel))
 pylab.xlabel("$Density\ Method$")
 pylab.ylabel("$Velocity\ Method$")
 pylab.savefig('density-velocity.pdf',dpi=200)

### 2014-09-12 data/results/MDmini/compare.py
changed fontsize in plots

@@ -57,8 +57,8 @@ pylab.legend(loc=1, borderaxespad=0.5)
 pylab.xscale('log')
 pylab.xlim([1E2,1E5])
 pylab.ylim([0,10])
-pylab.xlabel('$Number\ of\ Particles$')
-pylab.ylabel('$Concentration$')
+pylab.xlabel('$Number\ of\ Particles$',fontsize=20)
+pylab.ylabel('$Concentration$',fontsize=20)
 pylab.savefig('concentration.pdf',dpi=300)
 pylab.close()
 
@@ -68,8 +68,8 @@ pylab.xscale('log')
 pylab.yscale('log')
 pylab.xlim(xmin=np.amin(c_vel),xmax=np.amax(c_vel))
 pylab.ylim(ymin=np.amin(c_vel),ymax=np.amax(c_vel))
-pylab.xlabel("$Velocity\ Method$")
-pylab.ylabel("$Mass\ Method$")
+pylab.xlabel("$Velocity\ Method$",fontsize=20)
+pylab.ylabel("$Mass\ Method$",fontsize=20)
 pylab.savefig('velocity-mass.pdf',dpi=200)
 pylab.close()
 
@@ -79,8 +79,8 @@ pylab.xscale('log')
 pylab.yscale('log')
 pylab.xlim(xmin=np.amin(c_dens),xmax=np.amax(c_mcmc))
 pylab.ylim(ymin=np.amin(c_dens),ymax=np.amax(c_mcmc))
-pylab.xlabel("$Mass\ Method$")
-pylab.ylabel("$Density\ Method$")
+pylab.xlabel("$Mass\ Method$",fontsize=20)
+pylab.ylabel("$Density\ Method$",fontsize=20)
 pylab.savefig('mass-density.pdf',dpi=200)
 pylab.close()
 
@@ -90,7 +90,7 @@ pylab.xscale('log')
 pylab.yscale('log')
 pylab.xlim(xmin=np.amin(c_vel),xmax=np.amax(c_vel))
 pylab.ylim(ymin=np.amin(c_vel),ymax=np.amax(c_vel))
-pylab.xlabel("$Density\ Method$")
-pylab.ylabel("$Velocity\ Method$")
+pylab.xlabel("$Density\ Method$",fontsize=20)
+pylab.ylabel("$Velocity\ Method$",fontsize=20)
 pylab.savefig('density-velocity.pdf',dpi=200)
 pylab.close()

### 2014-09-13 data/results/MDmini/compare.py
changed plots axis

@@ -57,8 +57,8 @@ pylab.legend(loc=1, borderaxespad=0.5)
 pylab.xscale('log')
 pylab.xlim([1E2,1E5])
 pylab.ylim([0,10])
-pylab.xlabel('$Number\ of\ Particles$',fontsize=20)
-pylab.ylabel('$Concentration$',fontsize=20)
+pylab.xlabel('$\mathrm{Number\ of\ Particles}$',fontsize=20)
+pylab.ylabel('$\mathrm{Concentration}$',fontsize=20)
 pylab.savefig('concentration.pdf',dpi=300)
 pylab.close()
 
@@ -68,8 +68,8 @@ pylab.xscale('log')
 pylab.yscale('log')
 pylab.xlim(xmin=np.amin(c_vel),xmax=np.amax(c_vel))
 pylab.ylim(ymin=np.amin(c_vel),ymax=np.amax(c_vel))
-pylab.xlabel("$Velocity\ Method$",fontsize=20)
-pylab.ylabel("$Mass\ Method$",fontsize=20)
+pylab.xlabel("$\mathrm{Velocity\ Method}$",fontsize=20)
+pylab.ylabel("$\mathrm{Mass\ Method}$",fontsize=20)
 pylab.savefig('velocity-mass.pdf',dpi=200)
 pylab.close()
 
@@ -79,8 +79,8 @@ pylab.xscale('log')
 pylab.yscale('log')
 pylab.xlim(xmin=np.amin(c_dens),xmax=np.amax(c_mcmc))
 pylab.ylim(ymin=np.amin(c_dens),ymax=np.amax(c_mcmc))
-pylab.xlabel("$Mass\ Method$",fontsize=20)
-pylab.ylabel("$Density\ Method$",fontsize=20)
+pylab.xlabel("$\mathrm{Mass\ Method}$",fontsize=20)
+pylab.ylabel("$\mathrm{Density\ Method}$",fontsize=20)
 pylab.savefig('mass-density.pdf',dpi=200)
 pylab.close()
 
@@ -90,7 +90,7 @@ pylab.xscale('log')
 pylab.yscale('log')
 pylab.xlim(xmin=np.amin(c_vel),xmax=np.amax(c_vel))
 pylab.ylim(ymin=np.amin(c_vel),ymax=np.amax(c_vel))
-pylab.xlabel("$Density\ Method$",fontsize=20)
-pylab.ylabel("$Velocity\ Method$",fontsize=20)
[…]

### 2014-09-13 data/test/mock_100/error.py

@@ -31,8 +31,8 @@ pylab.plot(orig,orig,'--k',label='$real$')
 #pylab.plot(orig,vlct[:,3],'.g',label='$n=2000$')
 #pylab.plot(orig,vlct[:,4],'.c',label='$n=20000$')
 pylab.plot(orig,best_fit(orig,vlct[:,1:5]),'-r',label='$best\ fit$')
-pylab.xlabel('$Original$')
-pylab.ylabel('$Obtained$')
+pylab.xlabel('$\mathrm{Original}$')
+pylab.ylabel('$\mathrm{Obtained}$')
 pylab.legend(loc=4, borderaxespad=0.5)
 pylab.savefig('vlct.png',dpi=300)
 pylab.close()
@@ -49,8 +49,8 @@ pylab.plot(orig,orig,'--k',label='$real$')
 #pylab.plot(orig,mass[:,3],'.',label='$n=2000$',)
 #pylab.plot(orig,mass[:,4],'.',label='$n=20000$')
 pylab.plot(orig,best_fit(orig,mass[:,1:5]),'-r',label='$best\ fit$')
-pylab.xlabel('$Original$')
-pylab.ylabel('$Obtained$')
+pylab.xlabel('$\mathrm{Original}$')
+pylab.ylabel('$\mathrm{Obtained}$')
 pylab.legend(loc=4, borderaxespad=0.5)
 pylab.savefig('mass.png',dpi=300)
 pylab.close()
@@ -65,8 +65,8 @@ pylab.plot(orig,orig,label='$real$')
 #pylab.plot(orig,dens[:,2],'.',label='$n=200$')
 #pylab.plot(orig,dens[:,3],'.',label='$n=2000$')
 pylab.plot(orig,best_fit(orig,dens[:,1:5]),'-r',label='$best\ fit$')
-pylab.xlabel('$Original$')
-pylab.ylabel('$Obtained$')
+pylab.xlabel('$\mathrm{Original}$')
+pylab.ylabel('$\mathrm{Obtained}$')
 pylab.legend(loc=4, borderaxespad=0.5)
 pylab.savefig('dens.png',dpi=300)
 pylab.close()
@@ -82,8 +82,8 @@ pylab.plot([20,200,2000,20000],chi_dens,'^k',label='$Density$',ms=7)
 pylab.xscale('log')
 pylab.yscale('log')
 pylab.legend(loc=3)
[…]

### 2014-09-13 paper/article.tex
added new line

@@
 Where $V_{max}$ is the maximum velocity, to find the value of the concentration.
+We tested the three methods using the same data from the Mock Halos test.
+In order to see the accuracy of each method depending on the number of particles we define
+
+\begin{equation}
+\xi(n)=\frac{1}{\left|{\cal{H}}_n\right|}\sum_{{\cal{H}}_n}\left|\frac{c_{org}-c_{obt}}{c_{org}}\right|
+\end{equation}
+
+Where ${\cal{H}}_n$ corresponds to the set of haloes with $n$ particles, $c_{org}$ and $c_{obt}$ are the original and obtained concentrations respectively for each halo in ${\cal{H}}_n$ and $\left|{\cal{H}}_n\right|$ the number of haloes in ${\cal{H}}_n$.
+Then we calculate $\xi$ for each number of particles (20, 200, 2000 and 20000).
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{error.pdf}
+\end{center}
+\caption{Relative error Against number of Particles
+    \label{fig:error}}
+\end{figure}
+
+In Figure \ref{fig:error} we plotted $\xi$ for the three methods.
+We consider that $\xi$ is a good estimate because it is standardized, giving equal weight to all errors regardless of the magnitude of the concentrations or the number of halos.
+On the other hand we have that $\xi$ decreases quite fast with the number of particles for our method and is more precise in any case that the other methods.
+
+We also used these three methods to obtain the concentration for each halo in miniMDR1 and compared the results.
+As can be seen in the Figures \ref{fig:density-mass}, \ref{fig:density-velocity} and \ref{fig:velocity-mass} the three methods show mutually consistent results.
+However it can be inferred that the concentration values ​​obtained by the method of circular velocity are higher than those obtained by our method, and also the values ​​obtained by the density method are generally below the results of our method.
 
@@
 
-We tested the three methods using the same data from the Mock Halos test. In order to see the accuracy of each method depending on the number of particles we define
-
-\begin{equation}
-\xi(n)=\frac{1}{\left|{\cal{H}}_n\right|}\sum_{{\cal{H}}_n}\left|\frac{c_{org}-c_{obt}}{c_{org}}\right|
-\end{equation}
-
-Where ${\cal{H}}_n$ corresponds to the set of haloes with $n$ particles, $c_{org}$ and $c_{obt}$ are the original and obtained concentrations respectively for each halo in ${\cal{H}}_n$ and $\left|{\cal{H}}_n\right|$ the number of haloes in ${\cal{H}}_n$.
-Then we calculate $\xi$ for each number of particles (20, 200, 2000 and 20000).
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{error.pdf}
-\end{center}
-\caption{Relative error Against number of Particles
-    \label{fig:error}}
-\end{figure}
-
-In Figure \ref{fig:error} we plotted $\xi$ for the three methods.
-We consider that $\xi$ is a good estimate because it is standardized, giving equal weight to all errors regardless of the magnitude of the concentrations or the number of halos.
-On the other hand we have that $\xi$ decreases quite fast with the number of particles for our method and is more precise in any case that the other methods.
-
 \subsection{Concentration as a function of halo mass}
@@
 The bold lines in Figure \ref{fig:concentrations} corresponds to the median and the thinner lines corresponds to the quartiles.
+Showing that our method has values ​​ranging from those obtained from the other two methods.
 \subsection{Implication for comparisons against observations}

### 2014-09-13 data/results/MDmini/compare.py
new plots

@@ -52,7 +52,6 @@ pylab.fill_between(10**(bins_mcmc),quar1_mcmc,quar2_mcmc,color='r',alpha=0.4)
 pylab.plot(10**(bins_vel),median_vel,'-b',lw=2,label='Velocity')
 pylab.fill_between(10**(bins_vel),quar1_vel,quar2_vel,color='b',alpha=0.4)
 
-
 pylab.legend(loc=1, borderaxespad=0.5)
 pylab.xscale('log')
 pylab.xlim([1E2,1E5])
@@ -62,35 +61,41 @@ pylab.ylabel('$\mathrm{Concentration}$',fontsize=20)
 pylab.savefig('concentration.pdf',dpi=300)
 pylab.close()
 
-pylab.scatter(c_vel,c_mcmc,c='k',alpha=0.1)
-pylab.plot(c_vel,c_vel,'-r',alpha=0.4)
-pylab.xscale('log')
-pylab.yscale('log')
-pylab.xlim(xmin=np.amin(c_vel),xmax=np.amax(c_vel))
-pylab.ylim(ymin=np.amin(c_vel),ymax=np.amax(c_vel))
-pylab.xlabel("$\mathrm{Velocity\ Method}$",fontsize=20)
-pylab.ylabel("$\mathrm{Mass\ Method}$",fontsize=20)
-pylab.savefig('velocity-mass.pdf',dpi=200)
-pylab.close()
 
-pylab.scatter(c_mcmc,c_dens,c='k',alpha=0.1)
-pylab.plot(c_mcmc,c_mcmc,'-r',alpha=0.4)
-pylab.xscale('log')
-pylab.yscale('log')
-pylab.xlim(xmin=np.amin(c_dens),xmax=np.amax(c_mcmc))
-pylab.ylim(ymin=np.amin(c_dens),ymax=np.amax(c_mcmc))
-pylab.xlabel("$\mathrm{Mass\ Method}$",fontsize=20)
-pylab.ylabel("$\mathrm{Density\ Method}$",fontsize=20)
-pylab.savefig('mass-density.pdf',dpi=200)
-pylab.close()
+fig, (ax1,ax2,ax3) = pylab.subplots(1,3)
 
-pylab.scatter(c_dens,c_vel,c='k',alpha=0.1)
-pylab.plot(c_vel,c_vel,'-r',alpha=0.4)
-pylab.xscale('log')
-pylab.yscale('log')
[…]

### 2014-09-13 paper/article.tex
added new plot

@@
 \documentclass[useAMS,usenatbib]{mn2e}
+\usepackage{float}
 \usepackage{amsmath}
@@
 
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.99\textwidth]{mass-density-velocity.pdf}
+\end{center}
+\caption{Comparison between the obtained concentrations by the three methods
+    \label{fig:mdv}}
+\end{figure*}
+
 We also used these three methods to obtain the concentration for each halo in miniMDR1 and compared the results.
-As can be seen in the Figures \ref{fig:density-mass}, \ref{fig:density-velocity} and \ref{fig:velocity-mass} the three methods show mutually consistent results.
+As can be seen in Figure \ref{fig:mdv} the three methods show mutually consistent results.
 However it can be inferred that the concentration values ​​obtained by the method of circular velocity are higher than those obtained by our method, and also the values ​​obtained by the density method are generally below the results of our method.
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{mass-density.pdf}
-\end{center}
-\caption{Concentration obtained from the density method against the one obtained in the mass method
-    \label{fig:density-mass}}
-\end{figure}
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{density-velocity.pdf}
-\end{center}
-\caption{Concentration obtained from the velocity method against the one obtained in the density method
-    \label{fig:density-velocity}}
-\end{figure}
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{velocity-mass.pdf}
-\end{center}
-\caption{Concentration obtained from the mass method against the one obtained in the velocity method
-    \label{fig:velocity-mass}}
-\end{figure}
 
@@
 Aditionally we compared those three methods plotting the concentration as a function of the number of particles of each halo 
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{concentration.pdf}
-\end{center}
-\caption{Concentration against number of particles
-    \label{fig:concentrations}}
-\end{figure}
-
+%
+%\begin{figure}[h!]
+%\begin{center}
+%  \includegraphics[width=0.48\textwidth]{concentration.pdf}
+%\end{center}
+%\caption{Concentration against number of particles
+%    \label{fig:concentrations}}
+%\end{figure}
+%
 The bold lines in Figure \ref{fig:concentrations} corresponds to the median and the thinner lines corresponds to the quartiles.

### 2014-09-13 data/results/MDmini/compare.py
changed fontsize

@@ -91,11 +91,11 @@ ax3.set_ylabel("$\mathrm{Velocity\ Method}$",fontsize=15)
 ax3.set_xscale('log')
 ax3.set_yscale('log')
 
-fig.subplots_adjust(wspace=.4)
+fig.subplots_adjust(wspace=.3)
 ax1.set_aspect('equal')
 ax2.set_aspect('equal')
 ax3.set_aspect('equal')
-fig.set_size_inches(10,4)
+fig.set_size_inches(15,6)
 pylab.savefig('mass-density-velocity.pdf',dpi=200,bbox_inches='tight')
 pylab.savefig('mass-density-velocity.png',dpi=200,bbox_inches='tight')
 pylab.close()

### 2014-09-19 paper/article.tex
changed fontsize
added new info

@@
 On the other hand we have that $\xi$ decreases quite fast with the number of particles for our method and is more precise in any case that the other methods.
+As mentioned in FIXME "for a large fraction of halos, and for the most massive in particular, the NFW functional does not Represent a good fit to the density profile." This fact could explain why $\xi$ increases with the number of particles for the density method.
 
@@
 Aditionally we compared those three methods plotting the concentration as a function of the number of particles of each halo
-%
-%\begin{figure}[h!]
-%\begin{center}
-%  \includegraphics[width=0.48\textwidth]{concentration.pdf}
-%\end{center}
-%\caption{Concentration against number of particles
-%    \label{fig:concentrations}}
-%\end{figure}
-%
+
+\begin{figure}[h!]
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{concentration.pdf}
+\end{center}
+\caption{Concentration against number of particles
+    \label{fig:concentrations}}
+\end{figure}
+
 The bold lines in Figure \ref{fig:concentrations} corresponds to the median and the thinner lines corresponds to the quartiles.
-Showing that our method has values ​​ranging from those obtained from the other two methods.
+Showing that our method has values ​​ranging from those obtained from the other two methods.Also we can see that the concentration obtained by the velocity method is higher than that obtained by the density method, this fact is consistent with FIXME.
 \subsection{Implication for comparisons against observations}

### 2014-09-22 paper/article.tex
changed quote to italics

@@
 On the other hand we have that $\xi$ decreases quite fast with the number of particles for our method and is more precise in any case that the other methods.
-As mentioned in FIXME "for a large fraction of halos, and for the most massive in particular, the NFW functional does not Represent a good fit to the density profile." This fact could explain why $\xi$ increases with the number of particles for the density method.
+As mentioned in FIXME \textit{``for a large fraction of halos, and for the most massive in particular, the NFW functional does not Represent a good fit to the density profile."} This fact could explain why $\xi$ increases with the number of particles for the density method.
 

### 2014-09-23 paper/article.tex
new lines

@@
 
+Running another test with halos whose concentrations vary as a normal distribution of variance ${\sigma}^2$ we found that the concentrations obtained by the method of circular velocity are a 35\% greater than the ones obtained by the density method.
+However the concentrations obtained by the velocity method are barey higher (around 2\% or 3\%) than the ones obtained by our method.
+We did not find any significant variation in the concentration values obtained by any method by changing ${\sigma}^2$ in contrast with FIXME.
+
 \subsection{Concentration as a function of halo mass}

### 2014-09-23 data/results/MDmini/compare.py
massive changes

@@ -64,12 +64,12 @@ pylab.close()
 
 fig, (ax1,ax2,ax3) = pylab.subplots(1,3)
 
-ax1.scatter(c_vel,c_mcmc,c='k',alpha=0.1)
-ax1.plot(c_vel,c_vel,'-r',alpha=0.4,lw=2)
-ax1.set_xlim(xmin=np.amin(c_vel),xmax=np.amax(c_vel))
-ax1.set_ylim(ymin=np.amin(c_vel),ymax=np.amax(c_vel))
-ax1.set_xlabel("$\mathrm{Velocity\ Method}$",fontsize=15)
-ax1.set_ylabel("$\mathrm{Mass\ Method}$",fontsize=15)
+ax1.scatter(c_mcmc,c_vel,c='k',alpha=0.1)
+ax1.plot(c_mcmc,c_mcmc,'-r',alpha=0.4,lw=2)
+ax1.set_xlim(xmin=np.amin(c_vel),xmax=np.amax(c_mcmc))
+ax1.set_ylim(ymin=np.amin(c_vel),ymax=np.amax(c_mcmc))
+ax1.set_xlabel("$\mathrm{Mass\ Method}$",fontsize=15)
+ax1.set_ylabel("$\mathrm{Velocity\ Method}$",fontsize=15)
 ax1.set_xscale('log')
 ax1.set_yscale('log')
 

### 2014-09-23 data/results/MDmini/compare.py
Massive changes part II

@@ -56,7 +56,7 @@ pylab.legend(loc=1, borderaxespad=0.5)
 pylab.xscale('log')
 pylab.xlim([1E2,1E5])
 pylab.ylim([0,10])
-pylab.xlabel('$\mathrm{Number\ of\ Particles}$',fontsize=20)
+pylab.xlabel('$\mathrm{Number\ of\ particles}$',fontsize=20)
 pylab.ylabel('$\mathrm{Concentration}$',fontsize=20)
 pylab.savefig('concentration.pdf',dpi=300)
 pylab.close()

### 2014-09-23 data/test/mock_100/error.py

@@ -82,7 +82,7 @@ pylab.plot([20,200,2000,20000],chi_dens,'^k',label='$Density$',ms=7)
 pylab.xscale('log')
 pylab.yscale('log')
 pylab.legend(loc=3)
-pylab.xlabel('$\mathrm{Number\ of\ Points}$',fontsize=20)
+pylab.xlabel('$\mathrm{Number\ of\ particles}$',fontsize=20)
 pylab.ylabel('$\mathrm{\\xi}$',fontsize=20)
 pylab.savefig('error.png',dpi=200)
 pylab.savefig('error.pdf',dpi=200)

### 2014-09-30 paper/article.tex
massive changes
Massive changes part II
anadiendo texto

@@
 \label{sec:introduction}
+In the context of the concordance cosmology, the matter contents of
+the Universe are dominated by an unknown dark matter which behaves as
+a collisionless fluid only perturbed by gravity.
+
+Numerical experiments are able to follow the non-linear evolution of
+dark matter down to galactic scales. On these scales a common
+approximation considers the matter distribution as spherical with a
+radial depedence. The function describing this distribution is known
+as a radial density profile.
+
+The consensus is that density profiles are almost universal;
+almost independet of cosmological parameters and similar for different
+objects after some simple physical re-scalig is applied.
+
+The detailed halo structure influences the hosted galaxies.
+
+The concentration parameter is imporant in galaxy formation studies.
+
+Different studies vary about the result of the concentration-mass
+relationship.
+
+We propose a new way to obtain the concentration for halos in N-body
+simulations.
+
+We use the integrated mass profile because it
+allows us to use the data directly with the simulation without binning
+the particle positions and estimating a density.
+
+As an application we study the mass concentration relationship.
 
@@
 The most interesting feature of Eq. (\ref{eq:profile}) is that the
-concentration is the only free parameter to describe the shape of the
-halo densitry profile. In Figure \ref{fig:profiles} we show $m(<x)$ as
+concentration is the only free parameter to describe the density
+profile. In Figure \ref{fig:profiles} we show $m(<x)$ as 
 a function of $x$ for different values of the concentration in the range
@@
 
-\section{A Bayesian Approach to Halo Fitting}
+In Figure XXX we show the circular velocity profile for the same
+concentrations as in Figure \ref{fig:profiles}.
+
+\section{A new Approach to Halo Fitting}
 \label{sec:method}
 
-We proceed to find the value of the concentration parameter that
-best describes the simulation data, following the model in
-Eq. (\ref{eq:profile}). We use the integrated mass profile because it
-allows us to use the data directly with the simulation without binning
-the particle positions and estimating a density.
+We estimate the concentration parameter by fitting the
+integrated mass profile described in Equation
+(\ref{eq:profile}). First we define the center of the halo to be  at
+the position of the particle with the lowest gravitational
+potential.
 
@@
 the position of the $i$-th particle and $m_p$ is the mass of the
-computational particle.  We define the center of the halo to be  at
-the position of the particle with the lowest gravitational
-potential. In the process of building the mass profile we discard the
+computational particle.  In this process we discard the
 particle at the center.
@@
 We stop the construction of the integrated mass profile once we arrive
-at an average density of $\Delta_h\bar{\rho}$. This radius marks the
+at an average density of $\Delta_h\bar{\rho}$, with $\Delta_h=740$,
+roughly corresponding to 200 times the critical density. This radius marks the
 virial radius and the virial mass. We divide the total mass enclosed
-mass $M_i$ and the radii $r_i$ by these values to obtaine the
+mass $M_i$ and the radii $r_i$ by these values to obtain the
 dimensionless variables $x_i$ and $m_i$.
 
-Using these positions and masses we define the following $\chi^2$ function
+Using these new variables we define the following $\chi^2$ function
 
@@
 where $m(<x_i;c)$ corresponds to the values in Eq.(\ref{eq:profile}) at
-$x=x_i$ and a given value of the concentration parameter $c$.
+$x=x_i$ for a given value of the concentration parameter $c$.
 
-Finally we use a Metropolis-Hastings algorithm to sample the likelihood
-function distribution defined by ${\cal L}(c)=\exp(-\chi^2(c)/2)$ to
+We sample the likelihood function distribution defined by ${\cal
+  L}(c)=\exp(-\chi^2(c)/2)$ with a Metropolos-Hastings algorithms to
 find the optimum value of $c$ and its  associated uncertainty
@@
 
-\section{Numerical Experiments}
+{\bf Cuantos pasos usa la cadena? De cuanto es el sigma en
+los saltos de c en lca cadena?
+
+Falta alguna figura que muestre resultados de la -log likelihood para
+algunos casos representativos.
+}
+
+\section{Halo Samples}
+
+We apply our method to two different halo samples. The first one is a
+mock sample to test the algorithm and asses the impact of the number
+of computational particles on the concentration values. The second
+sample comes from a publicly available N-body cosmological
+simulation. These results for these sample can be then compared
+against other methods to find the concentration and feed the
+discussion about the implications of our method.
 
@@
 
-We generate $100$ mock halos with concentration values randomly
-placed in the range $1<c<20$. Each one of the halos is generated with
-four different total particle numbers: $20$, $200$, $2000$ and $20000$.
-
-The method we use to generate the halos is based on the integrated
+First, we test our method using mock halos with known values for the
+concentration. The method we use to generate the halos is based on the integrated
 mass profile. Given the number of particles $n$ and the concentration
@@
 times in order to generate the $x,y,z$ coordinates for each particle.
+
+We generate $100$ mock halos with concentration values randomly
+placed in the range $1<c<20$. Each one of the halos is generated with
+four different total particle numbers: $20$, $200$, $2000$ and
+$20000$. This gives us a total of $500$ halos.
 
@@
 \end{center}
-\caption{Relative error Against number of Particles
+\caption{Relative error against number of particles
     \label{fig:error}}
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \begin{center}

### 2014-09-30 paper/article.tex
added new plots

@@
 
-In Figure XXX we show the circular velocity profile for the same
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{vel_normalized.pdf}
+\end{center}
+\caption{Dimensionless velocity profiles as a function of the
+  dimensionless radius for different concentration values.
+    \label{fig:velocity}}
+\end{figure}
+
+In Figure \ref{fig:velocity} we show the circular velocity profile for the same
 concentrations as in Figure \ref{fig:profiles}.
@@
 
-{\bf Cuantos pasos usa la cadena? De cuanto es el sigma en
-los saltos de c en lca cadena?
+{\bf Cuantos pasos usa la cadena? (50000) De cuanto es el sigma en
+los saltos de c en lca cadena? (0.029)
 

### 2014-09-30 src/AnotherPaperPlots.py

@@ -8,8 +8,21 @@ for c in C:
 pylab.legend(loc=0, scatterpoints=1, prop={'size':20})
 filename = 'nfw_normalized'
 matplotlib.rcParams.update({'font.size': 18})
-pylab.xlabel('$r_{norm}$',fontsize=20)
-pylab.ylabel('$m_{norm}$',fontsize=20)
+pylab.xlabel('$x$',fontsize=20)
+pylab.ylabel('$m(<x)$',fontsize=20)
+pylab.savefig(filename+'.eps',transparent=True)
+pylab.savefig(filename+'.pdf',transparent=True)
+pylab.savefig(filename+'.png',transparent=True)
+pylab.close()
+
+
+for c in C:
+    pylab.plot(r,np.sqrt(nfw.mass_norm(r,c)/r),color='black',lw= np.log(c+1)/2,label="$c="+str(c)+"$")
+pylab.legend(loc=0, scatterpoints=1, prop={'size':20})
+filename = 'vel_normalized'
+matplotlib.rcParams.update({'font.size': 18})
+pylab.xlabel('$x$',fontsize=20)
+pylab.ylabel('$v(<x)$',fontsize=20)
 pylab.savefig(filename+'.eps',transparent=True)
 pylab.savefig(filename+'.pdf',transparent=True)
 pylab.savefig(filename+'.png',transparent=True)

### 2014-11-05 paper/article.tex
first pass intro

@@
 
-\title[Bayesian halo concentrations]{Dark matter halo
-  concentrations with a bayesian approach}
+\title[New approach to Halo concentrations]{A new method to estimate
+  dark matter halo concentrations}
 \author[Poveda \& Forero-Romero]{
@@
 \label{sec:introduction}
-In the context of the concordance cosmology, the matter contents of
-the Universe are dominated by an unknown dark matter which behaves as
-a collisionless fluid only perturbed by gravity.
+In the concordance cosmology paradigm the the matter content of the
+Universe are dominated by dark matter which behaves as a collisionless
+fluid under the influence of gravity. In the last three decades
+numerical experiments have made possible the simulation of large
+volumes of a Universe dominated by dark matter.
 
-Numerical experiments are able to follow the non-linear evolution of
-dark matter down to galactic scales. On these scales a common
-approximation considers the matter distribution as spherical with a
-radial depedence. The function describing this distribution is known
-as a radial density profile.
+One of the most striking results of these simulations is that dark
+matter clumps on galactic scales follows a universal density profile
+which in a first approximation is spherical symmetric and only
+dependent on the radial coordinate. These profiles seem to be
+universal; independent of the cosmological parameters and self-similar
+for different spatial scapes after an addecuate re-scaling is
+appplied.
 
-The consensus is that density profiles are almost universal;
-almost independet of cosmological parameters and similar for different
-objects after some simple physical re-scalig is applied.
+One the most commong parameterization of this density is known as the
+Navarro-Frenk-White (NFW) profile \citep{NFW}. This profile is a
+double power law in radius, where the transition between the two
+happens at the so-called scale radius $r_s$. The ratio between the
+scale radius and the virial radius of the halo $R_v$ is known as the
+concentration $c=R_V/r_s$, a quantity that has been found to be
+correlated with the halo mass.
 
-The detailed halo structure influences the hosted galaxies.
+The relationship between halo mass and concentration is in principle
+accesible to observations and provides a potential test of LCDM on
+galactic scales. With this promise a great deal of effort has been
+invested in calibrating this relationship with simulations but also
+finding the best possible way to constraint it with observations.
 
-The concentration parameter is imporant in galaxy formation studies.
+From the computational point of view there are two main methods to
+estimate the concetration parameter of a dark matter halo in a N-body
+simulation. The first method takes the particles comprosing the halos
+and bins them in logarithmic radii to estimate the density in each
+bin, then it proceeds with a fit of this density estimation as a
+function of radius. A second method uses an analytical property of the
+NFW that related the maximum of the ratio of the circular velocity to
+the virial velocity. In this method at each particle radius this ratio
+is estimated to find the maximum value for this ratio; this value is
+used to find the roots of an equation which represent the
+concentration parameter.
 
-Different studies vary about the result of the concentration-mass
-relationship.
+The first method although is straightforward to apply has two main
+disadvantages. First of all it requires a large number of particles in
+order to have a proper density estimate in each bin. For a very low
+number of particles is hard to define a large number of bins to
+proceed with the fit. The second problem is that, as in any process
+involving data binning, there is not an way to estimate the optimal
+bin size, which in turn can affect the results of the fit.
 
-We propose a new way to obtain the concentration for halos in N-body
-simulations.
+The second method solves the two problems mentioned above. It works
+with low particles numbers and does not involve data binning. However,
+it effectively takes into account a single data point and discards the
+behaviour of the ratio $V_{cirv}/V_{vir}$ below and above its
+maxima.
 
-We use the integrated mass profile because it
-allows us to use the data directly with the simulation without binning
-the particle positions and estimating a density.
+In this paper we propose a new method to estimate the dark matter halo
+concentration from N-body simulation results. This method has two
+advantages with respect to the methods mentioned above. First, it does
+not involve data binning. Second, it does not throw away data
+points. Third, it allows for an straightforward estimation of the
+uncertainties in the concentration parameter.
 
-As an application we study the mass concentration relationship.
+Our method consists in building the cumulative mass profile from the
+particle data in the N-body simulation to find the best possible
+concentration value using a Markov Chain Monte Carlo methodology by
+comparing the data against the analytical expectation.
 
-\citep{NFW}
+This paper is structured as follows. In Section \ref{sec:basics} we
+review the basic properties of the NFW density profile and define the
+basic notation for the rest of the paper. Next in Section
+\ref{sec:method} we present our new method to estimate the halo
+concentration, payin special attention to the bayesian framework to
+find the most probable value and its uncertaintt. In Section
+\ref{sec:halo_sample} we demonstrate the power of our method with two
+different halo samples; the first one generated under controlled
+conditions and the second taken from a cosmological N-body
+simulation. Next in \ref{sec:discussion} we discuss these results by
+comparing them against other methods to estimate the concentration and
+comment on the consequences for the concentration-mass
+relationship. We present our conclusions in Section \ref{sec:conclusions}.
 
@@
 
-\section{Halo Samples}
+\section{Results}
+\label{sec:results}
 
@@
 
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{percentual_diff.pdf}
+\end{center}
+\caption{Cumulative distribution of the fractional difference between
+  the input concentration in the mock halo generator, $c_{in}$ and the
+  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
+  halos generated with a different number of particles, $N$.
+    \label{fig:results_mocks}}
+\end{figure}
+
+In Figure \ref{fig:results_mocks} we show the integrated distribution
+percentual difference between the concentration measured with our
+fitting method $c_{out}$ in comparison with the concentration used to
+generate the mock halos, $c_{in}$, $D=(c_{in}-c_{out})/c_{in}$.
+Then we can see that as the number of particles increases, the curve becomes more pronounced at 0.
+Showing that for most of the halos $c_{in}$ is very similar to $c_{out}$.
+
 \subsection{Simulation Data}
@@
 
-\section{Results}
-\label{sec:results}
-
-\subsection{Mock Halos}
-\label{sec:results_mocks}
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{percentual_diff.pdf}
-\end{center}
-\caption{Cumulative distribution of the fractional difference between
-  the input concentration in the mock halo generator, $c_{in}$ and the
-  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
-  halos generated with a different number of particles, $N$.
-    \label{fig:results_mocks}}
-\end{figure}
-
-In Figure \ref{fig:results_mocks} we show the integrated distribution
-percentual difference between the concentration measured with our
-fitting method $c_{out}$ in comparison with the concentration used to
-generate the mock halos, $c_{in}$, $D=(c_{in}-c_{out})/c_{in}$.
-Then we can see that as the number of particles increases, the curve becomes more pronounced at 0.
-Showing that for most of the halos $c_{in}$ is very similar to $c_{out}$.
-
-\subsection{Simulation Data}
-\label{sec:results_mocks}
-
 \section{Discussion}
@@
 \subsection{Comparison against other methods}
-We compared this method against two methods: The first one consists in using shells for estimating the density in function of the radius and using the same MCMC method for fitting and the second one consists in using the circular velocity $V(r)=\sqrt{GM(<r)/r}$ and the relation for the NFW profile
+\label{sec:comparison}
+We compared this method against two methods: The first one consists in
+using shells for estimating the density in function of the radius and
+using the same MCMC method for fitting and the second one consists in
+using the circular velocity $V(r)=\sqrt{GM(<r)/r}$ and the relation
+for the NFW profile 
 \begin{equation}
@@
 
-Running another test with halos whose concentrations vary as a normal distribution of variance ${\sigma}^2$ we found that the concentrations obtained by the method of circular velocity are a 35\% greater than the ones obtained by the density method.
-However the concentrations obtained by the velocity method are barey higher (around 2\% or 3\%) than the ones obtained by our method.
-We did not find any significant variation in the concentration values obtained by any method by changing ${\sigma}^2$ in contrast with FIXME.
+Running another test with halos whose concentrations vary as a normal
+distribution of variance ${\sigma}^2$ we found that the concentrations
+obtained by the method of circular velocity are a 35\% greater than
+the ones obtained by the density method. However the concentrations
+obtained by the velocity method are barey higher (around 2\% or 3\%)
+than the ones obtained by our method. We did not find any significant
+variation in the concentration values obtained by any method by
+changing ${\sigma}^2$ in contrast with FIXME.
 
-\subsection{Concentration as a function of halo mass}
+\subsection{Impact on the mass-concentration relationship}
 Aditionally we compared those three methods plotting the concentration as a function of the number of particles of each halo
@@
 \subsection{Implication for comparisons against observations}
-FIXME: Ask to Jaime
+FIXME: Ask Jaime
 
@@
 \label{sec:conclusions}
-FIXME: Ask to Jaime
+FIXME: Ask Jaime
 
@@
 
+\verb"http://adsabs.harvard.edu/abs/2014ApJ...795..163U"
+\verb"http://adsabs.harvard.edu/abs/2012ApJS..199...25P" Figura 3!
 \end{document}

### 2015-01-13 paper/article.tex
writing the new method section

@@
 
-The Navarro-Frenk-White density profile can be written as
+\subsection{Density profile}
+
+The NFW density profile can be written as
 
@@
 \rho(r) = \frac{\rho_c\delta_c}{r/r_s(1+r/r_s)^2}, 
+\label{eq:definition}
 \end{equation}
@@
 is known as the scale radius, the radius that marks the transition
-between the two power law behaviour in the $\rho\propto r^{-1}$ for
+between the power law scaling $\rho\propto r^{-1}$ for
 $r<r_s$ and $\rho\propto r^{-3}$ for  $r>r_s$.
@@
 We define the virial radius of a halo, $r_v$, as the boundary of the
-spherical volume that encloses an average density of $\Delta_h$ times
+spherical volume that encloses a density of $\Delta_h$ times
 the average density of the Universe. The corresponding mass $M_{v}$,
@@
 
-We can now express the same quantity in terms of dimensionless the
+We express the same quantity in terms of dimensionless
 variables $x\equiv r/r_v$ and $m\equiv M(<r)/M_v$,
@@
 \begin{equation}
-A=\left[\ln\left(1+c\right)-\left(\frac{c}{c+1}\right)\right],
+A=\ln\left(1+c\right)-\left(\frac{c}{c+1}\right),
 \end{equation}
@@
 and the parameter $c$ is known as the concentration $c\equiv r_v/r_s$.
+
+From this normalization value and for later convenience we define the
+following function 
+%
+\begin{equation}
+f(x) = \ln\left(1+x\right)-\left(\frac{x}{x+1}\right).
+\label{eq:f_NFW}
+\end{equation}
+%
 
@@
 
-It is also customary to express the mass of the halo inte terms of the
+It is also customary to express the mass of the halo in terms of the
 circular velocity $V_{c}=\sqrt{GM(<r)/r}$. From this we can
 define a new dimensionless circular velocity $v(<x)\equiv
-V_{c}(<r)/V_{c}(<r_v)$, using the result in Equation \ref{eq:profile}
+V_{c}(<r)/V_{c}(<r_v)$, using the result in Eq. \ref{eq:profile}
 to have:
+
+In Figure \ref{fig:velocity} we show the circular velocity profile for the same
+concentrations as in Figure \ref{fig:profiles}.
 
@@
 \end{equation}
+%
+this normalized profile always shows a maximum provided that the
+concentration is larger than a values of $c>???$. 
+It is possible to show that for the NFW profile the maximum is
+provided by
+
+\begin{equation}
+\mathrm{max}(v(<x)) = \sqrt{\frac{c}{x_{\rm max}}\frac{f(x_{\rm
+      max})}{f(c)}}, 
+\label{eq:max_v}
+\end{equation}
+where $x_{\rm max}=2.163$ and the function $f(x)$ was defined in Eq. (\ref{eq:f_NFW}).
 
@@
 
-In Figure \ref{fig:velocity} we show the circular velocity profile for the same
-concentrations as in Figure \ref{fig:profiles}.
+\section{A new approach to estimate the halo concentration}
+\label{sec:method}
 
-\section{A new Approach to Halo Fitting}
-\label{sec:method}
+Once the density profile is expressed in dimensionless variables the
+only free variable is the concentration. 
+There are two main methods to estimate this values in dark matter
+halos extracted from N-body simulations.
+The first method bins the particles in the logarithm of the radial
+coordinate from the halo center to estimate the density in each
+logarithmic bin. 
+Then a direct fit to the density as a function of the radial
+coordinate is performed. This method has been most recently advocated
+by \cite{Ludlow2014} to study the mass-concentration-redshift relation
+of dark matter halos using the Millennium Simulation Series.
+
+A second method uses the circular velocity profile. 
+As it was shown in Fig. (\ref{fig:velocity}) the circular velocity
+shows a maximum for all profiles with concentration values larger than
+$c>???$. 
+For the numerical halos wne can then find the value of $x$ for which
+the normalized circular velocity $v(<x)$ shows a maximum and solve
+numerically for the corresponding value of the concentration using
+Eq. (\ref{eq:max_v}).  This method has been used by \cite{Klypin2014}
+to study the mass-concentration-redshift relation using the Multidark
+Simulation Suite.
 

### 2015-01-14 src/AnotherPaperPlots.py
correcting issue

@@ -1,10 +1,11 @@
 import pylab, numpy as np, nfw, matplotlib
 
 r = np.arange(0,1,0.001)
-C = np.linspace(1,20,6)
+C = np.linspace(1,20,4)
 
 for c in C:
-    pylab.plot(r,nfw.mass_norm(r,c),color='black',lw= np.log(c+1)/2,label="$c="+str(c)+"$")
+    c = int(c)
+    pylab.plot(r,nfw.mass_norm(r,c),color='black',lw = .2*c+1,label="$c="+str(c)+"$")
 pylab.legend(loc=0, scatterpoints=1, prop={'size':20})
 filename = 'nfw_normalized'
 matplotlib.rcParams.update({'font.size': 18})
@@ -17,7 +18,8 @@ pylab.close()
 
 
 for c in C:
-    pylab.plot(r,np.sqrt(nfw.mass_norm(r,c)/r),color='black',lw= np.log(c+1)/2,label="$c="+str(c)+"$")
+    c = int(c)
+    pylab.plot(r,np.sqrt(nfw.mass_norm(r,c)/r),color='black',lw = .2*c+1,label="$c="+str(c)+"$")
 pylab.legend(loc=0, scatterpoints=1, prop={'size':20})
 filename = 'vel_normalized'
 matplotlib.rcParams.update({'font.size': 18})

### 2015-01-14 data/results/MDmini/compare.py
another issue

@@ -1,5 +1,7 @@
 import numpy as np, pylab,sys
 
+dm = 8720999991.75 #https://raw.githubusercontent.com/forero/TrainingHalos/master/data/halo_ID/MDmini_all_halo-ID.csv
+
 def get_stats(log_mass,conc):
 
     bins = np.arange(0,np.amax(log_mass)+0.5,0.5)
@@ -43,21 +45,32 @@ bins_mcmc,median_mcmc,quar1_mcmc,quar2_mcmc = get_stats(np.log10(m_mcmc),c_mcmc)
 bins_vel,median_vel,quar1_vel,quar2_vel = get_stats(np.log10(m_vel),c_vel)
 bins_dens,median_dens,quar1_dens,quar2_dens = get_stats(np.log10(m_dens),c_dens)
 
-pylab.plot(10**(bins_dens),median_dens,'-g',lw=2,label='Density')
-pylab.fill_between(10**(bins_dens),quar1_dens,quar2_dens,color='g',alpha=0.4)
 
-pylab.plot(10**(bins_mcmc),median_mcmc,'-r',lw=2,label='Mass')
-pylab.fill_between(10**(bins_mcmc),quar1_mcmc,quar2_mcmc,color='r',alpha=0.4)
+fig, ax1 = pylab.subplots()
 
-pylab.plot(10**(bins_vel),median_vel,'-b',lw=2,label='Velocity')
-pylab.fill_between(10**(bins_vel),quar1_vel,quar2_vel,color='b',alpha=0.4)
+ax1.plot(10**(bins_dens)*dm,median_dens,'-g',lw=2,label='$\mathrm{Density}$')
+ax1.fill_between(10**(bins_dens)*dm,quar1_dens,quar2_dens,color='g',alpha=0.4)
 
-pylab.legend(loc=1, borderaxespad=0.5)
-pylab.xscale('log')
-pylab.xlim([1E2,1E5])
-pylab.ylim([0,10])
-pylab.xlabel('$\mathrm{Number\ of\ particles}$',fontsize=20)
-pylab.ylabel('$\mathrm{Concentration}$',fontsize=20)
+ax1.plot(10**(bins_mcmc)*dm,median_mcmc,'-r',lw=2,label='$\mathrm{Mass}$')
+ax1.fill_between(10**(bins_mcmc)*dm,quar1_mcmc,quar2_mcmc,color='r',alpha=0.4)
[…]

### 2015-01-14 paper/article.tex
added info about the steps for te MH

@@
 We sample the likelihood function distribution defined by ${\cal
-  L}(c)=\exp(-\chi^2(c)/2)$ with a Metropolos-Hastings algorithms to
+  L}(c)=\exp(-\chi^2(c)/2)$ with a Metropolis-Hastings algorithm to
 find the optimum value of $c$ and its  associated uncertainty
-$\sigma_c$.
-
-{\bf Cuantos pasos usa la cadena? (50000) De cuanto es el sigma en
-los saltos de c en lca cadena? (0.029)
-
-Falta alguna figura que muestre resultados de la -log likelihood para
-algunos casos representativos.
-}
+$\sigma_c$. We used 50000 steps for walk, where each step was randomly generated
+with a normal distribution centered around the last step with an standard
+deviation of $\sigma=0.03$.
 

### 2015-01-21 paper/article.tex
finished section on new method description

@@
 % definition to produce a "greater than or similar to" symbol
-
-% definition to produce a "greater than or similar to" symbol
 \def\gsim{~\rlap{$>$}{\lower 1.0ex\hbox{$\sim$}}}
@@
 
-\title[New approach to Halo concentrations]{A new method to estimate
+\title[A new method for concentrations]{A new method to estimate
   dark matter halo concentrations}
@@
 In the concordance cosmology paradigm the the matter content of the
-Universe are dominated by dark matter which behaves as a collisionless
+Universe is dominated by dark matter which behaves as a collisionless
 fluid under the influence of gravity. In the last three decades
-numerical experiments have made possible the simulation of large
-volumes of a Universe dominated by dark matter.
+numerical experiments have made possible the simulation of dark matter
+dominated universes, yielding valuable insights on the large scale
+structure formation process as depicted in observations.
 
 One of the most striking results of these simulations is that dark
-matter clumps on galactic scales follows a universal density profile
+matter clumps on galactic scales follow a universal density profile
 which in a first approximation is spherical symmetric and only
@@
 
-Once the density profile is expressed in dimensionless variables the
-only free variable is the concentration.
-There are two main methods to estimate this values in dark matter
-halos extracted from N-body simulations.
-The first method bins the particles in the logarithm of the radial
-coordinate from the halo center to estimate the density in each
-logarithmic bin.
-Then a direct fit to the density as a function of the radial
-coordinate is performed. This method has been most recently advocated
-by \cite{Ludlow2014} to study the mass-concentration-redshift relation
-of dark matter halos using the Millennium Simulation Series.
+As we saw in the previous sections, once the density profile is
+expressed in dimensionless variables the only free parameter in the
+density profile  is the concentration. There are two main methods to
+estimate concentrations in dark matter halos extracted from N-body
+simulations.
+
+The first method tries to directly estimate the density profile. 
+It takes all the particles in the halo and bins them in the logarithm
+of the radial coordinate from the halo center.
+Then, it estimates the density in each logarithmic bin counting the
+particles and divinding by the corresponding shell volume.
+At this point is is possible to make a direct fit to the density as a
+function of the radial coordinate. 
+This method has been most recently used by \cite{Ludlow2014} to study
+the mass-concentration-redshift relation of dark matter halos using
+the Millennium Simulation Series.
 
@@
 shows a maximum for all profiles with concentration values larger than
-$c>???$.
-For the numerical halos wne can then find the value of $x$ for which
-the normalized circular velocity $v(<x)$ shows a maximum and solve
-numerically for the corresponding value of the concentration using
-Eq. (\ref{eq:max_v}).  This method has been used by \cite{Klypin2014}
-to study the mass-concentration-redshift relation using the Multidark
+$c>2$.
+The method finds the value of $x$ for which the normalized circular
+velocity $v(<x)$ shows a maximum. 
+Using this value it solves numerically for the corresponding value of
+the concentration using Eq. (\ref{eq:max_v}).  
+This method has been most recently used by \cite{Klypin2014} to study
+the mass-concentration-redshift relation using the Multidark
 Simulation Suite.
 
-We estimate the concentration parameter by fitting the
-integrated mass profile described in Equation
-(\ref{eq:profile}). First we define the center of the halo to be  at
-the position of the particle with the lowest gravitational
-potential.
-
-We construct the integrated mass profile by ranking the particles by
-their increasing distance to the center of the halo. Once they are ranked,
-the total mass at a radius $r_i$, increases by $m_p$, where $r_i$ is
-the position of the $i$-th particle and $m_p$ is the mass of the
-computational particle.  In this process we discard the
-particle at the center.
+Our method is a third option that uses the integrated mass profile.
+First we define the center of the halo to be at the position of the
+particle with the lowest gravitational potential.
+Then we rank the particles by their increasing radial distance from
+the center.
+From this ranked list of $i=1,N$ particles, the total mass at a radius
+$r_i$ is $M_i=i\times m_p$, where $r_i$ is
+the position of the $i$-th particle and $m_p$ is the mass of a single
+computational particle.
+In this process we discard the particle at the center.
 
@@
 at an average density of $\Delta_h\bar{\rho}$, with $\Delta_h=740$,
-roughly corresponding to 200 times the critical density. This radius marks the
-virial radius and the virial mass. We divide the total mass enclosed
-mass $M_i$ and the radii $r_i$ by these values to obtain the
-dimensionless variables $x_i$ and $m_i$.
+roughly corresponding to 200 times the critical density. 
+This radius marks the virial radius and the virial mass. 
+We divide the enclosed mass mass $M_i$ and the radii $r_i$ by these
+virial values to obtain the dimensionless variables $m_i$ and $x_i$.
 
-Using these new variables we define the following $\chi^2$ function
+The construction of the numerical integrated mass profile has the
+advantage that it does not involve any binning and uses the
+information from all the particles in the halo, unlike the method that
+tries to directly build. 
+Furthermore, as it will be clear in the next paragraph, the fit of
+this computational profile to the analytic expectation uses the
+information from all points, not only a single maxima point as the
+method using the circular velocity profile.
+
+We use a Metropolis-Hastings algorithm to sample the likelihood
+function distribution defined by ${\cal L}(c)=\exp(-\chi^2(c)/2)$
+where the $\chi^2(c)$ is written as
 
 \begin{equation}
-\chi^2(c) = \sum_{i}[\log m_i - \log m(< x_i;c)]^2,
+\chi^2(c)= \sum_{i=1}^{N}[\log m_i - \log m(< x_i;c)]^2,
 \end{equation}
@@
 where $m(<x_i;c)$ corresponds to the values in Eq.(\ref{eq:profile}) at
-$x=x_i$ for a given value of the concentration parameter $c$.
+$x=x_i$ for a given value of the concentration parameter $c$ and the
+$i$ index sums over all the particles in the numerical profile.
 
-We sample the likelihood function distribution defined by ${\cal
-  L}(c)=\exp(-\chi^2(c)/2)$ with a Metropolis-Hastings algorithm to
-find the optimum value of $c$ and its  associated uncertainty
-$\sigma_c$. We used 50000 steps for walk, where each step was randomly generated
-with a normal distribution centered around the last step with an standard
-deviation of $\sigma=0.03$.
+For the walk in the Metropolis-Hastings algorithm we used 50000 steps
+where each step was randomly generated with a normal distribution
+centered around the last step with an standard deviation of
+$\sigma=0.03$. 
+From the $\chi^2$ distribution we find the optimal value of the
+concentration and  its associated uncertainty.
 

### 2015-01-21 paper/article.tex
intro de sec. resultados. subsubsec impact of particle number

@@
 
-We apply our method to two different halo samples. The first one is a
-mock sample to test the algorithm and asses the impact of the number
-of computational particles on the concentration values. The second
-sample comes from a publicly available N-body cosmological
-simulation. These results for these sample can be then compared
-against other methods to find the concentration and feed the
-discussion about the implications of our method.
+In this Section we present the results of applying our method on two
+different halo samples.
 
-\subsection{Mock Halos}
+The first sample is composed by mock halos generated to have known
+concentration values in perfect spherical symmetry following an NFW
+profile. 
+We use this sample to check that we can recover the expected values
+but also gauge the impact of the number of particles on the outcomes
+and the difference with respect to the two other fitting methods.
 
-First, we test our method using mock halos with known values for the
-concentration. The method we use to generate the halos is based on the integrated
-mass profile. Given the number of particles $n$ and the concentration
-$c$ we define the mass element as $\delta m = 1/n$ (this corresponds
-to the mass of each particle such that the total mass is one). Then
-for each number $k$ from $1$ to $n$ we find the value of $r$ such that
+The second sample comes from a publicly available N-body cosmological
+simulation. 
+From this sample we quantify again the differences between all the
+methods we have to fit the data.
+We also estimate the possible impact of the different methods in
+estimating the mass-concentration relationship from simulations.
+
+\subsection{Tests on Mock Halos}
+
+The method we use to generate the halos is based on the integrated
+mass profile. 
+We start by fixing the desired concentration $c$ and total number of
+particles $N$ in the mock halo 
+With this values we define the mass element as $\delta m = 1/M$, corresponding
+to the mass of each particle such that the total mass is one. 
+Then for each particle $i=1,\ldots,N$, we find the value of $r_i$ such that
 the difference
@@
 \begin{equation}
-m(<r;c)-k \cdot \delta m
+m(<r_i;c) - i \cdot \delta m
 \end{equation}
 %
-is zero using Ridders' method. This value of $r$ is the radius of
-the $k$th particle of the generated halo, then polar and azimuthal
-angles $\theta$ and $\phi$ are randomly generated. Finally these three
-coordinates are transformed into cartesian coordinates
-$(r,\theta,\phi) \rightarrow (x,y,z)$. This process is repeated $n$
-times in order to generate the $x,y,z$ coordinates for each particle.
+is zero using Ridders' method.
 
-We generate $100$ mock halos with concentration values randomly
-placed in the range $1<c<20$. Each one of the halos is generated with
-four different total particle numbers: $20$, $200$, $2000$ and
-$20000$. This gives us a total of $500$ halos.
+The value of $r_i$ is the radius of the $i$-th particle of the mock
+halo.
+Then we generate random polar and azimuthal angles $\theta$ and $\phi$
+for each particle to ensure spherical symmetry. 
+Finally these three spherical coordinates are transformed into cartesian coordinates
+$(r,\theta,\phi) \rightarrow (x,y,z)$.
+
+We generate in total $400$ mock halos splitted into four different
+groups of $100$ halos each. 
+The four groups differ in the total number of particles for their halos:
+$20$, $200$, $2000$ and $20000$.
+Inside each group the halos have random concentration values in
+the range $1<c<20$ with a flat distribution. 
+For all these halos with find the concentration values using the
+density, velocity and mass methods described in the previous
+section. We quantify the difference between the expected $c_{in}$
+and obtained $c_{out}$ values by $D=(c_{in}-c_{out})/c_{in}$.
+
+\subsubsection{The impact of particle number}
 
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{percentual_diff.pdf}
+  \includegraphics[width=0.50\textwidth]{percentual_diff.pdf}
 \end{center}
-\caption{Cumulative distribution of the fractional difference between
+\caption{Cumulative distribution of the fractional difference, $D$, between
   the input concentration in the mock halo generator, $c_{in}$ and the
@@
 
-In Figure \ref{fig:results_mocks} we show the integrated distribution
-percentual difference between the concentration measured with our
-fitting method $c_{out}$ in comparison with the concentration used to
-generate the mock halos, $c_{in}$, $D=(c_{in}-c_{out})/c_{in}$.
-Then we can see that as the number of particles increases, the curve becomes more pronounced at 0.
-Showing that for most of the halos $c_{in}$ is very similar to $c_{out}$.
+Figure \ref{fig:results_mocks} shows the integrated distribution for
+$D$ for the fits using our method, splitted into four different groups
+according the particle number. 
+From this Figure the first immediate
+conclusion is that increasing the number of particles increases the
+chances to recover the input values.
+
+We believe that the main effect that contributes to this trend
+is that the particle that our algorithm finds to be the halo center
+(where the potential is minimum) gets closer to the original
+geometrical center (where no particle sits by construction) used to
+generate the halo.  Poissonian noise makes this center fluctuate,
+changing the numerical radial profile from the analytical input.
+
+For particle number of $20$ the offset betwen the input and output
+concentration can be as large as $20\%$, with a slight bias around
+$-0.05\%$, i.e. the output concentration is biased towards lower
+values than the input.
+For particle numbers of $2000$ most of the offsets fall below $5\%$,
+with a clear peak around $0\%$ indicating that any appreciable bias is
+absent.
+
+\subsubsection{The impact of the input concentration}
+
+Hace falta hacer una figura para este caso.
 

### 2015-01-23 paper/article.tex
discutiendo la comparacione entre metodos con mock halos

@@
 section. We quantify the difference between the expected $c_{in}$
-and obtained $c_{out}$ values by $D=(c_{in}-c_{out})/c_{in}$.
+and obtained $c_{out}$ values by
+
+\begin{equation}
+D=(c_{in}-c_{out})/c_{in}.  
+\label{eq:D}
+\end{equation}
 
@@
 
-\subsection{Simulation Data}
-\label{sec:data}
-
-We use data from the MultiDark cosmological volume. This simulation
-follows the non-linear evolution of a dark matter density field
-sampled with $2048^3$ particles over a cubic box of $1000$ \hMpc on a
-side. The data is publicly available, more details about the structure
-of the database and the simulations can be found in
-\citep{2013AN....334..691R}.
-
-We select a sample of halos in a cubic sub-volumne of $100$ \hMpc on a
-side centered on the most massive halo in the simulation at
-$z=0$\footnote{This corresponds to the \texttt{miniMDR1} database in
-  the MultiDark webpage}. We select first all the halos at $z=0$
-detected with a Friends-of-Friends (FoF) algorithm with masses in the
-interval $10^{11}\leq M_{\rm FoF}/\hMsun \leq 10^{15}$. The FoF
-algorithm ran with a linking length of $0.17$ times the average
-interparticle distance. This choice translates into an overdensity
-$\Delta_h\sim 400-700$ that is dependent on the halo concentration
-\citep{More2011}.
-
-For each selected halo with the previous procedure we select from the database
-all the particles that belong to it. From the particles we follow the
-procedure spelled out in Section \ref{sec:method} with $\Delta_h=740$
-(corresponding to $200$ times the critical density) to find the
-halo concentration. Finally, we store the values obtained for the
-virial radius, virial mass and concentration.
-
-\section{Discussion}
-\label{sec:discussion}
-
-\subsection{Comparison against other methods}
-\label{sec:comparison}
-We compared this method against two methods: The first one consists in
-using shells for estimating the density in function of the radius and
-using the same MCMC method for fitting and the second one consists in
-using the circular velocity $V(r)=\sqrt{GM(<r)/r}$ and the relation
-for the NFW profile
-\begin{equation}
-\frac{V_{max}}{V(r_{v})} = \sqrt{\frac{0.216c}{M(r_{v};c)}}
-\end{equation}
-Where $V_{max}$ is the maximum velocity, to find the value of the concentration.
-We tested the three methods using the same data from the Mock Halos test.
-In order to see the accuracy of each method depending on the number of particles we define
-
-\begin{equation}
-\xi(n)=\frac{1}{\left|{\cal{H}}_n\right|}\sum_{{\cal{H}}_n}\left|\frac{c_{org}-c_{obt}}{c_{org}}\right|
-\end{equation}
-
-Where ${\cal{H}}_n$ corresponds to the set of haloes with $n$ particles, $c_{org}$ and $c_{obt}$ are the original and obtained concentrations respectively for each halo in ${\cal{H}}_n$ and $\left|{\cal{H}}_n\right|$ the number of haloes in ${\cal{H}}_n$.
-Then we calculate $\xi$ for each number of particles (20, 200, 2000 and 20000).
+\subsubsection{The impact of different methods}
 
@@
 \end{center}
-\caption{Relative error against number of particles
+\caption{Average value of the relative error in the concentration
+  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
+  the set of mock halos. Different symbols represent different
+  methods. Our method provide the most accurate estimate at fixed
+  particle number $N$. 
     \label{fig:error}}
@@
 
-In Figure \ref{fig:error} we plotted $\xi$ for the three methods.
-We consider that $\xi$ is a good estimate because it is standardized, giving equal weight to all errors regardless of the magnitude of the concentrations or the number of halos.
-On the other hand we have that $\xi$ decreases quite fast with the number of particles for our method and is more precise in any case that the other methods.
-As mentioned in FIXME \textit{``for a large fraction of halos, and for the most massive in particular, the NFW functional does not Represent a good fit to the density profile."} This fact could explain why $\xi$ increases with the number of particles for the density method.
+Using this dataset we also compare our method against the other two
+methods described earlier. Using shells to estimate the density as a
+function of radius radius and the maximum circular velocity method.
+In the first case we use the same Metropolis-Hastings algorithm we
+have in our methot to fit the density profile.
+
+We quantify the accuracy of each method with the following statistic:
+
+\begin{equation}
+\avg{|D|}=\frac{1}{\left|{\cal{H}}_N\right|}\sum_{{\cal{H}}_N} |D|,
+\end{equation}
+
+where ${\cal{H}}_N$ corresponds to the set of haloes with $N$
+particles, $D$ follows the definition in Eq. (\ref{eq:D}) and
+$\left|{\cal{H}}_n\right|$ is the number of haloes in ${\cal{H}}_n$.
+
+Figure \ref{fig:error} shows the behaviour of $\avg{|D|}$ as a function of
+particle number for the three different methods to estimate the
+concentration. 
+We find that our method always shows the lowest $\avg{|D|}$ values compared
+to the other two methods at fixed particle numbers. 
+The accuracy of this method to estimate the input concentration is on
+the order of $10\%$ for $20$ particles in the halo, going down to
+$0.1\%$ for halos with $20000$ particles. 
+The drop of $\avg{|D|}$ with increasing particle number $N$ goes
+approximately as $\avg{|D|}\propto N^{-1/2}$, which reinforces the hint that
+the accuracy of the method is related to a decrease of Poissonian
+noise.
+
+On the other hand we have that
+$\xi$ decreases quite fast with the number of particles for our method
+and is more precise in any case that the other methods. As mentioned
+in FIXME \textit{``for a large fraction of halos, and for the most
+  massive in particular, the NFW functional does not Represent a good
+  fit to the density profile."} This fact could explain why $\xi$
+increases with the number of particles for the density method.
+
+\subsection{Tests on N-body data}
+\label{sec:data}
+
+We use data from the MultiDark cosmological simulation. 
+It follows the non-linear evolution of a dark matter density field
+sampled with $2048^3$ particles over a cubic box of $1000$ \hMpc on a side. 
+The data is publicly available through \url{http://www.cosmosim.org/}.
+Mre details about the structure of the database and the simulation
+can be found in \citep{2013AN....334..691R}.
+
+We build a sample of all halos located in a cubic sub-volume of $100$
+\hMpc on a side centered on the most massive halo in the simulation at
+$z=0$ which corresponds to the \texttt{miniMDR1} tables in the
+database.   
+From this sample we select all the halos at $z=0$ detected with a
+Friends-of-Friends (FoF) algorithm with masses in the interval
+$10^{11}\leq M_{\rm FoF}/\hMsun \leq 10^{15}$. 
+The FoF algorithm used with a linking length of $0.17$ times the average
+interparticle distance. This choice translates into an overdensity
+$\Delta_h\sim 400-700$ dependent on the halo concentration
+\citep{More2011}. 
+Finally, for each FoF halo we select from all the particles that
+belong to it.
+
+From this set of particles we follow the procedure spelled out in
+Section \ref{sec:method} with $\Delta_h=740$  (corresponding to $200$
+times the critical density) to find the halo concentration. 
+This choice makes that our overdensities are fully included inside the
+original FoF particle group.
+Finally, we store the values obtained for the virial radius, virial
+mass and concentration.
 
@@
 
-We also used these three methods to obtain the concentration for each halo in miniMDR1 and compared the results.
-As can be seen in Figure \ref{fig:mdv} the three methods show mutually consistent results.
-However it can be inferred that the concentration values ​​obtained by the method of circular velocity are higher than those obtained by our method, and also the values ​​obtained by the density method are generally below the results of our method.
+We also used these three methods to obtain the concentration for each
+halo in miniMDR1 and compared the results. As can be seen in Figure
+\ref{fig:mdv} the three methods show mutually consistent
+results. However it can be inferred that the concentration values
+​​obtained by the method of circular velocity are higher than those
+obtained by our method, and also the values ​​obtained by the density
+method are generally below the results of our method.
 

### 2015-01-23 paper/article.tex
completa primera revision. Falta intro y conclusiones

@@
 
-Hace falta hacer una figura para este caso.
+{\bf Hace falta hacer una figura para este caso.}
 
@@
 Using this dataset we also compare our method against the other two
-methods described earlier. Using shells to estimate the density as a
-function of radius radius and the maximum circular velocity method.
+methods described earlier: using shells to estimate the density as a
+function of radius and the maximum circular velocity method.
 In the first case we use the same Metropolis-Hastings algorithm we
 have in our methot to fit the density profile. 
+In the second method we simply follow the procedure described in
+Section \ref{sec:method}
 
@@
 Figure \ref{fig:error} shows the behaviour of $\avg{|D|}$ as a function of
-particle number for the three different methods to estimate the
+halo particle number for the three different methods to estimate the
 concentration. 
-We find that our method always shows the lowest $\avg{|D|}$ values compared
-to the other two methods at fixed particle numbers. 
-The accuracy of this method to estimate the input concentration is on
-the order of $10\%$ for $20$ particles in the halo, going down to
-$0.1\%$ for halos with $20000$ particles. 
-The drop of $\avg{|D|}$ with increasing particle number $N$ goes
+At fixed particle numbers our method always shows the lowest
+$\avg{|D|}$ values compared to the other two methods.
+Its accuracy is on the order of $10\%$ for $20$ particles in the halo,
+going down to $0.1\%$ for halos with $20000$ particles. 
+The decrease of $\avg{|D|}$ with increasing particle number $N$ goes
 approximately as $\avg{|D|}\propto N^{-1/2}$, which reinforces the hint that
@@
 
-On the other hand we have that
-$\xi$ decreases quite fast with the number of particles for our method
-and is more precise in any case that the other methods. As mentioned
-in FIXME \textit{``for a large fraction of halos, and for the most
-  massive in particular, the NFW functional does not Represent a good
-  fit to the density profile."} This fact could explain why $\xi$
-increases with the number of particles for the density method.
+The second best accuracy is achieved by the method based on the
+maximum of the circular velocity. 
+It also shows a similar behaviour $\avg{|D|}\propto N^{-1/2}$. 
+Its accuracy is $2-5$ times less than in our method, on the order of
+$20\%$ for $20$ particle halos and $0.5\%$ for $20000$ particle halos.
+The method based on the direct density fit shows the lowest accuracy
+of all methods. 
+Its average values $\avg{|D|}$ are always between $30\%$ adn $50\%$
+regardless of the particle number. {\bf Necesitamos entender el
+  comportamiento de esto.}
 
@@
 \label{sec:data}
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.99\textwidth]{mass-density-velocity.pdf}
+\end{center}
+\caption{Comparison between the obtained concentrations by the three methods
+    \label{fig:mdv}}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.90\textwidth]{concentration.pdf}
+\end{center}
+\caption{Mass-concentration relationship for the three different
+  methods used on the same cosmological N-body data. The central lines
+  correspond the median and the shadowed region indicates the
+  quartiles. 
+    \label{fig:concentrations}}
+\end{figure*}
 
@@
 The data is publicly available through \url{http://www.cosmosim.org/}.
-Mre details about the structure of the database and the simulation
+More details about the structure of the database and the simulation
 can be found in \citep{2013AN....334..691R}.
@@
 original FoF particle group.
+We only report results from overdensities with at least $100$ particles.
 Finally, we store the values obtained for the virial radius, virial
@@
 
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.99\textwidth]{mass-density-velocity.pdf}
-\end{center}
-\caption{Comparison between the obtained concentrations by the three methods
-    \label{fig:mdv}}
-\end{figure*}
+Figure \ref{fig:mdv} shows the results that compare the concentration
+values in the simulated halos from the three different methods. 
+At zeroth order the results are consistent. 
+However, the concentration values from the velocity method produces
+concentrations that are $XXX$ times larger on average than the results
+from our method.
+On the other hand, the concentrations from the velocity method are
+$XXX$ times lower than in our method.
 
-We also used these three methods to obtain the concentration for each
-halo in miniMDR1 and compared the results. As can be seen in Figure
-\ref{fig:mdv} the three methods show mutually consistent
-results. However it can be inferred that the concentration values
-​​obtained by the method of circular velocity are higher than those
-obtained by our method, and also the values ​​obtained by the density
-method are generally below the results of our method.
+%Running another test with halos whose concentrations vary as a normal
+%distribution of variance ${\sigma}^2$ we found that the concentrations
+%obtained by the method of circular velocity are a 35\% greater than
+%the ones obtained by the density method. However the concentrations
+%obtained by the velocity method are barey higher (around 2\% or 3\%)
+%than the ones obtained by our method. We did not find any significant
+%variation in the concentration values obtained by any method by
+%changing ${\sigma}^2$ in contrast with FIXME.
 
-Running another test with halos whose concentrations vary as a normal
-distribution of variance ${\sigma}^2$ we found that the concentrations
-obtained by the method of circular velocity are a 35\% greater than
-the ones obtained by the density method. However the concentrations
-obtained by the velocity method are barey higher (around 2\% or 3\%)
-than the ones obtained by our method. We did not find any significant
-variation in the concentration values obtained by any method by
-changing ${\sigma}^2$ in contrast with FIXME.
-
-\subsection{Impact on the mass-concentration relationship}
-Aditionally we compared those three methods plotting the concentration as a function of the number of particles of each halo
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{concentration.pdf}
-\end{center}
-\caption{Concentration against number of particles
-    \label{fig:concentrations}}
-\end{figure}
-
-The bold lines in Figure \ref{fig:concentrations} corresponds to the median and the thinner lines corresponds to the quartiles.
-Showing that our method has values ​​ranging from those obtained from the other two methods.Also we can see that the concentration obtained by the velocity method is higher than that obtained by the density method, this fact is consistent with FIXME.
-\subsection{Implication for comparisons against observations}
-FIXME: Ask Jaime
+Figure \ref{fig:concentration} shows the mass-concentration
+relationship from the N-body data with the results of the three
+different methods.  
+The central lines correspond the median and the
+shadowed region indicates the quartiles.
+In this relationship our methods represents a compromise between the
+velocity and density methods.
+The slope is flatter and the overall normalization is below the
+velocity method and above the density.
 
@@
 \label{sec:conclusions}
-FIXME: Ask Jaime
 

### 2015-01-24 data/test/mock_100/error.py
solved issue

@@ -15,7 +15,7 @@ orig = vlct[:,0]
 
 def chi2(x_obs,x_org):
         return np.sum(np.abs((x_obs-x_org)/x_org))/len(x_obs)
-            
+
 def best_fit(original,results):
     ans = np.empty(len(original))
     for i in range(len(original)):
@@ -23,7 +23,7 @@ def best_fit(original,results):
         index = np.argmin(np.abs(original[i]-concentrations))
         ans[i] = concentrations[index]
     return ans
-    
+
 pylab.title('$Velocity$')
 pylab.plot(orig,orig,'--k',label='$real$')
 #pylab.plot(orig,vlct[:,1],'.b',label='$n=20$')
@@ -74,16 +74,20 @@ pylab.close()
 chi_dens = np.array([chi2(orig,dens[:,1]),chi2(orig,dens[:,2]),chi2(orig,dens[:,3]),chi2(orig,dens[:,4])])
 
 pylab.plot([20,200,2000,20000],chi_mass,'-k',lw=2)
-pylab.plot([20,200,2000,20000],chi_mass,'ok',label='$Mass$',ms=7)
+pylab.plot([20,200,2000,20000],chi_mass,'ok',label='$\mathrm{Our\ Method}$',ms=7)
 pylab.plot([20,200,2000,20000],chi_vlct,'-k',lw=2)
-pylab.plot([20,200,2000,20000],chi_vlct,'sk',label='$Velocity$',ms=7)
+pylab.plot([20,200,2000,20000],chi_vlct,'sk',label='$\mathrm{Velocity\ Method}$',ms=7)
 pylab.plot([20,200,2000,20000],chi_dens,'-k',lw=2)
-pylab.plot([20,200,2000,20000],chi_dens,'^k',label='$Density$',ms=7)
+pylab.plot([20,200,2000,20000],chi_dens,'^k',label='$\mathrm{Density\ Method}$',ms=7)
 pylab.xscale('log')
 pylab.yscale('log')
-pylab.legend(loc=3)
-pylab.xlabel('$\mathrm{Number\ of\ particles}$',fontsize=20)
-pylab.ylabel('$\mathrm{\\xi}$',fontsize=20)
+pylab.legend(loc=3, scatterpoints=1, prop={'size':20})
+pylab.xlabel('$\mathrm{Number\ of\ particles}$',fontsize=25)
+pylab.ylabel('$\mathrm{\langle|D|\\rangle}$',fontsize=25)
[…]

### 2015-01-24 paper/article.tex
quitando notas viejas
solved issue

@@
 \label{sec:data}
-\begin{figure*}
+\begin{figure}
   \begin{center}
-  \includegraphics[width=0.99\textwidth]{mass-density-velocity.pdf}
+    \includegraphics[width=0.48\textwidth]{mass-velocity.pdf}
   \end{center}
-\caption{Comparison between the obtained concentrations by the three methods
+  \caption{Comparison between the obtained concentrations by our method and the velocity method
   \label{fig:mdv}}
-\end{figure*}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.48\textwidth]{mass-density.pdf}
+  \end{center}
+  \caption{Comparison between the obtained concentrations by our method and the density method
+  \label{fig:mdv}}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.48\textwidth]{density-velocity.pdf}
+  \end{center}
+  \caption{Comparison between the obtained concentrations by the density method and the velocity method
+  \label{fig:mdv}}
+\end{figure}
 
@@
 
-\verb"http://adsabs.harvard.edu/abs/2014ApJ...795..163U"
-\verb"http://adsabs.harvard.edu/abs/2012ApJS..199...25P" Figura 3!
 \end{document}

### 2015-01-24 data/results/MDmini/compare.py

@@ -48,13 +48,13 @@ bins_dens,median_dens,quar1_dens,quar2_dens = get_stats(np.log10(m_dens),c_dens)
 
 fig, ax1 = pylab.subplots()
 
-ax1.plot(10**(bins_dens)*dm,median_dens,'-g',lw=2,label='$\mathrm{Density}$')
+ax1.plot(10**(bins_dens)*dm,median_dens,'-g',lw=2,label='$\mathrm{Density\ Method}$')
 ax1.fill_between(10**(bins_dens)*dm,quar1_dens,quar2_dens,color='g',alpha=0.4)
 
-ax1.plot(10**(bins_mcmc)*dm,median_mcmc,'-r',lw=2,label='$\mathrm{Mass}$')
+ax1.plot(10**(bins_mcmc)*dm,median_mcmc,'-r',lw=2,label='$\mathrm{Our\ Method}$')
 ax1.fill_between(10**(bins_mcmc)*dm,quar1_mcmc,quar2_mcmc,color='r',alpha=0.4)
 
-ax1.plot(10**(bins_vel)*dm,median_vel,'-b',lw=2,label='$\mathrm{Velocity}$')
+ax1.plot(10**(bins_vel)*dm,median_vel,'-b',lw=2,label='$\mathrm{Velocity\ Method}$')
 ax1.fill_between(10**(bins_vel)*dm,quar1_vel,quar2_vel,color='b',alpha=0.4)
 
 ax1.legend(loc=1, borderaxespad=0.5)
@@ -75,40 +75,41 @@ pylab.savefig('concentration.pdf',dpi=300)
 pylab.close()
 
 
-fig, (ax1,ax2,ax3) = pylab.subplots(1,3)
-
+fig, ax1 = pylab.subplots()
 ax1.scatter(c_mcmc,c_vel,c='k',alpha=0.1)
 ax1.plot(c_mcmc,c_mcmc,'-r',alpha=0.4,lw=2)
 ax1.set_xlim(xmin=np.amin(c_vel),xmax=np.amax(c_mcmc))
 ax1.set_ylim(ymin=np.amin(c_vel),ymax=np.amax(c_mcmc))
-ax1.set_xlabel("$\mathrm{Mass\ Method}$",fontsize=15)
-ax1.set_ylabel("$\mathrm{Velocity\ Method}$",fontsize=15)
+ax1.set_xlabel("$\mathrm{Concentration\ (Our\ Method)}$",fontsize=15)
[…]

### 2015-01-24 data/results/MDmini/compare.py
corrected font mistake

@@ -80,8 +80,8 @@ ax1.scatter(c_mcmc,c_vel,c='k',alpha=0.1)
 ax1.plot(c_mcmc,c_mcmc,'-r',alpha=0.4,lw=2)
 ax1.set_xlim(xmin=np.amin(c_vel),xmax=np.amax(c_mcmc))
 ax1.set_ylim(ymin=np.amin(c_vel),ymax=np.amax(c_mcmc))
-ax1.set_xlabel("$\mathrm{Concentration\ (Our\ Method)}$",fontsize=15)
-ax1.set_ylabel("$\mathrm{Concentration\ (Velocity\ Method)}$",fontsize=15)
+ax1.set_xlabel("$\mathrm{Concentration\ (Our\ Method)}$",fontsize=25)
+ax1.set_ylabel("$\mathrm{Concentration\ (Velocity\ Method)}$",fontsize=25)
 ax1.set_xscale('log')
 ax1.set_yscale('log')
 pylab.savefig('mass-velocity.pdf',dpi=200,bbox_inches='tight')

### 2015-01-26 paper/article.tex
abstract, mergerd figure 1 and figure 4

@@
 \begin{abstract}
-asd
+
+We present a new method to estimate the concentration of dark matter
+halos in N-body simulations. Our method is based on a fit to the
+integrated mass density as a function of halo radius. 
+The advantage of this method is that the full particle information
+without any binning. 
+We test our method both on mock and N-body halos to compare it against
+two popular methods to find concentrations: radial particle binning to
+estimate the density and the maximum radial velocity. 
+Tests on the mock halos show that the accuracy of our method to
+recover input concentrations can achieve $0.1\%$ whil for the maximum
+radial velocity and density methods it is on the order of $0.5\%$ and
+$40\%$ respectively. 
+We also measure the mass-concentration relationship on the N-body data with
+the three methods. With respect to the other two approaches our method
+produces a flatter relationship, while its normalization falls below
+the maximum velocity method and above the density method.
+
 \end{abstract}
@@
 
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{nfw_normalized.pdf}
+  \includegraphics[width=0.48\textwidth]{vel_normalized.pdf}
+\end{center}
+\caption{Dimensionless mass (left) and velocity (right) profiles as a
+  function of the dimensionless radius for different concentration
+  values. \label{fig:profiles}}
+\end{figure*}
+
 \subsection{Density profile}
@@
 
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{nfw_normalized.pdf}
-\end{center}
-\caption{Dimensionless mass profiles as a function of the
-  dimensionless radius for different concentration values.
-    \label{fig:profiles}}
-\end{figure}
-
 \subsection{Circular velocity}
@@
 
-In Figure \ref{fig:velocity} we show the circular velocity profile for the same
-concentrations as in Figure \ref{fig:profiles}.
+In the right panel of Figure \ref{fig:profiles} we show the circular
+velocity profile for the same concentrations as in the left panel of
+Figure \ref{fig:profiles}.
 
@@
 where $x_{\rm max}=2.163$ and the function $f(x)$ was defined in Eq. (\ref{eq:f_NFW}).
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{vel_normalized.pdf}
-\end{center}
-\caption{Dimensionless velocity profiles as a function of the
-  dimensionless radius for different concentration values.
-    \label{fig:velocity}}
-\end{figure}
 
@@
 \end{equation}
-
+%
 where ${\cal{H}}_N$ corresponds to the set of haloes with $N$
@@
 \label{sec:data}
-\begin{figure}
+\begin{figure*}
   \begin{center}
     \includegraphics[width=0.48\textwidth]{mass-velocity.pdf}
-  \end{center}
-  \caption{Comparison between the obtained concentrations by our method and the velocity method
-  \label{fig:mdv}}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
     \includegraphics[width=0.48\textwidth]{mass-density.pdf}
   \end{center}
-  \caption{Comparison between the obtained concentrations by our method and the density method
+  \caption{Comparison between the concentrations measured by our
+    method and the maximum velocity (left) and density (right)
+    methods. The line indicates the equal value between the two
+    techniques.
   \label{fig:mdv}}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.48\textwidth]{density-velocity.pdf}
-  \end{center}
-  \caption{Comparison between the obtained concentrations by the density method and the velocity method
-  \label{fig:mdv}}
-\end{figure}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.90\textwidth]{concentration.pdf}
-\end{center}
-\caption{Mass-concentration relationship for the three different
-  methods used on the same cosmological N-body data. The central lines
-  correspond the median and the shadowed region indicates the
-  quartiles.
-    \label{fig:concentrations}}
 \end{figure*}
@@
 
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.90\textwidth]{concentration.pdf}
+\end{center}
+\caption{Mass-concentration relationship for the three different
+  methods used on the same cosmological N-body data. The central lines
+  correspond the median and the shadowed region indicates the
+  quartiles.
+    \label{fig:concentrations}}
+\end{figure*}
+
 \section{Conclusions}

### 2015-01-26 paper/article.tex
fixed some typos

@@
 halos in N-body simulations. Our method is based on a fit to the
-integrated mass density as a function of halo radius. 
-The advantage of this method is that the full particle information
+integrated mass as a function of halo radius. 
+The main advantage of this method is that it uses the full particle information
 without any binning. 
 We test our method both on mock and N-body halos to compare it against
-two popular methods to find concentrations: radial particle binning to
-estimate the density and the maximum radial velocity. 
+two popular methods to find concentrations: maximum radial velocity
+measurements and radial particle binning to estimate the density.
 Tests on the mock halos show that the accuracy of our method to
-recover input concentrations can achieve $0.1\%$ whil for the maximum
+recover input concentrations can achieve $0.1\%$ while for the maximum
 radial velocity and density methods it is on the order of $0.5\%$ and
 $40\%$ respectively. 
-We also measure the mass-concentration relationship on the N-body data with
-the three methods. With respect to the other two approaches our method
-produces a flatter relationship, while its normalization falls below
-the maximum velocity method and above the density method.
+We also measure the mass-concentration relationship on the N-body
+data. With respect to the other two approaches our method produces a
+flatter relationship, while its normalization falls below the maximum
+velocity method and above the density method.
 
@@
 universal; independent of the cosmological parameters and self-similar
-for different spatial scapes after an addecuate re-scaling is
-appplied.
+for different spatial scales after an adequate re-scaling is
+app plied.
 
-One the most commong parameterization of this density is known as the
+One the most common parameterization of this density is known as the
 Navarro-Frenk-White (NFW) profile \citep{NFW}. This profile is a
@@
 The relationship between halo mass and concentration is in principle
-accesible to observations and provides a potential test of LCDM on
+accessible to observations and provides a potential test of LCDM on
 galactic scales. With this promise a great deal of effort has been
@@
 From the computational point of view there are two main methods to
-estimate the concetration parameter of a dark matter halo in a N-body
-simulation. The first method takes the particles comprosing the halos
+estimate the concentration parameter of a dark matter halo in a N-body
+simulation. The first method takes the particles composing the halos
 and bins them in logarithmic radii to estimate the density in each
 bin, then it proceeds with a fit of this density estimation as a
-function of radius. A second method uses an analytical property of the
+function of radius. A second method uses an analytic property of the
 NFW that related the maximum of the ratio of the circular velocity to
@@
 concentration value using a Markov Chain Monte Carlo methodology by
-comparing the data against the analytical expectation.
+comparing the data against the analytic expectation.
 
@@
 \ref{sec:method} we present our new method to estimate the halo
-concentration, payin special attention to the bayesian framework to
-find the most probable value and its uncertaintt. In Section
-\ref{sec:halo_sample} we demonstrate the power of our method with two
+concentration, paying special attention to the Bayesian framework to
+find the most probable value and its uncertainty. In Section
+\ref{sec:results} we demonstrate the power of our method with two
 different halo samples; the first one generated under controlled
 conditions and the second taken from a cosmological N-body
-simulation. Next in \ref{sec:discussion} we discuss these results by
-comparing them against other methods to estimate the concentration and
-comment on the consequences for the concentration-mass
-relationship. We present our conclusions in Section \ref{sec:conclusions}.
+simulation to comment on the consequences for the concentration-mass
+relationship. We present our conclusions in Section
+\ref{sec:conclusions}.
 
@@
 this normalized profile always shows a maximum provided that the
-concentration is larger than a values of $c>???$.
+concentration is larger than $c>2$.
 It is possible to show that for the NFW profile the maximum is
@@
 Then, it estimates the density in each logarithmic bin counting the
-particles and divinding by the corresponding shell volume.
+particles and dividing by the corresponding shell volume.
 At this point is is possible to make a direct fit to the density as a
@@
 A second method uses the circular velocity profile.
-As it was shown in Fig. (\ref{fig:velocity}) the circular velocity
-shows a maximum for all profiles with concentration values larger than
-$c>2$.
+As it was shown in the right panel of Figure (\ref{fig:profiles}) the
+circular velocity shows a maximum for all profiles with concentration
+values larger than $c>2$.
 The method finds the value of $x$ for which the normalized circular
@@
 for each particle to ensure spherical symmetry.
-Finally these three spherical coordinates are transformed into cartesian coordinates
+Finally these three spherical coordinates are transformed into Cartesian coordinates
 $(r,\theta,\phi) \rightarrow (x,y,z)$.
 
-We generate in total $400$ mock halos splitted into four different
+We generate in total $400$ mock halos split into four different
 groups of $100$ halos each.
@@
 Figure \ref{fig:results_mocks} shows the integrated distribution for
-$D$ for the fits using our method, splitted into four different groups
+$D$ for the fits using our method, split into four different groups
 according the particle number.
@@
 geometrical center (where no particle sits by construction) used to
-generate the halo.  Poissonian noise makes this center fluctuate,
-changing the numerical radial profile from the analytical input.
+generate the halo.  Poisson noise makes this center fluctuate,
+changing the numerical radial profile from the analytic input.
 
-For particle number of $20$ the offset betwen the input and output
+For particle number of $20$ the offset between the input and output
 concentration can be as large as $20\%$, with a slight bias around
@@
 
-Using this dataset we also compare our method against the other two
+Using this data-set we also compare our method against the other two
 methods described earlier: using shells to estimate the density as a
@@
 In the first case we use the same Metropolis-Hastings algorithm we
-have in our methot to fit the density profile.
+have in our method to fit the density profile.
 In the second method we simply follow the procedure described in
@@
 approximately as $\avg{|D|}\propto N^{-1/2}$, which reinforces the hint that
-the accuracy of the method is related to a decrease of Poissonian
+the accuracy of the method is related to a decrease of Poisson
 noise.
@@
 of all methods.
-Its average values $\avg{|D|}$ are always between $30\%$ adn $50\%$
+Its average values $\avg{|D|}$ are always between $30\%$ and $50\%$
 regardless of the particle number. {\bf Necesitamos entender el
@@
 The FoF algorithm used with a linking length of $0.17$ times the average
-interparticle distance. This choice translates into an overdensity
+inter-particle distance. This choice translates into an overdensity
 $\Delta_h\sim 400-700$ dependent on the halo concentration
@@
   quartiles.
-    \label{fig:concentrations}}
+    \label{fig:concentration}}
 \end{figure*}

### 2015-02-08 src/AnotherPaperPlots.py
added dv/dx plots

@@ -1,7 +1,7 @@
 import pylab, numpy as np, nfw, matplotlib
 
-r = np.arange(0,1,0.001)
-C = np.linspace(1,20,4)
+r = np.linspace(0,1,1000)
+C = [1,2,6,12,20]
 
 for c in C:
     c = int(c)
@@ -19,12 +19,45 @@ pylab.close()
 
 for c in C:
     c = int(c)
-    pylab.plot(r,np.sqrt(nfw.mass_norm(r,c)/r),color='black',lw = .2*c+1,label="$c="+str(c)+"$")
+    pylab.plot(r,nfw.velocity_norm(r,c),color='black',lw = .2*c+1,label="$c="+str(c)+"$")
 pylab.legend(loc=0, scatterpoints=1, prop={'size':20})
 filename = 'vel_normalized'
 matplotlib.rcParams.update({'font.size': 18})
 pylab.xlabel('$x$',fontsize=20)
 pylab.ylabel('$v(<x)$',fontsize=20)
+pylab.savefig(filename+'.eps',transparent=True)
+pylab.savefig(filename+'.pdf',transparent=True)
+pylab.savefig(filename+'.png',transparent=True)
+pylab.close()
+
+for c in C:
+    c = int(c)
+    dv_dx = (nfw.velocity_norm(np.delete(r,0),c)-nfw.velocity_norm(np.delete(r,-1),c))/(r[1]-r[0])
+    pylab.plot(np.delete(r,0),dv_dx,color='black',lw = .2*c+1,label="$c="+str(c)+"$")
+pylab.legend(loc=0, scatterpoints=1, prop={'size':20})
+filename = 'dv_dx'
+matplotlib.rcParams.update({'font.size': 18})
+pylab.xlabel('$x$',fontsize=20)
+pylab.ylabel('$dv/dx$',fontsize=20)
+pylab.yscale('log')
+pylab.ylim(ymin=1E-2)
+pylab.savefig(filename+'.eps',transparent=True)
+pylab.savefig(filename+'.pdf',transparent=True)
+pylab.savefig(filename+'.png',transparent=True)
+pylab.close()
+
+def f(x,c):
+    return ((2*c*x+1)*x*c/(c*x+1)**2 - np.log(c*x+1))
+c = np.linspace(1,20,1000)
+X,Y = pylab.meshgrid(r,c)
+
[…]

### 2015-02-08 src/nfw.py

@@ -20,6 +20,9 @@ def mass_norm(r_norm,c):
 def density_norm(r_norm,c):
     return ((1+c)**2/(r_norm*(1+r_norm*c)**2))
 
+def velocity_norm(r_norm,c):
+    return np.sqrt(mass_norm(r_norm,c)/r_norm)
+
 # Profiles in logarithmic scale
 # Parameters:
 #     logr: numpy array with the logarithm of the radial distances from the center of the halo
@@ -54,5 +57,5 @@ def loglogdensity(logr,loga,logb):
 def loglogmass_norm(logr_norm,logc):
     return np.log((np.log(1.0+np.exp(logr_norm+logc))-np.exp(logr_norm+logc)/(1.0+np.exp(logr_norm+logc)))/(np.log(1.0+np.exp(logc))-np.exp(logc)/(1.0+np.exp(logc))))
 
-def loglogdensity_norm(logr_norm,logc):    
+def loglogdensity_norm(logr_norm,logc):
     return 2.0*(np.log(1.0+np.exp(logc))-np.log(1.0+np.exp(logr_norm+logc)))-logr_norm

### 2015-02-23 paper/article.tex
added dv/dx plots
buen acuerdo a altas masas

@@
 
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{dv_dx.pdf}
+  \includegraphics[width=0.48\textwidth]{zeros.pdf}
+\end{center}
+\caption{Dimensionless derivative of the velocity profile as a
+  function of the dimensionless radius for different concentration
+  values. \label{fig:profiles}}
+\end{figure*}
+
 \subsection{Density profile}
@@
 v(<x)=\sqrt{\frac{1}{A}\left[\frac{\ln\left(1+xc\right)}{x}-\frac{c}{xc+1}\right]},
+\end{equation}
+
+\begin{equation}
+\frac{dv}{dx}=\frac{1}{A}\frac{\frac{2cx+1}{\left(cx+1\right)^{2}}cx-\log\left(cx+1\right)}{2x^{2}v\left(x\right)}
 \end{equation}
@@
 velocity method and above the density.
+We also note that at high masses ($M>10^{14}\hMsun$) our method 
+and the velocity method show a reasonable agreement within the
+uncertainties.
 

### 2015-02-23 paper/article.tex
nueva grafica de velocity-density method

@@
   \begin{center}
-    \includegraphics[width=0.48\textwidth]{mass-velocity.pdf}
-    \includegraphics[width=0.48\textwidth]{mass-density.pdf}
+    \includegraphics[width=0.33\textwidth]{mass-velocity.pdf}
+    \includegraphics[width=0.33\textwidth]{mass-density.pdf}
+    \includegraphics[width=0.33\textwidth]{density-velocity.pdf}
   \end{center}
   \caption{Comparison between the concentrations measured by our
-    method and the maximum velocity (left) and density (right)
+    method and the maximum velocity (left) and density (middle)
     methods. The line indicates the equal value between the two
-    techniques.
+    techniques. The right panel compares the results of the maximum
+    velocity and density methods.
   \label{fig:mdv}}

### 2015-02-23 paper/article.tex
new references added to the intro

@@
 \newcommand{\mnras}{MNRAS}
+\newcommand{\jcap}{JCAP}
 \newcommand{\mnrassub}{MNRAS accepted}
@@
 dominated universes, yielding valuable insights on the large scale
-structure formation process as depicted in observations.
+structure formation process as depicted in observations
+\citep{Springel2005,2011ApJ...740..102K}.
 
@@
 which in a first approximation is spherical symmetric and only
-dependent on the radial coordinate. These profiles seem to be
-universal; independent of the cosmological parameters and self-similar
-for different spatial scales after an adequate re-scaling is
-app plied.
+dependent on the radial coordinate. These profiles seem to be to a
+very good approximation universal \citep{NFW,Taylor2001}; independent
+of the cosmological parameters and self-similar for different spatial
+scales after an adequate re-scaling is applied.
 
@@
 scale radius and the virial radius of the halo $R_v$ is known as the
-concentration $c=R_V/r_s$, a quantity that has been found to be
+concentration $c=R_v/r_s$, a quantity that has been found to be
 correlated with the halo mass.
+
+In spite of the fact that high resolution simulations of
+Milky Way sized dark matter halos \citep{Navarro2010} show that the
+universality property is not  perfect and that a better fitting
+parameterization to the radial density profile is provided by the
+Einasto profile \citep{Einasto1965}, the NFW and its concentration
+have become a standard and useful way to describe the structure of
+dark matter halos.
 
@@
 accessible to observations and provides a potential test of LCDM on
-galactic scales. With this promise a great deal of effort has been
-invested in calibrating this relationship with simulations but also
-finding the best possible way to constraint it with observations.
+galactic scales. 
+With this promise a great deal of effort has been
+invested in calibrating this relationship with simulations
+\citep{Neto2007,Duffy2008,Munoz2011,Prada2012,Ludlow2014} but also
+finding the best possible way to constraint it with observations
+\citep{Buote2007,Comerford2007,Mandelbaum2008,Giocoli2014,Foex2014,Shan2015}.
 

### 2015-02-23 paper/article.tex
finished solving minor issues

@@
 M(<r) = 4\pi\rho_c\delta_c  r_s^3\left[\ln \left
-  (\frac{r_s+r}{r}\right) - \frac{r}{r_s+r}\right].
+  (\frac{r_s+r}{r_s}\right) - \frac{r}{r_s+r}\right].
 \end{equation}
@@
 \end{equation}
-where $x_{\rm max}=2.163$ and the function $f(x)$ was defined in Eq. (\ref{eq:f_NFW}).
+where $x_{\rm max}=2.163$ \citep{Klypin2014} and the function $f(x)$
+was defined in Eq. (\ref{eq:f_NFW}).
 
@@
 Inside each group the halos have random concentration values in
-the range $1<c<20$ with a flat distribution.
+the range $1<c<20$ with a uniform distribution.
 For all these halos with find the concentration values using the
@@
 \citep{More2011}.
-Finally, for each FoF halo we select from all the particles that
+Finally, for each FoF halo we select all the particles that
 belong to it.

### 2015-02-23 src/potential.c
reduced potential calculation time by two

@@ -21,7 +21,7 @@ int main(int argc, char** argv){
  double* k;
  FILE *rfile;
  FILE *cfile;
- 
+
  n_points = count_lines(argv[1]);
 
  rfile = fopen(argv[1], "r");
@@ -34,20 +34,19 @@ int main(int argc, char** argv){
 
  for (i = 0; i < n_points; i ++){
    fscanf(rfile,"%lf,%lf,%lf\n",&(x[i]),&(y[i]),&(z[i]));
+   k[i] = 0;
  }
- 
+
 for (i = 0; i < n_points; i ++){
-   count = 0.0;
-   for (j = 0; j < n_points; j ++){
-     if(i != j){
-       count += 1.0/sqrt(pow(x[i]-x[j],2.0) + pow(y[i]-y[j],2.0) + pow(z[i]-z[j],2.0)); 
-     }
-    k[i] = count;  
+   for (j = i+1; j < n_points; j ++){
+     count = 1.0/sqrt(pow(x[i]-x[j],2.0) + pow(y[i]-y[j],2.0) + pow(z[i]-z[j],2.0));
+     k[i] += count;
+     k[j] += count;    
    }
  }
  for (i = 0; i < n_points; i ++){
    fprintf(cfile,"%lf\n",k[i]);
- } 
+ }
 }
 
 // Counts lines of a file, copied from github.com/forero/ComputationalPhysicsUniandes repository
@@ -71,7 +70,7 @@ int count_lines(char *filename){
       n_lines++;
     }
   }while(c!=EOF);
-  
+
   rewind(in);
   fclose(in);
   return n_lines;

### 2015-02-23 src/main.py
removed unused libraries from main

@@ -1,5 +1,4 @@
-import numpy as np, pylab, math, sys, timeit, os, random, datetime, nfw, mcmc,fit , plotter, multiprocessing, time
-from scipy.optimize import fsolve
+import numpy as np, pylab, sys, os, datetime, nfw, mcmc, plotter, multiprocessing, time
 
 # Gets the concentration and virial radius for several haloes
 
@@ -8,7 +7,7 @@ config[-1] = config[-1].replace('\n','')
 
 processes = int(config[5])
 now = datetime.datetime.now().strftime("%Y-%m-%d-%H:%M:%S")
-mass_element = 1.0   
+mass_element = 1.0
 plt = 1
 total_list = os.listdir(str(config[0]))
 len_list = len(total_list)
@@ -21,12 +20,12 @@ if (config[7]=='0'):
 else:
     print 'Plotting mode enabled'
     plt = 1
-    
+
 if config[8]=='0':
     print 'Test mode disabled'
 else:
     print 'Test mode enabled'
- 
+
 os.system('mkdir mass_'+now)
 sys.stdout.write('\rCompiling the code used to calculate the center of each halo... ')
 sys.stdout.flush()
@@ -72,7 +71,7 @@ def run(directories,process_number):
 
     # Gets the radial distance from the new origin to each particle and sorts it
         r_values = np.sort(np.sqrt((x-x_center)**2 + (y-y_center)**2 + (z-z_center)**2), kind='quicksort')
-    
+
     # Removes the files used by "potential.out"
         os.system('rm '+potential_name+' '+positions_name)
 
@@ -97,7 +96,7 @@ def run(directories,process_number):
         else:
             r_vir = radius[-1]
             vir_index = len(avg_density)-1
-            
+
     # Removes the particles that have a greater radius than the virial radius
         mass = np.resize(mass,vir_index+1)
         radius = np.resize(radius,vir_index+1)
@@ -107,14 +106,14 @@ def run(directories,process_number):
         radius = radius/radius[-1]
 
     # Does the Metropolis algorithm in order to find the concentration
-        
+
         n_iterations = int(config[6])
 
         step = np.array([np.log(1.03)])
         guess = np.array([np.log(10)])
         reest = [lambda x: x >= 0]
 
-        chi_2 = lambda p : mcmc.chi2(p,nfw.loglogmass_norm,np.log(radius),np.log(mass),np.ones(len(radius)))    
[…]

### 2015-04-17 paper/article.tex
minor changes in .tex

@@
-\documentclass[useAMS,usenatbib]{mn2e}
-\usepackage{float}
-\usepackage{amsmath}
-\usepackage{amssymb}
+\documentclass{emulateapj}
+\submitted{{\it Submitted for publication in ApJ}}
+\usepackage{multirow,color,wrapfig,ulem}
+\usepackage {graphicx}
 \usepackage{graphics}
-\usepackage{graphicx}
-\usepackage{epsfig}
-\usepackage{hyperref}
-\def\be{\begin{equation}}
-\def\ee{\end{equation}}
-\def\ba{\begin{eqnarray}}
-\def\ea{\end{eqnarray}}
-
-% To highlight comments
-\usepackage{color}
-\definecolor{red}{rgb}{1,0.0,0.0}
-\newcommand{\red}{\color{red}}
-\definecolor{blue}{rgb}{0.1,0.3,0.9}
-\newcommand{\blue}{\color{blue}}
-
-\usepackage[normalem]{ulem}
-\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
-
-\newcommand{\documentname}{paper~}
-\newcommand{\LCDM}{$\Lambda$CDM~}
-\newcommand{\beq}{\begin{eqnarray}}
-\newcommand{\eeq}{\end{eqnarray}}
-\newcommand{\zz}{$z\sim 3$}
-
-\newcommand{\apj}{ApJ}
-\newcommand{\apjs}{ApJS}
-\newcommand{\apjl}{ApJL}
-\newcommand{\aj}{AJ}
-\newcommand{\mnras}{MNRAS}
+\usepackage[dvips]{epsfig}
+\bibliographystyle{apj}
 \newcommand{\jcap}{JCAP}  
-\newcommand{\mnrassub}{MNRAS accepted}
-\newcommand{\aap}{A\&A}
-\newcommand{\aaps}{A\&AS}
-\newcommand{\araa}{ARA\&A}
-\newcommand{\nat}{Nature}
-\newcommand{\physrep}{PhR}
-\newcommand{\pasp}{PASP}
-\newcommand{\pasj}{PASJ}
 \newcommand{\avg}[1]{\langle{#1}\rangle}  
-\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
+\newcommand{\nscatt}{\langle N_{\rm  scatt}\rangle}
+\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
 \newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}   
@@
 \newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
-        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$~}\fi}}
+        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
 \newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
@@
 \newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
-\newcommand{\lya}{{Lyman$\alpha$~}}
+\newcommand{\lya}{{Lyman $\alpha$~}}
 \newcommand{\clara}{{\texttt{CLARA}}~}
@@
 \newcommand{\hs}{{\hspace{1mm}}}  
-\newcommand{\muavg}{\vert\langle\cos\theta\rangle\vert}
+\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
 % definition to produce a "less than or similar to" symbol
 \def\lsim{~\rlap{$<$}{\lower 1.0ex\hbox{$\sim$}}}
-
 % definition to produce a "greater than or similar to" symbol
 \def\gsim{~\rlap{$>$}{\lower 1.0ex\hbox{$\sim$}}}
-
+%@arxiver{fig3.pdf,fig11a.pdf, fig11b.pdf} 
 \begin{document}
 
-\title[A new method for concentrations]{A new method to estimate
-  dark matter halo concentrations}
-\author[Poveda \& Forero-Romero]{
-\parbox[t]{\textwidth}{\raggedright
-  Christian Poveda$^{1}$ \&
-  Jaime E. Forero-Romero$^{1}$
-}
-\vspace*{6pt}\\
-$^{1}$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
-No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
-}
-\maketitle
+\title{A new method to estimate dark matter halo concentrations}
+\shorttitle{New method to estimate concentrations}
 
+\shortauthors{Poveda \& Forero-Romero}
+
+\author{Christian Poveda, Jaime E. Forero-Romero}
+\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
+No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
+\email{cn.poveda542@uniandes.edu.co}
+\email{je.forero@uniandes.edu.co}
+
+\keywords{ methods: numerical --- galaxies: halos --- cosmology: theory --- dark
+matter}
 \begin{abstract}
@@
 We present a new method to estimate the concentration of dark matter
-halos in N-body simulations. Our method is based on a fit to the
-integrated mass as a function of halo radius.
+halos in N-body simulations. 
+Our method is based on a fit to the integrated mass as a function of
+halo radius.  
 The main advantage of this method is that it uses the full particle information
@@
 We also measure the mass-concentration relationship on the N-body
-data. With respect to the other two approaches our method produces a
+data. 
+With respect to the other two approaches our method produces a
 flatter relationship, while its normalization falls below the maximum
 velocity method and above the density method.
-
 \end{abstract}
-\begin{keywords}
-methods: numerical, galaxies: haloes, cosmology: theory, dark
-matter
-\end{keywords}
 
@@
 
-\bibliographystyle{mn2e}
 \bibliography{references}

### 2015-04-20 paper/article.tex
edits in the introduction

@@
 \label{sec:introduction}
-In the concordance cosmology paradigm the the matter content of the
-Universe is dominated by dark matter which behaves as a collisionless
-fluid under the influence of gravity. In the last three decades
-numerical experiments have made possible the simulation of dark matter
-dominated universes, yielding valuable insights on the large scale
-structure formation process as depicted in observations
+In the concordance cosmology paradigm the matter content of the
+Universe is dominated by dark matter, a collisionless fluid shaped by
+gravitational interactions.
+In the last three decades numerical experiments have made possible the
+simulation of dark matter dominated universes, yielding valuable
+insights on the large scale structure formation process.
+This description shows a remarkable success in comparisons against
+observations of galaxy distributions on large scales
 \citep{Springel2005,2011ApJ...740..102K}.
 
-One of the most striking results of these simulations is that dark
-matter clumps on galactic scales follow a universal density profile
-which in a first approximation is spherical symmetric and only
-dependent on the radial coordinate. These profiles seem to be to a
-very good approximation universal \citep{NFW,Taylor2001}; independent
-of the cosmological parameters and self-similar for different spatial
-scales after an adequate re-scaling is applied.
+Regarding the small scale dark matter distribution, one of the most
+striking results of these simulations is that dark matter overdensities
+follow a universal density profile.
+In a first approximation this profile is spherically symmetric and its
+density only dependens on the radial coordinate. 
+The universality of this profiles seems to be independent of the
+cosmological parameters and self-similar for different spatial scales
+after an adequate re-scaling is applied.  
+\citep{NFW,Taylor2001}
 
-One the most common parameterization of this density is known as the
-Navarro-Frenk-White (NFW) profile \citep{NFW}. This profile is a
-double power law in radius, where the transition between the two
-happens at the so-called scale radius $r_s$. The ratio between the
-scale radius and the virial radius of the halo $R_v$ is known as the
-concentration $c=R_v/r_s$, a quantity that has been found to be
-correlated with the halo mass.
+One the most popular parameterization for a halo radial density
+distribution is known as the Navarro-Frenk-White (NFW) profile
+\citep{NFW}. 
+This profile is a  double power law in radius, where the transition
+between the two happens at the so-called scale radius $r_s$. 
+The ratio between the scale radius and the virial radius of the halo
+$R_v$ is known as the concentration $c=R_v/r_s$. 
+Simulations also show that the concentration is a function of halo
+mass.
 
-In spite of the fact that high resolution simulations of
-Milky Way sized dark matter halos \citep{Navarro2010} show that the
-universality property is not  perfect and that a better fitting
-parameterization to the radial density profile is provided by the
-Einasto profile \citep{Einasto1965}, the NFW and its concentration
-have become a standard and useful way to describe the structure of
-dark matter halos.
+High resolution simulations of Milky Way sized dark matter halos
+\citep{Navarro2010} show that the universality property is not
+perfect and that a better fitting parameterization to the radial
+density profile is provided by the Einasto profile
+\citep{Einasto1965}.
+However, the NFW density profile and its concentration have become a
+standard metric to describe the structure of dark matter
+halos.
 
-The relationship between halo mass and concentration is in principle
-accessible to observations and provides a potential test of LCDM on
-galactic scales. 
+Observationally, the relationship between halo mass and concentration
+could provides a potential test of LCDM on galactic scales. 
 With this promise a great deal of effort has been
@@
 estimate the concentration parameter of a dark matter halo in a N-body
-simulation. The first method takes the particles composing the halos
+simulation. 
+The first method takes the particles composing the halos
 and bins them in logarithmic radii to estimate the density in each
 bin, then it proceeds with a fit of this density estimation as a
-function of radius. A second method uses an analytic property of the
-NFW that related the maximum of the ratio of the circular velocity to
-the virial velocity. In this method at each particle radius this ratio
-is estimated to find the maximum value for this ratio; this value is
-used to find the roots of an equation which represent the
-concentration parameter.
+function of the radius. 
+A second method uses an analytic property of the
+NFW that relates the maximum of the ratio of the circular velocity to
+the virial velocity. 
+In this method the user estimates this ratio as a function of radius
+to determine its maxium value.
+Then, the user can take this value to find the roots of an equation
+which represent the concentration parameter.
 
-The first method although is straightforward to apply has two main
-disadvantages. First of all it requires a large number of particles in
-order to have a proper density estimate in each bin. For a very low
-number of particles is hard to define a large number of bins to
-proceed with the fit. The second problem is that, as in any process
-involving data binning, there is not an way to estimate the optimal
-bin size, which in turn can affect the results of the fit.
+The first method is straightforward to apply, but it has two 
+disadvantages. 
+First, it requires a large number of particles in
+order to have a proper density estimate in each bin. 
+This makes the method robust only when halos with at least  $10^3$
+particles are fitted.
+The second problem is that there is not a way to estimate the optimal
+bin size.
+Different choices affect the results of the fit.
 
-The second method solves the two problems mentioned above. It works
-with low particles numbers and does not involve data binning. However,
-it effectively takes into account a single data point and discards the
-behaviour of the ratio $V_{cirv}/V_{vir}$ below and above its
-maxima.
+The second method solves the two problems mentioned above. 
+It works with low particles numbers and does not involve data
+binning. 
+However, it effectively takes into account only a single data point
+and discards the behaviour of the ratio $V_{\rm circ}/V_{\rm vir}$ below and
+above its maxima. 
+Additionally, small fluctuations on the value of this maximum can
+yield large perturbations on the estimated concentration parameter.
+
+%%%
 

### 2015-04-22 paper/article.tex
finished first pass on in the introduction

@@
 
+In this paper we propose a new method to estimate the dark matter halo
+concentration in halos obtained in numerical simulations. 
+It consists in building the cumulative mass profile from the
+particle data in the N-body simulation to find the best possible
+concentration value using a Markov Chain Monte Carlo (MCMC)
+methodology by comparing the data against the analytic expectation.
+
+Our proposal has two advantages with respect to the two methods mentioned
+above. 
+First, it does not involve data binning. 
+Second, it does not throw away data points. 
+Furthermore, the MCMC approach allows for an straightforward
+estimation of the uncertainties in the concentration parameter, and
+inclusion of informative priors.
+
 %%%
-
-In this paper we propose a new method to estimate the dark matter halo
-concentration from N-body simulation results. This method has two
-advantages with respect to the methods mentioned above. First, it does
-not involve data binning. Second, it does not throw away data
-points. Third, it allows for an straightforward estimation of the
-uncertainties in the concentration parameter.
-
-Our method consists in building the cumulative mass profile from the
-particle data in the N-body simulation to find the best possible
-concentration value using a Markov Chain Monte Carlo methodology by
-comparing the data against the analytic expectation.
-
-This paper is structured as follows. In Section \ref{sec:basics} we
-review the basic properties of the NFW density profile and define the
-basic notation for the rest of the paper. Next in Section
-\ref{sec:method} we present our new method to estimate the halo
-concentration, paying special attention to the Bayesian framework to
-find the most probable value and its uncertainty. In Section
-\ref{sec:results} we demonstrate the power of our method with two
-different halo samples; the first one generated under controlled
-conditions and the second taken from a cosmological N-body
-simulation to comment on the consequences for the concentration-mass
-relationship. We present our conclusions in Section
-\ref{sec:conclusions}.
 

### 2015-08-20 paper/article.tex
new density test
rewritten the error part

@@
 
-We use a Metropolis-Hastings algorithm to sample the likelihood
+We use an Affine Invariant Markov chain Monte Carlo implemented in the python
+module emcee by FIXME (dfm et al) to sample the likelihood
 function distribution defined by ${\cal L}(c)=\exp(-\chi^2(c)/2)$
@@
 
-For the walk in the Metropolis-Hastings algorithm we used 50000 steps
-where each step was randomly generated with a normal distribution
-centered around the last step with an standard deviation of
-$\sigma=0.03$.
-From the $\chi^2$ distribution we find the optimal value of the
+For the walk in the MCMC algorithm we used the default emcee parameters which
+are optimal. From the $\chi^2$ distribution we find the optimal value of the
 concentration and  its associated uncertainty.
@@
 function of radius and the maximum circular velocity method.
-In the first case we use the same Metropolis-Hastings algorithm we
+In the first case we use the same MCMC algorithm we
 have in our method to fit the density profile.
@@
 concentration.
-At fixed particle numbers our method always shows the lowest
+
+At fixed particle numbers our method almost always shows the lowest
 $\avg{|D|}$ values compared to the other two methods.
@@
 
-The second best accuracy is achieved by the method based on the
-maximum of the circular velocity.
-It also shows a similar behaviour $\avg{|D|}\propto N^{-1/2}$.
-Its accuracy is $2-5$ times less than in our method, on the order of
-$20\%$ for $20$ particle halos and $0.5\%$ for $20000$ particle halos.
-The method based on the direct density fit shows the lowest accuracy
-of all methods.
-Its average values $\avg{|D|}$ are always between $30\%$ and $50\%$
-regardless of the particle number. {\bf Necesitamos entender el
-  comportamiento de esto.}
+The method based on the maximum of the circular velocity shows a similar
+behaviour $\avg{|D|}\propto N^{-1/2}$. Its accuracy is $2-5$ times less
+than in our method, on the order of $20\%$ for $20$ particle halos and
+$0.5\%$ for $20000$ particle halos. The method based on the direct density
+fit shows the an intermediate accuracy between the other two methods.
 

### 2015-08-20 paper/article.tex
small corrections
added plots about the impact of the input concentration

@@
 \begin{center}
-  \includegraphics[width=0.50\textwidth]{percentual_diff.pdf}
+  \includegraphics[width=0.50\textwidth]{mock_percentual_diff.pdf}
 \end{center}
@@
 
-{\bf Hace falta hacer una figura para este caso.}
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.50\textwidth]{mock_percentual_diff_conc_20.pdf}
+\end{center}
+\caption{Cumulative distribution of the fractional difference, $D$, between
+  the input concentration in the mock halo generator, $c_{in}$ and the
+  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
+  halos generated with an input concentration in a different range for
+  a number of particles $N=20$.
+    \label{fig:results_mocks_conc_20}}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.50\textwidth]{mock_percentual_diff_conc_20000.pdf}
+\end{center}
+\caption{Cumulative distribution of the fractional difference, $D$, between
+  the input concentration in the mock halo generator, $c_{in}$ and the
+  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
+  halos generated with an input concentration in a different range for
+  a number of particles $N=20000$.
+    \label{fig:results_mocks_conc_20000}}
+\end{figure}
+
+{\bf Hace falta discutir las figuras.}
 
@@
 $0.5\%$ for $20000$ particle halos. The method based on the direct density
-fit shows the an intermediate accuracy between the other two methods.
+fit shows the lowest accuracy for a low particle number and an intermediate
+accuracy between the other two methods for a high particle number.
 

### 2015-08-21 paper/article.tex
revised abstract

@@
 \email{je.forero@uniandes.edu.co}
+\author{Juan Carlos Mu\~noz-Cuartas}
+\affil{UdeA, Medell\'in, Colombia}
+\email{xxx@udea.edu.co}
 
@@
 halos in N-body simulations.
-Our method is based on a fit to the integrated mass as a function of
+Our method is based on a fit to the integrated mass profile as a function of
 halo radius.
@@
 Tests on the mock halos show that the accuracy of our method to
-recover input concentrations can achieve $0.1\%$ while for the maximum
-radial velocity and density methods it is on the order of $0.5\%$ and
-$40\%$ respectively.
+recover input concentrations varies with the number of particles in
+the halo. For halos sampled with $20$ particles our method recovers
+the input concentration with $10\%$ accuracy, while for the maximum
+radial velocity and density methods the accuracy is on the order of $20\%$ and
+$100\%$, respectively. For halos samples with $10^4$ particles our
+method achieves an accuracy of $0.01\%$ while the velocity and density
+methods achieve $0.1\%$ and $1\%$ accuracy, respectively.
 We also measure the mass-concentration relationship on the N-body

### 2015-08-21 paper/article.tex
integrated 2 figures

@@
 \label{sec:introduction}
-In the concordance cosmology paradigm the matter content of the
+In the concordance cosmology the matter content of the
 Universe is dominated by dark matter, a collisionless fluid shaped by
@@
 
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.50\textwidth]{mock_percentual_diff_conc_20.pdf}
-\end{center}
+\begin{figure*}
+
+  \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20.pdf}
+  \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20000.pdf}
+
 \caption{Cumulative distribution of the fractional difference, $D$, between
@@
   halos generated with an input concentration in a different range for
-  a number of particles $N=20$.
+  a number of particles $N=20$ (right panel) and $N=20000$ (left panel).
     \label{fig:results_mocks_conc_20}}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.50\textwidth]{mock_percentual_diff_conc_20000.pdf}
-\end{center}
-\caption{Cumulative distribution of the fractional difference, $D$, between
-  the input concentration in the mock halo generator, $c_{in}$ and the
-  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
-  halos generated with an input concentration in a different range for
-  a number of particles $N=20000$.
-    \label{fig:results_mocks_conc_20000}}
-\end{figure}
+\end{figure*}
 

### 2015-08-27 paper/article.tex
revised 3 paragraphs in the intro

@@
 \label{sec:introduction}
-In the concordance cosmology the matter content of the
+In the concordance cosmology paradigm the matter content of the
 Universe is dominated by dark matter, a collisionless fluid shaped by
 gravitational interactions.
-In the last three decades numerical experiments have made possible the
-simulation of dark matter dominated universes, yielding valuable
-insights on the large scale structure formation process.
-This description shows a remarkable success in comparisons against
-observations of galaxy distributions on large scales
+Simulations of dark matter dominated universes during the last three
+decades have provided valuable insights into the large scale structure
+formation process, showing a remarkable success when theoretical
+results are compared against observations of the galaxy distribution
+obtained from large surveys.
 \citep{Springel2005,2011ApJ...740..102K}.
 
-Regarding the small scale dark matter distribution, one of the most
-striking results of these simulations is that dark matter overdensities
-follow a universal density profile.
+On galactic scales the most striking results of these simulations is
+that dark matter overdensities closely follow a universal density
+profile. 
 In a first approximation this profile is spherically symmetric and its
@@
 The universality of this profiles seems to be independent of the
-cosmological parameters and self-similar for different spatial scales
-after an adequate re-scaling is applied.
+cosmological parameters and is self-similar for different spatial
+scales after an adequate re-scaling is applied. 
 \citep{NFW,Taylor2001}
@@
 \citep{NFW}.
-This profile is a  double power law in radius, where the transition
-between the two happens at the so-called scale radius $r_s$.
-The ratio between the scale radius and the virial radius of the halo
-$R_v$ is known as the concentration $c=R_v/r_s$.
-Simulations also show that the concentration is a function of halo
-mass.
+This profile is a  double power law in radius, where the transition break
+happens at the so-called scale radius $r_s$.
+The ratio between the scale radius and the virial radius, $R_v$ which
+defines a natural scale for the halo, is known as the concentration
+$c=R_v/r_s$. 
+Simulations show that the concentration is a strong function of halo mass and
+redshift.
+
+%%%
 

### 2015-09-10 paper/article.tex
minor edits and some new paragraphs

@@
 $\delta_c$ is the halo dimensionless characteristic density and $r_s$
-is known as the scale radius, the radius that marks the transition
+is the scale radius. This radius marks the transition
 between the power law scaling $\rho\propto r^{-1}$ for
@@
 spherical volume that encloses a density of $\Delta_h$ times
-the average density of the Universe. The corresponding mass $M_{v}$,
-the virial mass, can be written as $M_{v} =
-\frac{4\pi}{3}\bar{\rho}\Delta_h r_v^3$.
+the average density of the Universe. 
+The corresponding mass $M_{v}$, the virial mass, can be written as
+$M_{v} = \frac{4\pi}{3}\bar{\rho}\Delta_h r_v^3$.
 
@@
 We start by fixing the desired concentration $c$ and total number of
-particles $N$ in the mock halo
-With this values we define the mass element as $\delta m = 1/M$, corresponding
+particles $N$ in the mock halo.
+With these values we define the mass element as $\delta m = 1/M$, corresponding
 to the mass of each particle such that the total mass is one.
-Then for each particle $i=1,\ldots,N$, we find the value of $r_i$ such that
+Then for each particle, $i=1,\ldots,N$, we find the value of $r_i$ such that
 the difference
@@
 \begin{figure*}
-
   \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20.pdf}
   \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20000.pdf}
-
 \caption{Cumulative distribution of the fractional difference, $D$, between
@@
   a number of particles $N=20$ (right panel) and $N=20000$ (left panel).
-    \label{fig:results_mocks_conc_20}}
+    \label{fig:results_mocks_conc}}
 \end{figure*}
 
-{\bf Hace falta discutir las figuras.}
+Figure \ref{fig:results_mocks_conc} shows the integrared distribution
+for $D$ for the fits using our method, split into different input
+concentrations for two different particle numbers describing the mock
+halos. 
+On the left we have the case of halos sampled with $N=20$ particles
+and on the right we have show results for halos with $N=20000$
+particles. 
+The scale for $D$ varies by almost three orders of magnitude.
+The accuracy of our method increases with larger values of $N$. 
+This was already seen in the previous section. 
+We explore the exact dependence of $D$ with the number of particles in
+the next section when we compare the accuracy of different methods.
 
-\subsubsection{The impact of different methods}
+There are two interesting in Figure \ref{fig:results_mock_conc}. The
+first is that our method tends to underestimate the concentration
+and the second is that the degree of this underestimation increases
+with the input halo concentration.
+
+\subsubsection{The accuracy of different methods}
 
@@
 
-We use data from the MultiDark cosmological simulation.
-It follows the non-linear evolution of a dark matter density field
-sampled with $2048^3$ particles over a cubic box of $1000$ \hMpc on a side.
-The data is publicly available through \url{http://www.cosmosim.org/}.
-More details about the structure of the database and the simulation
-can be found in \citep{2013AN....334..691R}.
+We use data from a N-body cosmological simulation that follows the non
+non-linear evolution of a dark matter density field sampled with
+$512^3$ particles over a cubic box of $400$ \hMpc on a side. 
+This simulation was run with the public available version of the
+Gadget-2 code. 
+The simulation uses a standard $\Lambda$CDM cosmology with values of
+$\Omega_m=0.258$, $\Omega_\Lambda=0.742$ and $h=0.72$ for the matter
+density parameter, cosmological constant parameter and the reduce
+Hubble constant, respectively. 
+With these parameters the mass of an individual simulation particle
+corresponds to $3.41\times 10^{10}$\hMsun.
 
-We build a sample of all halos located in a cubic sub-volume of $100$
-\hMpc on a side centered on the most massive halo in the simulation at
-$z=0$ which corresponds to the \texttt{miniMDR1} tables in the
-database.
-From this sample we select all the halos at $z=0$ detected with a
-Friends-of-Friends (FoF) algorithm with masses in the interval
-$10^{11}\leq M_{\rm FoF}/\hMsun \leq 10^{15}$.
-The FoF algorithm used with a linking length of $0.17$ times the average
-inter-particle distance. This choice translates into an overdensity
-$\Delta_h\sim 400-700$ dependent on the halo concentration
-\citep{More2011}.
-Finally, for each FoF halo we select all the particles that
-belong to it.
+{\bf descripcion del halo finder}
 
-From this set of particles we follow the procedure spelled out in
-Section \ref{sec:method} with $\Delta_h=740$  (corresponding to $200$
-times the critical density) to find the halo concentration.
-This choice makes that our overdensities are fully included inside the
-original FoF particle group.
-We only report results from overdensities with at least $100$ particles.
-Finally, we store the values obtained for the virial radius, virial
-mass and concentration.
+{\bf descripcionde separacion por grado de relajacion}.
 
+{\bf describcion de los resultados}
 Figure \ref{fig:mdv} shows the results that compare the concentration
 values in the simulated halos from the three different methods.
-At zeroth order the results are consistent.
-However, the concentration values from the velocity method produces
-concentrations that are $XXX$ times larger on average than the results
-from our method.
-On the other hand, the concentrations from the velocity method are
-$XXX$ times lower than in our method.
-
-%Running another test with halos whose concentrations vary as a normal
-%distribution of variance ${\sigma}^2$ we found that the concentrations
-%obtained by the method of circular velocity are a 35\% greater than
-%the ones obtained by the density method. However the concentrations
-%obtained by the velocity method are barey higher (around 2\% or 3\%)
-%than the ones obtained by our method. We did not find any significant
-%variation in the concentration values obtained by any method by
-%changing ${\sigma}^2$ in contrast with FIXME.
-
-Figure \ref{fig:concentration} shows the mass-concentration
-relationship from the N-body data with the results of the three
-different methods.
-The central lines correspond the median and the
-shadowed region indicates the quartiles.
-In this relationship our methods represents a compromise between the
-velocity and density methods.
-The slope is flatter and the overall normalization is below the
-velocity method and above the density.
-We also note that at high masses ($M>10^{14}\hMsun$) our method
-and the velocity method show a reasonable agreement within the
-uncertainties.
 

### 2015-09-21 paper/article.tex
minor edits in the introduction

@@
 
-One the most popular parameterization for a halo radial density
-distribution is known as the Navarro-Frenk-White (NFW) profile
+One the most popular parameterization for a dark matter halo radial density
+distribution is the Navarro-Frenk-White (NFW) profile
 \citep{NFW}.
@@
 happens at the so-called scale radius $r_s$.
-The ratio between the scale radius and the virial radius, $R_v$ which
+The ratio between the scale radius and the virial radius $R_v$, which
 defines a natural scale for the halo, is known as the concentration
@@
 Observationally, the relationship between halo mass and concentration
-could provides a potential test of LCDM on galactic scales.
-With this promise a great deal of effort has been
+could provide a potential test of LCDM on galactic scales.
+For this motivation a great deal of effort has been
 invested in calibrating this relationship with simulations
-\citep{Neto2007,Duffy2008,Munoz2011,Prada2012,Ludlow2014} but also
+\citep{Neto2007,Duffy2008,Munoz2011,Prada2012,Ludlow2014} and 
 finding the best possible way to constraint it with observations
@@
 the virial velocity.
-In this method the user estimates this ratio as a function of radius
-to determine its maxium value.
-Then, the user can take this value to find the roots of an equation
-which represent the concentration parameter.
+The concentration can be then found as the root of an algorithmnic
+equation dependent on this maximum value.
 
-The first method is straightforward to apply, but it has two
+The first method is straightforward to apply but presents two
 disadvantages.
@@
 order to have a proper density estimate in each bin.
-This makes the method robust only when halos with at least  $10^3$
-particles are fitted.
+This makes the method robust only for halos with at least  $10^3$
+particles.
 The second problem is that there is not a way to estimate the optimal
-bin size.
-Different choices affect the results of the fit.
+bin size, different choices produce different results for the
+concentration.
 
@@
 concentration in halos obtained in numerical simulations.
-It consists in building the cumulative mass profile from the
-particle data in the N-body simulation to find the best possible
-concentration value using a Markov Chain Monte Carlo (MCMC)
-methodology by comparing the data against the analytic expectation.
+It builds the cumulative mass profile from the particle data in the
+N-body simulation to find the best possible concentration value using
+a Markov Chain Monte Carlo (MCMC) methodology.
 
@@
 above. 
-First, it does not involve data binning.
-Second, it does not throw away data points.
+It does not involve data binning and does not throw away data points.
 Furthermore, the MCMC approach allows for an straightforward

### 2015-09-22 paper/article.tex
starting to write the conclusions

@@
 
+In this paper, we presented a new method to estimate the
+concentration of dark matter halos in N-body simulations. 
+We tested our method on mock halo data to study the impact of total
+number of particles and input concentration on the retrieved values.
+We compared these results against two other methods commonly used in
+the literature to estimate concentrations.
+Finally, we applied our method to halos extracted from a cosmological
+N-body simulation to estimate the impact of our method on the mass
+concentration relationship.
+
+Comparison against other methods.\\
+
+The effect of the number of particles.\\
+
+The effect of the input concentration.\\
+
+The impact on the mass-concentration relationship.\\
+
+Comment and future.\\
+
 \bibliography{references}

### 2015-09-28 paper/article.tex
nuevo parrafo en conclusiones, nuevo orden de las graficas, nuevo apendice

@@
 
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{nfw_normalized.pdf}
-  \includegraphics[width=0.48\textwidth]{vel_normalized.pdf}
-\end{center}
-\caption{Dimensionless mass (left) and velocity (right) profiles as a
-  function of the dimensionless radius for different concentration
-  values. \label{fig:profiles}}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{dv_dx.pdf}
-  \includegraphics[width=0.48\textwidth]{zeros.pdf}
-\end{center}
-\caption{Dimensionless derivative of the velocity profile as a
-  function of the dimensionless radius for different concentration
-  values. \label{fig:profiles}}
-\end{figure*}
-
 \subsection{Density profile}
@@
 
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.75\textwidth]{error.pdf}
+\end{center}
+\caption{Average value of the relative error in the concentration
+  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
+  the set of mock halos. Different symbols represent different
+  methods. Our method provide the most accurate estimate at fixed
+  particle number $N$.
+    \label{fig:error}}
+\end{figure*}
+
 In this Section we present the results of applying our method on two
@@
 
-\subsection{Tests on Mock Halos}
+\subsection{Mock Halos}
 
@@
 
-\subsubsection{The impact of particle number}
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.50\textwidth]{mock_percentual_diff.pdf}
-\end{center}
-\caption{Cumulative distribution of the fractional difference, $D$, between
-  the input concentration in the mock halo generator, $c_{in}$ and the
-  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
-  halos generated with a different number of particles, $N$.
-    \label{fig:results_mocks}}
-\end{figure}
-
-Figure \ref{fig:results_mocks} shows the integrated distribution for
-$D$ for the fits using our method, split into four different groups
-according the particle number.
-From this Figure the first immediate
-conclusion is that increasing the number of particles increases the
-chances to recover the input values.
-
-We believe that the main effect that contributes to this trend
-is that the particle that our algorithm finds to be the halo center
-(where the potential is minimum) gets closer to the original
-geometrical center (where no particle sits by construction) used to
-generate the halo.  Poisson noise makes this center fluctuate,
-changing the numerical radial profile from the analytic input.
-
-For particle number of $20$ the offset between the input and output
-concentration can be as large as $20\%$, with a slight bias around
-$-0.05\%$, i.e. the output concentration is biased towards lower
-values than the input.
-For particle numbers of $2000$ most of the offsets fall below $5\%$,
-with a clear peak around $0\%$ indicating that any appreciable bias is
-absent.
-
-\subsubsection{The impact of the input concentration}
-
-\begin{figure*}
-  \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20.pdf}
-  \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20000.pdf}
-\caption{Cumulative distribution of the fractional difference, $D$, between
-  the input concentration in the mock halo generator, $c_{in}$ and the
-  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
-  halos generated with an input concentration in a different range for
-  a number of particles $N=20$ (right panel) and $N=20000$ (left panel).
-    \label{fig:results_mocks_conc}}
-\end{figure*}
-
-Figure \ref{fig:results_mocks_conc} shows the integrared distribution
-for $D$ for the fits using our method, split into different input
-concentrations for two different particle numbers describing the mock
-halos. 
-On the left we have the case of halos sampled with $N=20$ particles
-and on the right we have show results for halos with $N=20000$
-particles. 
-The scale for $D$ varies by almost three orders of magnitude.
-The accuracy of our method increases with larger values of $N$. 
-This was already seen in the previous section. 
-We explore the exact dependence of $D$ with the number of particles in
-the next section when we compare the accuracy of different methods.
-
-There are two interesting in Figure \ref{fig:results_mock_conc}. The
-first is that our method tends to underestimate the concentration
-and the second is that the degree of this underestimation increases
-with the input halo concentration.
-
 \subsubsection{The accuracy of different methods}
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{error.pdf}
-\end{center}
-\caption{Average value of the relative error in the concentration
-  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
-  the set of mock halos. Different symbols represent different
-  methods. Our method provide the most accurate estimate at fixed
-  particle number $N$.
-    \label{fig:error}}
-\end{figure}
 
@@
 
-\subsection{Tests on N-body data}
+\subsubsection{The impact of particle number}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.50\textwidth]{mock_percentual_diff.pdf}
+\end{center}
+\caption{Cumulative distribution of the fractional difference, $D$, between
+  the input concentration in the mock halo generator, $c_{in}$ and the
+  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
+  halos generated with a different number of particles, $N$.
+    \label{fig:results_mocks}}
+\end{figure}
+
+Figure \ref{fig:results_mocks} shows the integrated distribution for
+$D$ for the fits using our method, split into four different groups
+according the particle number.
+From this Figure the first immediate
+conclusion is that increasing the number of particles increases the
+chances to recover the input values.
+
+We believe that the main effect that contributes to this trend
+is that the particle that our algorithm finds to be the halo center
+(where the potential is minimum) gets closer to the original
+geometrical center (where no particle sits by construction) used to
+generate the halo.  Poisson noise makes this center fluctuate,
+changing the numerical radial profile from the analytic input.
+
+For particle number of $20$ the offset between the input and output
+concentration can be as large as $20\%$, with a slight bias around
+$-0.05\%$, i.e. the output concentration is biased towards lower
+values than the input.
+For particle numbers of $2000$ most of the offsets fall below $5\%$,
+with a clear peak around $0\%$ indicating that any appreciable bias is
+absent.
+
+\subsubsection{The impact of the input concentration}
+
+\begin{figure}
+  \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20.pdf}
+  \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20000.pdf}
+\caption{Cumulative distribution of the fractional difference, $D$, between
+  the input concentration in the mock halo generator, $c_{in}$ and the
+  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
+  halos generated with an input concentration in a different range for
+  a number of particles $N=20$ (right panel) and $N=20000$ (left panel).
+    \label{fig:results_mocks_conc}}
+\end{figure}
+
+Figure \ref{fig:results_mocks_conc} shows the integrared distribution
+for $D$ for the fits using our method, split into different input
+concentrations for two different particle numbers describing the mock
+halos. 
+On the left we have the case of halos sampled with $N=20$ particles
+and on the right we have show results for halos with $N=20000$
+particles. 
+The scale for $D$ varies by almost three orders of magnitude.
+The accuracy of our method increases with larger values of $N$. 
+This was already seen in the previous section. 
+We explore the exact dependence of $D$ with the number of particles in
+the next section when we compare the accuracy of different methods.
+
+There are two interesting in Figure \ref{fig:results_mock_conc}. The
+first is that our method tends to underestimate the concentration
+and the second is that the degree of this underestimation increases
+with the input halo concentration.
+
+\subsection{N-body data}
 \label{sec:data}
@@
 \begin{center}
-  \includegraphics[width=0.90\textwidth]{concentration.pdf}
+  \includegraphics[width=0.75\textwidth]{concentration.pdf}
 \end{center}
@@
 
-Comparison against other methods.\\
+The first benchmark was performed on mock halos generated with known
+concentration values for different particle numbers. 
+For all methods, the accuracy in retrieveing the input concentration
+increases with the number of particles as summarized in Figure \ref{fig:error}.
+Our method systematically shows smaller errors in the retrieved values
+compared to the other two methods, going from $10\%$ for halos with
+$20$ particles down to $0.01\%$ for halos with $2\times 10^4$ particles. 
+In our method the average error on the retrieved values decreases with
+the number of particles as $\langle|D|\rangle\propto N^{-1}$.
+The error in density method initially behaves as $\langle|D|\rangle\propto
+N^{-3/2}$ but at $N=2\times 10^3$ it saturates to $0.1\%$. 
+For the velocity method the error behaves closely to
+$\langle|D|\rangle\propto N^{-1/2}$
 
@@
 
+\appendix
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{nfw_normalized.pdf}
+  \includegraphics[width=0.48\textwidth]{vel_normalized.pdf}
+\end{center}
+\caption{Dimensionless mass (left) and velocity (right) profiles as a
+  function of the dimensionless radius for different concentration
+  values. \label{fig:profiles}}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{dv_dx.pdf}
+  \includegraphics[width=0.48\textwidth]{zeros.pdf}
+\end{center}
+\caption{Dimensionless derivative of the velocity profile as a
+  function of the dimensionless radius for different concentration
+  values. \label{fig:profiles}}
+\end{figure*}
+
 \end{document}

### 2015-10-07 paper/article.tex
short paragraph in the conclusions

@@
 \def\lsim{~\rlap{$<$}{\lower 1.0ex\hbox{$\sim$}}}
-% definition to produce a "greater than or similar to" symbol
+% definition to produce a "greater than or similar to" symbolxs
 \def\gsim{~\rlap{$>$}{\lower 1.0ex\hbox{$\sim$}}}
@@
 For the velocity method the error behaves closely to
-$\langle|D|\rangle\propto N^{-1/2}$
+$\langle|D|\rangle\propto N^{-1/2}$.
+We also gauged the effect of different concentration parameters at
+fixed particle numbers. 
+We found larger offsets for larger input concentrations. 
+The offset goes in the sense that the measured concentration tends to
+be underestimated.
+Nevertheless, the dominant effect on the measurement is the particle
+number.
 
-The effect of the number of particles.\\
-
-The effect of the input concentration.\\
-
-The impact on the mass-concentration relationship.\\
+We used a N-body cosmological simulation to test the impact of our
+method on the mass-concentration relationship.
+Although the three methods are in general agreement there are
+noticeable differences in the mass concentration relationship.
 

### 2015-10-19 paper/paper.tex
MNRAS style, abstract

\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
%\documentclass{latex/emulateapj} 
%External Packages and personalized macros
%=========================================================================
%		EXTERNAL PACKAGES
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
%\usepackage[section]{placeins}
\usepackage {graphicx}
%\usepackage{graphics}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{caption}
%Non reposionated tables
\usepackage{float}
\restylefloat{table}
%Multiple columns support for tables
\usepackage{array}
\usepackage{booktabs}
\setlength{\heavyrulewidth}{1.5pt}
\setlength{\abovetopsep}{4pt}
\pdfminorversion=5

%=========================================================================
%		INTERNAL MACROS
%=========================================================================
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
\newcommand{\before}[1]{\textcolor{red}{ #1}}
\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}

\newcommand{\LCDM}{$\Lambda$CDM~}
\newcommand{\beq}{\begin{eqnarray}}  
\newcommand{\eeq}{\end{eqnarray}}  
\newcommand{\zz}{$z\sim 3$} 
\newcommand{\apj}{ApJ}  
\newcommand{\apjs}{ApJS}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}    
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc}\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc}\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
%SAMPLES
\newcommand{\GHBDM}{\texttt{GH}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\GHFOF}{\texttt{GH}$_{\mbox{\tiny{FOF}}}$ }
\newcommand{\IHBDM}{\texttt{IH}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\IHFOF}{\texttt{IH}$_{\mbox{\tiny{FOF}}}$ }
\newcommand{\PBDM}{\texttt{P}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\PFOF}{\texttt{P}$_{\mbox{\tiny{FOF}}}$ }
\newcommand{\IPBDM}{\texttt{IP}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\IPFOF}{\texttt{IP}$_{\mbox{\tiny{FOF}}}$ }
\newcommand{\RIPBDM}{\texttt{RIP}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\RIPFOF}{\texttt{RIP}$_{\mbox{\tiny{FOF}}}$ }

%MY COMMANDS #############################################################
\newcommand{\sub}[1]{\mbox{\scriptsize{#1}}}
\newcommand{\dtot}[2]{ \frac{ d #1 }{d #2} }
\newcommand{\dpar}[2]{ \frac{ \partial #1 }{\partial #2} }
\newcommand{\pr}[1]{ \left( #1 \right) }
\newcommand{\corc}[1]{ \left[ #1 \right] }
\newcommand{\lla}[1]{ \left\{ #1 \right\} }
\newcommand{\bds}[1]{\boldsymbol{ #1 }}
\newcommand{\oiint}{\displaystyle\bigcirc\!\!\!\!\!\!\!\!\int\!\!\!\!\!\int}
\newcommand{\mathsize}[2]{\mbox{\fontsize{#1}{#1}\selectfont $#2$}}
\newcommand{\eq}[2]{\begin{equation} \label{eq:#1} #2 \end{equation}}
\newcommand{\lth}{$\lambda_{th}$ }
\newcommand{\reff}{{\ifmmode{r_{\mbox{\tiny eff}}}\else{$r_{\mbox{\tiny eff}}$}\fi}}
%#########################################################################

\begin{document}

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{A new method to estimate dark matter halo concentrations}
\author[C. Poveda, J.E. Forero-Romero & J.C. Mu\~noz-Cuartas]{
\parbox[t]{\textwidth}{\raggedright 
  C. Poveda \thanks{cn.poveda542@uniandes.edu.co}$^{1}$,
  J. E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{1}$,
  J. C. Mu\~noz-Cuartas \thanks{xxxx@udea.edu.co}$^{2}$
}
\vspace*{6pt}\\
$^1$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
$^2$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia
}

\maketitle

\begin{abstract}

We present a new method to estimate the concentration of dark matter
halos in N-body simulations.
Our method finds the concentration value to match integrated mass profile as a function of
halo radius.
The main advantage of this method is that it uses the full particle informatio
without any binning.
We test our method both on mock and N-body halos to compare it against
two popular methods to find concentrations: maximum radial velocity
measurements and radial particle binning to estimate the density.
Tests on the mock halos show that the accuracy of our method to
recover input concentrations varies with the number of particles in
the halo. 
For halos sampled with $20$ particles our method recovers the input
concentration with $10\%$ accuracy, while for the maximumradial
velocity and density methods the accuracy is on the order of $20\%$
and $100\%$, respectively.  
For halos with $2\times 10^4$ particles our method achieves an accuracy of
$0.01\%$ while the velocity and  methods achieve $0.1\%$ and $1\%$,
respectively.  
We also measure the mass-concentration relationship on N-body data
taking care of using halos sampled with at least $200$ particles..
We find that at low masses $10^{12}\hMsun < M<10^{13}\hMsun$ our
method yields median concentration values lower by a $15\%-20\%$
compared to the velocity and density methods. 
At higher masses $3\times 10^{13}\hMsun < M < 2\times 10^{14}\hMsun$ the
three methods give similar results.
\end{abstract}

\begin{keywords}
Cosmology: theory - large-scale structure of Universe -
Methods: data analysis - numerical - N-body simulations
\end{keywords}

%*************************************************************************
\section{Introduction}
\label{sec:introduction}
%*************************************************************************

\citep{NFW,Taylor2001}

\bibliographystyle{mn2e}
\bibliography{references}

\end{document}
The tracer that we use to define the voids is the fractional
anisotropy (FA) computed from the set of eigenvalues of the tensor
under consideration. 
The FA was initially introduced by \citet{Basser95} to quantify the
anisotropy degree of the diffusivity of water molecules through
cerebral tissue in nuclear magnetic resonance imaging, thereby allowing to 
detect structures that restrict the otherwise isotropic Brownian movement 
of water molecules. Taking into account that this process is identical to 
the velocity shear in the large-scale matter distribution, 
\citet{Libeskind13} introduced the concept of the FA in the context of 
Cosmic Web classification schemes.

%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

In the next sections (\S \ref{sec:algorithms_cosmic_web} and \S
\ref{sec:bulk_voids}) we establish the FA as a void tracer and then
proceed to identify individual voids as basins of FA local minima.  At
this point we implement a \textit{watershed transform algorithm}
\citep{Beucher79,Beucher93} which has been used to define voids as
catching basins of local minima of the density field \citep{Platen07,Neyrinck08}.
Finally we find and charachterize voids in a N-body (\S
\ref{sec:simulations} and \S \ref{sec:results}) using density, velocity and
fractional anisotropy profiles.  We use these results to comment on
the qualities of our algorithm (\S \ref{sec:conclusions}).

%*************************************************************************
\section{Algorithms to find the Cosmic Web}
\label{sec:algorithms_cosmic_web}
%*************************************************************************

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Different fields in a slice of
    $1\hMpc$ width in the Bolshoi simulation. Top/bottom panels correspond
    to the T-Web/V-Web.      
    Fractional Anisotropy field (left); cosmic web classification
    (middle) for a given value of the threshold eigenvalue
    $\lambda_{\rm th}$ where voids are white, sheets are light gray,
    filaments are dark gray and knots are black; individual voids (right) found by 
    the a watershed algorithm on the Fractional Anisotropy field. Colours
    in the right panel correspond with the effective radius of each void. }
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

Our new void finding method is based on two existing cosmic web
classification schemes that work on cosmological N-body simulations.
Both schemes depend on the construction of tensors based on the
Hessian of the potential (T-Web scheme) and the shear of the velocity
(V-Web scheme). 
These algorithms have been used to develop other
kind of studies such as the alignment of the shape, spin and peculiar
velocity of dark matter halos with the cosmic web
\citep{Libeskind13,Forero2014}. 
Here we summarize the most relevant aspects of each scheme. 
We refer the reader to the papers of \cite{Forero09} (T-Web) and
\cite{Hoffman12} (V-Web) for detailed descriptions.

%-------------------------------------------------------------------------
\subsection{The tidal web (T-Web)}
\label{subsec:Tweb}
%-------------------------------------------------------------------------

This scheme was initially proposed by \citet{Hahn07}  to find the
Cosmic Web based on the tidal tensor. 
The tidal tensor allows a classification in terms of the orbital
dynamics of the matter field.
This approach extends to second-order the equations of motion around 
local minima of the gravitational potential. 
The second-order term corresponds to the tidal tensor, which is
defined as the Hessian matrix of the normalized gravitational
potential

%.........................................................................
%Tidal Tensor
\eq{V_web}
{	T_{\alpha\beta} = \frac{\partial^2\phi}{\partial x_{\alpha}\partial x_{\beta}},	}
%.........................................................................
where the physical gravitational potential has been rescaled by a
factor of   $4\pi G\bar{\rho}$ in such a way that $\phi$ satisfies the following 
Poisson equation

%.........................................................................
%Poisson
\eq{Poisson}
{	\nabla^2\phi = \delta,	}
%.........................................................................
with $\bar{\rho}$ the average density in the Universe, $G$ the 
gravitational constant and $\delta$ the dimensionless matter
overdensity.

Since the tidal tensor can be represented by a real and  symmetric
$3\times 3$ matrix, it is always possible to diagonalize  
it and obtain three real eigenvalues $\lambda_{1}\geq\lambda_{2}\geq
\lambda_3$ with its corresponding eigenvectors ${\bf u}_{1}$, ${\bf u}_{2}$,
${\bf u}_{3}$. 
The eigenvalues are indicators of the local  orbital stability
in each direction ${\bf u}_i$. 
The sign of the eigenvalues can be used to classify the Cosmic Web.
The number of positive (stable) or negative (unstable) eigenvalues allows 
to label a location into one of the next four types of environment: 
voids (3 negative eigenvalues), sheets (2), filaments (1) and knots (0).

A modification to this scheme was introduced by \citet{Forero09}
by means of a relaxation of the stability criterion. 
The relative strength  of each eigenvalue is no longer defined by the
sign, but instead by a threshold value $\lambda_{\rm th}$ that can be
tuned in such a way that the visual impression of the web-like matter
distribution is reproduced.

%-------------------------------------------------------------------------
\subsection{The velocity web (V-Web)}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

The V-web scheme for environment finding introduced by
\cite{Hoffman12} is based on the local velocity shear tensor
calculated from the smoothed dark matter  velocity field in the
simulation. 
This tensor is given by the  following expression

%.........................................................................
%V-Web Definition
\eq{V_web}
{	\Sigma_{\alpha\beta} = -\frac{1}{2H_0}\pr{\frac{\partial v_{\alpha}}
{\partial x_{\beta}}+\frac{\partial v_{\beta}}{\partial x_{\alpha}}},}
%.........................................................................
where $v_{\alpha}$ and $x_{\alpha}$ represent the $\alpha$ component of 
the comoving velocity and position, respectively. Like the tidal tensor, 
$\Sigma_{\alpha\beta}$ can be represented by a $3\times 3$ symmetric 
matrix with real values, making it possible to find three real
eigenvalues and its corresponding eigenvectors.

In this case we also use the relative strength of the three eigenvalues with 
respect to a threshold value $\lambda_{th}$ to classify the cosmic web
in the four web types already mentioned.

Usually, the threshold $\lambda_{th}$ is a free parameter that is
tuned to reproduce the visual appearance of the comic web. 
However, in this paper this threshold does not play any role in our
computations.
In Figure \ref{fig:L1_correlations} we offer a threshold estimate
(from the FA=$0.95$ as a function of $\lambda_1$, this choice is
explained in the next section) only as a guide to readers familiar
with its meaning.

%-------------------------------------------------------------------------
%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
  width=0.33\textwidth]{FA_L1.pdf}  
  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
  width=0.33\textwidth]{delta_L1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
  width=0.33\textwidth]{FA_delta.pdf}
  \captionof{figure}{
    Fractional Anisotropy  as a function of
    the overdensity (left) and the eigenvalue $\lambda_1$ (middle), and
    density contrast (right) as a function of the
    eigenvalue $\lambda_1$ for each web scheme (T-Web,  continuous
    lines. V-Web, dashed lines).     
    Fractional Anisotropy  as a function of $\lambda_1$ (left),
    overdensity as a function of $\lambda_1$ (middle) and Fractional
    Anisotropy as a function of the overdensity (right).
    Thick central lines are the median
    and filled regions include $50\%$ of the cells in each bin. 
    The left panel shows the tight correlation between FA and
    $\lambda_1$ in voids.
    In the middle and right panel we show the equivalent eigenvalue
    threshold for the T-Web and V-web corresponding to FA=$0.95$. 
    The right panel confirms that underdense regions can be
    identified with Fractional Anisotropy values less than $0.95$.
    For this reason we define voids to be composed by cells with
    Fractional Anisotropy equal or less than this value.
    The threshold $\lambda_{\rm th}$ on the eigenvalues does not
    influence our results. 
    We show it as a guide to readers familiar with the
    order of magnitude expectation for this quantity.}
  \label{fig:L1_correlations}

\end{figure*}
%.........................................................................

%-------------------------------------------------------------------------
%FIGURE 3: Histograms for each environment regarding the FA value
\begin{figure}
\centering
  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{FA_environment.pdf}
   \captionof{figure}{\small Volume of each environment per FA
   ($dV_i/dFA,\ \ i=v,s,f,k$) normalized by the total volume per FA
   ($dV/dFA$). 
  Top/bottom corresponds to the T-Web/V-Web. For a given value of the FA, 
  each line represents the volume contribution of the respective 
  environment to the total volume with the same FA value. Above FA=0.95,
  only sheets and filaments contribute to all the volume of the simulation
  within that range of FA.}
  \label{fig:FA_environment}
\end{figure}
%.........................................................................

%*************************************************************************
\section{A new void finding technique}
\label{sec:bulk_voids}
%*************************************************************************

%-------------------------------------------------------------------------
\subsection{The fractional anisotropy}
\label{subsec:FA_voids}
%-------------------------------------------------------------------------

% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

The fractional anisotropy (FA), as developed by \citet{Basser95}, 
was conceived to quantify the anisotropy of the diffusivity of water
molecules through cerebral tissue in nuclear magnetic resonance imaging. 
In this manner, barriers such as microtubules and cell membranes, that 
restrict the otherwise isotropic Brownian motion of water molecules, can 
be detected. In a cosmological context, the problem of finding structures 
is very similar, where filaments and sheets restrict the otherwise 
isotropic collapsing/expanding dynamics of the matter. Taking this into 
account, we present here the FA, much in the same way as \citet{Libeskind13}, 
to use it as a tracer of cosmic voids.

%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

The FA is defined as follows
%.........................................................................
%Fractional anisotropy
\eq{fractional_anisotropy}
{{\mathrm{FA}} = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
\lambda_2^2 + \lambda_3^2} },}
%.........................................................................
where the eigenvalues can be taken from either the T-Web or the V-Web 
(FA-T-Web and FA-V-Web respectively). Such as it is defined, FA$=0$ 
corresponds to an isotropic distribution ($\lambda_1=\lambda_2=\lambda_3$) 
and FA$=1$ to a highly anisotropic distribution.

In the left and middle panels of Fig. \ref{fig:FA_field} we show the
FA field and web classification for both  web schemes over a slice of
an N-body simulation (described in Section \ref{sec:simulations}). 
Comparing these two panels we see that voids and knots (white
and black in the middle panel of Fig. 1) display low FA values at
their  centres, becoming gradually more anisotropic at outer regions.  
On the other hand the filamentary structure (grey in the middle panel
of Fig. 1) is traced by middle to high FA values.  
This characteristic is the  key to use the FA as a tracer of cosmic
voids.

%-------------------------------------------------------------------------
\subsection{Fractional anisotropy as a void tracer}
\label{subsec:web_voids}
%-------------------------------------------------------------------------

Voids are regions where $\lambda_3\leq\lambda_2\leq
\lambda_1\leq\lambda_{\rm th}$. 
This implies that a void is completely fixed by the relative strength
of the $\lambda_1$ eigenvalue with respect to the threshold.   
As we increase/decrease the threshold value $\lambda_{\rm th}$, voids
increase/decrease progressively through contours of
increasing/decreasing $\lambda_1$.  
Voids are thus characterized by low values of both FA and
$\lambda_1$.

In Fig. \ref{fig:L1_correlations}  we show that the these two values
are correlated. 
The left panel shows the correlation between the FA and $\lambda_1$
and the middle panel between the overdensity $\delta$ and $\lambda_1$.
The right panel shows the correlation between $\delta$ and the
FA. 
This shows that the  density has a larger scatter at fixed
$\lambda_1$ than the FA, yet large and  small values of the density
remain still associated to low values of the FA.

At this point, the eigenvalue $\lambda_1$ and the FA appear to be
equally potential candidates for tracing cosmic voids, however, the 
eigenvalue $\lambda_1$ presents, along with the overdensity, an undesirable 
feature for a void tracer. 
As we move out from inner parts of voids to outer parts, $\lambda_1$
and $\delta$ increase monotonically making unclear where to set the
void boundary, while for low density regions ($\delta<1$) the FA traces
the boundary where anisotropic collapsing regions begin to 
dominate, i.e. at the ridge reached around $\delta = 0$ as shown in the 
right panel of Fig. \ref{fig:L1_correlations}.
According to Fig. \ref{fig:FA_environment} these anisotropic areas are
mainly associated to sheets and, to a lesser extent, filaments.

From Figs. \ref{fig:FA_field} and \ref{fig:L1_correlations} we
conclude that the FA is a good tracer of voids as it is almost perfectly
correlated with low values of $\lambda_1$. 
We propose that voids should be composed completely by regions of
FA$<0.95$.
If we increase the values of $\lambda_1$ from its minimum until it
we reach FA$=0.95$ in \ref{fig:L1_correlations} we find that this
correspond to critical values of $\lambda_{1}^T = 0.265$ and
$\lambda_{1}^V = 0.175$ for the T-Web and V-Web, respectively.
This means that setting $\lambda_{th}$ to either
$\lambda_{1}^T$/$\lambda_{1}^{V}$ automatically produces voids with
all the cells FA$<0.95$.   
The middle panels in Fig. \ref{fig:FA_field} show the web
classification for this choice of $\lambda_{th}$, demonstrating that
this FA level is a reasonable choice to define voids.

%-------------------------------------------------------------------------
\subsection{Defining voids with a watershed algorithm}
\label{subsec:watershed}
%-------------------------------------------------------------------------

The previous Section shows that FA is a good void tracer, but how
should we actually define the boundary of individual voids?
For this purpose, we use the \textit{watershed transform algorithm}
\citep{Beucher79,Beucher93} to identify a void as the basin of FA
local minima with boundaries of FA$=0.95$. 
The advantage of this definition is that it does not require any
assumption on the shape and/or morphology of the tentative voids.

However, there are two main differences in our approach with respect to other
watershed implementations.
First, the watershed technique commonly uses the density field
instead of the FA field as we do here
\citep{Platen07,Neyrinck08}.   
Second, we estimate all relevant quantities on a Cartesian mesh of
fixed cell size, while other works use an adaptive Delaunay tessellation
\citep{Schaap00}.
Nevertheless, in our case the average number of particles per cell
  is large enough ($512$ particles/cell) ensuring that the lowest
  density regions are sampled with at least $\sim 10$ particles
  ($\delta \sim-0.98$), which seems to avoid spurious results from a
  noisy density field sampling.

The watershed algorithm also needs a threshold value to reduce
spurious features and prevent void hierarchization.  
If the density field is used, a typical threshold is
$\delta = -0.8$ \citep{Platen07},  which means that, given two neighbouring 
voids, if the mean value of the density across their common boundary is 
below that threshold, the two voids are merged.
In our case we have to find a corresponding FA value
to define this threshold.

In the right panel of Fig. \ref{fig:L1_correlations} we see how 
the FA correlates with the matter overdensity. 
A value of $\delta=-0.8$ corresponds to a value of FA$\sim 0.65$
regardless of the web-finding scheme. 
This is the value we choose to remove ridges between two watershed
voids. 
The right column in Fig. \ref{fig:FA_field} shows all the individual
voids that have been identified using the watershed algorithm on the
FA field.

%.........................................................................
%FIGURE 4: volume functions
\begin{figure*}
\centering

  \includegraphics[trim = 2mm 2mm 2mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_regions_volume_all.pdf}
  \includegraphics[trim = 2mm 2mm 2mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_regions_volume_compensated.pdf}

  \captionof{figure}{\small Left panel, void size distribution. Right
    panel, fraction of overcompensated/subcompensated ($C>1/C<1$)voids as a
    function of the effective radius. The continuous (dashed)
    curves correspond to the T-Web (V-Web).
    The abundance for small ($\reff <2.0\hMpc$) overcompensated voids
    shoots up in the V-Web scheme.
    We provide in the body of the paper two reasons for this behaviour.}
  \label{fig:volume_function}

\end{figure*}
%.........................................................................

\section{Numerical Simulation}
\label{sec:simulations}

We use the Bolshoi simulation to test our void finding method. 
This simulation follows the non-linear evolution of a dark
matter density field on a cubic volume of  size $250$\hMpc\ sampled
with $2048^3$ particles. 
The cosmological parameters in the simulation are $\Omega_{\rm
  m}=0.27$,  $\Omega_{\Lambda}  =0.73$, $h=0.70$, $n=0.95$ and
$\sigma_{8}=0.82$ for the matter density,   cosmological 
constant, dimensionless Hubble parameter, spectral index of
primordial density perturbations and normalization for the power
spectrum, respectively. 
These values are consistent with the ninth year of data of the
Wilkinson  Microwave Anisotropy Probe (WMAP) \citep{Hinshaw2013}. 
For more detailed  technical information about the simulation, see
\citet{Klypin11}.

We use data for the cosmic web identification that is publicly
available through the MultiDark database
\url{http://www.multidark.org/MultiDark/} which is described in
\citet{Riebe11}. 
Here we briefly describe the process to obtain the data. 
For details see \cite{Forero09} (T-Web);
\cite{Hoffman12,Forero2014} (V-Web). 
This data is based on a  \textit{cloud-in-cell} (\texttt{CIC})
interpolation of the density and velocity fields of the simulation
onto a grid of $256^3$  cells, corresponding to a spatial resolution
of $0.98$\hMpc\ per cell side.    
These fields are smoothed with a gaussian filter with a width of 
$\sigma=0.98$\hMpc. 
The tidal and shear tensors and corresponding eigenvalues are computed
through finite-differences over the potential and velocity fields.

%*************************************************************************
\section{Results}
\label{sec:results}
%*************************************************************************

We limit our results to voids with effective radius larger than the
smoothing length of the density field, i.e. $\sim 1$\hMpc.  
For smaller interpolation/smoothing scales the shot noise in
  the low density regions starts to be noticeable.
With that choice we find a void volume filling fraction $54.88\%$ and
$47.06\%$ for the FA-Vweb and the FA-Tweb, respectively.  
For larger smoothing scales ($>5\hMpc$) the density and shear fields
  tend to be Gaussian and therefore follow closely the analytical
  environment abundance predictions for Gaussian random fields
  \citep{Forero09,Alonso2015}.  
In this paper we limit ourselves to a smoothing scale $\sim 1$ \hMpc.

In the following subsections we describe the results for the size
distribution and different radial profiles for all our samples.

%-------------------------------------------------------------------------
\subsection{The void size distribution}
\label{subsec:shape_voids}
%-------------------------------------------------------------------------

Void shapes exhibit a wide range of geometries.
To define their size we use its equivalent spherical radius or
effective radius, defined as $\reff = [3/(4\pi)V]^{1/3}$, with $V$ the 
total volume of the void computed from the individual grid cells
assigned to the void.   
In Fig. \ref{fig:volume_function} we show the void size
distributions for the T-Web and the V-Web.

We see that the void distribution for the T-Web is broadly consistent with the
expectations from a two-barrier problem  \citep{Sheth04}. 
The formation of large voids is limited by the \textit{void-in-void}
mechanism (first barrier) where large voids are constituted
hierarchically of smaller ones. 
In turn, the formation of small voids is damped by the
\textit{void-in-cloud} mechanism (second barrier),  where nearby
collapsing structures limit the abundance of small embedded voids.

We also find that the V-Web scheme produces an over-abundance of small
voids compared to T-Web.
A large number of these small voids are embedded in overdense regions. 
They are already visible in the middle panel of Fig. \ref{fig:FA_field} as
tiny white bubbles located inside sheets.
The existence of these small voids can be explained by
dynamics of shell crossing in collapsing sheets as discussed in
\citet{Hoffman12}.    
The main argument is that as matter collides into a pancake-like
fashion crossing sheets encounter each other at the symmetry plane.
This effectively gives a positive divergence in the velocity
field, resulting in a void identification by the V-Web algorithm.

Comparing the abundance of large voids in the two web schemes, we find
that the largest voids in the V-Web have $\reff \sim 10$\hMpc,
while the T-Web scheme includes voids as large as $\reff \sim 15$\hMpc. 
This suggests that large voids in the T-Web scheme have a velocity
structure that splits them in the V-Web. 
This increased granularity in the velocity structure of voids is
evident in the left and right panels of Fig. \ref{fig:FA_field}.

%.........................................................................
%FIGURE 5: Density profile of voids for each defined scheme
\begin{figure*}
\centering
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_density_TwebFAG1.pdf}

  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_density_VwebFAG0.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_density_VwebFAG1.pdf}

  \captionof{figure}{\small Spherically averaged radial density profiles for
    stacked voids with different effective radii. The sample is split
    into subcompensated and overcompensated voids (right and left) for
    the web schemes T-Web and V-Web (top and bottom).}
  \label{fig:density_profile}
  \vspace{0.1 cm}
\end{figure*}

\begin{figure*}
\centering  
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_velocity_TwebFAG1.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_velocity_VwebFAG0.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_velocity_VwebFAG1.pdf}
  \captionof{figure}{\small Spherically averaged radial velocity
    profiles for stacked voids with different effective radii. The
    sample is split into subcompensated and overcompensated voids
    (right and left) for the web schemes T-Web and V-Web (top and
    bottom).} 
  \label{fig:velocity_profile}
  \vspace{0.1 cm}
\end{figure*}

\begin{figure*}
\centering  
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_FA_TwebFAG0.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_FA_TwebFAG1.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_FA_VwebFAG0.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_FA_VwebFAG1.pdf}

  \captionof{figure}{\small Spherically averaged Fractional Anisotropy
    profiles for stacked voids with different effective radii. The
    sample is split into subcompensated and overcompensated voids
    (right and left) for the web schemes T-Web and V-Web (top and
    bottom).} 
  \label{fig:FA_profile}
  \vspace{0.1 cm}

\end{figure*}
%.........................................................................

%-------------------------------------------------------------------------
\subsection{Subcompensated and overcompensated voids}
\label{subsec:enclosedmass}
%-------------------------------------------------------------------------

We find that voids are distributed in two different families
differentiated by the 
presence/absence of an overdense matter ridge in their density
profiles. 
To discriminate each void in one of the families we use the
compensation  index $C$
It is defined as the mass of a void enclosed in a spherical volume of
radius $R$ and normalized by the mass of the same volume assuming
it is filled by matter with the mean background density.

\eq{compensation}
{C= \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr}

We choose an integration radius of $R=4\reff$, that is large enough to 
enclose the compensation ridge for a typical void in case there is one. 
This leads us to voids with $C>1$ having more mass than expected, 
constituting the family of overcompensated voids. 
These voids generally  exhibit a compensation ridge associated to
dense nearby structures. 
In the same fashion, voids with $C<1$ constitute the family
of  subcompensated voids.

In Fig. \ref{fig:density_profile} we show the density and velocity profiles
of voids split in these two families. 
In the left column it becomes clear the difference between sub- and
overcompensated voids. 
Table \ref{tab:number_voids} lists the number of voids in 
each effective radius bin for the two web finding methods.

%.........................................................................
\begin{table}[!htbp]
\centering
\begin{tabular}{c | c c | c c}
\toprule
\multicolumn{1}{c}{}&  \multicolumn{2}{c}{\textbf{Tweb}} & \multicolumn{2}{c}{\textbf{Vweb}}\\
%\midrule
\textbf{${\bf \reff }$[\hMpc]}   & $\bf{C<1}$   & $\bf{C>1}$    & $\bf{C<1}$   & $\bf{C>1}$\\ \hline
%\midrule
$<2.0$        &  997 & 495   & 13480  & 711\\
$2.0-3.2$     &  791 & 471   & 2581   & 583\\
$3.2-4.4$     &  941 & 469   & 2168   & 656\\
$4.4-5.6$     &  869 & 467   & 1934   & 724\\
$5.6-6.8$     &  769 & 395   & 1287   & 584\\
$6.8-8.3$     &  665 & 362   & 700    & 315\\
$8.3-12.0$    &  587 & 333   & 123    & 61\\
$>12.0$       &  29  & 23    & 0      & 0\\ \hline
\textbf{total}& 5648 & 3015  & 22273  & 3634\\
\bottomrule
\end{tabular}
\caption{Number of voids for each bin of effective radius and for 
subcompensanted and overcompansated samples.}
\label{tab:number_voids}
\end{table}
%.........................................................................

%.........................................................................
\subsection{Density profiles}
\label{subsec:density_voids}
%.........................................................................

We calculate the contrast density, radial-projected velocity and 
FA profiles. 
For this purpose we stack voids with similar effective radius.
We also compute the profiles separately  for subcompensated and
overcompensated voids. 
For each void,  
we take the distance of each member cell to the void centre along with the 
properties of interest. 
We normalize the radial distance with the effective radius and add the
result to the stack.

Fig. \ref{fig:density_profile} shows the results of stacked density
profiles for different void sizes.  
We calculate the profile out to a radius $8\ \reff$  to capture the
point where the overdensity reaches the mean value.

The first interesting result is the overdensity value at the void's
centre.
We find that larger voids have a lower overdensity value.
The largest voids ($8.3-12\ \hMpc$) have an underdensity
$\delta \sim-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\sim 
-0.8$ at their centres.
This holds for both web schemes. 
These values are consistent with most of the void finding schemes
based on smooth and continuous fields from simulation or
reconstruction procedures on surveys \citep{Plionis02, Colberg05,
  Shandarin06,  Platen07, Neyrinck08, MunozCuartas11, Ceccarelli13,
  Paz13, Neyrinck13, Ricciardelli2013}, unlike geometrical approaches based 
on point distributions, where central density values are generally higher
\citep{Colberg08}.

A second feature about these profiles is their steepness at inner
regions.  
In subcompensated voids, larger voids are steeper.
Smaller voids exhibit moderate slopes, reaching the mean density at
larger radii than larger voids.
This suggests that small subcompensated voids are embedded into low
density structures, while large subcompensated voids are surrounded
by dense structures, reaching the mean density at lower effective
radii than smaller voids. 
In the overcompensated case larger voids reach first  both the
compensation ridge and then the mean density value.

Regarding overcompensated voids, a final result is related to the height 
of the compensation ridge: the larger the void size, the lower the ridge
height. This implies that overcompensated smaller voids are embedded in 
very high density regions, unlike their subcompensated counterpart, thus 
indicating two possibly different processes for small voids formation. 
Larger voids exhibit lower ridges as outer radial layers also includes all
sort of structures, thus being the difference between large overcompensated
and subcompensated voids less conclusive.

All the previous results hold for both finding schemes.
This suggests an universal behaviour for the radial density profile in
two families of subcompensated and overcompensanted voids. 
This goes in the same direction of recent results about the internal
\citep{Colberg05,  Ricciardelli2013} and external structure of voids
\citep{Lavaux12, Ceccarelli13, Paz13, Hamaus14}. 
Indeed, our results extend the findings of \cite{Hamaus14} into the
range of voids with size $\reff <10$\hMpc.

%.........................................................................
\subsection{Velocity profiles}
\label{subsec:velocity_voids}
%.........................................................................

In Fig. \ref{fig:velocity_profile} we present the radial velocity
profiles. 
Positive values correspond to outflows with respect to the centre.

We find that subcompensated voids have outflowing velocity profiles
all the way up to the radius where the average radial
density reaches zero.
In voids with sizes $\reff <8\hMpc$ the outflow is always
positive, consistent with the fact that their density profiles do not
reach the level $\delta=0$ in the range of explored radii.
This behaviour indicates that matter is being pulled out of the void
into external higher density features.

On the other hand, overcompensated voids initially exhibit outward
profiles, (as expected from a low density region) and approximately at
the radius of the compensation ridge, the velocity reaches a peak,
decreases and becomes negative, showing the infalling flow of matter
further than the compensation ridge. 
This shows that the high density structures associated to the
compensation ridge dominate the matter flow both from inside and
outside the void.

As in the density, these results are also consistent with a Universal
velocity profile for voids \citep{Paz13, Hamaus14}.

%.........................................................................
\subsection{Fractional Anisotropy profiles}
\label{subsec:FA_voids}
%.........................................................................

Fig. \ref{fig:FA_profile} shows the results for the FA profiles.
We find that the FA clearly magnifies the difference between the
internal profile $r/\reff <1$ and the external profile $r/\reff >1$. 
Subcompensanted voids in the T-Web reach an asymptotic background
value of F=$0.8$ almost right at $r/\reff =2$. 
For the V-Web the results are similar, albeit with a slower trend with
the effective radius. 
Overcompensated voids reach a maximum FA at the same effective radius
$r/\reff =1$ and decline to reach an asymptotic value of FA=$0.85$
at larger radii.

The central FA values also show a magnified trend with the void size. 
Large voids have lower FA values, amplifying the same trend
observed with the central density value. 
Finally, we observe that voids in the V-Web scheme span a larger range
of central FA values than in the T-Web scheme.

The difference between the radius where the density ridge is reached 
($r/\reff =3$) and the radius of the FA maxima ($r/\reff =1$, most
manifest in the T-Web voids) justifies in a more quantitative way the
qualitative argument we present in sub-section \ref{subsec:watershed}
to define void boundaries in our method.  
Namely that as we increase the void boundary moving away from the
centre, we reach first middle density walls, before reaching high
density structures associated with high anisotropy.  
This implies that voids defined with the FA never present positive
overdensities, making the FA maximum a reasonable boundary for voids
compared to the traditional definition that puts the boundary at the
density ridge.

We recognize that our choice produces smaller voids as compared with
other voids finding methods. 
We consider that this has the advantage of
avoiding the contamination from external structures.

%*************************************************************************
\section{Conclusions}
\label{sec:conclusions}
%*************************************************************************

In this paper we propose that the anisotropy of the eigenvalues from
tidal and velocity shear tensors is a good tracer of  cosmic voids. 
Based on this idea we go on to implement a watershed
algorithm on the fractional anisotropy to find voids in a N-body
cosmological simulation.
We perform different test on the voids found on the anisotropy of two
tensorial schemes, the T-Web and the V-web.

The first quantity we examine is the void size distribution
characterized by an effective radius. 
We find that for the T-Web scheme the void size distribution has a
shape consistent with standard expectations from a two-barrier setup. 
However, for the V-Web we find an overabundance of the smallest voids.
This is due to two reasons. 
First, there are artefacts in the web
finding scheme inside sheets. 
Second, there V-web produces smaller
fragmented voids inside the largest voids found in the T-Web
classification.  
This void fragmentation hints at a complex velocity structure in large
voids compared to its simpler density/gravitational potential anatomy.

A second step in the void characterization 
is the separation into subcompensated and overcompensated samples. 
In the T-Web $35\%$ of the voids are overcompensated and $65\%$
subcompensated, meaning that they are located in denser regions with
a clear delimiting ridge.   
For the V-web the subcompensated fraction rises to $85\%$ as the
void size decreases, supporting the picture of smaller spurious voids
located in medium density matter sheets.

Finally we proceed with a more detailed void characterization
through the radially averaged profiles of density, radial velocity and
fractional anisotropy. 
In this case we study separately the subcompensated and
overcompensated voids, split this time in samples with different
effective radii.

For the density the most interesting feature is that the  profile has
a similar shape for all the different void sizes once the radial
coordinate is expressed in units of the effective radius.  
In these profiles it is evident the presence of an overdense ridge
around $2<r/\reff <3$ for the overcompensated voids.
Subcompensated voids do not show such a ridge keeping its density
lower than the average value up to $r/\reff \sim 8$.

In other studies where voids are found using considerations on the
density fields the ridge is, almost by definition, located around
$r/\reff \sim 1$ and the subcompensated voids reach average
density around $r/\reff \sim 3$. 
This indicates that voids defined by FA boundaries are smaller  than
voids found by density only considerations close by a radial factor of
$2$.

The velocity profiles show the expected correlation with the features
already observed in the density.
Most notably the radial velocity goes to zero close to flat regions in
the density profile and is positive around regions of increasing
density with radius.

The FA profiles also show remarkable similarities
inside each class of subcompensated and overcompensated voids
and a close correlation with the behaviour in the density and velocity
profiles. 
From these profiles it becomes clear that the limit of overcompensated
void coincides with a ridge in of FA values close to $0.9$. 
This value is close to the limit FA=$0.95$ we impose in the watershed
algorithm, indicating that these voids are very close to spherical.
For the subcompensated voids the FA quickly increases to FA values of 
$\sim 0.7-0.8$ at $r/\reff \sim 1$ to find a plateau, which is
quite far from the limiting FA$=0.95$ suggesting that these voids are
ellipsoidal.

Put together, the results for the radially averaged profiles support the 
evidence for a universal density profile.  
Our results extend to smaller void sizes the work done by
\cite{Hamaus14} on simulations and by \cite{Ceccarelli13} on SDSS data.

The method we present here finds voids with reasonable properties
compared to different results published in the literature. 
This gives support to a new tracer, the Fractional Anisotropy, to be
used in the study of cosmic voids. 
Furthermore, the complementary physical picture in the two different
web finding algorithms opens the possibilities to make a joint
analysis of the tidal and dynamical structure of voids.

%*************************************************************************
\section*{Acknowledgments}  
%*************************************************************************

We would like to thank Fiona Hoyle and Rien van de Weygaert for their
exhaustive and thoughtful reviews, accompanied with very detailed and
helpful suggestions on earlier versions of this manuscript.  
We also thank Nelson Padilla and Yehuda Hoffman for enlightening
comments and discussions.
SB also thanks Juan Carlos Mu\~noz-Cuartas 
for many clarifying discussions and helpful ideas.
JEFR acknowledges financial support from Vicerrector\'ia de
Investigaciones at Universidad de los Andes (Colombia) through a FAPA
grant.

\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{{Abazajian}, et al. \& {(the SDSS
  Collaboration)}}{{Abazajian} et~al.}{2003}]{Abazajian03}
{Abazajian} K.,  et al.   {(the SDSS Collaboration)} 2003, \aj, 126, 2081

\bibitem[\protect\citeauthoryear{{Alonso}, {Eardley} \& {Peacock}}{{Alonso}
  et~al.}{2015}]{Alonso2015}
{Alonso} D.,  {Eardley} E.,    {Peacock} J.~A.,  2015, \mnras, 447, 2683

\bibitem[\protect\citeauthoryear{{Basser}}{{Basser}}{1995}]{Basser95}
{Basser} P.,  1995, NMR in Biomedical Imaging, 8, 333

\bibitem[\protect\citeauthoryear{{Bertschinger}}{{Bertschinger}}{1985}]{Bertschinger85}
{Bertschinger} E.,  1985, \apjs, 58, 1

\bibitem[\protect\citeauthoryear{{Beucher} \& {Lantuejoul}}{{Beucher} \&
  {Lantuejoul}}{1979}]{Beucher79}
{Beucher} S.,  {Lantuejoul} C.,  1979, in Proceedings Interna- tional Workshop
  on Image Processing, CCETT/IRISA, Rennes, France

\bibitem[\protect\citeauthoryear{{Beucher} \& {Meyer}}{{Beucher} \&
  {Meyer}}{1993}]{Beucher93}
{Beucher} S.,  {Meyer} F.,  1993, {Mathematical Morphology in Image
  Processing}.
Marcel Deker, New York

\bibitem[\protect\citeauthoryear{{Blumenthal}, {da Costa}, {Goldwirth}, {Lecar}
  \& {Piran}}{{Blumenthal} et~al.}{1992}]{Blumenthal92}
{Blumenthal} G.~R.,  {da Costa} L.~N.,  {Goldwirth} D.~S.,  {Lecar} M.,
  {Piran} T.,  1992, \apj, 388, 234

\bibitem[\protect\citeauthoryear{{Bond}, {Kofman} \& {Pogosyan}}{{Bond}
  et~al.}{1996}]{Bond96}
{Bond} J.~R.,  {Kofman} L.,    {Pogosyan} D.,  1996, \nat, 380, 603

\bibitem[\protect\citeauthoryear{{Brunino}, {Trujillo}, {Pearce} \&
  {Thomas}}{{Brunino} et~al.}{2007}]{Brunino07}
{Brunino} R.,  {Trujillo} I.,  {Pearce} F.~R.,    {Thomas} P.~A.,  2007,
  \mnras, 375, 184

\bibitem[\protect\citeauthoryear{{Ceccarelli}, {Padilla}, {Valotto} \&
  {Lambas}}{{Ceccarelli} et~al.}{2006}]{Ceccarelli06}
{Ceccarelli} L.,  {Padilla} N.~D.,  {Valotto} C.,    {Lambas} D.~G.,  2006,
  \mnras, 373, 1440

\bibitem[\protect\citeauthoryear{{Ceccarelli}, {Paz}, {Lares}, {Padilla} \&
  {Lambas}}{{Ceccarelli} et~al.}{2013}]{Ceccarelli13}
{Ceccarelli} L.,  {Paz} D.,  {Lares} M.,  {Padilla} N.,    {Lambas} D.~G.,
  2013, \mnras, 434, 1435

\bibitem[\protect\citeauthoryear{{Chincarini} \& {Rood}}{{Chincarini} \&
  {Rood}}{1975}]{Chincarini75}
{Chincarini} G.,  {Rood} H.~J.,  1975, \nat, 257, 294

\bibitem[\protect\citeauthoryear{{Colberg}, {Pearce} \& et al.}{{Colberg}
  et~al.}{2008}]{Colberg08}
{Colberg} J.~M.,  {Pearce} F.,    et al. 2008, \mnras, 387, 933

\bibitem[\protect\citeauthoryear{{Colberg}, {Sheth}, {Diaferio}, {Gao} \&
  {Yoshida}}{{Colberg} et~al.}{2005}]{Colberg05}
{Colberg} J.~M.,  {Sheth} R.~K.,  {Diaferio} A.,  {Gao} L.,    {Yoshida} N.,
  2005, \mnras, 360, 216

\bibitem[\protect\citeauthoryear{{Colless}, et al. \& {(the 2dFGRS
  Team),}}{{Colless} et~al.}{2001}]{Colless01}
{Colless} M.,  et al.   {(the 2dFGRS Team),} 2001, \mnras, 328, 1039

\bibitem[\protect\citeauthoryear{{Colless}, et al. \& {(the 2dFGRS
  Team),}}{{Colless} et~al.}{2003}]{Colless03}
{Colless} M.,  et al.   {(the 2dFGRS Team),} 2003, VizieR Online Data Catalog,
  7226

\bibitem[\protect\citeauthoryear{{Croton} \& et al.}{{Croton} \&
  et~al.}{2004}]{Croton04}
{Croton} D.~J.,  et al. 2004, \mnras, 352, 828

\bibitem[\protect\citeauthoryear{{Dubinski}, {da Costa}, {Goldwirth}, {Lecar}
  \& {Piran}}{{Dubinski} et~al.}{1993}]{Dubinski93}
{Dubinski} J.,  {da Costa} L.~N.,  {Goldwirth} D.~S.,  {Lecar} M.,    {Piran}
  T.,  1993, \apj, 410, 458

\bibitem[\protect\citeauthoryear{{Einasto}, {Joeveer} \& {Saar}}{{Einasto}
  et~al.}{1980a}]{Einasto80M}
{Einasto} J.,  {Joeveer} M.,    {Saar} E.,  1980a, \mnras, 193, 353

\bibitem[\protect\citeauthoryear{{Einasto}, {Joeveer} \& {Saar}}{{Einasto}
  et~al.}{1980b}]{Einasto80N}
{Einasto} J.,  {Joeveer} M.,    {Saar} E.,  1980b, \nat, 283, 47

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Contreras} \&
  {Padilla}}{{Forero-Romero} et~al.}{2014}]{Forero2014}
{Forero-Romero} J.~E.,  {Contreras} S.,    {Padilla} N.,  2014, \mnras, 443,
  1090

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Hoffman}, {Gottl{\"o}ber},
  {Klypin} \& {Yepes}}{{Forero-Romero} et~al.}{2009}]{Forero09}
{Forero-Romero} J.~E.,  {Hoffman} Y.,  {Gottl{\"o}ber} S.,  {Klypin} A.,
  {Yepes} G.,  2009, \mnras, 396, 1815

\bibitem[\protect\citeauthoryear{{Foster} \& {Nelson}}{{Foster} \&
  {Nelson}}{2009}]{Foster09}
{Foster} C.,  {Nelson} L.~A.,  2009, \apj, 699, 1252

\bibitem[\protect\citeauthoryear{{Gottl{\"o}ber}, {{\L}okas}, {Klypin} \&
  {Hoffman}}{{Gottl{\"o}ber} et~al.}{2003}]{Gottlober03}
{Gottl{\"o}ber} S.,  {{\L}okas} E.~L.,  {Klypin} A.,    {Hoffman} Y.,  2003,
  \mnras, 344, 715

\bibitem[\protect\citeauthoryear{{Gregory} \& {Thompson}}{{Gregory} \&
  {Thompson}}{1978}]{Gregory78}
{Gregory} S.~A.,  {Thompson} L.~A.,  1978, \apj, 222, 784

\bibitem[\protect\citeauthoryear{{Hahn}, {Porciani}, {Carollo} \&
  {Dekel}}{{Hahn} et~al.}{2007}]{Hahn07}
{Hahn} O.,  {Porciani} C.,  {Carollo} C.~M.,    {Dekel} A.,  2007, \mnras, 375,
  489

\bibitem[\protect\citeauthoryear{{Hamaus}, {Sutter} \& {Wandelt}}{{Hamaus}
  et~al.}{2014}]{Hamaus14}
{Hamaus} N.,  {Sutter} P.~M.,    {Wandelt} B.~D.,  2014, Physical Review
  Letters, 112, 251302

\bibitem[\protect\citeauthoryear{{Hinshaw} et~al.,}{{Hinshaw}
  et~al.}{2013}]{Hinshaw2013}
{Hinshaw} G.  et~al., 2013, \apjs, 208, 19

\bibitem[\protect\citeauthoryear{{Hoffman}, {Metuki}, {Yepes}, {Gottl{\"o}ber},
  {Forero-Romero}, {Libeskind} \& {Knebe}}{{Hoffman} et~al.}{2012}]{Hoffman12}
{Hoffman} Y.,  {Metuki} O.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Forero-Romero}
  J.~E.,  {Libeskind} N.~I.,    {Knebe} A.,  2012, \mnras, 425, 2049

\bibitem[\protect\citeauthoryear{{Hoffman} \& {Shaham}}{{Hoffman} \&
  {Shaham}}{1982}]{Hoffman82}
{Hoffman} Y.,  {Shaham} J.,  1982, \apjl, 262, L23

\bibitem[\protect\citeauthoryear{{Hoyle} \& {Vogeley}}{{Hoyle} \&
  {Vogeley}}{2004}]{Hoyle04}
{Hoyle} F.,  {Vogeley} M.~S.,  2004, \apj, 607, 751

\bibitem[\protect\citeauthoryear{{Icke}}{{Icke}}{1984}]{Icke84}
{Icke} V.,  1984, \mnras, 206, 1P

\bibitem[\protect\citeauthoryear{{Kauffmann} \& {Fairall}}{{Kauffmann} \&
  {Fairall}}{1991}]{Kauffmann91}
{Kauffmann} G.,  {Fairall} A.~P.,  1991, \mnras, 248, 313

\bibitem[\protect\citeauthoryear{{Kirshner}, {Oemler} Jr., {Schechter} \&
  {Shectman}}{{Kirshner} et~al.}{1981}]{Kirshner81}
{Kirshner} R.~P.,  {Oemler} Jr. A.,  {Schechter} P.~L.,    {Shectman} S.~A.,
  1981, \apjl, 248, L57

\bibitem[\protect\citeauthoryear{{Kirshner}, {Oemler} Jr., {Schechter} \&
  {Shectman}}{{Kirshner} et~al.}{1987}]{Kirshner87}
{Kirshner} R.~P.,  {Oemler} Jr. A.,  {Schechter} P.~L.,    {Shectman} S.~A.,
  1987, \apj, 314, 493

\bibitem[\protect\citeauthoryear{{Klypin}, {Trujillo-Gomez} \&
  {Primack}}{{Klypin} et~al.}{2011}]{Klypin11}
{Klypin} A.~A.,  {Trujillo-Gomez} S.,    {Primack} J.,  2011, \apj, 740, 102

\bibitem[\protect\citeauthoryear{{Lavaux} \& {Wandelt}}{{Lavaux} \&
  {Wandelt}}{2012}]{Lavaux12}
{Lavaux} G.,  {Wandelt} B.~D.,  2012, \apj, 754, 109

\bibitem[\protect\citeauthoryear{{Libeskind}, {Hoffman}, {Forero-Romero},
  {Gottl{\"o}ber}, {Knebe}, {Steinmetz} \& {Klypin}}{{Libeskind}
  et~al.}{2013}]{Libeskind13}
{Libeskind} N.~I.,  {Hoffman} Y.,  {Forero-Romero} J.,  {Gottl{\"o}ber} S.,
  {Knebe} A.,  {Steinmetz} M.,    {Klypin} A.,  2013, \mnras, 428, 2489

\bibitem[\protect\citeauthoryear{{Martel} \& {Wasserman}}{{Martel} \&
  {Wasserman}}{1990}]{Martel90}
{Martel} H.,  {Wasserman} I.,  1990, \apj, 348, 1

\bibitem[\protect\citeauthoryear{{Micheletti} et~al.,}{{Micheletti}
  et~al.}{2014}]{Micheletti14}
{Micheletti} D.  et~al., 2014, \aap, 570, A106

\bibitem[\protect\citeauthoryear{{Mu{\~n}oz-Cuartas}, {M{\"u}ller} \&
  {Forero-Romero}}{{Mu{\~n}oz-Cuartas} et~al.}{2011}]{MunozCuartas11}
{Mu{\~n}oz-Cuartas} J.~C.,  {M{\"u}ller} V.,    {Forero-Romero} J.~E.,  2011,
  \mnras, 417, 1303

\bibitem[\protect\citeauthoryear{{M{\"u}ller}, {Arbabi-Bidgoli}, {Einasto} \&
  {Tucker}}{{M{\"u}ller} et~al.}{2000}]{Muller00}
{M{\"u}ller} V.,  {Arbabi-Bidgoli} S.,  {Einasto} J.,    {Tucker} D.,  2000,
  \mnras, 318, 280

\bibitem[\protect\citeauthoryear{{Nadathur} \& {Hotchkiss}}{{Nadathur} \&
  {Hotchkiss}}{2014}]{Nadathur14}
{Nadathur} S.,  {Hotchkiss} S.,  2014, \mnras, 440, 1248

\bibitem[\protect\citeauthoryear{{Neyrinck}}{{Neyrinck}}{2008}]{Neyrinck08}
{Neyrinck} M.~C.,  2008, \mnras, 386, 2101

\bibitem[\protect\citeauthoryear{{Neyrinck}, {Falck} \& {Szalay}}{{Neyrinck}
  et~al.}{2013}]{Neyrinck13}
{Neyrinck} M.~C.,  {Falck} B.~L.,    {Szalay} A.~S.,  2013, ArXiv e-prints

\bibitem[\protect\citeauthoryear{{Padilla}, {Ceccarelli} \& {Lambas}}{{Padilla}
  et~al.}{2005}]{Padilla05}
{Padilla} N.~D.,  {Ceccarelli} L.,    {Lambas} D.~G.,  2005, \mnras, 363, 977

\bibitem[\protect\citeauthoryear{{Pan}, {Vogeley}, {Hoyle}, {Choi} \&
  {Park}}{{Pan} et~al.}{2012}]{Pan10}
{Pan} D.~C.,  {Vogeley} M.~S.,  {Hoyle} F.,  {Choi} Y.-Y.,    {Park} C.,  2012,
  \mnras, 421, 926

\bibitem[\protect\citeauthoryear{{Patiri}, {Betancort-Rijo} \&
  {Prada}}{{Patiri} et~al.}{2006}]{Patiri06a}
{Patiri} S.~G.,  {Betancort-Rijo} J.,    {Prada} F.,  2006, \mnras, 368, 1132

\bibitem[\protect\citeauthoryear{{Patiri}, {Prada}, {Holtzman}, {Klypin} \&
  {Betancort-Rijo}}{{Patiri} et~al.}{2006}]{Patiri06b}
{Patiri} S.~G.,  {Prada} F.,  {Holtzman} J.,  {Klypin} A.,    {Betancort-Rijo}
  J.,  2006, \mnras, 372, 1710

\bibitem[\protect\citeauthoryear{{Paz}, {Lares}, {Ceccarelli}, {Padilla} \&
  {Lambas}}{{Paz} et~al.}{2013}]{Paz13}
{Paz} D.,  {Lares} M.,  {Ceccarelli} L.,  {Padilla} N.,    {Lambas} D.~G.,
  2013, \mnras, 436, 3480

\bibitem[\protect\citeauthoryear{{Platen}, {van de Weygaert} \&
  {Jones}}{{Platen} et~al.}{2007}]{Platen07}
{Platen} E.,  {van de Weygaert} R.,    {Jones} B.~J.~T.,  2007, \mnras, 380,
  551

\bibitem[\protect\citeauthoryear{{Plionis} \& {Basilakos}}{{Plionis} \&
  {Basilakos}}{2002}]{Plionis02}
{Plionis} M.,  {Basilakos} S.,  2002, \mnras, 330, 399

\bibitem[\protect\citeauthoryear{{Regos} \& {Geller}}{{Regos} \&
  {Geller}}{1991}]{Regos91}
{Regos} E.,  {Geller} M.~J.,  1991, \apj, 377, 14

\bibitem[\protect\citeauthoryear{{Ricciardelli}, {Quilis} \&
  {Planelles}}{{Ricciardelli} et~al.}{2013}]{Ricciardelli2013}
{Ricciardelli} E.,  {Quilis} V.,    {Planelles} S.,  2013, \mnras, 434, 1192

\bibitem[\protect\citeauthoryear{{Riebe} et~al.,}{{Riebe}
  et~al.}{2013}]{Riebe11}
{Riebe} K.  et~al., 2013, Astronomische Nachrichten, 334, 691

\bibitem[\protect\citeauthoryear{{Rojas}, {Vogeley}, {Hoyle} \&
  {Brinkmann}}{{Rojas} et~al.}{2005}]{Rojas05}
{Rojas} R.~R.,  {Vogeley} M.~S.,  {Hoyle} F.,    {Brinkmann} J.,  2005, \apj,
  624, 571

\bibitem[\protect\citeauthoryear{{Schaap} \& {van de Weygaert}}{{Schaap} \&
  {van de Weygaert}}{2000}]{Schaap00}
{Schaap} W.~E.,  {van de Weygaert} R.,  2000, \aap, 363, L29

\bibitem[\protect\citeauthoryear{{Shandarin}, {Feldman}, {Heitmann} \&
  {Habib}}{{Shandarin} et~al.}{2006}]{Shandarin06}
{Shandarin} S.,  {Feldman} H.~A.,  {Heitmann} K.,    {Habib} S.,  2006, \mnras,
  367, 1629

\bibitem[\protect\citeauthoryear{{Sheth} \& {van de Weygaert}}{{Sheth} \& {van
  de Weygaert}}{2004}]{Sheth04}
{Sheth} R.~K.,  {van de Weygaert} R.,  2004, \mnras, 350, 517

\bibitem[\protect\citeauthoryear{{Sutter} et~al.,}{{Sutter}
  et~al.}{2015}]{Sutter14}
{Sutter} P.~M.  et~al., 2015, Astronomy and Computing, 9, 1

\bibitem[\protect\citeauthoryear{{Sutter}, {Lavaux}, {Wandelt} \&
  {Weinberg}}{{Sutter} et~al.}{2012}]{Sutter12b}
{Sutter} P.~M.,  {Lavaux} G.,  {Wandelt} B.~D.,    {Weinberg} D.~H.,  2012,
  \apj, 761, 44

\bibitem[\protect\citeauthoryear{{Sutter}, {Lavaux}, {Wandelt}, {Weinberg} \&
  {Warren}}{{Sutter} et~al.}{2014}]{Sutter14a}
{Sutter} P.~M.,  {Lavaux} G.,  {Wandelt} B.~D.,  {Weinberg} D.~H.,    {Warren}
  M.~S.,  2014, \mnras, 438, 3177

\bibitem[\protect\citeauthoryear{{Tikhonov}}{{Tikhonov}}{2006}]{Tikhonov06}
{Tikhonov} A.~V.,  2006, Astronomy Letters, 32, 727

\bibitem[\protect\citeauthoryear{{Tikhonov}}{{Tikhonov}}{2007}]{Tikhonov07}
{Tikhonov} A.~V.,  2007, Astronomy Letters, 33, 499

\bibitem[\protect\citeauthoryear{{van de Weygaert} \& {van Kampen}}{{van de
  Weygaert} \& {van Kampen}}{1993}]{Weygaert93}
{van de Weygaert} R.,  {van Kampen} E.,  1993, \mnras, 263, 481

\bibitem[\protect\citeauthoryear{{von Benda-Beckmann} \& {M{\"u}ller}}{{von
  Benda-Beckmann} \& {M{\"u}ller}}{2008}]{BendaBeckmann08}
{von Benda-Beckmann} A.~M.,  {M{\"u}ller} V.,  2008, \mnras, 384, 1189

\bibitem[\protect\citeauthoryear{{York}, et al. \& {(the SDSS
  Collaboration),}}{{York} et~al.}{2000}]{York00}
{York} D.~G.,  et al.   {(the SDSS Collaboration),} 2000, \aj, 120, 1579

\bibitem[\protect\citeauthoryear{{Zeldovich}, {Einasto} \&
  {Shandarin}}{{Zeldovich} et~al.}{1982}]{Zeldovich82}
{Zeldovich} I.~B.,  {Einasto} J.,    {Shandarin} S.~F.,  1982, \nat, 300, 407

\bibitem[\protect\citeauthoryear{{Zel'dovich}}{{Zel'dovich}}{1970}]{Zeldovich70}
{Zel'dovich} Y.~B.,  1970, \aap, 5, 84

\end{thebibliography}

\end{document}

### 2015-10-19 paper/paper.tex
intro

@@
 \newcommand{\apj}{ApJ}  
+\newcommand{\jcap}{JCAP}  
 \newcommand{\apjs}{ApJS}  
@@
 \title{A new method to estimate dark matter halo concentrations}
-\author[C. Poveda, J.E. Forero-Romero & J.C. Mu\~noz-Cuartas]{
+\author[C. Poveda, J.E. Forero-Romero, J.C. Mu\~noz-Cuartas]{
 \parbox[t]{\textwidth}{\raggedright 
-  C. Poveda \thanks{cn.poveda542@uniandes.edu.co}$^{1}$,
-  J. E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{1}$,
+  C. Poveda \thanks{cn.poveda542@uniandes.edu.co}$^{1}$
+  J. E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{1}$
   J. C. Mu\~noz-Cuartas \thanks{xxxx@udea.edu.co}$^{2}$
@@
 %*************************************************************************
-
+In the concordance cosmological paradigm the matter content of the
+Universe is dominated by dark matter, a collisionless fluid shaped by
+gravitational interactions.
+In the last three decades simulations of dark matter dominated
+universes have provided valuable insights into the large scale
+structure formation process, showing a remarkable success in the
+comparison between theoretical results and observations of the
+galaxy distribution obtained from surveys.
+\citep{Springel2005,2011ApJ...740..102K}.
+
+On galactic scales the most striking result is that dark matter
+overdensities closely follow a universal density profile. 
+In a first approximation this profile is spherically symmetric and its
+density only dependens on the radial coordinate.
+The universality of this profiles seems to be independent of the
+cosmological parameters and is self-similar for different spatial
+scales after an adequate re-scaling is applied. 
 \citep{NFW,Taylor2001}
+
+One the most popular parameterization for a dark matter halo radial
+density distribution is the Navarro-Frenk-White (NFW) profile
+\citep{NFW}.
+This profile is a double power law in radius, where the transition break
+happens at the so-called scale radius, $r_s$.
+The ratio between the scale radius and the virial radius $R_v$, which
+defines a natural scale for the halo, is known as the concentration
+$c=R_v/r_s$. 
+Simulations also show that the concentration is a strong function of
+halo mass and redshift.
+
+However, high resolution simulations of Milky Way sized dark matter halos
+\citep{Navarro2010} show that the universality property is not
+perfect and that a better fitting parameterization to the radial
+density profile is provided by the Einasto profile
+\citep{Einasto1965}.
+Nevertheless, the NFW density profile and its concentration have
+become a standard metric to describe the structure of dark matter
+halos.
+
+Observationally, the relationship between halo mass and concentration
+could provide a potential test of the Cold Dark Matter (CDM) paradigm
+on galactic scales. 
+For this motivation a great deal of effort has been
+invested in calibrating this relationship with simulations
+\citep{Neto2007,Duffy2008,Munoz2011,Prada2012,Ludlow2014} and 
+finding the best possible way to constraint it with observations
+\citep{Buote2007,Comerford2007,Mandelbaum2008,Giocoli2014,Foex2014,Shan2015}.
+
+In N-body simulations there are two main methods to estimate the
+concentration parameter of a dark matter halo in a N-body simulation.
+The first method takes the particles composing the halos
+and bins them in logarithmic radii to estimate the density in each
+bin, then it proceeds to fit the density as a function of the radius
+to the NFW profile.
+A second method uses an analytic property of the
+NFW profile that relates the maximum of the ratio of the circular velocity to
+the virial velocity.
+The concentration can be then found as the root of a algebraic 
+equation dependent on this maximum value.
+
+The first method is straightforward to apply but presents two
+disadvantages.
+First, it requires a large number of particles in
+order to have a proper density estimate in each bin.
+This makes the method robust only for halos with at least  $10^3$
+particles.
+The second problem is that there is not a way to estimate the optimal
+radial bin size, different choices produce different results for the
+concentration.
+
+The second method solves the two problems mentioned above.
+It works with low particles numbers and does not involve data
+binning.
+However, it effectively takes into account only a single data point
+and discards the behaviour of the ratio $V_{\rm circ}/V_{\rm vir}$ below and
+above its maxima.
+Additionally, small fluctuations on the value of this maximum can
+yield large perturbations on the estimated concentration parameter.
+
+In this paper we propose a new method to estimate the dark matter halo
+concentration in halos from N-body simulations.
+Our method builds the cumulative mass profile from the particle
+to find the best possible concentration value fitting this
+distribution. 
+This proposal has two advantages with respect to the two methods mentioned
+above. 
+It does not involve any data binning and does not throw away data points.
 
@@
 \end{document}
+
 The tracer that we use to define the voids is the fractional

### 2015-10-19 paper/paper.tex
empieza a escribir resultados, borra texto del paper con sebas

@@
 
+\section{Basic properties of the NFW density profile}
+\label{sec:basics}
+
+Let us review first the basic properties of the NFW density
+profile. 
+This help us to define our notation and review the important
+assumptions of the two different methods commonly used to measure the
+concentration to finally present the new method.
+
+\subsection{Density profile}
+
+The NFW density profile can be written as
+
+\begin{equation}
+\rho(r) = \frac{\rho_c\delta_c}{r/r_s(1+r/r_s)^2},
+\label{eq:definition}
+\end{equation}
+%
+where $\rho_c\equiv 3H^2/8\pi G$ is the Universe critical density
+constructed from the Hubble constant $H$ and the universal
+gravitational constant $G$,
+$\delta_c$ is the halo dimensionless characteristic density and $r_s$
+is the scale radius. This radius marks the transition
+between the power law scaling $\rho\propto r^{-1}$ for
+$r<r_s$ and $\rho\propto r^{-3}$ for  $r>r_s$.
+
+We define the virial radius of a halo, $r_v$, as the boundary of the
+spherical volume that encloses a density of $\Delta_h$ times
+the average density of the Universe. 
+The corresponding mass $M_{v}$, the virial mass, can be written as
+$M_{v} = \frac{4\pi}{3}\bar{\rho}\Delta_h r_v^3$.
+From these virial quantities we define new dimensionless variables for
+the radius and mass $x\equiv r/r_v$ and $m\equiv
+M(<r)/M_v$.
+
+In this paper we use $\Delta_h=740$ roughly corresponding to 200 times
+the critical density.
+
+\subsection{Integrated mass profile}
+From these definitions we can compute the total mass enclosed inside a
+radius $r$:
+\begin{equation}
+M(<r) = 4\pi\rho_c\delta_c  r_s^3\left[\ln \left
+  (\frac{r_s+r}{r_s}\right) - \frac{r}{r_s+r}\right],
+\end{equation}
+%
+or in terms of the dimensionless mass and radius variables
+
+\begin{equation}
+m(<x) =
+\frac{1}{A}\left[\ln\left(1+xc\right)-\left(\frac{xc}{xc+1}\right)\right],
+\label{eq:profile}
+\end{equation}
+%
+where
+%
+\begin{equation}
+A=\ln\left(1+c\right)-\left(\frac{c}{c+1}\right),
+\end{equation}
+%
+and the parameter $c$ corresponds to the concentration $c\equiv r_v/r_s$.
+
+From this normalization value and for later convenience we define the
+following function
+%
+\begin{equation}
+f(x) = \ln\left(1+x\right)-\left(\frac{x}{x+1}\right).
+\label{eq:f_NFW}
+\end{equation}
+%
+The most interesting feature of Eq. (\ref{eq:profile}) is that the
+concentration is the only free parameter to describe the integrated
+mass profile.
+
+%In Figure \ref{fig:profiles} we show $m(<x)$ as
+%a function of $x$ for different values of the concentration in the range
+%$1\leq c \leq 20$.
+
+\subsection{Circular velocity profile}
+
+It is also customary to express the mass of the halo in terms of the
+circular velocity $V_{c}=\sqrt{GM(<r)/r}$.
+From this we can define a new dimensionless circular velocity $v(<x)\equiv
+V_{c}(<r)/V_{c}(<r_v)$, using the result in Eq. \ref{eq:profile}
+to have:
+
+\begin{equation}
+v(<x)=\sqrt{\frac{1}{A}\left[\frac{\ln\left(1+xc\right)}{x}-\frac{c}{xc+1}\right]},
+\end{equation}
+
+This normalized profile always shows a maximum provided that the
+concentration is larger than $c>2$.
+It is possible to show that for the NFW profile the maximum is
+provided by
+
+\begin{equation}
+\mathrm{max}(v(<x)) = \sqrt{\frac{c}{x_{\rm max}}\frac{f(x_{\rm
+      max})}{f(c)}},
+\label{eq:max_v}
+\end{equation}
+where $x_{\rm max}=2.163$ \citep{Klypin2014} and the function $f(x)$
+was defined in Eq. (\ref{eq:f_NFW}).
+
+\section{Methods to estimate the concentration from N-body simulations}
+\label{sec:method}
+
+\subsection{Estimates from the density and velocity profiles}
+There are two standard methods to estimate concentrations in dark matter
+halos extracted from N-body simulations.
+
+The first method tries to directly estimate the density profile.
+It takes all the particles in the halo and bins them in the logarithm
+of the radial coordinate from the halo center.
+Then, it estimates the density in each logarithmic bin counting the
+particles and dividing by the corresponding shell volume.
+At this point is is possible to make a direct fit to the density as a
+function of the radial coordinate.
+This method has been most recently used by \cite{Ludlow2014} to study
+the mass-concentration-redshift relation of dark matter halos using
+the Millennium Simulation Series.
+
+A second method uses the circular velocity profile.
+It finds the value of $x$ for which the normalized circular
+velocity $v(<x)$ shows a maximum.
+Using this value it solves numerically for the corresponding value of
+the concentration using Eq. (\ref{eq:max_v}).
+This method has been most recently used by \cite{Klypin2014} to study
+the mass-concentration-redshift relation using the Multidark
+Simulation Suite.
+
+\subsection{Our proposal: estimate from the integrated mass profile}
+Our method uses the integrated mass profile.
+First we define the center of the halo to be at the position of the
+particle with the lowest gravitational potential.
+Then we rank the particles by their increasing radial distance from
+the center.
+From this ranked list of $i=1,N$ particles, the total mass at a radius
+$r_i$ is $M_i=i\times m_p$, where $r_i$ is
+the position of the $i$-th particle and $m_p$ is the mass of a single
+computational particle.
+In this process we discard the particle at the center.
+
+We divide the enclosed mass mass $M_i$ and the radii $r_i$ by their
+virial values to obtain the dimensionless variables $m_i$ and $x_i$.
+Once the mass profile is expressed in dimensionless variables the
+concentration is the only free parameter. We use an Affine Invariant
+Markov chain Monte Carlo implemented in the python module emcee
+\citep{emcee} to sample the likelihood function distribution defined
+by ${\cal L}(c)\propto \exp(-\chi^2(c)/2)$ where the $\chi^2(c)$ is written as
+
+\begin{equation}
+\chi^2(c)= \sum_{i=1}^{N}[\log m_i - \log m(< x_i;c)]^2,
+\end{equation}
+%
+where $m(<x_i;c)$ corresponds to the values in Eq.(\ref{eq:profile}) at
+$x=x_i$ for a given value of the concentration parameter $c$ and the
+$i$ index sums over all the particles in the numerical profile.
+From the $\chi^2$ distribution we find the optimal value of the
+concentration and  its associated uncertainty.
+
+The construction of the numerical integrated mass profile has two
+advantages with respect to the density and velocity methods, it does
+not involve any binning (unlike the density methods ) and the
+sampling method uses the information from all the particles in the
+halo (unlike the velocity method).
+
+\section{Results}
+\label{sec:results}
+
+We now present the results of applying the three methods above
+mentione on two different halo samples.
+The first sample is composed by mock halos generated to have known
+concentration values in perfect spherical symmetry following an NFW
+profile.
+We use this sample to check that we can recover the expected values
+but also gauge the impact of the number of particles on the outcomes.
+The second sample comes from a publicly available N-body cosmological
+simulation.
+From this sample we quantify again the differences between all the
+methods and also estimate the impact on the mass-concentration
+relationship.
+
+\subsection{Mock halo sample}
+
+The method we use to generate the mock halos is based on the integrated
+mass profile.
+We start by fixing the desired concentration $c$ and total number of
+particles $N$ in the mock halo.
+With these values we define the mass element as $\delta m = 1/M$, corresponding
+to the mass of each particle such that the total mass is one.
+Then for each particle, $i=1,\ldots,N$, we find the value of $r_i$ such that
+the difference
+%
+\begin{equation}
+m(<r_i;c) - i \cdot \delta m
+\end{equation}
+%
+is zero using Ridders' method.
+
+The value of $r_i$ is the radius of the $i$-th particle of the mock
+halo.
+Then we generate random polar and azimuthal angles $\theta$ and $\phi$
+for each particle to ensure spherical symmetry.
+Finally these three spherical coordinates are transformed into Cartesian coordinates
+$(r,\theta,\phi) \rightarrow (x,y,z)$.
+
+We generate in total $400$ mock halos split into four different
+groups of $100$ halos each.
+The four groups differ in the total number of particles for their halos:
+$20$, $200$, $2000$ and $20000$.
+Inside each group the halos have random concentration values in
+the range $1<c<20$ with a uniform distribution.
+For all these halos ww the concentration values using the
+density, velocity and mass methods described in the previous
+section. 
+We quantify the difference between the expected $c_{in}$
+and obtained $c_{out}$ values by
+%
+\begin{equation}
+D=(c_{in}-c_{out})/c_{in},
+\label{eq:D}
+\end{equation}
+%
+and
+%
+\begin{equation}
+\avg{|D|}=\frac{1}{\left|{\cal{H}}\right|}\sum_{{\cal{H}}} |D|,
+\end{equation}
+%
+where ${\cal{H}}$ corresponds to a set of mock halos, 
+and $\left|{\cal{H}}\right|$ is the number of haloes in
+${\cal{H}}$.
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.70\textwidth]{error.pdf}
+\end{center}
+\caption{Average value of the relative error in the concentration
+  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
+  the set of mock halos. Different symbols represent different
+  methods. Our method provide the most accurate estimate at fixed
+  particle number $N$.
+    \label{fig:error}}
+\end{figure*}
+
+Figure \ref{fig:error} shows the behaviour of $\avg{|D|}$ as a function of
+halo particle number for the three different methods to estimate the
+concentration.
+
+At fixed particle numbers our method always shows the lowest
+$\avg{|D|}$ values compared to the other two methods.
+Its accuracy is on the order of $10\%$ for $20$ particles in the halo,
+going down to $0.01\%$ for halos with $20000$ particles.
+The dependence of $\avg{|D|}$ with the particle number $N$ goes
+approximately as $\avg{|D|}\propto N^{-1/2}$, hinting that
+the accuracy of the method is related to a decrease of Poisson
+noise.
+
+The method based on the maximum of the circular velocity shows a similar
+behaviour $\avg{|D|}\propto N^{-1/2}$. 
+Its accuracy is $2-5$ times less
+than in our method, on the order of $20\%$ for $20$ particle halos and
+$0.5\%$ for $20000$ particle halos. 
+The method based on the direct density
+fit shows the lowest accuracy for a low particle number and an intermediate
+accuracy between the other two methods for a high particle number.
+
+\subsection{Halos from a cosmological simulation}
+
 \bibliographystyle{mn2e}
@@
 \end{document}
-
-The tracer that we use to define the voids is the fractional
-anisotropy (FA) computed from the set of eigenvalues of the tensor
-under consideration. 
-The FA was initially introduced by \citet{Basser95} to quantify the
-anisotropy degree of the diffusivity of water molecules through
-cerebral tissue in nuclear magnetic resonance imaging, thereby allowing to 
-detect structures that restrict the otherwise isotropic Brownian movement 
-of water molecules. Taking into account that this process is identical to 
-the velocity shear in the large-scale matter distribution, 
-\citet{Libeskind13} introduced the concept of the FA in the context of 
-Cosmic Web classification schemes.
-
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-
-In the next sections (\S \ref{sec:algorithms_cosmic_web} and \S
-\ref{sec:bulk_voids}) we establish the FA as a void tracer and then
-proceed to identify individual voids as basins of FA local minima.  At
-this point we implement a \textit{watershed transform algorithm}
-\citep{Beucher79,Beucher93} which has been used to define voids as
-catching basins of local minima of the density field \citep{Platen07,Neyrinck08}.
-Finally we find and charachterize voids in a N-body (\S
-\ref{sec:simulations} and \S \ref{sec:results}) using density, velocity and
-fractional anisotropy profiles.  We use these results to comment on
-the qualities of our algorithm (\S \ref{sec:conclusions}).
-
-%*************************************************************************
-\section{Algorithms to find the Cosmic Web}
-\label{sec:algorithms_cosmic_web}
-%*************************************************************************
-
-%.........................................................................
-%FIGURE 1: FA and vissual impression
-\begin{figure*}
-  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
-  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
-  \caption{Different fields in a slice of
-    $1\hMpc$ width in the Bolshoi simulation. Top/bottom panels correspond
-    to the T-Web/V-Web.      
-    Fractional Anisotropy field (left); cosmic web classification
-    (middle) for a given value of the threshold eigenvalue
-    $\lambda_{\rm th}$ where voids are white, sheets are light gray,
-    filaments are dark gray and knots are black; individual voids (right) found by 
-    the a watershed algorithm on the Fractional Anisotropy field. Colours
-    in the right panel correspond with the effective radius of each void. }
-  \label{fig:FA_field}
-\end{figure*}
-%.........................................................................
-
-Our new void finding method is based on two existing cosmic web
-classification schemes that work on cosmological N-body simulations.
-Both schemes depend on the construction of tensors based on the
-Hessian of the potential (T-Web scheme) and the shear of the velocity
-(V-Web scheme). 
-These algorithms have been used to develop other
-kind of studies such as the alignment of the shape, spin and peculiar
-velocity of dark matter halos with the cosmic web
-\citep{Libeskind13,Forero2014}. 
-Here we summarize the most relevant aspects of each scheme. 
-We refer the reader to the papers of \cite{Forero09} (T-Web) and
-\cite{Hoffman12} (V-Web) for detailed descriptions.
-
-%-------------------------------------------------------------------------
-\subsection{The tidal web (T-Web)}
-\label{subsec:Tweb}
-%-------------------------------------------------------------------------
-
-This scheme was initially proposed by \citet{Hahn07}  to find the
-Cosmic Web based on the tidal tensor. 
-The tidal tensor allows a classification in terms of the orbital
-dynamics of the matter field.
-This approach extends to second-order the equations of motion around 
-local minima of the gravitational potential. 
-The second-order term corresponds to the tidal tensor, which is
-defined as the Hessian matrix of the normalized gravitational
-potential
-
-%.........................................................................
-%Tidal Tensor
-\eq{V_web}
-{	T_{\alpha\beta} = \frac{\partial^2\phi}{\partial x_{\alpha}\partial x_{\beta}},	}
-%.........................................................................
-where the physical gravitational potential has been rescaled by a
-factor of   $4\pi G\bar{\rho}$ in such a way that $\phi$ satisfies the following 
-Poisson equation
-
-%.........................................................................
-%Poisson
-\eq{Poisson}
-{	\nabla^2\phi = \delta,	}
-%.........................................................................
-with $\bar{\rho}$ the average density in the Universe, $G$ the 
-gravitational constant and $\delta$ the dimensionless matter
-overdensity.
-
-Since the tidal tensor can be represented by a real and  symmetric
-$3\times 3$ matrix, it is always possible to diagonalize  
-it and obtain three real eigenvalues $\lambda_{1}\geq\lambda_{2}\geq
-\lambda_3$ with its corresponding eigenvectors ${\bf u}_{1}$, ${\bf u}_{2}$,
-${\bf u}_{3}$. 
-The eigenvalues are indicators of the local  orbital stability
-in each direction ${\bf u}_i$. 
-The sign of the eigenvalues can be used to classify the Cosmic Web.
-The number of positive (stable) or negative (unstable) eigenvalues allows 
-to label a location into one of the next four types of environment: 
-voids (3 negative eigenvalues), sheets (2), filaments (1) and knots (0).
-
-A modification to this scheme was introduced by \citet{Forero09}
-by means of a relaxation of the stability criterion. 
-The relative strength  of each eigenvalue is no longer defined by the
-sign, but instead by a threshold value $\lambda_{\rm th}$ that can be
-tuned in such a way that the visual impression of the web-like matter
-distribution is reproduced.
-
-%-------------------------------------------------------------------------
-\subsection{The velocity web (V-Web)}
-\label{subsec:Vweb}
-%-------------------------------------------------------------------------
-
-The V-web scheme for environment finding introduced by
-\cite{Hoffman12} is based on the local velocity shear tensor
-calculated from the smoothed dark matter  velocity field in the
-simulation. 
-This tensor is given by the  following expression
-
-%.........................................................................
-%V-Web Definition
-\eq{V_web}
-{	\Sigma_{\alpha\beta} = -\frac{1}{2H_0}\pr{\frac{\partial v_{\alpha}}
-{\partial x_{\beta}}+\frac{\partial v_{\beta}}{\partial x_{\alpha}}},}
-%.........................................................................
-where $v_{\alpha}$ and $x_{\alpha}$ represent the $\alpha$ component of 
-the comoving velocity and position, respectively. Like the tidal tensor, 
-$\Sigma_{\alpha\beta}$ can be represented by a $3\times 3$ symmetric 
-matrix with real values, making it possible to find three real
-eigenvalues and its corresponding eigenvectors.
-
-In this case we also use the relative strength of the three eigenvalues with 
-respect to a threshold value $\lambda_{th}$ to classify the cosmic web
-in the four web types already mentioned.
-
-Usually, the threshold $\lambda_{th}$ is a free parameter that is
-tuned to reproduce the visual appearance of the comic web. 
-However, in this paper this threshold does not play any role in our
-computations.
-In Figure \ref{fig:L1_correlations} we offer a threshold estimate
-(from the FA=$0.95$ as a function of $\lambda_1$, this choice is
-explained in the next section) only as a guide to readers familiar
-with its meaning.
-
-%-------------------------------------------------------------------------
-%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
-\begin{figure*}
-\centering
-  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
-  width=0.33\textwidth]{FA_L1.pdf}  
-  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
-  width=0.33\textwidth]{delta_L1.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
-  width=0.33\textwidth]{FA_delta.pdf}
-  \captionof{figure}{
-    Fractional Anisotropy  as a function of
-    the overdensity (left) and the eigenvalue $\lambda_1$ (middle), and
-    density contrast (right) as a function of the
-    eigenvalue $\lambda_1$ for each web scheme (T-Web,  continuous
-    lines. V-Web, dashed lines).     
-    Fractional Anisotropy  as a function of $\lambda_1$ (left),
-    overdensity as a function of $\lambda_1$ (middle) and Fractional
-    Anisotropy as a function of the overdensity (right).
-    Thick central lines are the median
-    and filled regions include $50\%$ of the cells in each bin. 
-    The left panel shows the tight correlation between FA and
-    $\lambda_1$ in voids.
-    In the middle and right panel we show the equivalent eigenvalue
-    threshold for the T-Web and V-web corresponding to FA=$0.95$. 
-    The right panel confirms that underdense regions can be
-    identified with Fractional Anisotropy values less than $0.95$.
-    For this reason we define voids to be composed by cells with
-    Fractional Anisotropy equal or less than this value.
-    The threshold $\lambda_{\rm th}$ on the eigenvalues does not
-    influence our results. 
-    We show it as a guide to readers familiar with the
-    order of magnitude expectation for this quantity.}
-  \label{fig:L1_correlations}
-
-\end{figure*}
-%.........................................................................
-
-%-------------------------------------------------------------------------
-%FIGURE 3: Histograms for each environment regarding the FA value
-\begin{figure}
-\centering
-  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{FA_environment.pdf}
-   \captionof{figure}{\small Volume of each environment per FA
-   ($dV_i/dFA,\ \ i=v,s,f,k$) normalized by the total volume per FA
-   ($dV/dFA$). 
-  Top/bottom corresponds to the T-Web/V-Web. For a given value of the FA, 
-  each line represents the volume contribution of the respective 
-  environment to the total volume with the same FA value. Above FA=0.95,
-  only sheets and filaments contribute to all the volume of the simulation
-  within that range of FA.}
-  \label{fig:FA_environment}
-\end{figure}
-%.........................................................................
-
-%*************************************************************************
-\section{A new void finding technique}
-\label{sec:bulk_voids}
-%*************************************************************************
-
-%-------------------------------------------------------------------------
-\subsection{The fractional anisotropy}
-\label{subsec:FA_voids}
-%-------------------------------------------------------------------------
-
-% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-
-The fractional anisotropy (FA), as developed by \citet{Basser95}, 
-was conceived to quantify the anisotropy of the diffusivity of water
-molecules through cerebral tissue in nuclear magnetic resonance imaging. 
-In this manner, barriers such as microtubules and cell membranes, that 
-restrict the otherwise isotropic Brownian motion of water molecules, can 
-be detected. In a cosmological context, the problem of finding structures 
-is very similar, where filaments and sheets restrict the otherwise 
-isotropic collapsing/expanding dynamics of the matter. Taking this into 
-account, we present here the FA, much in the same way as \citet{Libeskind13}, 
-to use it as a tracer of cosmic voids.
-
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-
-The FA is defined as follows
-%.........................................................................
-%Fractional anisotropy
-\eq{fractional_anisotropy}
-{{\mathrm{FA}} = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
-(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
-\lambda_2^2 + \lambda_3^2} },}
-%.........................................................................
-where the eigenvalues can be taken from either the T-Web or the V-Web 
-(FA-T-Web and FA-V-Web respectively). Such as it is defined, FA$=0$ 
-corresponds to an isotropic distribution ($\lambda_1=\lambda_2=\lambda_3$) 
-and FA$=1$ to a highly anisotropic distribution.
-
-In the left and middle panels of Fig. \ref{fig:FA_field} we show the
-FA field and web classification for both  web schemes over a slice of
-an N-body simulation (described in Section \ref{sec:simulations}). 
-Comparing these two panels we see that voids and knots (white
-and black in the middle panel of Fig. 1) display low FA values at
-their  centres, becoming gradually more anisotropic at outer regions.  
-On the other hand the filamentary structure (grey in the middle panel
-of Fig. 1) is traced by middle to high FA values.  
-This characteristic is the  key to use the FA as a tracer of cosmic
-voids.
-
-%-------------------------------------------------------------------------
-\subsection{Fractional anisotropy as a void tracer}
-\label{subsec:web_voids}
-%-------------------------------------------------------------------------
-
-Voids are regions where $\lambda_3\leq\lambda_2\leq
-\lambda_1\leq\lambda_{\rm th}$. 
-This implies that a void is completely fixed by the relative strength
-of the $\lambda_1$ eigenvalue with respect to the threshold.   
-As we increase/decrease the threshold value $\lambda_{\rm th}$, voids
-increase/decrease progressively through contours of
-increasing/decreasing $\lambda_1$.  
-Voids are thus characterized by low values of both FA and
-$\lambda_1$.
-
-In Fig. \ref{fig:L1_correlations}  we show that the these two values
-are correlated. 
-The left panel shows the correlation between the FA and $\lambda_1$
-and the middle panel between the overdensity $\delta$ and $\lambda_1$.
-The right panel shows the correlation between $\delta$ and the
-FA. 
-This shows that the  density has a larger scatter at fixed
-$\lambda_1$ than the FA, yet large and  small values of the density
-remain still associated to low values of the FA.
-
-At this point, the eigenvalue $\lambda_1$ and the FA appear to be
-equally potential candidates for tracing cosmic voids, however, the 
-eigenvalue $\lambda_1$ presents, along with the overdensity, an undesirable 
-feature for a void tracer. 
-As we move out from inner parts of voids to outer parts, $\lambda_1$
-and $\delta$ increase monotonically making unclear where to set the
-void boundary, while for low density regions ($\delta<1$) the FA traces
-the boundary where anisotropic collapsing regions begin to 
-dominate, i.e. at the ridge reached around $\delta = 0$ as shown in the 
-right panel of Fig. \ref{fig:L1_correlations}.
-According to Fig. \ref{fig:FA_environment} these anisotropic areas are
-mainly associated to sheets and, to a lesser extent, filaments.
-
-From Figs. \ref{fig:FA_field} and \ref{fig:L1_correlations} we
-conclude that the FA is a good tracer of voids as it is almost perfectly
-correlated with low values of $\lambda_1$. 
-We propose that voids should be composed completely by regions of
-FA$<0.95$.
-If we increase the values of $\lambda_1$ from its minimum until it
-we reach FA$=0.95$ in \ref{fig:L1_correlations} we find that this
-correspond to critical values of $\lambda_{1}^T = 0.265$ and
-$\lambda_{1}^V = 0.175$ for the T-Web and V-Web, respectively.
-This means that setting $\lambda_{th}$ to either
-$\lambda_{1}^T$/$\lambda_{1}^{V}$ automatically produces voids with
-all the cells FA$<0.95$.   
-The middle panels in Fig. \ref{fig:FA_field} show the web
-classification for this choice of $\lambda_{th}$, demonstrating that
-this FA level is a reasonable choice to define voids.
-
-%-------------------------------------------------------------------------
-\subsection{Defining voids with a watershed algorithm}
-\label{subsec:watershed}
-%-------------------------------------------------------------------------
-
-The previous Section shows that FA is a good void tracer, but how
-should we actually define the boundary of individual voids?
-For this purpose, we use the \textit{watershed transform algorithm}
-\citep{Beucher79,Beucher93} to identify a void as the basin of FA
-local minima with boundaries of FA$=0.95$. 
-The advantage of this definition is that it does not require any
-assumption on the shape and/or morphology of the tentative voids.
-
-However, there are two main differences in our approach with respect to other
-watershed implementations.
-First, the watershed technique commonly uses the density field
-instead of the FA field as we do here
-\citep{Platen07,Neyrinck08}.   
-Second, we estimate all relevant quantities on a Cartesian mesh of
-fixed cell size, while other works use an adaptive Delaunay tessellation
-\citep{Schaap00}.
-Nevertheless, in our case the average number of particles per cell
-  is large enough ($512$ particles/cell) ensuring that the lowest
-  density regions are sampled with at least $\sim 10$ particles
-  ($\delta \sim-0.98$), which seems to avoid spurious results from a
-  noisy density field sampling.
-
-The watershed algorithm also needs a threshold value to reduce
-spurious features and prevent void hierarchization.  
-If the density field is used, a typical threshold is
-$\delta = -0.8$ \citep{Platen07},  which means that, given two neighbouring 
-voids, if the mean value of the density across their common boundary is 
-below that threshold, the two voids are merged.
-In our case we have to find a corresponding FA value
-to define this threshold.
-
-In the right panel of Fig. \ref{fig:L1_correlations} we see how 
-the FA correlates with the matter overdensity. 
-A value of $\delta=-0.8$ corresponds to a value of FA$\sim 0.65$
-regardless of the web-finding scheme. 
-This is the value we choose to remove ridges between two watershed
-voids. 
-The right column in Fig. \ref{fig:FA_field} shows all the individual
-voids that have been identified using the watershed algorithm on the
-FA field.
-
-%.........................................................................
-%FIGURE 4: volume functions
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 2mm 2mm 2mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_regions_volume_all.pdf}
-  \includegraphics[trim = 2mm 2mm 2mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_regions_volume_compensated.pdf}
-
-  \captionof{figure}{\small Left panel, void size distribution. Right
-    panel, fraction of overcompensated/subcompensated ($C>1/C<1$)voids as a
-    function of the effective radius. The continuous (dashed)
-    curves correspond to the T-Web (V-Web).
-    The abundance for small ($\reff <2.0\hMpc$) overcompensated voids
-    shoots up in the V-Web scheme.
-    We provide in the body of the paper two reasons for this behaviour.}
-  \label{fig:volume_function}
-
-\end{figure*}
-%.........................................................................
-
-\section{Numerical Simulation}
-\label{sec:simulations}
-
-We use the Bolshoi simulation to test our void finding method. 
-This simulation follows the non-linear evolution of a dark
-matter density field on a cubic volume of  size $250$\hMpc\ sampled
-with $2048^3$ particles. 
-The cosmological parameters in the simulation are $\Omega_{\rm
-  m}=0.27$,  $\Omega_{\Lambda}  =0.73$, $h=0.70$, $n=0.95$ and
-$\sigma_{8}=0.82$ for the matter density,   cosmological 
-constant, dimensionless Hubble parameter, spectral index of
-primordial density perturbations and normalization for the power
-spectrum, respectively. 
-These values are consistent with the ninth year of data of the
-Wilkinson  Microwave Anisotropy Probe (WMAP) \citep{Hinshaw2013}. 
-For more detailed  technical information about the simulation, see
-\citet{Klypin11}.
-
-We use data for the cosmic web identification that is publicly
-available through the MultiDark database
-\url{http://www.multidark.org/MultiDark/} which is described in
-\citet{Riebe11}. 
-Here we briefly describe the process to obtain the data. 
-For details see \cite{Forero09} (T-Web);
-\cite{Hoffman12,Forero2014} (V-Web). 
-This data is based on a  \textit{cloud-in-cell} (\texttt{CIC})
-interpolation of the density and velocity fields of the simulation
-onto a grid of $256^3$  cells, corresponding to a spatial resolution
-of $0.98$\hMpc\ per cell side.    
-These fields are smoothed with a gaussian filter with a width of 
-$\sigma=0.98$\hMpc. 
-The tidal and shear tensors and corresponding eigenvalues are computed
-through finite-differences over the potential and velocity fields.
-
-%*************************************************************************
-\section{Results}
-\label{sec:results}
-%*************************************************************************
-
-We limit our results to voids with effective radius larger than the
-smoothing length of the density field, i.e. $\sim 1$\hMpc.  
-For smaller interpolation/smoothing scales the shot noise in
-  the low density regions starts to be noticeable.
-With that choice we find a void volume filling fraction $54.88\%$ and
-$47.06\%$ for the FA-Vweb and the FA-Tweb, respectively.  
-For larger smoothing scales ($>5\hMpc$) the density and shear fields
-  tend to be Gaussian and therefore follow closely the analytical
-  environment abundance predictions for Gaussian random fields
-  \citep{Forero09,Alonso2015}.  
-In this paper we limit ourselves to a smoothing scale $\sim 1$ \hMpc.
-
-In the following subsections we describe the results for the size
-distribution and different radial profiles for all our samples.
-
-%-------------------------------------------------------------------------
-\subsection{The void size distribution}
-\label{subsec:shape_voids}
-%-------------------------------------------------------------------------
-
-Void shapes exhibit a wide range of geometries.
-To define their size we use its equivalent spherical radius or
-effective radius, defined as $\reff = [3/(4\pi)V]^{1/3}$, with $V$ the 
-total volume of the void computed from the individual grid cells
-assigned to the void.   
-In Fig. \ref{fig:volume_function} we show the void size
-distributions for the T-Web and the V-Web.
-
-We see that the void distribution for the T-Web is broadly consistent with the
-expectations from a two-barrier problem  \citep{Sheth04}. 
-The formation of large voids is limited by the \textit{void-in-void}
-mechanism (first barrier) where large voids are constituted
-hierarchically of smaller ones. 
-In turn, the formation of small voids is damped by the
-\textit{void-in-cloud} mechanism (second barrier),  where nearby
-collapsing structures limit the abundance of small embedded voids.
-
-We also find that the V-Web scheme produces an over-abundance of small
-voids compared to T-Web.
-A large number of these small voids are embedded in overdense regions. 
-They are already visible in the middle panel of Fig. \ref{fig:FA_field} as
-tiny white bubbles located inside sheets.
-The existence of these small voids can be explained by
-dynamics of shell crossing in collapsing sheets as discussed in
-\citet{Hoffman12}.    
-The main argument is that as matter collides into a pancake-like
-fashion crossing sheets encounter each other at the symmetry plane.
-This effectively gives a positive divergence in the velocity
-field, resulting in a void identification by the V-Web algorithm.
-
-Comparing the abundance of large voids in the two web schemes, we find
-that the largest voids in the V-Web have $\reff \sim 10$\hMpc,
-while the T-Web scheme includes voids as large as $\reff \sim 15$\hMpc. 
-This suggests that large voids in the T-Web scheme have a velocity
-structure that splits them in the V-Web. 
-This increased granularity in the velocity structure of voids is
-evident in the left and right panels of Fig. \ref{fig:FA_field}.
-
-%.........................................................................
-%FIGURE 5: Density profile of voids for each defined scheme
-\begin{figure*}
-\centering
-  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_density_TwebFAG0.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_density_TwebFAG1.pdf}
-
-  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_density_VwebFAG0.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_density_VwebFAG1.pdf}
-
-  \captionof{figure}{\small Spherically averaged radial density profiles for
-    stacked voids with different effective radii. The sample is split
-    into subcompensated and overcompensated voids (right and left) for
-    the web schemes T-Web and V-Web (top and bottom).}
-  \label{fig:density_profile}
-  \vspace{0.1 cm}
-\end{figure*}
-
-\begin{figure*}
-\centering  
-  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_velocity_TwebFAG0.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_velocity_TwebFAG1.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_velocity_VwebFAG0.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_velocity_VwebFAG1.pdf}
-  \captionof{figure}{\small Spherically averaged radial velocity
-    profiles for stacked voids with different effective radii. The
-    sample is split into subcompensated and overcompensated voids
-    (right and left) for the web schemes T-Web and V-Web (top and
-    bottom).} 
-  \label{fig:velocity_profile}
-  \vspace{0.1 cm}
-\end{figure*}
-
-\begin{figure*}
-\centering  
-  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_FA_TwebFAG0.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_FA_TwebFAG1.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_FA_VwebFAG0.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_FA_VwebFAG1.pdf}
-
-  \captionof{figure}{\small Spherically averaged Fractional Anisotropy
-    profiles for stacked voids with different effective radii. The
-    sample is split into subcompensated and overcompensated voids
-    (right and left) for the web schemes T-Web and V-Web (top and
-    bottom).} 
-  \label{fig:FA_profile}
-  \vspace{0.1 cm}
-
-\end{figure*}
-%.........................................................................
-
-%-------------------------------------------------------------------------
-\subsection{Subcompensated and overcompensated voids}
-\label{subsec:enclosedmass}
-%-------------------------------------------------------------------------
-
-We find that voids are distributed in two different families
-differentiated by the 
-presence/absence of an overdense matter ridge in their density
-profiles. 
-To discriminate each void in one of the families we use the
-compensation  index $C$
-It is defined as the mass of a void enclosed in a spherical volume of
-radius $R$ and normalized by the mass of the same volume assuming
-it is filled by matter with the mean background density.
-
-\eq{compensation}
-{C= \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr}
-
-We choose an integration radius of $R=4\reff$, that is large enough to 
-enclose the compensation ridge for a typical void in case there is one. 
-This leads us to voids with $C>1$ having more mass than expected, 
-constituting the family of overcompensated voids. 
-These voids generally  exhibit a compensation ridge associated to
-dense nearby structures. 
-In the same fashion, voids with $C<1$ constitute the family
-of  subcompensated voids.
-
-In Fig. \ref{fig:density_profile} we show the density and velocity profiles
-of voids split in these two families. 
-In the left column it becomes clear the difference between sub- and
-overcompensated voids. 
-Table \ref{tab:number_voids} lists the number of voids in 
-each effective radius bin for the two web finding methods.
-
-%.........................................................................
-\begin{table}[!htbp]
-\centering
-\begin{tabular}{c | c c | c c}
-\toprule
-\multicolumn{1}{c}{}&  \multicolumn{2}{c}{\textbf{Tweb}} & \multicolumn{2}{c}{\textbf{Vweb}}\\
-%\midrule
-\textbf{${\bf \reff }$[\hMpc]}   & $\bf{C<1}$   & $\bf{C>1}$    & $\bf{C<1}$   & $\bf{C>1}$\\ \hline
-%\midrule
-$<2.0$        &  997 & 495   & 13480  & 711\\
-$2.0-3.2$     &  791 & 471   & 2581   & 583\\
-$3.2-4.4$     &  941 & 469   & 2168   & 656\\
-$4.4-5.6$     &  869 & 467   & 1934   & 724\\
-$5.6-6.8$     &  769 & 395   & 1287   & 584\\
-$6.8-8.3$     &  665 & 362   & 700    & 315\\
-$8.3-12.0$    &  587 & 333   & 123    & 61\\
-$>12.0$       &  29  & 23    & 0      & 0\\ \hline
-\textbf{total}& 5648 & 3015  & 22273  & 3634\\
-\bottomrule
-\end{tabular}
-\caption{Number of voids for each bin of effective radius and for 
-subcompensanted and overcompansated samples.}
-\label{tab:number_voids}
-\end{table}
-%.........................................................................
-
-%.........................................................................
-\subsection{Density profiles}
-\label{subsec:density_voids}
-%.........................................................................
-
-We calculate the contrast density, radial-projected velocity and 
-FA profiles. 
-For this purpose we stack voids with similar effective radius.
-We also compute the profiles separately  for subcompensated and
-overcompensated voids. 
-For each void,  
-we take the distance of each member cell to the void centre along with the 
-properties of interest. 
-We normalize the radial distance with the effective radius and add the
-result to the stack.
-
-Fig. \ref{fig:density_profile} shows the results of stacked density
-profiles for different void sizes.  
-We calculate the profile out to a radius $8\ \reff$  to capture the
-point where the overdensity reaches the mean value.
-
-The first interesting result is the overdensity value at the void's
-centre.
-We find that larger voids have a lower overdensity value.
-The largest voids ($8.3-12\ \hMpc$) have an underdensity
-$\delta \sim-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\sim 
--0.8$ at their centres.
-This holds for both web schemes. 
-These values are consistent with most of the void finding schemes
-based on smooth and continuous fields from simulation or
-reconstruction procedures on surveys \citep{Plionis02, Colberg05,
-  Shandarin06,  Platen07, Neyrinck08, MunozCuartas11, Ceccarelli13,
-  Paz13, Neyrinck13, Ricciardelli2013}, unlike geometrical approaches based 
-on point distributions, where central density values are generally higher
-\citep{Colberg08}.
-
-A second feature about these profiles is their steepness at inner
-regions.  
-In subcompensated voids, larger voids are steeper.
-Smaller voids exhibit moderate slopes, reaching the mean density at
-larger radii than larger voids.
-This suggests that small subcompensated voids are embedded into low
-density structures, while large subcompensated voids are surrounded
-by dense structures, reaching the mean density at lower effective
-radii than smaller voids. 
-In the overcompensated case larger voids reach first  both the
-compensation ridge and then the mean density value.
-
-Regarding overcompensated voids, a final result is related to the height 
-of the compensation ridge: the larger the void size, the lower the ridge
-height. This implies that overcompensated smaller voids are embedded in 
-very high density regions, unlike their subcompensated counterpart, thus 
-indicating two possibly different processes for small voids formation. 
-Larger voids exhibit lower ridges as outer radial layers also includes all
-sort of structures, thus being the difference between large overcompensated
-and subcompensated voids less conclusive.
-
-All the previous results hold for both finding schemes.
-This suggests an universal behaviour for the radial density profile in
-two families of subcompensated and overcompensanted voids. 
-This goes in the same direction of recent results about the internal
-\citep{Colberg05,  Ricciardelli2013} and external structure of voids
-\citep{Lavaux12, Ceccarelli13, Paz13, Hamaus14}. 
-Indeed, our results extend the findings of \cite{Hamaus14} into the
-range of voids with size $\reff <10$\hMpc.
-
-%.........................................................................
-\subsection{Velocity profiles}
-\label{subsec:velocity_voids}
-%.........................................................................
-
-In Fig. \ref{fig:velocity_profile} we present the radial velocity
-profiles. 
-Positive values correspond to outflows with respect to the centre.
-
-We find that subcompensated voids have outflowing velocity profiles
-all the way up to the radius where the average radial
-density reaches zero.
-In voids with sizes $\reff <8\hMpc$ the outflow is always
-positive, consistent with the fact that their density profiles do not
-reach the level $\delta=0$ in the range of explored radii.
-This behaviour indicates that matter is being pulled out of the void
-into external higher density features.
-
-On the other hand, overcompensated voids initially exhibit outward
-profiles, (as expected from a low density region) and approximately at
-the radius of the compensation ridge, the velocity reaches a peak,
-decreases and becomes negative, showing the infalling flow of matter
-further than the compensation ridge. 
-This shows that the high density structures associated to the
-compensation ridge dominate the matter flow both from inside and
-outside the void.
-
-As in the density, these results are also consistent with a Universal
-velocity profile for voids \citep{Paz13, Hamaus14}.
-
-%.........................................................................
-\subsection{Fractional Anisotropy profiles}
-\label{subsec:FA_voids}
-%.........................................................................
-
-Fig. \ref{fig:FA_profile} shows the results for the FA profiles.
-We find that the FA clearly magnifies the difference between the
-internal profile $r/\reff <1$ and the external profile $r/\reff >1$. 
-Subcompensanted voids in the T-Web reach an asymptotic background
-value of F=$0.8$ almost right at $r/\reff =2$. 
-For the V-Web the results are similar, albeit with a slower trend with
-the effective radius. 
-Overcompensated voids reach a maximum FA at the same effective radius
-$r/\reff =1$ and decline to reach an asymptotic value of FA=$0.85$
-at larger radii.
-
-The central FA values also show a magnified trend with the void size. 
-Large voids have lower FA values, amplifying the same trend
-observed with the central density value. 
-Finally, we observe that voids in the V-Web scheme span a larger range
-of central FA values than in the T-Web scheme.
-
-The difference between the radius where the density ridge is reached 
-($r/\reff =3$) and the radius of the FA maxima ($r/\reff =1$, most
-manifest in the T-Web voids) justifies in a more quantitative way the
-qualitative argument we present in sub-section \ref{subsec:watershed}
-to define void boundaries in our method.  
-Namely that as we increase the void boundary moving away from the
-centre, we reach first middle density walls, before reaching high
-density structures associated with high anisotropy.  
-This implies that voids defined with the FA never present positive
-overdensities, making the FA maximum a reasonable boundary for voids
-compared to the traditional definition that puts the boundary at the
-density ridge.
-
-We recognize that our choice produces smaller voids as compared with
-other voids finding methods. 
-We consider that this has the advantage of
-avoiding the contamination from external structures.
-
-%*************************************************************************
-\section{Conclusions}
-\label{sec:conclusions}
-%*************************************************************************
-
-In this paper we propose that the anisotropy of the eigenvalues from
-tidal and velocity shear tensors is a good tracer of  cosmic voids. 
-Based on this idea we go on to implement a watershed
-algorithm on the fractional anisotropy to find voids in a N-body
-cosmological simulation.
-We perform different test on the voids found on the anisotropy of two
-tensorial schemes, the T-Web and the V-web.
-
-The first quantity we examine is the void size distribution
-characterized by an effective radius. 
-We find that for the T-Web scheme the void size distribution has a
-shape consistent with standard expectations from a two-barrier setup. 
-However, for the V-Web we find an overabundance of the smallest voids.
-This is due to two reasons. 
-First, there are artefacts in the web
-finding scheme inside sheets. 
-Second, there V-web produces smaller
-fragmented voids inside the largest voids found in the T-Web
-classification.  
-This void fragmentation hints at a complex velocity structure in large
-voids compared to its simpler density/gravitational potential anatomy.
-
-A second step in the void characterization 
-is the separation into subcompensated and overcompensated samples. 
-In the T-Web $35\%$ of the voids are overcompensated and $65\%$
-subcompensated, meaning that they are located in denser regions with
-a clear delimiting ridge.   
-For the V-web the subcompensated fraction rises to $85\%$ as the
-void size decreases, supporting the picture of smaller spurious voids
-located in medium density matter sheets.
-
-Finally we proceed with a more detailed void characterization
-through the radially averaged profiles of density, radial velocity and
-fractional anisotropy. 
-In this case we study separately the subcompensated and
-overcompensated voids, split this time in samples with different
-effective radii.
-
-For the density the most interesting feature is that the  profile has
-a similar shape for all the different void sizes once the radial
-coordinate is expressed in units of the effective radius.  
-In these profiles it is evident the presence of an overdense ridge
-around $2<r/\reff <3$ for the overcompensated voids.
-Subcompensated voids do not show such a ridge keeping its density
-lower than the average value up to $r/\reff \sim 8$.
-
-In other studies where voids are found using considerations on the
-density fields the ridge is, almost by definition, located around
-$r/\reff \sim 1$ and the subcompensated voids reach average
-density around $r/\reff \sim 3$. 
-This indicates that voids defined by FA boundaries are smaller  than
-voids found by density only considerations close by a radial factor of
-$2$.
-
-The velocity profiles show the expected correlation with the features
-already observed in the density.
-Most notably the radial velocity goes to zero close to flat regions in
-the density profile and is positive around regions of increasing
-density with radius.
-
-The FA profiles also show remarkable similarities
-inside each class of subcompensated and overcompensated voids
-and a close correlation with the behaviour in the density and velocity
-profiles. 
-From these profiles it becomes clear that the limit of overcompensated
-void coincides with a ridge in of FA values close to $0.9$. 
-This value is close to the limit FA=$0.95$ we impose in the watershed
-algorithm, indicating that these voids are very close to spherical.
-For the subcompensated voids the FA quickly increases to FA values of 
-$\sim 0.7-0.8$ at $r/\reff \sim 1$ to find a plateau, which is
-quite far from the limiting FA$=0.95$ suggesting that these voids are
-ellipsoidal.
-
-Put together, the results for the radially averaged profiles support the 
-evidence for a universal density profile.  
-Our results extend to smaller void sizes the work done by
-\cite{Hamaus14} on simulations and by \cite{Ceccarelli13} on SDSS data.
-
-The method we present here finds voids with reasonable properties
-compared to different results published in the literature. 
-This gives support to a new tracer, the Fractional Anisotropy, to be
-used in the study of cosmic voids. 
-Furthermore, the complementary physical picture in the two different
-web finding algorithms opens the possibilities to make a joint
-analysis of the tidal and dynamical structure of voids.
-
-%*************************************************************************
-\section*{Acknowledgments}  
-%*************************************************************************
-
-We would like to thank Fiona Hoyle and Rien van de Weygaert for their
-exhaustive and thoughtful reviews, accompanied with very detailed and
-helpful suggestions on earlier versions of this manuscript.  
-We also thank Nelson Padilla and Yehuda Hoffman for enlightening
-comments and discussions.
-SB also thanks Juan Carlos Mu\~noz-Cuartas 
-for many clarifying discussions and helpful ideas.
-JEFR acknowledges financial support from Vicerrector\'ia de
-Investigaciones at Universidad de los Andes (Colombia) through a FAPA
-grant.
-
-\begin{thebibliography}{}
-
-\bibitem[\protect\citeauthoryear{{Abazajian}, et al. \& {(the SDSS
-  Collaboration)}}{{Abazajian} et~al.}{2003}]{Abazajian03}
-{Abazajian} K.,  et al.   {(the SDSS Collaboration)} 2003, \aj, 126, 2081
-
-\bibitem[\protect\citeauthoryear{{Alonso}, {Eardley} \& {Peacock}}{{Alonso}
-  et~al.}{2015}]{Alonso2015}
-{Alonso} D.,  {Eardley} E.,    {Peacock} J.~A.,  2015, \mnras, 447, 2683
-
-\bibitem[\protect\citeauthoryear{{Basser}}{{Basser}}{1995}]{Basser95}
-{Basser} P.,  1995, NMR in Biomedical Imaging, 8, 333
-
-\bibitem[\protect\citeauthoryear{{Bertschinger}}{{Bertschinger}}{1985}]{Bertschinger85}
-{Bertschinger} E.,  1985, \apjs, 58, 1
-
-\bibitem[\protect\citeauthoryear{{Beucher} \& {Lantuejoul}}{{Beucher} \&
-  {Lantuejoul}}{1979}]{Beucher79}
-{Beucher} S.,  {Lantuejoul} C.,  1979, in Proceedings Interna- tional Workshop
-  on Image Processing, CCETT/IRISA, Rennes, France
-
-\bibitem[\protect\citeauthoryear{{Beucher} \& {Meyer}}{{Beucher} \&
-  {Meyer}}{1993}]{Beucher93}
-{Beucher} S.,  {Meyer} F.,  1993, {Mathematical Morphology in Image
-  Processing}.
-Marcel Deker, New York
-
-\bibitem[\protect\citeauthoryear{{Blumenthal}, {da Costa}, {Goldwirth}, {Lecar}
-  \& {Piran}}{{Blumenthal} et~al.}{1992}]{Blumenthal92}
-{Blumenthal} G.~R.,  {da Costa} L.~N.,  {Goldwirth} D.~S.,  {Lecar} M.,
-  {Piran} T.,  1992, \apj, 388, 234
-
-\bibitem[\protect\citeauthoryear{{Bond}, {Kofman} \& {Pogosyan}}{{Bond}
-  et~al.}{1996}]{Bond96}
-{Bond} J.~R.,  {Kofman} L.,    {Pogosyan} D.,  1996, \nat, 380, 603
-
-\bibitem[\protect\citeauthoryear{{Brunino}, {Trujillo}, {Pearce} \&
-  {Thomas}}{{Brunino} et~al.}{2007}]{Brunino07}
-{Brunino} R.,  {Trujillo} I.,  {Pearce} F.~R.,    {Thomas} P.~A.,  2007,
-  \mnras, 375, 184
-
-\bibitem[\protect\citeauthoryear{{Ceccarelli}, {Padilla}, {Valotto} \&
-  {Lambas}}{{Ceccarelli} et~al.}{2006}]{Ceccarelli06}
-{Ceccarelli} L.,  {Padilla} N.~D.,  {Valotto} C.,    {Lambas} D.~G.,  2006,
-  \mnras, 373, 1440
-
-\bibitem[\protect\citeauthoryear{{Ceccarelli}, {Paz}, {Lares}, {Padilla} \&
-  {Lambas}}{{Ceccarelli} et~al.}{2013}]{Ceccarelli13}
-{Ceccarelli} L.,  {Paz} D.,  {Lares} M.,  {Padilla} N.,    {Lambas} D.~G.,
-  2013, \mnras, 434, 1435
-
-\bibitem[\protect\citeauthoryear{{Chincarini} \& {Rood}}{{Chincarini} \&
-  {Rood}}{1975}]{Chincarini75}
-{Chincarini} G.,  {Rood} H.~J.,  1975, \nat, 257, 294
-
-\bibitem[\protect\citeauthoryear{{Colberg}, {Pearce} \& et al.}{{Colberg}
-  et~al.}{2008}]{Colberg08}
-{Colberg} J.~M.,  {Pearce} F.,    et al. 2008, \mnras, 387, 933
-
-\bibitem[\protect\citeauthoryear{{Colberg}, {Sheth}, {Diaferio}, {Gao} \&
-  {Yoshida}}{{Colberg} et~al.}{2005}]{Colberg05}
-{Colberg} J.~M.,  {Sheth} R.~K.,  {Diaferio} A.,  {Gao} L.,    {Yoshida} N.,
-  2005, \mnras, 360, 216
-
-\bibitem[\protect\citeauthoryear{{Colless}, et al. \& {(the 2dFGRS
-  Team),}}{{Colless} et~al.}{2001}]{Colless01}
-{Colless} M.,  et al.   {(the 2dFGRS Team),} 2001, \mnras, 328, 1039
-
-\bibitem[\protect\citeauthoryear{{Colless}, et al. \& {(the 2dFGRS
-  Team),}}{{Colless} et~al.}{2003}]{Colless03}
-{Colless} M.,  et al.   {(the 2dFGRS Team),} 2003, VizieR Online Data Catalog,
-  7226
-
-\bibitem[\protect\citeauthoryear{{Croton} \& et al.}{{Croton} \&
-  et~al.}{2004}]{Croton04}
-{Croton} D.~J.,  et al. 2004, \mnras, 352, 828
-
-\bibitem[\protect\citeauthoryear{{Dubinski}, {da Costa}, {Goldwirth}, {Lecar}
-  \& {Piran}}{{Dubinski} et~al.}{1993}]{Dubinski93}
-{Dubinski} J.,  {da Costa} L.~N.,  {Goldwirth} D.~S.,  {Lecar} M.,    {Piran}
-  T.,  1993, \apj, 410, 458
-
-\bibitem[\protect\citeauthoryear{{Einasto}, {Joeveer} \& {Saar}}{{Einasto}
-  et~al.}{1980a}]{Einasto80M}
-{Einasto} J.,  {Joeveer} M.,    {Saar} E.,  1980a, \mnras, 193, 353
-
-\bibitem[\protect\citeauthoryear{{Einasto}, {Joeveer} \& {Saar}}{{Einasto}
-  et~al.}{1980b}]{Einasto80N}
-{Einasto} J.,  {Joeveer} M.,    {Saar} E.,  1980b, \nat, 283, 47
-
-\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Contreras} \&
-  {Padilla}}{{Forero-Romero} et~al.}{2014}]{Forero2014}
-{Forero-Romero} J.~E.,  {Contreras} S.,    {Padilla} N.,  2014, \mnras, 443,
-  1090
-
-\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Hoffman}, {Gottl{\"o}ber},
-  {Klypin} \& {Yepes}}{{Forero-Romero} et~al.}{2009}]{Forero09}
-{Forero-Romero} J.~E.,  {Hoffman} Y.,  {Gottl{\"o}ber} S.,  {Klypin} A.,
-  {Yepes} G.,  2009, \mnras, 396, 1815
-
-\bibitem[\protect\citeauthoryear{{Foster} \& {Nelson}}{{Foster} \&
-  {Nelson}}{2009}]{Foster09}
-{Foster} C.,  {Nelson} L.~A.,  2009, \apj, 699, 1252
-
-\bibitem[\protect\citeauthoryear{{Gottl{\"o}ber}, {{\L}okas}, {Klypin} \&
-  {Hoffman}}{{Gottl{\"o}ber} et~al.}{2003}]{Gottlober03}
-{Gottl{\"o}ber} S.,  {{\L}okas} E.~L.,  {Klypin} A.,    {Hoffman} Y.,  2003,
-  \mnras, 344, 715
-
-\bibitem[\protect\citeauthoryear{{Gregory} \& {Thompson}}{{Gregory} \&
-  {Thompson}}{1978}]{Gregory78}
-{Gregory} S.~A.,  {Thompson} L.~A.,  1978, \apj, 222, 784
-
-\bibitem[\protect\citeauthoryear{{Hahn}, {Porciani}, {Carollo} \&
-  {Dekel}}{{Hahn} et~al.}{2007}]{Hahn07}
-{Hahn} O.,  {Porciani} C.,  {Carollo} C.~M.,    {Dekel} A.,  2007, \mnras, 375,
-  489
-
-\bibitem[\protect\citeauthoryear{{Hamaus}, {Sutter} \& {Wandelt}}{{Hamaus}
-  et~al.}{2014}]{Hamaus14}
-{Hamaus} N.,  {Sutter} P.~M.,    {Wandelt} B.~D.,  2014, Physical Review
-  Letters, 112, 251302
-
-\bibitem[\protect\citeauthoryear{{Hinshaw} et~al.,}{{Hinshaw}
-  et~al.}{2013}]{Hinshaw2013}
-{Hinshaw} G.  et~al., 2013, \apjs, 208, 19
-
-\bibitem[\protect\citeauthoryear{{Hoffman}, {Metuki}, {Yepes}, {Gottl{\"o}ber},
-  {Forero-Romero}, {Libeskind} \& {Knebe}}{{Hoffman} et~al.}{2012}]{Hoffman12}
-{Hoffman} Y.,  {Metuki} O.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Forero-Romero}
-  J.~E.,  {Libeskind} N.~I.,    {Knebe} A.,  2012, \mnras, 425, 2049
-
-\bibitem[\protect\citeauthoryear{{Hoffman} \& {Shaham}}{{Hoffman} \&
-  {Shaham}}{1982}]{Hoffman82}
-{Hoffman} Y.,  {Shaham} J.,  1982, \apjl, 262, L23
-
-\bibitem[\protect\citeauthoryear{{Hoyle} \& {Vogeley}}{{Hoyle} \&
-  {Vogeley}}{2004}]{Hoyle04}
-{Hoyle} F.,  {Vogeley} M.~S.,  2004, \apj, 607, 751
-
-\bibitem[\protect\citeauthoryear{{Icke}}{{Icke}}{1984}]{Icke84}
-{Icke} V.,  1984, \mnras, 206, 1P
-
-\bibitem[\protect\citeauthoryear{{Kauffmann} \& {Fairall}}{{Kauffmann} \&
-  {Fairall}}{1991}]{Kauffmann91}
-{Kauffmann} G.,  {Fairall} A.~P.,  1991, \mnras, 248, 313
-
-\bibitem[\protect\citeauthoryear{{Kirshner}, {Oemler} Jr., {Schechter} \&
-  {Shectman}}{{Kirshner} et~al.}{1981}]{Kirshner81}
-{Kirshner} R.~P.,  {Oemler} Jr. A.,  {Schechter} P.~L.,    {Shectman} S.~A.,
-  1981, \apjl, 248, L57
-
-\bibitem[\protect\citeauthoryear{{Kirshner}, {Oemler} Jr., {Schechter} \&
-  {Shectman}}{{Kirshner} et~al.}{1987}]{Kirshner87}
-{Kirshner} R.~P.,  {Oemler} Jr. A.,  {Schechter} P.~L.,    {Shectman} S.~A.,
-  1987, \apj, 314, 493
-
-\bibitem[\protect\citeauthoryear{{Klypin}, {Trujillo-Gomez} \&
-  {Primack}}{{Klypin} et~al.}{2011}]{Klypin11}
-{Klypin} A.~A.,  {Trujillo-Gomez} S.,    {Primack} J.,  2011, \apj, 740, 102
-
-\bibitem[\protect\citeauthoryear{{Lavaux} \& {Wandelt}}{{Lavaux} \&
-  {Wandelt}}{2012}]{Lavaux12}
-{Lavaux} G.,  {Wandelt} B.~D.,  2012, \apj, 754, 109
-
-\bibitem[\protect\citeauthoryear{{Libeskind}, {Hoffman}, {Forero-Romero},
-  {Gottl{\"o}ber}, {Knebe}, {Steinmetz} \& {Klypin}}{{Libeskind}
-  et~al.}{2013}]{Libeskind13}
-{Libeskind} N.~I.,  {Hoffman} Y.,  {Forero-Romero} J.,  {Gottl{\"o}ber} S.,
-  {Knebe} A.,  {Steinmetz} M.,    {Klypin} A.,  2013, \mnras, 428, 2489
-
-\bibitem[\protect\citeauthoryear{{Martel} \& {Wasserman}}{{Martel} \&
-  {Wasserman}}{1990}]{Martel90}
-{Martel} H.,  {Wasserman} I.,  1990, \apj, 348, 1
-
-\bibitem[\protect\citeauthoryear{{Micheletti} et~al.,}{{Micheletti}
-  et~al.}{2014}]{Micheletti14}
-{Micheletti} D.  et~al., 2014, \aap, 570, A106
-
-\bibitem[\protect\citeauthoryear{{Mu{\~n}oz-Cuartas}, {M{\"u}ller} \&
-  {Forero-Romero}}{{Mu{\~n}oz-Cuartas} et~al.}{2011}]{MunozCuartas11}
-{Mu{\~n}oz-Cuartas} J.~C.,  {M{\"u}ller} V.,    {Forero-Romero} J.~E.,  2011,
-  \mnras, 417, 1303
-
-\bibitem[\protect\citeauthoryear{{M{\"u}ller}, {Arbabi-Bidgoli}, {Einasto} \&
-  {Tucker}}{{M{\"u}ller} et~al.}{2000}]{Muller00}
-{M{\"u}ller} V.,  {Arbabi-Bidgoli} S.,  {Einasto} J.,    {Tucker} D.,  2000,
-  \mnras, 318, 280
-
-\bibitem[\protect\citeauthoryear{{Nadathur} \& {Hotchkiss}}{{Nadathur} \&
-  {Hotchkiss}}{2014}]{Nadathur14}
-{Nadathur} S.,  {Hotchkiss} S.,  2014, \mnras, 440, 1248
-
-\bibitem[\protect\citeauthoryear{{Neyrinck}}{{Neyrinck}}{2008}]{Neyrinck08}
-{Neyrinck} M.~C.,  2008, \mnras, 386, 2101
-
-\bibitem[\protect\citeauthoryear{{Neyrinck}, {Falck} \& {Szalay}}{{Neyrinck}
-  et~al.}{2013}]{Neyrinck13}
-{Neyrinck} M.~C.,  {Falck} B.~L.,    {Szalay} A.~S.,  2013, ArXiv e-prints
-
-\bibitem[\protect\citeauthoryear{{Padilla}, {Ceccarelli} \& {Lambas}}{{Padilla}
-  et~al.}{2005}]{Padilla05}
-{Padilla} N.~D.,  {Ceccarelli} L.,    {Lambas} D.~G.,  2005, \mnras, 363, 977
-
-\bibitem[\protect\citeauthoryear{{Pan}, {Vogeley}, {Hoyle}, {Choi} \&
-  {Park}}{{Pan} et~al.}{2012}]{Pan10}
-{Pan} D.~C.,  {Vogeley} M.~S.,  {Hoyle} F.,  {Choi} Y.-Y.,    {Park} C.,  2012,
-  \mnras, 421, 926
-
-\bibitem[\protect\citeauthoryear{{Patiri}, {Betancort-Rijo} \&
-  {Prada}}{{Patiri} et~al.}{2006}]{Patiri06a}
-{Patiri} S.~G.,  {Betancort-Rijo} J.,    {Prada} F.,  2006, \mnras, 368, 1132
-
-\bibitem[\protect\citeauthoryear{{Patiri}, {Prada}, {Holtzman}, {Klypin} \&
-  {Betancort-Rijo}}{{Patiri} et~al.}{2006}]{Patiri06b}
-{Patiri} S.~G.,  {Prada} F.,  {Holtzman} J.,  {Klypin} A.,    {Betancort-Rijo}
-  J.,  2006, \mnras, 372, 1710
-
-\bibitem[\protect\citeauthoryear{{Paz}, {Lares}, {Ceccarelli}, {Padilla} \&
-  {Lambas}}{{Paz} et~al.}{2013}]{Paz13}
-{Paz} D.,  {Lares} M.,  {Ceccarelli} L.,  {Padilla} N.,    {Lambas} D.~G.,
-  2013, \mnras, 436, 3480
-
-\bibitem[\protect\citeauthoryear{{Platen}, {van de Weygaert} \&
-  {Jones}}{{Platen} et~al.}{2007}]{Platen07}
-{Platen} E.,  {van de Weygaert} R.,    {Jones} B.~J.~T.,  2007, \mnras, 380,
-  551
-
-\bibitem[\protect\citeauthoryear{{Plionis} \& {Basilakos}}{{Plionis} \&
-  {Basilakos}}{2002}]{Plionis02}
-{Plionis} M.,  {Basilakos} S.,  2002, \mnras, 330, 399
-
-\bibitem[\protect\citeauthoryear{{Regos} \& {Geller}}{{Regos} \&
-  {Geller}}{1991}]{Regos91}
-{Regos} E.,  {Geller} M.~J.,  1991, \apj, 377, 14
-
-\bibitem[\protect\citeauthoryear{{Ricciardelli}, {Quilis} \&
-  {Planelles}}{{Ricciardelli} et~al.}{2013}]{Ricciardelli2013}
-{Ricciardelli} E.,  {Quilis} V.,    {Planelles} S.,  2013, \mnras, 434, 1192
-
-\bibitem[\protect\citeauthoryear{{Riebe} et~al.,}{{Riebe}
-  et~al.}{2013}]{Riebe11}
-{Riebe} K.  et~al., 2013, Astronomische Nachrichten, 334, 691
-
-\bibitem[\protect\citeauthoryear{{Rojas}, {Vogeley}, {Hoyle} \&
-  {Brinkmann}}{{Rojas} et~al.}{2005}]{Rojas05}
-{Rojas} R.~R.,  {Vogeley} M.~S.,  {Hoyle} F.,    {Brinkmann} J.,  2005, \apj,
-  624, 571
-
-\bibitem[\protect\citeauthoryear{{Schaap} \& {van de Weygaert}}{{Schaap} \&
-  {van de Weygaert}}{2000}]{Schaap00}
-{Schaap} W.~E.,  {van de Weygaert} R.,  2000, \aap, 363, L29
-
-\bibitem[\protect\citeauthoryear{{Shandarin}, {Feldman}, {Heitmann} \&
-  {Habib}}{{Shandarin} et~al.}{2006}]{Shandarin06}
-{Shandarin} S.,  {Feldman} H.~A.,  {Heitmann} K.,    {Habib} S.,  2006, \mnras,
-  367, 1629
-
-\bibitem[\protect\citeauthoryear{{Sheth} \& {van de Weygaert}}{{Sheth} \& {van
-  de Weygaert}}{2004}]{Sheth04}
-{Sheth} R.~K.,  {van de Weygaert} R.,  2004, \mnras, 350, 517
-
-\bibitem[\protect\citeauthoryear{{Sutter} et~al.,}{{Sutter}
-  et~al.}{2015}]{Sutter14}
-{Sutter} P.~M.  et~al., 2015, Astronomy and Computing, 9, 1
-
-\bibitem[\protect\citeauthoryear{{Sutter}, {Lavaux}, {Wandelt} \&
-  {Weinberg}}{{Sutter} et~al.}{2012}]{Sutter12b}
-{Sutter} P.~M.,  {Lavaux} G.,  {Wandelt} B.~D.,    {Weinberg} D.~H.,  2012,
-  \apj, 761, 44
-
-\bibitem[\protect\citeauthoryear{{Sutter}, {Lavaux}, {Wandelt}, {Weinberg} \&
-  {Warren}}{{Sutter} et~al.}{2014}]{Sutter14a}
-{Sutter} P.~M.,  {Lavaux} G.,  {Wandelt} B.~D.,  {Weinberg} D.~H.,    {Warren}
-  M.~S.,  2014, \mnras, 438, 3177
-
-\bibitem[\protect\citeauthoryear{{Tikhonov}}{{Tikhonov}}{2006}]{Tikhonov06}
-{Tikhonov} A.~V.,  2006, Astronomy Letters, 32, 727
-
-\bibitem[\protect\citeauthoryear{{Tikhonov}}{{Tikhonov}}{2007}]{Tikhonov07}
-{Tikhonov} A.~V.,  2007, Astronomy Letters, 33, 499
-
-\bibitem[\protect\citeauthoryear{{van de Weygaert} \& {van Kampen}}{{van de
-  Weygaert} \& {van Kampen}}{1993}]{Weygaert93}
-{van de Weygaert} R.,  {van Kampen} E.,  1993, \mnras, 263, 481
-
-\bibitem[\protect\citeauthoryear{{von Benda-Beckmann} \& {M{\"u}ller}}{{von
-  Benda-Beckmann} \& {M{\"u}ller}}{2008}]{BendaBeckmann08}
-{von Benda-Beckmann} A.~M.,  {M{\"u}ller} V.,  2008, \mnras, 384, 1189
-
-\bibitem[\protect\citeauthoryear{{York}, et al. \& {(the SDSS
-  Collaboration),}}{{York} et~al.}{2000}]{York00}
-{York} D.~G.,  et al.   {(the SDSS Collaboration),} 2000, \aj, 120, 1579
-
-\bibitem[\protect\citeauthoryear{{Zeldovich}, {Einasto} \&
-  {Shandarin}}{{Zeldovich} et~al.}{1982}]{Zeldovich82}
-{Zeldovich} I.~B.,  {Einasto} J.,    {Shandarin} S.~F.,  1982, \nat, 300, 407
-
-\bibitem[\protect\citeauthoryear{{Zel'dovich}}{{Zel'dovich}}{1970}]{Zeldovich70}
-{Zel'dovich} Y.~B.,  1970, \aap, 5, 84
-
-\end{thebibliography}
-
-\end{document}

### 2015-10-19 paper/article.tex
primera version completa

--- 2015-09-22 paper/article.tex
@@
 \label{sec:basics}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{nfw_normalized.pdf}
-  \includegraphics[width=0.48\textwidth]{vel_normalized.pdf}
-\end{center}
-\caption{Dimensionless mass (left) and velocity (right) profiles as a
-  function of the dimensionless radius for different concentration
-  values. \label{fig:profiles}}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{dv_dx.pdf}
-  \includegraphics[width=0.48\textwidth]{zeros.pdf}
-\end{center}
-\caption{Dimensionless derivative of the velocity profile as a
-  function of the dimensionless radius for different concentration
-  values. \label{fig:profiles}}
-\end{figure*}
 
@@
 
-\section{Conclusions}
-\label{sec:conclusions}
-
-In this paper, we presented a new method to estimate the
-concentration of dark matter halos in N-body simulations. 
-We tested our method on mock halo data to study the impact of total
-number of particles and input concentration on the retrieved values.
-We compared these results against two other methods commonly used in
-the literature to estimate concentrations.
-Finally, we applied our method to halos extracted from a cosmological
-N-body simulation to estimate the impact of our method on the mass
-concentration relationship.
-
-Comparison against other methods.\\
-
-The effect of the number of particles.\\
-
-The effect of the input concentration.\\
-
-The impact on the mass-concentration relationship.\\
-
 Comment and future.\\

### 2015-10-19 paper/paper.tex
primera version completa

@@
 
+\label{sec:data}
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.33\textwidth]{mass-velocity.pdf}
+    \includegraphics[width=0.33\textwidth]{mass-density.pdf}
+    \includegraphics[width=0.33\textwidth]{density-velocity.pdf}
+  \end{center}
+  \caption{Comparison between the concentrations measured by our
+    method and the maximum velocity (left) and density (middle)
+    methods. The line indicates the equal value between the two
+    techniques. The right panel compares the results of the maximum
+    velocity and density methods.
+  \label{fig:mdv}}
+\end{figure*}
+
+We use data from the MultiDark cosmological simulation that follows
+the non-linear evolution of a dark matter density field sampled with
+$2048^3$ particles over a cubic box of $1000$ \hMpc on a side. 
+The data is publicly available through \url{http://www.cosmosim.org/}.
+More details about the structure of the database and the simulation
+can be found in \citep{2013AN....334..691R}.
+
+We build a sample of all halos located in a cubic sub-volume of $100$
+\hMpc on a side centered on the most massive halo in the simulation at
+$z=0$ which corresponds to the \texttt{miniMDR1} tables in the
+database.
+From this sample we select all the halos at $z=0$ detected with a
+Friends-of-Friends (FoF) algorithm with masses in the interval
+$10^{12}\leq M_{\rm FoF}/\hMsun \leq 10^{15}$.
+The FoF algorithm used with a linking length of $0.17$ times the average
+inter-particle distance. This choice translates into an overdensity
+$\Delta_h\sim 400-700$ dependent on the halo concentration
+\citep{More2011}.
+Finally, we select from the database all the particles that belong to
+each FoF group.
+
+From this set of particles we follow the procedure spelled out in
+Section \ref{sec:method} with $\Delta_h=740$  (corresponding to $200$
+times the critical density) to select an spherical region that we
+redefine to be our halo.
+This choice makes that our overdensities are fully included inside the
+original FoF particle group.
+On the interest of providing a fair comparison against the density
+method we only report results from overdensities with at least $200$
+particles.
+
+Figure \ref{fig:concentration} shows the results of the
+mass-concentration relationship.
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.75\textwidth]{concentration.pdf}
+\end{center}
+\caption{Mass-concentration relationship for the three different
+  methods used on the same cosmological N-body data. 
+  The lines correspond to the median concentration values in each bin.
+    \label{fig:concentration}}
+\end{figure*}
+
+\section{Conclusions}
+\label{sec:conclusions}
+
+In this paper, we presented a new method to estimate the
+concentration of dark matter halos in N-body simulations. 
+We tested our method on mock halo data to study the impact of total
+number of particles and input concentration on the retrieved values.
+We compared these results against two other methods commonly used in
+the literature to estimate concentrations.
+Finally, we applied our method to halos extracted from a cosmological
+N-body simulation to estimate the impact of our method on the mass
+concentration relationship.
+
+The first benchmark was performed on mock halos generated with known
+concentration values for different particle numbers. 
+For all methods, the accuracy in retrieveing the input concentration
+increases with the number of particles as summarized in Figure \ref{fig:error}.
+Our method systematically shows smaller errors in the retrieved values
+compared to the other two methods, going from $10\%$ for halos with
+$20$ particles down to $0.01\%$ for halos with $2\times 10^4$ particles. 
+In our method the average error on the retrieved values decreases with
+the number of particles as $\langle|D|\rangle\propto N^{-1}$.
+The error in density method initially behaves as $\langle|D|\rangle\propto
+N^{-3/2}$ but at $N=2\times 10^3$ it saturates to $0.1\%$. 
+For the velocity method the error behaves closely to
+$\langle|D|\rangle\propto N^{-1/2}$.
+We also gauged the effect of different concentration parameters at
+fixed particle numbers. 
+We found larger offsets for larger input concentrations. 
+The offset goes in the sense that the measured concentration tends to
+be underestimated.
+Nevertheless, the dominant effect on the measurement is the particle
+number.
+
+We used a N-body cosmological simulation to test the impact of our
+method on the mass-concentration relationship.
+Although the three methods are in general agreement there are
+noticeable differences in the mass concentration relationship.
+
 \bibliographystyle{mn2e}

### 2015-10-31 paper/paper.tex
comparison plots inside manuscript
version con comentarios de Juan Carlos

@@
 We present a new method to estimate the concentration of dark matter
-halos in N-body simulations.
-Our method finds the concentration value to match integrated mass profile as a function of
-halo radius.
-The main advantage of this method is that it uses the full particle informatio
-without any binning.
-We test our method both on mock and N-body halos to compare it against
-two popular methods to find concentrations: maximum radial velocity
-measurements and radial particle binning to estimate the density.
-Tests on the mock halos show that the accuracy of our method to
-recover input concentrations varies with the number of particles in
-the halo. 
-For halos sampled with $20$ particles our method recovers the input
-concentration with $10\%$ accuracy, while for the maximumradial
-velocity and density methods the accuracy is on the order of $20\%$
-and $100\%$, respectively.  
-For halos with $2\times 10^4$ particles our method achieves an accuracy of
-$0.01\%$ while the velocity and  methods achieve $0.1\%$ and $1\%$,
-respectively.  
-We also measure the mass-concentration relationship on N-body data
-taking care of using halos sampled with at least $200$ particles..
-We find that at low masses $10^{12}\hMsun < M<10^{13}\hMsun$ our
-method yields median concentration values lower by a $15\%-20\%$
-compared to the velocity and density methods. 
-At higher masses $3\times 10^{13}\hMsun < M < 2\times 10^{14}\hMsun$ the
-three methods give similar results.
+halos in N-body simulations.  Our method finds the concentration value
+to match {\bf the} integrated mass profile as a function of halo
+radius.  The main advantage of this method is that it uses the full
+particle information without any binning, {\bf which makes it very
+  switable in cases when resolution becomes important}. We test our
+method both on mock and N-body halos to compare it against two popular
+methods to find concentrations: maximum radial velocity measurements
+and radial particle binning to {\bf fit the density profile}. Tests on
+the mock halos show that the accuracy of our method to recover input
+concentrations varies with the halo {\bf resolution}. For halos
+sampled with $20$ particles our method recovers the input
+concentration with $10\%$ accuracy. {\bf For the maximum radial
+  velocity method it is on the order of $20\%$ while density profile
+  methods perform worst at the low resolution limit since they require
+  at least 200 particles inside the virial radius to make a reliable
+  estimate of the density profile}. For halos with $2\times 10^4$
+particles our method achieves an accuracy of $0.01\%$ while the
+velocity and density profile methods achieve $0.1\%$ and $1\%$,
+respectively. We measure the mass-concentration relationship on N-body
+data taking care of using halos sampled with at least $200$
+particles. We find that at low masses $10^{12}\hMsun <
+M<10^{13}\hMsun$ our method yields median concentration values lower
+by a $15\%-20\%$ compared to the velocity and density methods ({\bf
+  why?}).  At higher masses $3\times 10^{13}\hMsun < M < 2\times
+10^{14}\hMsun$ the three methods give similar results.
 \end{abstract}
@@
 Universe is dominated by dark matter, a collisionless fluid shaped by
-gravitational interactions.
-In the last three decades simulations of dark matter dominated
-universes have provided valuable insights into the large scale
-structure formation process, showing a remarkable success in the
-comparison between theoretical results and observations of the
-galaxy distribution obtained from surveys.
+gravitational interactions.  In the last three decades simulations of
+dark matter dominated universes have provided valuable insights into
+the large scale structure formation process, showing a remarkable
+success in the comparison between theoretical results and observations
+of the galaxy distribution obtained from surveys.
 \citep{Springel2005,2011ApJ...740..102K}.
 
-On galactic scales the most striking result is that dark matter
-overdensities closely follow a universal density profile. 
-In a first approximation this profile is spherically symmetric and its
-density only dependens on the radial coordinate.
-The universality of this profiles seems to be independent of the
-cosmological parameters and is self-similar for different spatial
-scales after an adequate re-scaling is applied. 
-\citep{NFW,Taylor2001}
+{\bf Navarro et.al. 2010 have used high resolution simulations to show
+  that the full halo density profile is not universal and follows an
+  Einasto density distribution. However, if one is not interested in
+  the very central region of the dark matter halo (where galaxy
+  formation takes place, and where the effects of baryon physics on
+  dark matter distribution is still an uncknown), one can assume an
+  approximation where dark matter overdensities closely follow an
+  universal density profile. In a first approximation this profile is
+  spherically symmetric and its density only dependens on the radial
+  coordinate. Although it is well known that the characteristics of
+  this densty profile depends on redshift (Maccio et.al. 2008), its
+  universal shape seems to be independent of the cosmological
+  parameters and is self-similar for different spatial scales after an
+  adequate re-scaling is applied. \citep{NFW,Taylor2001}
+}
 
-One the most popular parameterization for a dark matter halo radial
-density distribution is the Navarro-Frenk-White (NFW) profile
-\citep{NFW}.
-This profile is a double power law in radius, where the transition break
-happens at the so-called scale radius, $r_s$.
-The ratio between the scale radius and the virial radius $R_v$, which
-defines a natural scale for the halo, is known as the concentration
-$c=R_v/r_s$. 
-Simulations also show that the concentration is a strong function of
-halo mass and redshift.
-
-However, high resolution simulations of Milky Way sized dark matter halos
-\citep{Navarro2010} show that the universality property is not
-perfect and that a better fitting parameterization to the radial
-density profile is provided by the Einasto profile
-\citep{Einasto1965}.
-Nevertheless, the NFW density profile and its concentration have
-become a standard metric to describe the structure of dark matter
-halos.
+{\bf In such circumstances}, one the most popular parameterizations
+for dark matter halo radial density distribution is the
+Navarro-Frenk-White (NFW) profile \citep{NFW}.  This profile is a
+double power law in radius, where the transition break happens at the
+so-called scale radius, $r_s$.  The ratio between the scale radius and
+the virial radius $R_v$ is known as the concentration $c=R_v/r_s$.
+Simulations show that the concentration is a strong function of halo
+mass and redshift and provides information about the mass assembly of
+the dark matter halo (Citar paper que reproduce mis graficas y conecta
+C con m(z)).
 
@@
 could provide a potential test of the Cold Dark Matter (CDM) paradigm
-on galactic scales. 
-For this motivation a great deal of effort has been
-invested in calibrating this relationship with simulations
-\citep{Neto2007,Duffy2008,Munoz2011,Prada2012,Ludlow2014} and 
-finding the best possible way to constraint it with observations
+on galactic scales.  For this motivation a great deal of effort has
+been invested in calibrating this relationship with simulations
+\citep{Neto2007,Duffy2008,Munoz2011,Prada2012,Ludlow2014} and finding
+the best possible way to constraint it with observations
 \citep{Buote2007,Comerford2007,Mandelbaum2008,Giocoli2014,Foex2014,Shan2015}.
@@
 concentration parameter of a dark matter halo in a N-body simulation.
-The first method takes the particles composing the halos
-and bins them in logarithmic radii to estimate the density in each
-bin, then it proceeds to fit the density as a function of the radius
-to the NFW profile.
-A second method uses an analytic property of the
-NFW profile that relates the maximum of the ratio of the circular velocity to
-the virial velocity.
-The concentration can be then found as the root of a algebraic 
-equation dependent on this maximum value.
+The first method takes the particles composing the halos and bins them
+in logarithmic radii to estimate the density in each bin, then it
+proceeds to fit the density as a function of the radius to the NFW
+profile.  A second method uses an analytic property of the NFW profile
+that relates the maximum of the ratio of the circular velocity to the
+virial velocity.  The concentration can be then found as the root of a
+algebraic equation dependent on this maximum value.
 
 The first method is straightforward to apply but presents two
-disadvantages.
-First, it requires a large number of particles in
-order to have a proper density estimate in each bin.
-This makes the method robust only for halos with at least  $10^3$
-particles.
-The second problem is that there is not a way to estimate the optimal
+disadvantages.  First, it requires a large number of particles in
+order to have a proper density estimate in each bin.  This makes the
+method robust only for halos with at least $10^3$ particles.  The
+second problem is that there is not a way to estimate the optimal
 radial bin size, different choices produce different results for the
@@
 
-The second method solves the two problems mentioned above.
-It works with low particles numbers and does not involve data
-binning.
-However, it effectively takes into account only a single data point
-and discards the behaviour of the ratio $V_{\rm circ}/V_{\rm vir}$ below and
-above its maxima.
-Additionally, small fluctuations on the value of this maximum can
-yield large perturbations on the estimated concentration parameter.
+The second method solves the two problems mentioned above.  It works
+with low particle numbers and does not involve data binning.  However,
+it effectively takes into account only a single data point and
+discards the behaviour of the ratio $V_{\rm circ}/V_{\rm vir}$ below
+and above its maxima.  Additionally, small fluctuations on the value
+of this maximum can yield large perturbations on the estimated
+concentration parameter.
 
 In this paper we propose a new method to estimate the dark matter halo
-concentration in halos from N-body simulations.
-Our method builds the cumulative mass profile from the particle
-to find the best possible concentration value fitting this
-distribution. 
-This proposal has two advantages with respect to the two methods mentioned
-above. 
-It does not involve any data binning and does not throw away data points.
+concentration in halos from N-body simulations.  Our method builds the
+cumulative mass profile from the particle to find the best possible
+concentration value fitting this distribution.  This proposal has two
+advantages with respect to the two methods mentioned above.  It does
+not involve any data binning and does not throw away data points {\bf
+  resulting in a robust estimate even at low resolution/particle
+  numbers. In the same sence, since the method does not require any
+  binning, there is no need to tune numerical parameters, which
+  provide definitive/independent estimates for the concentration
+  parameter.}.
+
+{\it mi opinión es que el método es muy bueno, y sobresalta sobre los
+  otros dos en sus ventaja: robusto, no requiere bineo, aplica bien en
+  resoluciones pobres. Como herramienta (que es lo que se está
+  vendiendo en el trabajo, un método, eso es lo que hay que recalcar y
+  resaltar)}
 
@@
 
-Let us review first the basic properties of the NFW density
-profile. 
-This help us to define our notation and review the important
+Let us review first the basic properties of the NFW density profile.
+This shall help us to define our notation and review the important
 assumptions of the two different methods commonly used to measure the
@@
 %
-where $\rho_c\equiv 3H^2/8\pi G$ is the Universe critical density
-constructed from the Hubble constant $H$ and the universal
-gravitational constant $G$,
+where $\rho_c\equiv 3H^2/8\pi G$ is the Universe critical density, $H$
+is the Hubble constant, $G$ and the universal gravitational constant,
 $\delta_c$ is the halo dimensionless characteristic density and $r_s$
-is the scale radius. This radius marks the transition
-between the power law scaling $\rho\propto r^{-1}$ for
+is the scale radius. This radius marks {\bf the point where the
+  logarithmic slope of the density profile is equal to -2} marking the
+transition between the power law scaling $\rho\propto r^{-1}$ for
 $r<r_s$ and $\rho\propto r^{-3}$ for $r>r_s$.
@@
 We define the virial radius of a halo, $r_v$, as the boundary of the
-spherical volume that encloses a density of $\Delta_h$ times
-the average density of the Universe. 
-The corresponding mass $M_{v}$, the virial mass, can be written as
-$M_{v} = \frac{4\pi}{3}\bar{\rho}\Delta_h r_v^3$.
-From these virial quantities we define new dimensionless variables for
-the radius and mass $x\equiv r/r_v$ and $m\equiv
+spherical volume that encloses a density of $\Delta_h$ times the mean
+density of the Universe.  The corresponding mass $M_{v}$, the virial
+mass, can be written as $M_{v} = \frac{4\pi}{3}\bar{\rho}\Delta_h
+r_v^3$.  From these virial quantities we define new dimensionless
+variables for the radius and mass $x\equiv r/r_v$ and $m\equiv
 M(<r)/M_v$.
@@
 In this paper we use $\Delta_h=740$ roughly corresponding to 200 times
-the critical density.
+the critical density {\bf at redshift z=0}.
 
 \subsection{Integrated mass profile}
+
 From these definitions we can compute the total mass enclosed inside a
@@
 
-%In Figure \ref{fig:profiles} we show $m(<x)$ as
-%a function of $x$ for different values of the concentration in the range
-%$1\leq c \leq 20$.
-
 \subsection{Circular velocity profile}
@@
 \subsection{Estimates from the density and velocity profiles}
-There are two standard methods to estimate concentrations in dark matter
-halos extracted from N-body simulations.
+{\bf To date,} there are two standard methods to estimate
+concentrations in dark matter halos extracted from N-body simulations.
 
-The first method tries to directly estimate the density profile.
-It takes all the particles in the halo and bins them in the logarithm
-of the radial coordinate from the halo center.
-Then, it estimates the density in each logarithmic bin counting the
-particles and dividing by the corresponding shell volume.
-At this point is is possible to make a direct fit to the density as a
-function of the radial coordinate.
-This method has been most recently used by \cite{Ludlow2014} to study
-the mass-concentration-redshift relation of dark matter halos using
-the Millennium Simulation Series.
+The first method tries to directly estimate the density profile.  It
+takes all the particles in the halo and bins them in the logarithm of
+the radial coordinate from the halo center.  Then, it estimates the
+density in each logarithmic bin counting the particles and dividing by
+the corresponding shell volume.  At this point is is possible to make
+a direct fit to the density as a function of the radial coordinate.
+This method has been {\bf used broadly for more than two decades} to
+study the mass-concentration-redshift relation of dark matter halos
+using the Millennium Simulation Series.
 
-A second method uses the circular velocity profile.
-It finds the value of $x$ for which the normalized circular
-velocity $v(<x)$ shows a maximum.
-Using this value it solves numerically for the corresponding value of
-the concentration using Eq. (\ref{eq:max_v}).
+{\it no veo la necesidad de citar el ``trabajo mas'' reciente que usa
+  el metodo, cuando ha sido usado durante mas de dos decadas!}
+
+A second method uses the circular velocity profile.  It finds the
+value of $x$ for which the normalized circular velocity $v(<x)$ shows
+a maximum.  Using this value it solves numerically for the
+corresponding value of the concentration using Eq. (\ref{eq:max_v}).
 This method has been most recently used by \cite{Klypin2014} to study
@@
 \subsection{Our proposal: estimate from the integrated mass profile}
-Our method uses the integrated mass profile.
-First we define the center of the halo to be at the position of the
-particle with the lowest gravitational potential.
-Then we rank the particles by their increasing radial distance from
-the center.
-From this ranked list of $i=1,N$ particles, the total mass at a radius
-$r_i$ is $M_i=i\times m_p$, where $r_i$ is
-the position of the $i$-th particle and $m_p$ is the mass of a single
-computational particle.
-In this process we discard the particle at the center.
+Our method uses the integrated mass profile.  First we define the
+center of the halo to be at the position of the particle with the
+lowest gravitational potential.  Then we rank the particles by their
+increasing radial distance from the center.  From this ranked list of
+$i=1,N$ particles, the total mass at a radius $r_i$ is $M_i=i\times
+m_p$, where $r_i$ is the position of the $i$-th particle and $m_p$ is
+the mass of a single computational particle. In this process we
+discard the particle at the center.
 
@@
 concentration is the only free parameter. We use an Affine Invariant
-Markov chain Monte Carlo implemented in the python module emcee
+Markov chain Monte Carlo implemented in the python module {\em emcee}
 \citep{emcee} to sample the likelihood function distribution defined
-by ${\cal L}(c)\propto \exp(-\chi^2(c)/2)$ where the $\chi^2(c)$ is written as
+by ${\cal L}(c)\propto \exp(-\chi^2(c)/2)$ where the $\chi^2(c)$ is
+written as
 
@@
 %
-where $m(<x_i;c)$ corresponds to the values in Eq.(\ref{eq:profile}) at
-$x=x_i$ for a given value of the concentration parameter $c$ and the
-$i$ index sums over all the particles in the numerical profile.
+where $m(<x_i;c)$ corresponds to the values in Eq.(\ref{eq:profile})
+at $x=x_i$ for a given value of the concentration parameter $c$ and
+the $i$ index sums over all the particles in the numerical profile.
 From the $\chi^2$ distribution we find the optimal value of the
@@
 advantages with respect to the density and velocity methods, it does
-not involve any binning (unlike the density methods ) and the
-sampling method uses the information from all the particles in the
-halo (unlike the velocity method).
+not involve any binning (unlike the density methods ) and the sampling
+method uses the information from all the particles in the halo (unlike
+the velocity method).
 
@@
 We now present the results of applying the three methods above
-mentione on two different halo samples.
-The first sample is composed by mock halos generated to have known
-concentration values in perfect spherical symmetry following an NFW
-profile.
-We use this sample to check that we can recover the expected values
-but also gauge the impact of the number of particles on the outcomes.
-The second sample comes from a publicly available N-body cosmological
-simulation.
-From this sample we quantify again the differences between all the
-methods and also estimate the impact on the mass-concentration
-relationship.
+mentione on two different halo samples.  The first sample is composed
+by mock halos generated to have known concentration values in perfect
+spherical symmetry following an NFW profile.  We use this sample to
+check that we can recover the expected values but also gauge the
+impact of the number of particles on the outcomes.  The second sample
+comes from a publicly available N-body cosmological simulation.  From
+this sample we quantify again the differences between all the methods
+and also estimate the impact on the mass-concentration relationship.
 
@@
 
-The method we use to generate the mock halos is based on the integrated
-mass profile.
-We start by fixing the desired concentration $c$ and total number of
-particles $N$ in the mock halo.
-With these values we define the mass element as $\delta m = 1/M$, corresponding
-to the mass of each particle such that the total mass is one.
-Then for each particle, $i=1,\ldots,N$, we find the value of $r_i$ such that
-the difference
+The method we use to generate the mock halos is based on the
+integrated mass profile.  We start by fixing the desired concentration
+$c$ and total number of particles $N$ in the mock halo.  With these
+values we define the mass element as $\delta m = 1/M$, corresponding
+to the mass of each particle such that the total mass is one.  Then
+for each particle, $i=1,\ldots,N$, we find the value of $r_i$ such
+that the difference
 %
@@
 The value of $r_i$ is the radius of the $i$-th particle of the mock
-halo.
-Then we generate random polar and azimuthal angles $\theta$ and $\phi$
-for each particle to ensure spherical symmetry.
-Finally these three spherical coordinates are transformed into Cartesian coordinates
+halo.  Then we generate random polar and azimuthal angles $\theta$ and
+$\phi$ for each particle to ensure spherical symmetry.  Finally these
+three spherical coordinates are transformed into Cartesian coordinates
 $(r,\theta,\phi) \rightarrow (x,y,z)$.
 
-We generate in total $400$ mock halos split into four different
-groups of $100$ halos each.
-The four groups differ in the total number of particles for their halos:
-$20$, $200$, $2000$ and $20000$.
-Inside each group the halos have random concentration values in
-the range $1<c<20$ with a uniform distribution.
-For all these halos ww the concentration values using the
-density, velocity and mass methods described in the previous
-section. 
-We quantify the difference between the expected $c_{in}$
-and obtained $c_{out}$ values by
+We generate in total $400$ mock halos split into four different groups
+of $100$ halos each.  The four groups differ in the total number of
+particles for their halos: $20$, $200$, $2000$ and $20000$.  Inside
+each group the halos have random concentration values in the range
+$1<c<20$ with a uniform distribution.  For all these halos {\bf ww?}
+the concentration values using the density, velocity and mass methods
+described in the previous section.  We quantify the difference between
+the expected $c_{in}$ and obtained $c_{out}$ values by
 %
@@
 %
-where ${\cal{H}}$ corresponds to a set of mock halos, 
-and $\left|{\cal{H}}\right|$ is the number of haloes in
-${\cal{H}}$.
+where ${\cal{H}}$ corresponds to a set of mock halos, and
+$\left|{\cal{H}}\right|$ is the number of haloes in ${\cal{H}}$. {\bf
+  The larger the value of $\avg{|D|}$, the larger the discrepace of
+  the concentrations obtained for that method}
 
@@
   methods. Our method provide the most accurate estimate at fixed
-  particle number $N$.
+  particle number $N$.  {\it Con respecto a esta figura tengo una
+    pregunta. Yo ajusté los perfiles con menos de 200 partulas? no
+    recuerdo!}
     \label{fig:error}}
@@
 At fixed particle numbers our method always shows the lowest
-$\avg{|D|}$ values compared to the other two methods.
-Its accuracy is on the order of $10\%$ for $20$ particles in the halo,
-going down to $0.01\%$ for halos with $20000$ particles.
-The dependence of $\avg{|D|}$ with the particle number $N$ goes
-approximately as $\avg{|D|}\propto N^{-1/2}$, hinting that
-the accuracy of the method is related to a decrease of Poisson
-noise.
+$\avg{|D|}$ values compared to the other two methods.  Its accuracy is
+on the order of $10\%$ for $20$ particles in the halo, going down to
+$0.01\%$ for halos with $20000$ particles.  The dependence of
+$\avg{|D|}$ with the particle number $N$ goes approximately as
+$\avg{|D|}\propto N^{-1/2}$, hinting that the accuracy of the method
+is related to a decrease of Poisson noise.
 
-The method based on the maximum of the circular velocity shows a similar
-behaviour $\avg{|D|}\propto N^{-1/2}$. 
-Its accuracy is $2-5$ times less
-than in our method, on the order of $20\%$ for $20$ particle halos and
-$0.5\%$ for $20000$ particle halos. 
-The method based on the direct density
-fit shows the lowest accuracy for a low particle number and an intermediate
-accuracy between the other two methods for a high particle number.
+The method based on the maximum of the circular velocity shows a
+similar behaviour $\avg{|D|}\propto N^{-1/2}$.  Its accuracy is $2-5$
+times less than in our method, on the order of $20\%$ for $20$
+particle halos and $0.5\%$ for $20000$ particle halos. {\bf The method
+  based on the direct density fit shows the lowest accuracy for a low
+  particle number. As it is discussed in \citep{Munoz2011}, density
+  binning for halos with particle numbers below $\sim200$ leads to a
+  biased estimation of the mass density profile, and therefore to a
+  biased estimation of the concentration parameter. This behaviour is
+  evident in the large values of $\avg{|D|}$ for halos with number of
+  particles below ~200 and an intermediate accuracy between the other
+  two methods for a high particle number.}
 
@@
   \begin{center}
-    \includegraphics[width=0.33\textwidth]{mass-velocity.pdf}
-    \includegraphics[width=0.33\textwidth]{mass-density.pdf}
-    \includegraphics[width=0.33\textwidth]{density-velocity.pdf}
+    \includegraphics[width=0.33\textwidth]{conc_mass_vel.pdf}
+    \includegraphics[width=0.33\textwidth]{conc_mass_dens.pdf}
+    \includegraphics[width=0.33\textwidth]{conc_dens_vel.pdf}
   \end{center}
@@
 
+{\bf The results presented in the previous section show that in an
+  idealized setup (perfect spherical halos, pure NFW desity profiles,
+  total isolation) our method of the mass profile performs better than
+  the other two methods commonly used to measure concentrations in
+  simulated dark matter haos. However, actual simulated dark matter
+  halos are much more complex. They are not isolated, many of them
+  experience mergers that take them out of the equilibrium. Halos may
+  have also plenty of substructure, etc. All these effects disturb the
+  mass density profile, taking it away from the ideal NFW profile we
+  assume in this wok. In order to see the real performance of our new
+  method use it to estimate the concentration parameter in dark matter
+  halos obtained from a cosmological Nbody simulation and compare with
+  the other two calsical methods.}
+
 We use data from the MultiDark cosmological simulation that follows
 the non-linear evolution of a dark matter density field sampled with
-$2048^3$ particles over a cubic box of $1000$ \hMpc on a side. 
-The data is publicly available through \url{http://www.cosmosim.org/}.
+$2048^3$ particles over a cubic box of $1000$ \hMpc on a side.  The
+data is publicly available through \url{http://www.cosmosim.org/}.
 More details about the structure of the database and the simulation
@@
 $z=0$ which corresponds to the \texttt{miniMDR1} tables in the
-database.
-From this sample we select all the halos at $z=0$ detected with a
-Friends-of-Friends (FoF) algorithm with masses in the interval
-$10^{12}\leq M_{\rm FoF}/\hMsun \leq 10^{15}$.
-The FoF algorithm used with a linking length of $0.17$ times the average
-inter-particle distance. This choice translates into an overdensity
-$\Delta_h\sim 400-700$ dependent on the halo concentration
-\citep{More2011}.
+database.  From this sample we select all the halos at $z=0$ detected
+with a Friends-of-Friends (FoF) algorithm with masses in the interval
+$10^{12}\leq M_{\rm FoF}/\hMsun \leq 10^{15}$.  The FoF algorithm used
+with a linking length of $0.17$ times the {\bf mean} inter-particle
+distance. This choice translates into an overdensity $\Delta_h\sim
+400-700$ dependent on the halo concentration \citep{More2011}.
 Finally, we select from the database all the particles that belong to
@@
 times the critical density) to select an spherical region that we
-redefine to be our halo.
-This choice makes that our overdensities are fully included inside the
-original FoF particle group.
-On the interest of providing a fair comparison against the density
-method we only report results from overdensities with at least $200$
-particles.
+redefine to be our halo.  This choice makes that our overdensities are
+fully included inside the original FoF particle group.  On the
+interest of providing a fair comparison against the density method we
+only report results from overdensities with at least $200$ particles.
 
@@
 
+{\em Aqui hay algo importante que hay que entender antes de discutir
+  esta gráfica , y es la razón por la cual el metodo del perfil de
+  masa da valores de concentración tan bajos a baja masa y comparables
+  a los de los otros dos métodos a alta masa. Es importante entender
+  la razón de esto!.  Se me ocurren unas preguntas para tratar de
+  entender. \\ 1) La grafica de c-M \ref{fig:concentration} usa todos
+  los halos o solo los halos relajados? La inclusión de halos no
+  relajados introduce in bias en la mediana en Cvir, así que vale la
+  pena inclusive agregar una linea mas a la gráfica con los halos
+  relajados y sin ellos. Para los otros dos métodos ya se sabe que
+  hace la población de halos no relajados en la medida así que no creo
+  necesario agregarlas para esos métodos. \\ Hay que explicar un poco
+  mas la gráfica en el sentido de que se grafica y como se
+  calculó. mean concentration?, Median concentrations? o mean in
+  logscale?  Mas bins de cuanto? Mínimo cuantos halos por mass bin?,
+  Halos relajados en todos los casos, o indistintos?}
+
 \section{Conclusions}
@@
 
-In this paper, we presented a new method to estimate the
-concentration of dark matter halos in N-body simulations. 
-We tested our method on mock halo data to study the impact of total
-number of particles and input concentration on the retrieved values.
-We compared these results against two other methods commonly used in
-the literature to estimate concentrations.
-Finally, we applied our method to halos extracted from a cosmological
-N-body simulation to estimate the impact of our method on the mass
-concentration relationship.
+In this paper, we presented a new method to estimate the concentration
+of dark matter halos in N-body simulations.  We tested our method on
+mock halo data to study the impact of total number of particles and
+input concentration on the retrieved values.  We compared these
+results against two other methods commonly used in the literature to
+estimate concentrations.  Finally, we applied our method to halos
+extracted from a cosmological N-body simulation to estimate the impact
+of our method on the mass concentration relationship.
 
 The first benchmark was performed on mock halos generated with known
-concentration values for different particle numbers. 
-For all methods, the accuracy in retrieveing the input concentration
-increases with the number of particles as summarized in Figure \ref{fig:error}.
-Our method systematically shows smaller errors in the retrieved values
+concentration values for different particle numbers.  For all methods,
+the accuracy in retrieveing the input concentration increases with the
+number of particles as summarized in Figure \ref{fig:error}.  Our
+method systematically shows smaller errors in the retrieved values
 compared to the other two methods, going from $10\%$ for halos with
-$20$ particles down to $0.01\%$ for halos with $2\times 10^4$ particles. 
-In our method the average error on the retrieved values decreases with
-the number of particles as $\langle|D|\rangle\propto N^{-1}$.
-The error in density method initially behaves as $\langle|D|\rangle\propto
-N^{-3/2}$ but at $N=2\times 10^3$ it saturates to $0.1\%$. 
-For the velocity method the error behaves closely to
-$\langle|D|\rangle\propto N^{-1/2}$.
-We also gauged the effect of different concentration parameters at
-fixed particle numbers. 
-We found larger offsets for larger input concentrations. 
+$20$ particles down to $0.01\%$ for halos with $2\times 10^4$
+particles.  In our method the average error on the retrieved values
+decreases with the number of particles as $\langle|D|\rangle\propto
+N^{-1}$.  The error in density method initially behaves as
+$\langle|D|\rangle\propto N^{-3/2}$ but at $N=2\times 10^3$ it
+saturates to $0.1\%$.  For the velocity method the error behaves
+closely to $\langle|D|\rangle\propto N^{-1/2}$.  We also gauged the
+effect of different concentration parameters at fixed particle
+numbers.  We found larger offsets for larger input concentrations.
 The offset goes in the sense that the measured concentration tends to
-be underestimated.
-Nevertheless, the dominant effect on the measurement is the particle
-number.
+be underestimated.  Nevertheless, the dominant effect on the
+measurement is the particle number.
 
 We used a N-body cosmological simulation to test the impact of our
-method on the mass-concentration relationship.
-Although the three methods are in general agreement there are
-noticeable differences in the mass concentration relationship.
+method on the mass-concentration relationship.  Although the three
+methods are in general agreement there are noticeable differences in
+the mass concentration relationship.
 

### 2015-11-01 paper/paper.tex
nuevo personaje principal

@@
 %=========================================================================
-\title{A new method to estimate dark matter halo concentrations}
+\title{Estimating dark matter halo concentration from the integrated mass profile}
 \author[C. Poveda, J.E. Forero-Romero, J.C. Mu\~noz-Cuartas]{
@@
 
-We present a new method to estimate the concentration of dark matter
-halos in N-body simulations.  Our method finds the concentration value
-to match {\bf the} integrated mass profile as a function of halo
-radius.  The main advantage of this method is that it uses the full
+Here we show that the concentration parameter in dark matter halos from
+N-body simulations can be reliably estimated from the radially integrated mass
+profile.
+The main advantage of this method is that it uses the full
 particle information without any binning, {\bf which makes it very

### 2015-11-06 paper/paper.tex
abstract revisado

@@
 %=========================================================================
-\title{Estimating dark matter halo concentration from the integrated mass profile}
+\title{Estimating dark matter halo concentration using the integrated
+  mass profile} 
 \author[C. Poveda, J.E. Forero-Romero, J.C. Mu\~noz-Cuartas]{
@@
 
+In a dark matter dominated Universe galaxy properties are driven by
+dark matter halo characteristics. 
+One of the key structural halo properties is the concentration. 
+[EN QUE MODELOS IMPORTA LA CONCENTRACION?]
+For these reasons there has been a lot of effort to have a reliable
+concentration estimate from N-body simulations.
 Here we show that the concentration parameter in dark matter halos from
@@
 profile.
-The main advantage of this method is that it uses the full
-particle information without any binning, {\bf which makes it very
-  switable in cases when resolution becomes important}. We test our
-method both on mock and N-body halos to compare it against two popular
-methods to find concentrations: maximum radial velocity measurements
-and radial particle binning to {\bf fit the density profile}. Tests on
-the mock halos show that the accuracy of our method to recover input
-concentrations varies with the halo {\bf resolution}. For halos
+The main advantage of this approach is that it uses the full
+particle information without any binning, which makes it reliable in
+cases when low numerical resolution becomes a limitation for other
+methods.   
+We show the good performance of this method by estimating halo
+concentration both on mock and N-body halos. 
+We compare these results against two other methods:
+maximum radial velocity measurements and radial particle binning to
+fit the density profile. 
+Tests on  the mock halos show that the accuracy of our method to recover input
+concentrations varies with halo resolution. For halos
 sampled with $20$ particles our method recovers the input
-concentration with $10\%$ accuracy. {\bf For the maximum radial
-  velocity method it is on the order of $20\%$ while density profile
-  methods perform worst at the low resolution limit since they require
-  at least 200 particles inside the virial radius to make a reliable
-  estimate of the density profile}. For halos with $2\times 10^4$
-particles our method achieves an accuracy of $0.01\%$ while the
-velocity and density profile methods achieve $0.1\%$ and $1\%$,
-respectively. We measure the mass-concentration relationship on N-body
+concentration with $10\%$ accuracy. 
+For the maximum radial velocity method it is on the order of $20\%$
+while density profile methods perform worst at the low resolution
+limit since they require at least 200 particles inside the virial
+radius to make a reliable estimate of the density profile. 
+For halos with $2\times 10^4$ particles our method achieves an
+accuracy of $0.01\%$ while the velocity and density profile methods
+achieve $0.1\%$ and $1\%$, respectively. 
+We measure the mass-concentration relationship on N-body
 data taking care of using halos sampled with at least $200$
@@
 by a $15\%-20\%$ compared to the velocity and density methods ({\bf
-  why?}).  At higher masses $3\times 10^{13}\hMsun < M < 2\times
+  why?}).  
+At higher masses $3\times 10^{13}\hMsun < M < 2\times
 10^{14}\hMsun$ the three methods give similar results.

### 2015-11-06 paper/paper.tex
intro revisada

@@
 
-In a dark matter dominated Universe galaxy properties are driven by
-dark matter halo characteristics. 
+In a dark matter dominated universe galaxy properties are driven by
+the dark matter halo host.
 One of the key structural halo properties is the concentration. 
 [EN QUE MODELOS IMPORTA LA CONCENTRACION?]
-For these reasons there has been a lot of effort to have a reliable
-concentration estimate from N-body simulations.
+For these reasons it is important to have a reliable concentration
+estimate from N-body simulations. 
 Here we show that the concentration parameter in dark matter halos from
@@
 
-{\bf Navarro et.al. 2010 have used high resolution simulations to show
+{\bf FALTA CITEP Navarro et.al. 2010} have used high resolution simulations to show
 that the full halo density profile is not universal and follows an
-  Einasto density distribution. However, if one is not interested in
-  the very central region of the dark matter halo (where galaxy
-  formation takes place, and where the effects of baryon physics on
-  dark matter distribution is still an uncknown), one can assume an
-  approximation where dark matter overdensities closely follow an
-  universal density profile. In a first approximation this profile is
-  spherically symmetric and its density only dependens on the radial
-  coordinate. Although it is well known that the characteristics of
-  this densty profile depends on redshift (Maccio et.al. 2008), its
-  universal shape seems to be independent of the cosmological
-  parameters and is self-similar for different spatial scales after an
-  adequate re-scaling is applied. \citep{NFW,Taylor2001}
-}
+Einasto density distribution. 
+However, if one is not interested in the very central region of the
+dark matter halo (where galaxy formation takes place, and where the
+effects of baryon physics on dark matter distribution is still an
+uncknown), one can assume an approximation where dark matter
+overdensities closely follow an universal density profile. 
+In a first approximation this profile is spherically symmetric and
+its density only dependens on the radial coordinate. 
+Although it is well known that the characteristics of
+this densty profile depend on redshift {\bf FALTA CITEP (Maccio
+  et.al. 2008)}, its universal shape seems to be independent of the
+cosmological parameters and is self-similar for different spatial
+scales after an adequate re-scaling is applied \citep{NFW,Taylor2001}.
 
-{\bf In such circumstances}, one the most popular parameterizations
+In such circumstances, one the most popular parameterizations
 for dark matter halo radial density distribution is the
-Navarro-Frenk-White (NFW) profile \citep{NFW}.  This profile is a
-double power law in radius, where the transition break happens at the
-so-called scale radius, $r_s$.  The ratio between the scale radius and
-the virial radius $R_v$ is known as the concentration $c=R_v/r_s$.
+Navarro-Frenk-White (NFW) profile \citep{NFW}.  
+This profile is a double power law in radius, where the transition
+break happens at the so-called scale radius, $r_s$.  
+The ratio between the scale radius and the virial radius $R_v$ is
+known as the concentration $c=R_v/r_s$. 
 Simulations show that the concentration is a strong function of halo
 mass and redshift and provides information about the mass assembly of
-the dark matter halo (Citar paper que reproduce mis graficas y conecta
-C con m(z)).
+the dark matter halo {\bf (Citar paper que reproduce mis graficas y conecta
+C con m(z))}.
 
-Observationally, the relationship between halo mass and concentration
-could provide a potential test of the Cold Dark Matter (CDM) paradigm
-on galactic scales.  For this motivation a great deal of effort has
+{\bf usos de modelos de formacion de galaxias}
+The relationship between halo mass and concentration
+could also provide a potential test of the Cold Dark Matter (CDM)
+paradigm.
+
+For all these reasons mentioned above a great deal of effort has
 been invested in calibrating this relationship with simulations
@@
 In N-body simulations there are two main methods to estimate the
-concentration parameter of a dark matter halo in a N-body simulation.
-The first method takes the particles composing the halos and bins them
-in logarithmic radii to estimate the density in each bin, then it
+concentration parameter of a dark matter halo.
+The first method takes the halo particles and bins them into
+logarithmic radii to estimate the density in each bin, then it 
 proceeds to fit the density as a function of the radius to the NFW
-profile.  A second method uses an analytic property of the NFW profile
+profile.  
+A second method uses an analytic property of the NFW profile
 that relates the maximum of the ratio of the circular velocity to the
@@
 The first method is straightforward to apply but presents two
-disadvantages.  First, it requires a large number of particles in
-order to have a proper density estimate in each bin.  This makes the
-method robust only for halos with at least $10^3$ particles.  The
-second problem is that there is not a way to estimate the optimal
+disadvantages.  
+First, it requires a large number of particles in
+order to have a proper density estimate in each bin.  
+This makes the method robust only for halos with at least $10^3$ particles.  
+The second problem is that there is not a way to estimate the optimal
 radial bin size, different choices produce different results for the
@@
 
-The second method solves the two problems mentioned above.  It works
-with low particle numbers and does not involve data binning.  However,
-it effectively takes into account only a single data point and
+The second method solves the two problems mentioned above.  
+It works with low particle numbers and does not involve data binning.  
+However, it effectively takes into account only a single data point and
 discards the behaviour of the ratio $V_{\rm circ}/V_{\rm vir}$ below
-and above its maxima.  Additionally, small fluctuations on the value
-of this maximum can yield large perturbations on the estimated
-concentration parameter.
+and above its maxima.  
+Additionally, small fluctuations on the value of this maximum can
+yield large perturbations on the estimated concentration parameter.
 
-In this paper we propose a new method to estimate the dark matter halo
-concentration in halos from N-body simulations.  Our method builds the
-cumulative mass profile from the particle to find the best possible
-concentration value fitting this distribution.  This proposal has two
-advantages with respect to the two methods mentioned above.  It does
-not involve any data binning and does not throw away data points {\bf
-  resulting in a robust estimate even at low resolution/particle
-  numbers. In the same sence, since the method does not require any
-  binning, there is no need to tune numerical parameters, which
-  provide definitive/independent estimates for the concentration
-  parameter.}.
-
-{\it mi opinión es que el método es muy bueno, y sobresalta sobre los
-  otros dos en sus ventaja: robusto, no requiere bineo, aplica bien en
-  resoluciones pobres. Como herramienta (que es lo que se está
-  vendiendo en el trabajo, un método, eso es lo que hay que recalcar y
-  resaltar)}
+In this paper we show that integrated mass profile can be used  to
+estimate the dark matter halo concentration in halos from N-body
+simulations.  
+This has two advantages with respect to the two methods mentioned
+above.  
+It does not involve any data binning and does not throw away data
+points resulting in a robust estimate even at low resolution/particle
+numbers.  
+Furthermore, since the method does not require any binning,
+there is no need to tune numerical parameters, providing a new
+independent method to estimate the concentration parameter.
 

### 2015-11-06 paper/paper.tex
descripcion metodo

@@
 $\delta_c$ is the halo dimensionless characteristic density and $r_s$
-is the scale radius. This radius marks {\bf the point where the
-  logarithmic slope of the density profile is equal to -2} marking the
-transition between the power law scaling $\rho\propto r^{-1}$ for
-$r<r_s$ and $\rho\propto r^{-3}$ for $r>r_s$.
+is the scale radius. 
+This radius marks the point where the logarithmic slope of the density
+profile is equal to -2, marking the transition between the power law
+scaling $\rho\propto r^{-1}$ for $r<r_s$ and $\rho\propto r^{-3}$ for
+$r>r_s$.
 
@@
 spherical volume that encloses a density of $\Delta_h$ times the mean
-density of the Universe.  The corresponding mass $M_{v}$, the virial
-mass, can be written as $M_{v} = \frac{4\pi}{3}\bar{\rho}\Delta_h
-r_v^3$.  From these virial quantities we define new dimensionless
-variables for the radius and mass $x\equiv r/r_v$ and $m\equiv
-M(<r)/M_v$.
+density of the Universe.  
+The corresponding mass $M_{v}$, the virial mass, can be written as
+$M_{v} = \frac{4\pi}{3}\bar{\rho}\Delta_h r_v^3$.  
+From these virial quantities we define new dimensionless variables for
+the radius and mass $x\equiv r/r_v$ and $m\equiv M(<r)/M_v$.
 
 In this paper we use $\Delta_h=740$ roughly corresponding to 200 times
-the critical density {\bf at redshift z=0}.
+the critical density at redshift z=0.
 
@@
 
-From this normalization value and for later convenience we define the
+From this normalization and for later convenience we define the
 following function
@@
 \end{equation}
-
+%
 This normalized profile always shows a maximum provided that the
@@
 where $x_{\rm max}=2.163$ \citep{Klypin2014} and the function $f(x)$
-was defined in Eq. (\ref{eq:f_NFW}).
+correspondes to the definition in Eq. (\ref{eq:f_NFW}).
 
@@
 \subsection{Estimates from the density and velocity profiles}
-{\bf To date,} there are two standard methods to estimate
-concentrations in dark matter halos extracted from N-body simulations.
 
-The first method tries to directly estimate the density profile.  It
-takes all the particles in the halo and bins them in the logarithm of
-the radial coordinate from the halo center.  Then, it estimates the
-density in each logarithmic bin counting the particles and dividing by
-the corresponding shell volume.  At this point is is possible to make
-a direct fit to the density as a function of the radial coordinate.
-This method has been {\bf used broadly for more than two decades} to
-study the mass-concentration-redshift relation of dark matter halos
-using the Millennium Simulation Series.
+To date, there are two standard methods to estimate concentrations in
+dark matter halos extracted from N-body simulations.
 
-{\it no veo la necesidad de citar el ``trabajo mas'' reciente que usa
-  el metodo, cuando ha sido usado durante mas de dos decadas!}
+The first method tries to directly estimate the density profile.  
+It takes all the particles in the halo and bins them in the logarithm of
+the radial coordinate from the halo center.  
+Then, it estimates the density in each logarithmic bin counting the
+particles and dividing by the corresponding shell volume.  
+At this point is possible to make a direct fit to the density as a function of the radial coordinate.
+This method has been used broadly for more than two decades to study
+the mass-concentration-redshift relation of dark matter halos.
 
-A second method uses the circular velocity profile.  It finds the
-value of $x$ for which the normalized circular velocity $v(<x)$ shows
-a maximum.  Using this value it solves numerically for the
-corresponding value of the concentration using Eq. (\ref{eq:max_v}).
+A second method uses the circular velocity profile.  
+It finds the value of $x$ for which the normalized circular velocity
+$v(<x)$ shows a maximum.  
+Using this value it solves numerically for the corresponding value of
+the concentration using Eq. (\ref{eq:max_v}). 
 This method has been most recently used by \cite{Klypin2014} to study
@@
 \subsection{Our proposal: estimate from the integrated mass profile}
-Our method uses the integrated mass profile.  First we define the
-center of the halo to be at the position of the particle with the
-lowest gravitational potential.  Then we rank the particles by their
-increasing radial distance from the center.  From this ranked list of
-$i=1,N$ particles, the total mass at a radius $r_i$ is $M_i=i\times
-m_p$, where $r_i$ is the position of the $i$-th particle and $m_p$ is
-the mass of a single computational particle. In this process we
-discard the particle at the center.
+
+Our method uses the integrated mass profile.  
+First we define the center of the halo to be at the position of the
+particle with the lowest gravitational potential.  
+Then we rank the particles by their increasing radial distance from
+the center. 
+From this ranked list of $i=1,N$ particles, the total mass at a radius
+$r_i$ is $M_i=i\times m_p$, where $r_i$ is the position of the $i$-th
+particle and $m_p$ is the mass of a single computational particle. In
+this process we discard the particle at the center.
 
@@
 Once the mass profile is expressed in dimensionless variables the
-concentration is the only free parameter. We use an Affine Invariant
-Markov chain Monte Carlo implemented in the python module {\em emcee}
-\citep{emcee} to sample the likelihood function distribution defined
-by ${\cal L}(c)\propto \exp(-\chi^2(c)/2)$ where the $\chi^2(c)$ is
+concentration is the only free parameter. 
+We use an Affine Invariant Markov Chain Monte Carlo implemented in the
+python module {\em emcee} \citep{emcee} to sample the likelihood
+function distribution defined by ${\cal L}(c)\propto
+\exp(-\chi^2(c)/2)$ where the $\chi^2(c)$ is 
 written as
@@
 advantages with respect to the density and velocity methods, it does
-not involve any binning (unlike the density methods ) and the sampling
+not involve any binning (unlike the density methods) and the sampling
 method uses the information from all the particles in the halo (unlike
@@
 
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.70\textwidth]{error.pdf}
+\end{center}
+\caption{Average value of the relative error in the concentration
+  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
+  the set of mock halos. Different symbols represent different
+  methods. Our method provide the most accurate estimate at fixed
+  particle number $N$.  {\it Con respecto a esta figura tengo una
+    pregunta. Yo ajusté los perfiles con menos de 200 partulas? no
+    recuerdo!}
+    \label{fig:error}}
+\end{figure*}
+
 The method we use to generate the mock halos is based on the
-integrated mass profile.  We start by fixing the desired concentration
-$c$ and total number of particles $N$ in the mock halo.  With these
-values we define the mass element as $\delta m = 1/M$, corresponding
-to the mass of each particle such that the total mass is one.  Then
-for each particle, $i=1,\ldots,N$, we find the value of $r_i$ such
-that the difference
+integrated mass profile.  
+We start by fixing the desired concentration $c$ and total number of
+particles $N$ in the mock halo.  
+With these values we define the mass element as $\delta m = 1/M$, corresponding
+to the mass of each particle such that the total mass is one.   
+Then for each particle, $i=1,\ldots,N$, we find the value of $r_i$
+such that the difference 
 % 
@@
 The value of $r_i$ is the radius of the $i$-th particle of the mock
-halo.  Then we generate random polar and azimuthal angles $\theta$ and
-$\phi$ for each particle to ensure spherical symmetry.  Finally these
-three spherical coordinates are transformed into Cartesian coordinates
-$(r,\theta,\phi) \rightarrow (x,y,z)$.
+halo.  
+Then we generate random polar and azimuthal angles $\theta$ and
+$\phi$ for each particle to ensure spherical symmetry.  
+Finally these three spherical coordinates are transformed into
+Cartesian coordinates $(r,\theta,\phi) \rightarrow (x,y,z)$.
 
@@
 of $100$ halos each.  The four groups differ in the total number of
-particles for their halos: $20$, $200$, $2000$ and $20000$.  Inside
-each group the halos have random concentration values in the range
-$1<c<20$ with a uniform distribution.  For all these halos {\bf ww?}
-the concentration values using the density, velocity and mass methods
-described in the previous section.  We quantify the difference between
-the expected $c_{in}$ and obtained $c_{out}$ values by
+particles for their halos: $20$, $200$, $2000$ and $20000$.  
+Inside each group the halos have random concentration values in the range
+$1<c<20$ with a uniform distribution.  
+For all these halos we find  the concentration values using the
+density, velocity and integrated mass methods described in the
+previous section.
+
+We quantify the difference between the expected $c_{in}$ and measured
+$c_{out}$ values by 
 %
@@
 where ${\cal{H}}$ corresponds to a set of mock halos, and
-$\left|{\cal{H}}\right|$ is the number of haloes in ${\cal{H}}$. {\bf
+$\left|{\cal{H}}\right|$ is the number of haloes in ${\cal{H}}$. 
   The larger the value of $\avg{|D|}$, the larger the discrepace of
-  the concentrations obtained for that method}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.70\textwidth]{error.pdf}
-\end{center}
-\caption{Average value of the relative error in the concentration
-  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
-  the set of mock halos. Different symbols represent different
-  methods. Our method provide the most accurate estimate at fixed
-  particle number $N$.  {\it Con respecto a esta figura tengo una
-    pregunta. Yo ajusté los perfiles con menos de 200 partulas? no
-    recuerdo!}
-    \label{fig:error}}
-\end{figure*}
+  the concentrations obtained for that method.
 

### 2015-11-07 paper/paper.tex
reescribiendo cada frase (?)

@@
 
-In a dark matter dominated universe galaxy properties are driven by
-the dark matter halo host.
-One of the key structural halo properties is the concentration. 
+Galaxy properties are driven by its dark matter halo host.
+A dark matter halo's concentration is on the key structural
+properties. 
 [EN QUE MODELOS IMPORTA LA CONCENTRACION?]
-For these reasons it is important to have a reliable concentration
-estimate from N-body simulations. 
-Here we show that the concentration parameter in dark matter halos from
-N-body simulations can be reliably estimated from the radially integrated mass
-profile.
+This drives the pursue to make the concentration estimates of
+simulated halos as reliable as possible. 
+Here we show the radially integrated mass profile can be converted
+into a powerful tool to estimate concentratios.
+
 The main advantage of this approach is that it uses the full
@@
 the non-linear evolution of a dark matter density field sampled with
-$2048^3$ particles over a cubic box of $1000$ \hMpc on a side.  The
+$2048^3$ particles over a cubic box of $1000\ \hMpc$ on a side.  The
 data is publicly available through \url{http://www.cosmosim.org/}.

### 2015-11-09 paper/paper.tex
ahora la intro fluye mejor

@@
 
-Galaxy properties are driven by its dark matter halo host.
-A dark matter halo's concentration is on the key structural
-properties. 
-[EN QUE MODELOS IMPORTA LA CONCENTRACION?]
-This drives the pursue to make the concentration estimates of
-simulated halos as reliable as possible. 
-Here we show the radially integrated mass profile can be converted
-into a powerful tool to estimate concentratios.
-
+Galaxy properties are coupled to the structural of its dark
+matter halo host. 
+One of the key quantities is the halo density profile which, assuming
+a  Navarro-Frenk-White parameterization, can be described by the
+concentration.
+This has motivated the development of different algorithms to estimate
+the concentraion in N-body halos.
+Here we present a new algorithm to estimate the concentration
+based on the radially integrated mass profile
 The main advantage of this approach is that it uses the full
@@
 For the maximum radial velocity method it is on the order of $20\%$
-while density profile methods perform worst at the low resolution
-limit since they require at least 200 particles inside the virial
-radius to make a reliable estimate of the density profile. 
+while density profile methods perform worst at the low resolution.
 For halos with $2\times 10^4$ particles our method achieves an
@@
 M<10^{13}\hMsun$ our method yields median concentration values lower
-by a $15\%-20\%$ compared to the velocity and density methods ({\bf
-  why?}).  
+by a $15\%-20\%$ compared to the velocity and density methods 
 At higher masses $3\times 10^{13}\hMsun < M < 2\times
@@
 %*************************************************************************
-In the concordance cosmological paradigm the matter content of the
-Universe is dominated by dark matter, a collisionless fluid shaped by
-gravitational interactions.  In the last three decades simulations of
-dark matter dominated universes have provided valuable insights into
-the large scale structure formation process, showing a remarkable
-success in the comparison between theoretical results and observations
-of the galaxy distribution obtained from surveys.
-\citep{Springel2005,2011ApJ...740..102K}.
+In the current structure formation paradigm the properties of galaxies
+are coupled to the evolution of their dark matter (DM) hosting halo.
+This dependence has motivated the detailed study of dark matter halo
+properties defining its formation history and internal structure. 
+In particular, the DM distribution inside a halo is key to
+understand the sizes and dynamics of galaxies.
 
-{\bf FALTA CITEP Navarro et.al. 2010} have used high resolution simulations to show
-that the full halo density profile is not universal and follows an
-Einasto density distribution. 
-However, if one is not interested in the very central region of the
+The internal matter distribution is parameterized through the density
+profile. 
+In a first approximation this profile is spherically symmetric and
+its density only dependens on the radial coordinate. 
+One the most popular parameterizations for DM halo radial
+density distribution is the Navarro-Frenk-White (NFW) profile
+\citep{NFW}.   
+Furthermore, if one is not interested in the very central region of the
 dark matter halo (where galaxy formation takes place, and where the
 effects of baryon physics on dark matter distribution is still an
-uncknown), one can assume an approximation where dark matter
-overdensities closely follow an universal density profile. 
-In a first approximation this profile is spherically symmetric and
-its density only dependens on the radial coordinate. 
-Although it is well known that the characteristics of
-this densty profile depend on redshift {\bf FALTA CITEP (Maccio
-  et.al. 2008)}, its universal shape seems to be independent of the
-cosmological parameters and is self-similar for different spatial
-scales after an adequate re-scaling is applied \citep{NFW,Taylor2001}.
-
-In such circumstances, one the most popular parameterizations
-for dark matter halo radial density distribution is the
-Navarro-Frenk-White (NFW) profile \citep{NFW}.  
+unknown), one can assume that this profile is universal.
+\citep{Navarro2010}.  
  This profile is a double power law in radius, where the transition
@@
 known as the concentration $c=R_v/r_s$.
-Simulations show that the concentration is a strong function of halo
-mass and redshift and provides information about the mass assembly of
-the dark matter halo {\bf (Citar paper que reproduce mis graficas y conecta
-C con m(z))}.
 
-{\bf usos de modelos de formacion de galaxias}
-The relationship between halo mass and concentration
-could also provide a potential test of the Cold Dark Matter (CDM)
-paradigm.
+The NFW profile parameterization thus provides the conceptual
+framework to study simulated dark matter halos as a function of
+redshift and cosmological parameters.
+Here the central quantity is the concentration. 
+In these studies 
+\citep{Neto2007,Maccio2008,Duffy2008,Munoz2011,Prada2012,Ludlow2014} 
+the results are summarized through the
+mass-concentration relationship; that is the distribution of
+concentration values at a fixed halo mass and redshift.
+The biggest challenge in such numerical experiments is having a
+reliable algorithm to estimate the concentration. 
+Such an algorithm should provide unbiased results and must be robust
+when applied to simulations of different numerical resolution.
 
-For all these reasons mentioned above a great deal of effort has
-been invested in calibrating this relationship with simulations
-\citep{Neto2007,Duffy2008,Munoz2011,Prada2012,Ludlow2014} and finding
-the best possible way to constraint it with observations
-\citep{Buote2007,Comerford2007,Mandelbaum2008,Giocoli2014,Foex2014,Shan2015}.
-
-In N-body simulations there are two main methods to estimate the
-concentration parameter of a dark matter halo.
+There are two main algorithms to estimate the concentration parameter
+of a N-body dark matter halo. 
 The first method takes the halo particles and bins them into
@@
 and above its maxima.  
-Additionally, small fluctuations on the value of this maximum can
-yield large perturbations on the estimated concentration parameter.
+Small fluctuations on the value of this maximum can yield large
+perturbations on the estimated concentration parameter.
 
-In this paper we show that integrated mass profile can be used  to
-estimate the dark matter halo concentration in halos from N-body
-simulations.  
-This has two advantages with respect to the two methods mentioned
-above.  
+In this paper we present a third alternative based on fitting the
+integrated mass profile.
+This approach has two advantages with respect to the above mentioned
+methods.  
 It does not involve any data binning and does not throw away data
-points resulting in a robust estimate even at low resolution/particle
+points. 
+This results in a robust estimate even at low resolution/particle
 numbers.   
-Furthermore, since the method does not require any binning,
-there is no need to tune numerical parameters, providing a new
-independent method to estimate the concentration parameter.
+Furthermore, since the method does not require any binning, there is
+no need to tune numerical parameters, providing a new independent
+method to estimate the concentration parameter. 
+Here we provide a detailed description of this method and a
+comparison against the two traditional methods by measuring its
+performance both on mock halos and N-body halos.
 

### 2015-11-09 paper/paper.tex
abstract + fluido

@@
 based on the radially integrated mass profile
-The main advantage of this approach is that it uses the full
-particle information without any binning, which makes it reliable in
+The algorithm is easy to implement. It main advantages is that uses the full
+particle information without any binning, making it realiable in
 cases when low numerical resolution becomes a limitation for other
@@
 Let us review first the basic properties of the NFW density profile.
-This shall help us to define our notation and review the important
-assumptions of the two different methods commonly used to measure the
-concentration to finally present the new method.
+This shall help us to define our notation.
 
@@
 This radius marks the point where the logarithmic slope of the density
-profile is equal to -2, marking the transition between the power law
+profile is equal to -2, the transition between the power law
 scaling $\rho\propto r^{-1}$ for $r<r_s$ and $\rho\propto r^{-3}$ for
@@
 
-In this paper we use $\Delta_h=740$ roughly corresponding to 200 times
-the critical density at redshift z=0.
+In this paper we use $\Delta_h=740$, a number roughly corresponding to
+200 times the critical density at redshift z=0.
 
@@
 \label{sec:method}
+
+We now review the key assumptions of the different methods used
+to estimate the concentration.
 

### 2015-11-09 paper/paper.tex
nueva estructura para que quepa en una letter

@@
 
-Galaxy properties are coupled to the structural of its dark
-matter halo host. 
-One of the key quantities is the halo density profile which, assuming
-a  Navarro-Frenk-White parameterization, can be described by the
-concentration.
-This has motivated the development of different algorithms to estimate
-the concentraion in N-body halos.
-Here we present a new algorithm to estimate the concentration
-based on the radially integrated mass profile
-The algorithm is easy to implement. It main advantages is that uses the full
-particle information without any binning, making it realiable in
-cases when low numerical resolution becomes a limitation for other
-methods. 
-We show the good performance of this method by estimating halo
+We present a new algorithm to estimate the concentration of N-body
+dark matter halos based on the radially integrated mass profile
+Its main advantage is that it uses the full particle information
+without any binning, making it realiable in  cases when low numerical
+resolution becomes a limitation for other methods.  Additionally, the
+algorithm is straightforward to implement.  
+We test the performance of this method by estimating halo
 concentration both on mock and N-body halos. 
@@
 Tests on  the mock halos show that the accuracy of our method to recover input
-concentrations varies with halo resolution. For halos
+concentrations varies with halo resolution, outperforming the other
+two methods. For halos
 sampled with $20$ particles our method recovers the input
@@
 For the maximum radial velocity method it is on the order of $20\%$
-while density profile methods perform worst at the low resolution.
+while density profile methods fail at the $100\%$ level.
 For halos with $2\times 10^4$ particles our method achieves an
@@
 This dependence has motivated the detailed study of dark matter halo
-properties defining its formation history and internal structure. 
-In particular, the DM distribution inside a halo is key to
-understand the sizes and dynamics of galaxies.
+properties such as its formation history and internal structure. 
+In particular, the sizes and dynamics of galaxies are determined by
+the DM distribution inside a halo.
 
-The internal matter distribution is parameterized through the density
+The internal DM distribution is parameterized through the density
 profile. 
@@
 \citep{NFW}.   
-Furthermore, if one is not interested in the very central region of the
+If one is not interested in the very central region of the
 dark matter halo (where galaxy formation takes place, and where the
 effects of baryon physics on dark matter distribution is still an
-unknown), one can assume that this profile is universal.
+unknown) one can also assume that this profile is universal.
 \citep{Navarro2010}.  
@@
 
-The NFW profile parameterization thus provides the conceptual
+The concentration of the NFW profile provides the conceptual
 framework to study simulated dark matter halos as a function of
 redshift and cosmological parameters.
-Here the central quantity is the concentration. 
 In these studies 
@@
 concentration values at a fixed halo mass and redshift.
-The biggest challenge in such numerical experiments is having a
+A big challenge in such numerical experiments is having a
 reliable algorithm to estimate the concentration. 
@@
 comparison against the two traditional methods by measuring its
-performance both on mock halos and N-body halos.
+performance both on mock and N-body halos.
 
@@
 We now review the key assumptions of the different methods used
-to estimate the concentration.
+to estimate the concentration before presenting our proposal.
 
@@
 dark matter halos extracted from N-body simulations. 
-
 The first method tries to directly estimate the density profile.  
@@
 particles and dividing by the corresponding shell volume.  
-At this point is possible to make a direct fit to the density as a function of the radial coordinate.
-This method has been used broadly for more than two decades to study
+At this point is possible to make a direct fit to the density as a
+function of the radial coordinate. 
+This method has been broadly used for more than two decades to study
 the mass-concentration-redshift relation of dark matter halos.
@@
 
-Our method uses the integrated mass profile.  
-First we define the center of the halo to be at the position of the
+Our method uses the integrated mass profile defined in
+Eq. (\ref{eq:profile}).
+To build it from N-body data we follow the next steps.
+First, we define the center of the halo to be at the position of the
 particle with the lowest gravitational potential.  
@@
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-  \includegraphics[width=0.70\textwidth]{error.pdf}
+  \includegraphics[width=0.50\textwidth]{error.pdf}
 \end{center}
@@
     \label{fig:error}}
+\end{figure}
+
+\label{sec:data}
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.32\textwidth]{conc_mass_vel.pdf}
+    \includegraphics[width=0.32\textwidth]{conc_mass_dens.pdf}
+    \includegraphics[width=0.32\textwidth]{conc_dens_vel.pdf}
+  \end{center}
+  \caption{Comparison between the concentrations measured by our
+    method and the maximum velocity (left) and density (middle)
+    methods. The line indicates the equal value between the two
+    techniques. The right panel compares the results of the maximum
+    velocity and density methods.
+  \label{fig:mdv}}
 \end{figure*}
@@
 
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.50\textwidth]{concentration.pdf}
+\end{center}
+\caption{Mass-concentration relationship for the three different
+  methods used on the same cosmological N-body data. 
+  The lines correspond to the median concentration values in each bin.
+  \label{fig:concentration}}
+\end{figure}
+
 Figure \ref{fig:error} shows the behaviour of $\avg{|D|}$ as a function of
@@
 \subsection{Halos from a cosmological simulation}
-
-\label{sec:data}
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=0.33\textwidth]{conc_mass_vel.pdf}
-    \includegraphics[width=0.33\textwidth]{conc_mass_dens.pdf}
-    \includegraphics[width=0.33\textwidth]{conc_dens_vel.pdf}
-  \end{center}
-  \caption{Comparison between the concentrations measured by our
-    method and the maximum velocity (left) and density (middle)
-    methods. The line indicates the equal value between the two
-    techniques. The right panel compares the results of the maximum
-    velocity and density methods.
-  \label{fig:mdv}}
-\end{figure*}
 
@@
 
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.75\textwidth]{concentration.pdf}
-\end{center}
-\caption{Mass-concentration relationship for the three different
-  methods used on the same cosmological N-body data. 
-  The lines correspond to the median concentration values in each bin.
-  \label{fig:concentration}}
-\end{figure*}
-
-{\em Aqui hay algo importante que hay que entender antes de discutir
-  esta gráfica , y es la razón por la cual el metodo del perfil de
-  masa da valores de concentración tan bajos a baja masa y comparables
-  a los de los otros dos métodos a alta masa. Es importante entender
-  la razón de esto!.  Se me ocurren unas preguntas para tratar de
-  entender. \\ 1) La grafica de c-M \ref{fig:concentration} usa todos
-  los halos o solo los halos relajados? La inclusión de halos no
-  relajados introduce in bias en la mediana en Cvir, así que vale la
-  pena inclusive agregar una linea mas a la gráfica con los halos
-  relajados y sin ellos. Para los otros dos métodos ya se sabe que
-  hace la población de halos no relajados en la medida así que no creo
-  necesario agregarlas para esos métodos. \\ Hay que explicar un poco
-  mas la gráfica en el sentido de que se grafica y como se
-  calculó. mean concentration?, Median concentrations? o mean in
-  logscale?  Mas bins de cuanto? Mínimo cuantos halos por mass bin?,
-  Halos relajados en todos los casos, o indistintos?}
+%{\em Aqui hay algo importante que hay que entender antes de discutir
+%  esta gráfica , y es la razón por la cual el metodo del perfil de
+%  masa da valores de concentración tan bajos a baja masa y comparables
+%  a los de los otros dos métodos a alta masa. Es importante entender
+%  la razón de esto!.  Se me ocurren unas preguntas para tratar de
+%  entender. \\ 1) La grafica de c-M \ref{fig:concentration} usa todos
+%  los halos o solo los halos relajados? La inclusión de halos no
+%  relajados introduce in bias en la mediana en Cvir, así que vale la
+%  pena inclusive agregar una linea mas a la gráfica con los halos
+%  relajados y sin ellos. Para los otros dos métodos ya se sabe que
+%  hace la población de halos no relajados en la medida así que no creo
+%  necesario agregarlas para esos métodos. \\ Hay que explicar un poco
+%  mas la gráfica en el sentido de que se grafica y como se
+%  calculó. mean concentration?, Median concentrations? o mean in
+%  logscale?  Mas bins de cuanto? Mínimo cuantos halos por mass bin?,
+%  Halos relajados en todos los casos, o indistintos?}
 

### 2015-11-11 paper/paper.tex
puliendo

@@
 %=========================================================================
-\title{Estimating dark matter halo concentration using the integrated
-  mass profile} 
+\title[Halo concentration from the mass profile]{Estimating dark matter
+  halo concentration using the integrated mass profile} 
 \author[C. Poveda, J.E. Forero-Romero, J.C. Mu\~noz-Cuartas]{
@@
 \begin{abstract}
-
 We present a new algorithm to estimate the concentration of N-body
-dark matter halos based on the radially integrated mass profile
+dark matter halos.
+The method uses the integrated mass profile to find the optimal
+concentration value. 
 Its main advantage is that it uses the full particle information
 without any binning, making it realiable in  cases when low numerical
-resolution becomes a limitation for other methods.  Additionally, the
-algorithm is straightforward to implement.  
+resolution becomes a limitation for other methods.  
+Additionally, the algorithm is straightforward to implement.  
 We test the performance of this method by estimating halo
@@
 sampled with $20$ particles our method recovers the input
-concentration with $10\%$ accuracy. 
-For the maximum radial velocity method it is on the order of $20\%$
-while density profile methods fail at the $100\%$ level.
-For halos with $2\times 10^4$ particles our method achieves an
+concentration with $10\%$ accuracy, while for the maximum radial
+velocity method it is on the order of $20\%$ 
+and density profile methods fail at the $100\%$ level.
+For halos with $2\times 10^4$ particles our method achieves a recovery
 accuracy of $0.01\%$ while the velocity and density profile methods
 achieve $0.1\%$ and $1\%$, respectively. 
-We measure the mass-concentration relationship on N-body
-data taking care of using halos sampled with at least $200$
-particles. We find that at low masses $10^{12}\hMsun <
-M<10^{13}\hMsun$ our method yields median concentration values lower
-by a $15\%-20\%$ compared to the velocity and density methods 
-At higher masses $3\times 10^{13}\hMsun < M < 2\times
-10^{14}\hMsun$ the three methods give similar results.
+We also measure the mass-concentration relationship on N-body
+data. We find that within the probed mass range ($10^{12}\hMsun <
+10^{14}\hMsun$) the three methods give consistent results within the
+statistical uncertainties.   
+We only find a small discrepancy at low masses, $M<10^{13}\hMsun$, where
+our method yields lower median concentration values by $15\%-20\%$
+compared to the velocity and density methods. 
+From these results we believe that the new method deserves to be
+included in a simulator's toolkit to probe the internal structure of
+dark matter halos.
 \end{abstract}
@@
 
-In this paper we present a third alternative based on fitting the
+In this letter we present a third alternative based on fitting the
 integrated mass profile.
@@
 
-In this paper we use $\Delta_h=740$, a number roughly corresponding to
+In this letter we use $\Delta_h=740$, a number roughly corresponding to
 200 times the critical density at redshift z=0.
@@
 
-We now review the key assumptions of the different methods used
-to estimate the concentration before presenting our proposal.
-
 \subsection{Estimates from the density and velocity profiles}
@@
 dark matter halos extracted from N-body simulations.
+
 The first method tries to directly estimate the density profile.  
@@
 Eq. (\ref{eq:profile}).
-To build it from N-body data we follow the next steps.
+We build it from N-body data following the next steps.
 First, we define the center of the halo to be at the position of the
@@
 $r_i$ is $M_i=i\times m_p$, where $r_i$ is the position of the $i$-th
-particle and $m_p$ is the mass of a single computational particle. In
-this process we discard the particle at the center.
+particle and $m_p$ is the mass of a single computational particle. 
+In this process we discard the particle at the center.
 
@@
 concentration is the only free parameter. 
-We use an Affine Invariant Markov Chain Monte Carlo implemented in the
+We then use an Affine Invariant Markov Chain Monte Carlo implemented in the
 python module {\em emcee} \citep{emcee} to sample the likelihood
@@
 
-The construction of the numerical integrated mass profile has two
-advantages with respect to the density and velocity methods, it does
-not involve any binning (unlike the density methods) and the sampling
-method uses the information from all the particles in the halo (unlike
-the velocity method).
-
 \section{Results}
@@
 
-We now present the results of applying the three methods above
-mentione on two different halo samples.  The first sample is composed
-by mock halos generated to have known concentration values in perfect
-spherical symmetry following an NFW profile.  We use this sample to
-check that we can recover the expected values but also gauge the
-impact of the number of particles on the outcomes.  The second sample
-comes from a publicly available N-body cosmological simulation.  From
-this sample we quantify again the differences between all the methods
-and also estimate the impact on the mass-concentration relationship.
+We apply the three methods mentioned above on two different halo
+samples.
+The first sample is composed by mock halos generated to have known
+concentration values in perfect spherical symmetry following an NFW
+profile.    
+Using this sample we want to quantify the ability to recover the
+expected concentration as a function of particle numbe.
+The second sample comes from a publicly available N-body cosmological
+simulation.  
+In this way we test the new method on more realistic and complex
+data. 
+We summarize the results on this dataset by showing the impact on the
+mass-concentration relationship.
 
@@
 
-In this paper, we presented a new method to estimate the concentration
-of dark matter halos in N-body simulations.  We tested our method on
-mock halo data to study the impact of total number of particles and
-input concentration on the retrieved values.  We compared these
+In this letter we presented a new method to estimate the concentration
+of dark matter halos in N-body simulations.  
+We tested our method on mock halo data to study the impact of total
+number of particles and input concentration on the retrieved values.  
+We compared these
 results against two other methods commonly used in the literature to

### 2015-11-11 paper/paper.tex
puliendo texto del paper

@@
 compared to the velocity and density methods. 
-From these results we believe that the new method deserves to be
-included in a simulator's toolkit to probe the internal structure of
-dark matter halos.
+From these results we believe that the new method is promising tool
+to probe the internal structure of dark matter halos.
 \end{abstract}
@@
 are coupled to the evolution of their dark matter (DM) hosting halo.
-This dependence has motivated the detailed study of dark matter halo
+For instance, the sizes and dynamics of galaxies are determined by
+the DM distribution inside a halo.
+This dependence has motivated the detailed study of DM halo
 properties such as its formation history and internal structure.
-In particular, the sizes and dynamics of galaxies are determined by
-the DM distribution inside a halo.
 
@@
 concentration values at a fixed halo mass and redshift.
-A big challenge in such numerical experiments is having a
+The success of such numerical experiments rests on a
 reliable algorithm to estimate the concentration. 

### 2015-11-11 paper/paper.tex
puliendo texto

@@
 We generate in total $400$ mock halos split into four different groups
-of $100$ halos each.  The four groups differ in the total number of
-particles for their halos: $20$, $200$, $2000$ and $20000$.  
+of $100$ halos each.  
+The four groups differ in the total number of particles for their
+halos: $20$, $200$, $2000$ and $20000$.   
 Inside each group the halos have random concentration values in the range
 $1<c<20$ with a uniform distribution.  
-For all these halos we find  the concentration values using the
+We find the concentration values for all these halos using the
 density, velocity and integrated mass methods described in the
@@
 $\left|{\cal{H}}\right|$ is the number of haloes in ${\cal{H}}$. 
-  The larger the value of $\avg{|D|}$, the larger the discrepace of
-  the concentrations obtained for that method.
+A large discrepacy between the estimated and input concentrations are
+quantified by a large $\avg{|D|}$.
 
@@
 Figure \ref{fig:error} shows the behaviour of $\avg{|D|}$ as a function of
-halo particle number for the three different methods to estimate the
-concentration.
+halo particle number for the three different methods.
 
 At fixed particle numbers our method always shows the lowest
-$\avg{|D|}$ values compared to the other two methods.  Its accuracy is
-on the order of $10\%$ for $20$ particles in the halo, going down to
-$0.01\%$ for halos with $20000$ particles.  The dependence of
-$\avg{|D|}$ with the particle number $N$ goes approximately as
-$\avg{|D|}\propto N^{-1/2}$, hinting that the accuracy of the method
-is related to a decrease of Poisson noise.
+$\avg{|D|}$ values compared to the other two.
+Its accuracy is on the order of $10\%$ for $20$ particles in the halo,
+decreasing to $0.01\%$ for halos with $20000$ particles.  
+The dependence of $\avg{|D|}$ with the particle number $N$
+goesapproximately as $\avg{|D|}\propto N^{-1/2}$.   
+This hints that the accuracy of the method could be due to a decrease
+of Poisson noise.
 
 The method based on the maximum of the circular velocity shows a
-similar behaviour $\avg{|D|}\propto N^{-1/2}$.  Its accuracy is $2-5$
-times less than in our method, on the order of $20\%$ for $20$
-particle halos and $0.5\%$ for $20000$ particle halos. {\bf The method
-  based on the direct density fit shows the lowest accuracy for a low
-  particle number. As it is discussed in \citep{Munoz2011}, density
-  binning for halos with particle numbers below $\sim200$ leads to a
-  biased estimation of the mass density profile, and therefore to a
-  biased estimation of the concentration parameter. This behaviour is
-  evident in the large values of $\avg{|D|}$ for halos with number of
-  particles below ~200 and an intermediate accuracy between the other
-  two methods for a high particle number.}
+similar behaviour $\avg{|D|}\propto N^{-1/2}$.  
+Its accuracy is $2-5$ times lower than in our method, on the order of
+$20\%$ for $20$  particle halos and $0.5\%$ for $20000$ particle
+halos. 
+The method  based on the direct density fit shows the lowest accuracy for a low
+  particle number. 
+  As it is discussed in \citep{Munoz2011}, density binning for halos
+  with particle numbers below $\sim200$ leads to a biased estimation
+  of the mass density profile, and therefore to a biased estimation of
+  the concentration parameter. 
+This behaviour is evident in the large values of $\avg{|D|}$ for halos
+with number of particles below ~200 and an intermediate accuracy
+between the other two methods for a high particle number.
 
@@
 
-{\bf The results presented in the previous section show that in an
-  idealized setup (perfect spherical halos, pure NFW desity profiles,
-  total isolation) our method of the mass profile performs better than
-  the other two methods commonly used to measure concentrations in
-  simulated dark matter haos. However, actual simulated dark matter
-  halos are much more complex. They are not isolated, many of them
-  experience mergers that take them out of the equilibrium. Halos may
-  have also plenty of substructure, etc. All these effects disturb the
-  mass density profile, taking it away from the ideal NFW profile we
-  assume in this wok. In order to see the real performance of our new
-  method use it to estimate the concentration parameter in dark matter
-  halos obtained from a cosmological Nbody simulation and compare with
-  the other two calsical methods.}
+The results presented in the previous section show that in an
+idealized setup (pure NFW desity profiles, perfect spherical halos in
+total isolation) our method performs better than the other two
+methods commonly used in the literature.
+
+However, simulated dark matter halos in a cosmological context are
+complex. 
+They are not isolated, many of them  experience mergers that take them
+out of the equilibrium. 
+Halos may have also plenty of substructure, etc. All these effects
+disturb the mass density profile, taking it  away from the ideal NFW
+profile. 
+In order to see the completeley explore performance of our method, we use
+it to estimate the  concentration parameter in dark matter halos
+obtained from a cosmological N-body simulation and compare with the
+other two classical methods.
 
@@
 the non-linear evolution of a dark matter density field sampled with
-$2048^3$ particles over a cubic box of $1000\ \hMpc$ on a side.  The
-data is publicly available through \url{http://www.cosmosim.org/}.
+$2048^3$ particles over a cubic box of $1000\ \hMpc$ on a side.  
+The data is publicly available at \url{http://www.cosmosim.org/}.
 More details about the structure of the database and the simulation
@@
 
-We build a sample of all halos located in a cubic sub-volume of $100$
-\hMpc on a side centered on the most massive halo in the simulation at
-$z=0$ which corresponds to the \texttt{miniMDR1} tables in the
-database.  From this sample we select all the halos at $z=0$ detected
+%%%%%%%
+
+We use a halo sample containing all the halos located in a cubic
+sub-volume of $100$ \hMpc on a side centered on the most massive halo
+in the simulation at $z=0$  which corresponds to the \texttt{miniMDR1}
+table in the  database.  
+From this sample we select all the halos at $z=0$ detected
 with a Friends-of-Friends (FoF) algorithm with masses in the interval
-$10^{12}\leq M_{\rm FoF}/\hMsun \leq 10^{15}$.  The FoF algorithm used
-with a linking length of $0.17$ times the {\bf mean} inter-particle
-distance. This choice translates into an overdensity $\Delta_h\sim
-400-700$ dependent on the halo concentration \citep{More2011}.
+$10^{12}\leq M_{\rm FoF}/\hMsun \leq 10^{14}$.  
+The FoF algorithm used a linking length of $0.17$ times the mean
+inter-particle distance. This choice translates into an overdensity
+$\Delta_h\sim  400-700$ dependent on the halo concentration \citep{More2011}.
 Finally, we select from the database all the particles that belong to
@@
 times the critical density) to select an spherical region that we
-redefine to be our halo.  This choice makes that our overdensities are
-fully included inside the original FoF particle group.  On the
-interest of providing a fair comparison against the density method we
+redefine to be our halo.  
+This choice makes that our overdensities are fully included inside the
+original FoF particle group.   
+On the interest of providing a fair comparison against the density method we
 only report results from overdensities with at least $200$ particles.

### 2015-11-14 paper/paper.tex
minor changes

@@
 concentrations varies with halo resolution, outperforming the other
-two methods. For halos
-sampled with $20$ particles our method recovers the input
+two methods. 
+For halos sampled with $20$ particles our method recovers the input
 concentration with $10\%$ accuracy, while for the maximum radial
-velocity method it is on the order of $20\%$ 
-and density profile methods fail at the $100\%$ level.
+velocity method it is on the order of $20\%$ and density profile
+methods fail at the $100\%$ level. 
 For halos with $2\times 10^4$ particles our method achieves a recovery
@@
 We also measure the mass-concentration relationship on N-body
-data. We find that within the probed mass range ($10^{12}\hMsun <
+data. 
+We find that in the probed mass range ($10^{12}\hMsun <
 10^{14}\hMsun$) the three methods give consistent results within the
@@
 compared to the velocity and density methods. 
-From these results we believe that the new method is promising tool
+From these results we believe that the new method is a promising tool
 to probe the internal structure of dark matter halos.

### 2015-12-16 paper/paper.tex
improved plot description in body paper

@@
   methods used on the same cosmological N-body data. 
-  The lines correspond to the median concentration values in each bin.
+  All halos are used regardless of their relaxation state.
+  The lines correspond to the median concentration values in each mass bin.
+  The shaded region presents 10 and 90 per cent spread.
+  For clarity we only show the spread for the concentrations estimated
+  using our method. The other two methods have a similar spread. The
+  dotted line corresponds to fits reported by \citep{Prada2012}.
   \label{fig:concentration}}

### 2015-12-17 paper/paper.tex
report power law fit
fit description
minor edits in the paper

@@
 We present a new algorithm to estimate the concentration of N-body
-dark matter halos.
-The method uses the integrated mass profile to find the optimal
-concentration value. 
-Its main advantage is that it uses the full particle information
-without any binning, making it realiable in  cases when low numerical
-resolution becomes a limitation for other methods.  
+dark matter halos using the integrated mass profile.
+The method uses the full particle information without any binning,
+making it realiable in  cases when low numerical resolution becomes a
+limitation for other methods.   
 Additionally, the algorithm is straightforward to implement.  
@@
 fit the density profile. 
-Tests on the mock halos show that the accuracy of our method to recover input
-concentrations varies with halo resolution, outperforming the other
-two methods. 
+Tests on the mock halos show that the accuracy of our method to
+recover known input concentrations varies with halo resolution,
+outperforming the other two methods. 
 For halos sampled with $20$ particles our method recovers the input
@@
 statistical uncertainties.   
-We only find a small discrepancy at low masses, $M<10^{13}\hMsun$, where
+We only find a small deviation at low masses, $M<10^{13}\hMsun$, where
 our method yields lower median concentration values by $15\%-20\%$
@@
 For instance, the sizes and dynamics of galaxies are determined by
-the DM distribution inside a halo.
-This dependence has motivated the detailed study of DM halo
-properties such as its formation history and internal structure.
+the DM distribution inside a halo. This motivates the detailed study
+a DM halo internal structure.
 
-The internal DM distribution is parameterized through the density
+The internal DM distribution in a halo can be parameterized through the density
 profile.  
@@
 its density only dependens on the radial coordinate. 
-One the most popular parameterizations for DM halo radial
-density distribution is the Navarro-Frenk-White (NFW) profile
+One the most popular radial parameterizations is  is the
+Navarro-Frenk-White (NFW) profile 
 \citep{NFW}.   
@@
 dark matter halo (where galaxy formation takes place, and where the
-effects of baryon physics on dark matter distribution is still an
+effects of baryon physics on dark matter distribution are still 
 unknown) one can also assume that this profile is universal.
@@
 break happens at the so-called scale radius, $r_s$.  
-The ratio between the scale radius and the virial radius $R_v$ is
+The ratio between the scale radius and the halo virial radius $R_v$ is
 known as the concentration $c=R_v/r_s$.
@@
 redshift and cosmological parameters.
-In these studies 
+In many numerical studies 
 \citep{Neto2007,Maccio2008,Duffy2008,Munoz2011,Prada2012,Ludlow2014} 
@@
 that relates the maximum of the ratio of the circular velocity to the
-virial velocity.  The concentration can be then found as the root of a
-algebraic equation dependent on this maximum value.
+virial velocity, $V_{\rm circ}$/$V_{\rm vir}$.  The concentration can
+be then found as the root of an algebraic equation dependent on this
+maximum value.
 
@@
 points. 
-This results in a robust estimate even at low resolution/particle
+This translates into a robust estimate even at low resolution/particle
 numbers.   
 Furthermore, since the method does not require any binning, there is
-no need to tune numerical parameters, providing a new independent
-method to estimate the concentration parameter. 
-Here we provide a detailed description of this method and a
-comparison against the two traditional methods by measuring its
+no need to tune numerical parameters.
+This provides a new independent method to estimate the concentration
+parameter.   
+Here we provide a detailed description of the method and a
+comparison against the two traditional techniques by measuring its
 performance both on mock and N-body halos.
@@
 V_{c}(<r)/V_{c}(<r_v)$, using the result in Eq. \ref{eq:profile}
-to have:
+we have:
 
@@
 Using this sample we want to quantify the ability to recover the
-expected concentration as a function of particle numbe.
+expected concentration as a function of particle number.
 The second sample comes from a publicly available N-body cosmological
@@
 The dependence of $\avg{|D|}$ with the particle number $N$
-goesapproximately as $\avg{|D|}\propto N^{-1/2}$.   
-This hints that the accuracy of the method could be due to a decrease
-of Poisson noise.
+goes approximately as $\avg{|D|}\propto N^{-1/2}$.   
+This hints that the increasing accuracy of the method could be due to
+a decrease of Poisson noise.
 
 The method based on the maximum of the circular velocity shows a
-similar behaviour $\avg{|D|}\propto N^{-1/2}$.  
+similar behaviour with $\avg{|D|}\propto N^{-1/3}$.  
 Its accuracy is $2-5$ times lower than in our method, on the order of
@@
 This behaviour is evident in the large values of $\avg{|D|}$ for halos
-with number of particles below ~200 and an intermediate accuracy
+with number of particles below $\sim 200$ and an intermediate accuracy
 between the other two methods for a high particle number.
@@
 out of the equilibrium. 
-Halos may have also plenty of substructure, etc. All these effects
+Halos may have also plenty of substructure. All these effects
 disturb the mass density profile, taking it  away from the ideal NFW
 profile. 
-In order to see the completeley explore performance of our method, we use
-it to estimate the  concentration parameter in dark matter halos
+In order to explore the performance of our method in this setting, we
+use it to estimate the  concentration parameter in dark matter halos
 obtained from a cosmological N-body simulation and compare with the
@@
 We use a halo sample containing all the halos located in a cubic
-sub-volume of $100$ \hMpc on a side centered on the most massive halo
-in the simulation at $z=0$  which corresponds to the \texttt{miniMDR1}
+sub-volume of $100$ \hMpc\ on a side centered on the most massive halo
+in the simulation at $z=0$.
+This dataset corresponds to the \texttt{miniMDR1}
 table in the  database.  
@@
 mass-concentration relationship.
+
+We find that the median concentraion can be fit by the following
+relationship
+\begin{equation}
+c_{200} = 5.62 \left(\frac{M_{200}}{10^{12}\hMsun}\right)^{-0.061}, 
+\end{equation}
+%
+which has a similar power value compared to the $-0.075$ reported by
+\citep{Prada2012}, while the normalization is $\sim 20\%$ lower
+compared to the $7.28$ value reported by the same authors.
 

### 2015-12-17 paper/paper.tex
nueva version revisada del texto

@@
   methods. Our method provide the most accurate estimate at fixed
-  particle number $N$.  {\it Con respecto a esta figura tengo una
-    pregunta. Yo ajusté los perfiles con menos de 200 partulas? no
-    recuerdo!}
+  particle number $N$.  
     \label{fig:error}}
@@
     method and the maximum velocity (left) and density (middle)
-    methods. The line indicates the equal value between the two
-    techniques. The right panel compares the results of the maximum
-    velocity and density methods.
-  \label{fig:mdv}}
+    methods. The solid line indicates the equal value between the two
+    techniques. The dashed line shows the upper 15 per cent difference
+    between two methods.
+  \label{fig:comparison}}
 \end{figure*}
@@
 
-Figure \ref{fig:concentration} shows the results of the
+Figure \ref{fig:comparison} shows the comparison between the
+concentration values obtained by the three different methods. 
+The diagonal line marks a one-to-one correspondence if all the values
+were equal.
+The three methods show a broad general agreement. 
+The largest difference is present at high concentration $c>5$ where
+our method produces systematic lower values than the other two
+methods. Most of the differences are at the $20\%$ level, with some
+extreme cases for the highest concentration values with $50\%$
+differences.  The velocity and density methods produce consistent
+values within a $20\%$ scatter, only some halos with very high
+concentrations $c\sim 10$ have a $15\%$ lower concentration with the
+velocity method.
+
+We explored halo shape and relaxation as a source of this
+differences. We found shape does not bias the concentration
+estimation; relaxation, quantified by the
+offset between the center of mass and minimum of the potential, can
+only explain at most $5\%$ of the offset between methods.  We note
+that the highest concentration values correspond to the smallest halos
+with $\sim 200$ particles, a regime where both the density and
+velocity methods are reliable only the $5\%$ in a perfect spherical
+halo.  From this we suggest that asserting with confidence the
+systematic difference between the different methods should be
+confirmed  a higher resolution simulation and larger statistics. We
+leave this comparison for future work.
+
+Figure \ref{fig:concentration} summarizes the previous results in the
 mass-concentration relationship.
@@
 
-%{\em Aqui hay algo importante que hay que entender antes de discutir
-%  esta gráfica , y es la razón por la cual el metodo del perfil de
-%  masa da valores de concentración tan bajos a baja masa y comparables
-%  a los de los otros dos métodos a alta masa. Es importante entender
-%  la razón de esto!.  Se me ocurren unas preguntas para tratar de
-%  entender. \\ 1) La grafica de c-M \ref{fig:concentration} usa todos
-%  los halos o solo los halos relajados? La inclusión de halos no
-%  relajados introduce in bias en la mediana en Cvir, así que vale la
-%  pena inclusive agregar una linea mas a la gráfica con los halos
-%  relajados y sin ellos. Para los otros dos métodos ya se sabe que
-%  hace la población de halos no relajados en la medida así que no creo
-%  necesario agregarlas para esos métodos. \\ Hay que explicar un poco
-%  mas la gráfica en el sentido de que se grafica y como se
-%  calculó. mean concentration?, Median concentrations? o mean in
-%  logscale?  Mas bins de cuanto? Mínimo cuantos halos por mass bin?,
-%  Halos relajados en todos los casos, o indistintos?}
-
 \section{Conclusions}
@@
 number of particles and input concentration on the retrieved values.  
-We compared these
-results against two other methods commonly used in the literature to
-estimate concentrations.  Finally, we applied our method to halos
-extracted from a cosmological N-body simulation to estimate the impact
-of our method on the mass concentration relationship.
+We compared these results against two other methods commonly used in
+the literature to estimate concentrations.  Finally, we applied our
+method to halos extracted from a cosmological N-body simulation to
+estimate the impact of our method on the mass concentration relationship.
 
@@
 method systematically shows smaller errors in the retrieved values
-compared to the other two methods, going from $10\%$ for halos with
-$20$ particles down to $0.01\%$ for halos with $2\times 10^4$
-particles.  In our method the average error on the retrieved values
-decreases with the number of particles as $\langle|D|\rangle\propto
-N^{-1}$.  The error in density method initially behaves as
-$\langle|D|\rangle\propto N^{-3/2}$ but at $N=2\times 10^3$ it
-saturates to $0.1\%$.  For the velocity method the error behaves
-closely to $\langle|D|\rangle\propto N^{-1/2}$.  We also gauged the
-effect of different concentration parameters at fixed particle
-numbers.  We found larger offsets for larger input concentrations.
-The offset goes in the sense that the measured concentration tends to
-be underestimated.  Nevertheless, the dominant effect on the
-measurement is the particle number.
+compared to the other two methods.
 
@@
 method on the mass-concentration relationship.  Although the three
-methods are in general agreement there are noticeable differences in
-the mass concentration relationship.
+methods are in general agreement there are some noticeable differences
+in the mass concentration relationship.
 

### 2015-12-23 paper/paper.tex
nuevo texto en el paper
Update paper.tex
Un par de cambio menores en el texto (lineas 180 y 225)

@@
   J. E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{1}$
-  J. C. Mu\~noz-Cuartas \thanks{xxxx@udea.edu.co}$^{2}$
+  J. C. Mu\~noz-Cuartas \thanks{juan.munozc@udea.edu.co}$^{2}$
 }
@@
 its density only dependens on the radial coordinate. 
-One the most popular radial parameterizations is  is the
+One the most popular radial parameterizations is the
 Navarro-Frenk-White (NFW) profile 
@@
 The second problem is that there is not a way to estimate the optimal
-radial bin size, different choices produce different results for the
+radial bin size, different choices may produce different results for the
 concentration.
@@
 velocity methods are reliable only the $5\%$ in a perfect spherical
-halo.  From this we suggest that asserting with confidence the
-systematic difference between the different methods should be
-confirmed  a higher resolution simulation and larger statistics. We
-leave this comparison for future work.
+halo.  
+This difference might actually signal a deviation from the NFW profile
+due to the low resolution in the simulation. From this we suggest that
+asserting with confidence the systematic difference between the
+different methods should be confirmed  a higher resolution simulation
+and larger statistics. We leave this comparison for future work.
 

### 2015-12-24 paper/paper.tex
massive refactor
Update paper.tex
agradecimientos
updated conclusions

@@
   halo concentration using the integrated mass profile} 
-\author[C. Poveda, J.E. Forero-Romero, J.C. Mu\~noz-Cuartas]{
+\author[C.N. Poveda-Ruiz, J.E. Forero-Romero, J.C. Mu\~noz-Cuartas]{
 \parbox[t]{\textwidth}{\raggedright 
-  C. Poveda \thanks{cn.poveda542@uniandes.edu.co}$^{1}$
+  C. N. Poveda-Ruiz \thanks{cn.poveda542@uniandes.edu.co}$^{1}$
   J. E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{1}$
@@
 We compare these results against two other methods:
-maximum radial velocity measurements and radial particle binning to
-fit the density profile. 
+maximum radial velocity measurements and radial particle binning.
 Tests on the mock halos show that the accuracy of our method to
@@
 concentration with $10\%$ accuracy, while for the maximum radial
-velocity method it is on the order of $20\%$ and density profile
-methods fail at the $100\%$ level. 
+velocity method it is on the order of $20\%$ while density profile
+methods just fail at such low resolution limits.
 For halos with $2\times 10^4$ particles our method achieves a recovery
@@
 We only find a small deviation at low masses, $M<10^{13}\hMsun$, where
-our method yields lower median concentration values by $15\%-20\%$
+our method yields lower median concentration values by $20\%-30\%$
 compared to the velocity and density methods. 
@@
 \begin{keywords}
-Cosmology: theory - large-scale structure of Universe -
-Methods: data analysis - numerical - N-body simulations
+Cosmology: theory, large-scale structure of Universe --
+Methods: data analysis, numerical 
 \end{keywords}
@@
 where $x_{\rm max}=2.163$ \citep{Klypin2014} and the function $f(x)$
-correspondes to the definition in Eq. (\ref{eq:f_NFW}).
+corresponds to the definition in Eq. (\ref{eq:f_NFW}).
 
@@
 mass-concentration relationship. 
-
-We find that the median concentraion can be fit by the following
-relationship
-\begin{equation}
-c_{200} = 5.62 \left(\frac{M_{200}}{10^{12}\hMsun}\right)^{-0.061}, 
+We find that the median concentraion
+can be fit by the following relationship
+\begin{equation} c_{200} = 5.62 \left(\frac{M_{200}}{10^{12}\hMsun}\right)^{-0.061}, 
 \end{equation}
@@
 of dark matter halos in N-body simulations.  
-We tested our method on mock halo data to study the impact of total
+We tested the method on mock halo data to study the impact of total
 number of particles and input concentration on the retrieved values.  
 We compared these results against two other methods commonly used in
-the literature to estimate concentrations.  Finally, we applied our
-method to halos extracted from a cosmological N-body simulation to
-estimate the impact of our method on the mass concentration relationship.
+the literature to estimate concentrations.  
+For all methods, the accuracy in retrieving the input concentration
+increases with the number of particles as summarized in Figure
+\ref{fig:error}.  Our method systematically overperforms the other two.
 
-The first benchmark was performed on mock halos generated with known
-concentration values for different particle numbers.  For all methods,
-the accuracy in retrieveing the input concentration increases with the
-number of particles as summarized in Figure \ref{fig:error}.  Our
-method systematically shows smaller errors in the retrieved values
-compared to the other two methods.
+We also applied the method to halos extracted from a cosmological
+N-body simulation to estimate the impact on the mass concentration
+relationship. Although the three  methods are in broad agreement there
+are some noticeable differences in the mass concentration relationship
+at lower masses $<10^{13}\hMsun$ at the $20-30\% level$.
 
-We used a N-body cosmological simulation to test the impact of our
-method on the mass-concentration relationship.  Although the three
-methods are in general agreement there are some noticeable differences
-in the mass concentration relationship.
+These are encouraging results. They show that using the integrated
+mass profile to find the DM halo concentration is a tool deserving
+deeper scrutiny. Further tests with larger simulated volumes, varying
+numerical resolution and different density profiles are
+the next natural step to explore the full potential of this
+new method.
+
+\vspace{0.5cm}
+
+ The authors acknowldge the technical support from the new
+ high-performance computing facility at Uniandes. JEF-R acknowledges
+ financial support from Vicerrector\'ia de Investigaciones at Uniandes
+ through a FAPA project. JCMC acknowledges financial support from
+ ``Estrategia de  sostenibilidad 2014-2015, Universidad de
+ Antioquia''.
 

### 2015-12-24 paper/paper.tex
fixed typos

@@
 The method uses the full particle information without any binning,
-making it realiable in cases when low numerical resolution becomes a
+making it reliable in cases when low numerical resolution becomes a
 limitation for other methods.   
@@
 maximum radial velocity measurements and radial particle binning.
-Tests on the mock halos show that the accuracy of our method to
+Tests on the mock halos show that the accuracy of the new method to
 recover known input concentrations varies with halo resolution,
 outperforming the other two methods. 
-For halos sampled with $20$ particles our method recovers the input
+For halos sampled with $20$ particles the new method recovers the input
 concentration with $10\%$ accuracy, while for the maximum radial
@@
 methods just fail at such low resolution limits.
-For halos with $2\times 10^4$ particles our method achieves a recovery
+For halos with $2\times 10^4$ particles the new method achieves a recovery
 accuracy of $0.01\%$ while the velocity and density profile methods
@@
 We only find a small deviation at low masses, $M<10^{13}\hMsun$, where
-our method yields lower median concentration values by $20\%-30\%$
+the new method yields lower median concentration values by $20\%-30\%$
 compared to the velocity and density methods. 
@@
 In a first approximation this profile is spherically symmetric and
-its density only dependens on the radial coordinate. 
+its density only depends on the radial coordinate. 
 One the most popular radial parameterizations is the
@@
 However, it effectively takes into account only a single data point and
-discards the behaviour of the ratio $V_{\rm circ}/V_{\rm vir}$ below
+discards the behavior of the ratio $V_{\rm circ}/V_{\rm vir}$ below
 and above its maxima.  
@@
 
-Our method uses the integrated mass profile defined in
+The new method uses the integrated mass profile defined in
 Eq. (\ref{eq:profile}).
@@
 \end{center}
+\vspace{-0.5cm}
 \caption{Average value of the relative error in the concentration
@@
   the set of mock halos. Different symbols represent different
-  methods. Our method provide the most accurate estimate at fixed
-  particle number $N$.  
+  methods. The new method provides the most accurate estimate at fixed
+  particle number.  
     \label{fig:error}}
@@
   \end{center}
-  \caption{Comparison between the concentrations measured by our
+\vspace{-0.5cm}
+  \caption{Comparison between the concentrations measured by the new 
     method and the maximum velocity (left) and density (middle)
@@
 $\left|{\cal{H}}\right|$ is the number of haloes in ${\cal{H}}$. 
-A large discrepacy between the estimated and input concentrations are
+A large discrepancy between the estimated and input concentrations are
 quantified by a large $\avg{|D|}$.
@@
 \end{center}
+\vspace{-0.5cm}
 \caption{Mass-concentration relationship for the three different
@@
   For clarity we only show the spread for the concentrations estimated
-  using our method. The other two methods have a similar spread. The
+  using the new method. The other two methods have a similar spread. The
   dotted line corresponds to fits reported by \citep{Prada2012}.
@@
 
-At fixed particle numbers our method always shows the lowest
+At fixed particle numbers the new method always shows the lowest
 $\avg{|D|}$ values compared to the other two.
@@
 similar behaviour with $\avg{|D|}\propto N^{-1/3}$.  
-Its accuracy is $2-5$ times lower than in our method, on the order of
+Its accuracy is $2-5$ times lower than in the new method, on the order of
 $20\%$ for $20$ particle halos and $0.5\%$ for $20000$ particle
@@
 The results presented in the previous section show that in an
-idealized setup (pure NFW desity profiles, perfect spherical halos in
-total isolation) our method performs better than the other two
+idealized setup (pure NFW density profiles, perfect spherical halos in
+total isolation) the new method performs better than the other two
 methods commonly used in the literature.
@@
 out of the equilibrium. 
-Halos may have also plenty of substructure. All these effects
-disturb the mass density profile, taking it  away from the ideal NFW
-profile. 
-In order to explore the performance of our method in this setting, we
+Halos may have also plenty of substructure. 
+All these effects disturb the mass density profile, taking it  away
+from the ideal NFW profile. 
+In order to explore the performance of the new method in this setting, we
 use it to estimate the  concentration parameter in dark matter halos
-obtained from a cosmological N-body simulation and compare with the
+obtained from a cosmological N-body simulation and compare it with the
 other two classical methods.
@@
 can be found in \citep{2013AN....334..691R}.
-
-%%%%%%%
 
@@
 redefine to be our halo.  
-This choice makes that our overdensities are fully included inside the
+This choice makes that the overdensities are fully included inside the
 original FoF particle group.   
@@
 The largest difference is present at high concentration $c>5$ where
-our method produces systematic lower values than the other two
+the new method produces systematic lower values than the other two
 methods. Most of the differences are at the $20\%$ level, with some
@@
 We explored halo shape and relaxation as a source of this
-differences. We found shape does not bias the concentration
+differences. We found that shape does not bias the concentration
 estimation; relaxation, quantified by the
 offset between the center of mass and minimum of the potential, can
-only explain at most $5\%$ of the offset between methods.  We note
-that the highest concentration values correspond to the smallest halos
+only offset at most $5\%$ the median results between methods.  
+We note that the highest concentration values correspond to the smallest halos
 with $\sim 200$ particles, a regime where both the density and
@@
 halo.
-This difference might actually signal a deviation from the NFW profile
-due to the low resolution in the simulation. From this we suggest that
-asserting with confidence the systematic difference between the
-different methods should be confirmed  a higher resolution simulation
-and larger statistics. We leave this comparison for future work.
+
+The differences we find might signal a deviation from the NFW profile
+due to the low resolution of these halos. We suggest that asserting
+with confidence the systematic difference between the different
+methods should be confirmed  a higher resolution simulation and larger
+statistics. We leave this comparison for future work.
 
@@
 mass-concentration relationship. 
-We find that the median concentraion
+We find that the median concentration
 can be fit by the following relationship
@@
 increases with the number of particles as summarized in Figure
-\ref{fig:error}.  Our method systematically overperforms the other two.
+\ref{fig:error}.  The new method systematically outperforms the other two.
 
@@
 are some noticeable differences in the mass concentration relationship
-at lower masses $<10^{13}\hMsun$ at the $20-30\% level$.
+at lower masses, $<10^{13}\hMsun$, at the $20-30\%$ level.
 
@@
 
- The authors acknowldge the technical support from the new
+ The authors acknowledge the technical support from the new
  high-performance computing facility at Uniandes. JEF-R acknowledges

### 2015-12-24 paper/paper.tex
references inside main file

@@
 \bibliographystyle{mn2e}
-\bibliography{references}
+%\bibliography{references}
+\begin{thebibliography}{}
+
+\bibitem[\protect\citeauthoryear{{Duffy}, {Schaye}, {Kay} \& {Dalla
+  Vecchia}}{{Duffy} et~al.}{2008}]{Duffy2008}
+{Duffy} A.~R.,  {Schaye} J.,  {Kay} S.~T.,    {Dalla Vecchia} C.,  2008,
+  \mnras, 390, L64
+
+\bibitem[\protect\citeauthoryear{{Foreman-Mackey}, {Hogg}, {Lang} \&
+  {Goodman}}{{Foreman-Mackey} et~al.}{2013}]{emcee}
+{Foreman-Mackey} D.,  {Hogg} D.~W.,  {Lang} D.,    {Goodman} J.,  2013, \pasp,
+  125, 306
+
+\bibitem[\protect\citeauthoryear{{Klypin}, {Yepes}, {Gottlober}, {Prada} \&
+  {Hess}}{{Klypin} et~al.}{2014}]{Klypin2014}
+{Klypin} A.,  {Yepes} G.,  {Gottlober} S.,  {Prada} F.,    {Hess} S.,  2014,
+  ArXiv e-prints
+
+\bibitem[\protect\citeauthoryear{{Ludlow}, {Navarro}, {Angulo},
+  {Boylan-Kolchin}, {Springel}, {Frenk} \& {White}}{{Ludlow}
+  et~al.}{2014}]{Ludlow2014}
+{Ludlow} A.~D.,  {Navarro} J.~F.,  {Angulo} R.~E.,  {Boylan-Kolchin} M.,
+  {Springel} V.,  {Frenk} C.,    {White} S.~D.~M.,  2014, \mnras, 441, 378
+
+\bibitem[\protect\citeauthoryear{{Macci{\`o}}, {Dutton} \& {van den
+  Bosch}}{{Macci{\`o}} et~al.}{2008}]{Maccio2008}
+{Macci{\`o}} A.~V.,  {Dutton} A.~A.,    {van den Bosch} F.~C.,  2008, \mnras,
+  391, 1940
+
+\bibitem[\protect\citeauthoryear{{More}, {Kravtsov}, {Dalal} \&
+  {Gottl{\"o}ber}}{{More} et~al.}{2011}]{More2011}
+{More} S.,  {Kravtsov} A.~V.,  {Dalal} N.,    {Gottl{\"o}ber} S.,  2011, \apjs,
+  195, 4
+
+\bibitem[\protect\citeauthoryear{{Mu{\~n}oz-Cuartas}, {Macci{\`o}},
+  {Gottl{\"o}ber} \& {Dutton}}{{Mu{\~n}oz-Cuartas} et~al.}{2011}]{Munoz2011}
+{Mu{\~n}oz-Cuartas} J.~C.,  {Macci{\`o}} A.~V.,  {Gottl{\"o}ber} S.,
+  {Dutton} A.~A.,  2011, \mnras, 411, 584
+
+\bibitem[\protect\citeauthoryear{{Navarro}, {Frenk} \& {White}}{{Navarro}
+  et~al.}{1997}]{NFW}
+{Navarro} J.~F.,  {Frenk} C.~S.,    {White} S.~D.~M.,  1997, \apj, 490, 493
+
+\bibitem[\protect\citeauthoryear{{Navarro}, {Ludlow}, {Springel}, {Wang},
+  {Vogelsberger}, {White}, {Jenkins}, {Frenk} \& {Helmi}}{{Navarro}
+  et~al.}{2010}]{Navarro2010}
+{Navarro} J.~F.,  {Ludlow} A.,  {Springel} V.,  {Wang} J.,  {Vogelsberger} M.,
+  {White} S.~D.~M.,  {Jenkins} A.,  {Frenk} C.~S.,    {Helmi} A.,  2010,
+  \mnras, 402, 21
+
+\bibitem[\protect\citeauthoryear{{Neto}, {Gao}, {Bett}, {Cole}, {Navarro},
+  {Frenk}, {White}, {Springel} \& {Jenkins}}{{Neto} et~al.}{2007}]{Neto2007}
+{Neto} A.~F.,  {Gao} L.,  {Bett} P.,  {Cole} S.,  {Navarro} J.~F.,  {Frenk}
+  C.~S.,  {White} S.~D.~M.,  {Springel} V.,    {Jenkins} A.,  2007, \mnras,
+  381, 1450
+
+\bibitem[\protect\citeauthoryear{{Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo}
+  \& {Primack}}{{Prada} et~al.}{2012}]{Prada2012}
+{Prada} F.,  {Klypin} A.~A.,  {Cuesta} A.~J.,  {Betancort-Rijo} J.~E.,
+  {Primack} J.,  2012, \mnras, 423, 3018
+
+\bibitem[\protect\citeauthoryear{{Riebe}, {Partl}, {Enke}, {Forero-Romero},
+  {Gottl{\"o}ber}, {Klypin}, {Lemson}, {Prada}, {Primack}, {Steinmetz} \&
+  {Turchaninov}}{{Riebe} et~al.}{2013}]{2013AN....334..691R}
+{Riebe} K.,  {Partl} A.~M.,  {Enke} H.,  {Forero-Romero} J.,  {Gottl{\"o}ber}
+  S.,  {Klypin} A.,  {Lemson} G.,  {Prada} F.,  {Primack} J.~R.,  {Steinmetz}
+  M.,    {Turchaninov} V.,  2013, Astronomische Nachrichten, 334, 691
+
+\end{thebibliography}
 

### 2015-12-24 paper/paper.tex
shorter abstract, updated running title

@@
 %=========================================================================
-\title[Halo concentration from the mass profile]{Estimating dark matter
-  halo concentration using the integrated mass profile} 
+\title[Halo concentration via the integrated mass profile]{Estimating dark matter  halo concentration using the integrated mass profile} 
 \author[C.N. Poveda-Ruiz, J.E. Forero-Romero, J.C. Mu\~noz-Cuartas]{
@@
 limitation for other methods.   
-Additionally, the algorithm is straightforward to implement.  
 We test the performance of this method by estimating halo
@@
 outperforming the other two methods. 
-For halos sampled with $20$ particles the new method recovers the input
-concentration with $10\%$ accuracy, while for the maximum radial
-velocity method it is on the order of $20\%$ while density profile
-methods just fail at such low resolution limits.
-For halos with $2\times 10^4$ particles the new method achieves a recovery
-accuracy of $0.01\%$ while the velocity and density profile methods
-achieve $0.1\%$ and $1\%$, respectively. 
 We also measure the mass-concentration relationship on N-body

### 2016-04-17 paper/paper.tex
new concentration plot
paper updated with new plots
updated plots and text

@@
 are coupled to the evolution of their dark matter (DM) hosting halo.
-For instance, the sizes and dynamics of galaxies are determined by
-the DM distribution inside a halo. This motivates the detailed study
-a DM halo internal structure.
+In this paradigm the sizes and dynamics of galaxies are driven by
+the DM distribution inside a halo. This has motivated the detailed study
+a DM halo internal structure in the last three decades.
 
-The internal DM distribution in a halo can be parameterized through the density
-profile.  
-In a first approximation this profile is spherically symmetric and
-its density only depends on the radial coordinate. 
+The internal DM distribution in a halo is usually parameterized
+through the density profile.  
+In a first approximation this profile is spherically symmetric; the
+density only depends on the radial coordinate.  
 One the most popular radial parameterizations is the
@@
 
-The concentration of the NFW profile provides the conceptual
+The concentration of the NFW profile provides a conceptual
 framework to study simulated dark matter halos as a function of
@@
 
-There are two main algorithms to estimate the concentration parameter
+There are two stablished algorithms to estimate the concentration parameter
 of a N-body dark matter halo. 
@@
 no need to tune numerical parameters.
-This provides a new independent method to estimate the concentration
-parameter.   
+This method provides a new independent method to estimate the
+concentration parameter.   
 Here we provide a detailed description of the method and a
@@
 profile.    
-Using this sample we want to quantify the ability to recover the
-expected concentration as a function of particle number.
+Using this sample we quantify the ability to recover the expected
+concentration as a function of particle number. 
 The second sample comes from a publicly available N-body cosmological
-simulation.  
-In this way we test the new method on more realistic and complex
-data. 
-We summarize the results on this dataset by showing the impact on the
-mass-concentration relationship.
+simulation to test the new method on more realistic and complex data
+to show the impact on the mass-concentration relationship.
 
-\subsection{Mock halo sample}
+\subsection{Retrieving known concentrations from a mock halo sample}
 
@@
 
-\label{sec:data}
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=0.32\textwidth]{conc_mass_vel.pdf}
-    \includegraphics[width=0.32\textwidth]{conc_mass_dens.pdf}
-    \includegraphics[width=0.32\textwidth]{conc_dens_vel.pdf}
-  \end{center}
-\vspace{-0.5cm}
-  \caption{Comparison between the concentrations measured by the new 
-    method and the maximum velocity (left) and density (middle)
-    methods. The solid line indicates the equal value between the two
-    techniques. The dashed line shows the upper 15 per cent difference
-    between two methods.
-  \label{fig:comparison}}
-\end{figure*}
+%\label{sec:data}
+%\begin{figure*}
+%  \begin{center}
+%    \includegraphics[width=0.32\textwidth]{conc_mass_vel.pdf}
+%    \includegraphics[width=0.32\textwidth]{conc_mass_dens.pdf}
+%    \includegraphics[width=0.32\textwidth]{conc_dens_vel.pdf}
+%  \end{center}
+%\vspace{-0.5cm}
+%  \caption{Comparison between the concentrations measured by the new 
+%    method and the maximum velocity (left) and density (middle)
+%    methods. The solid line indicates the equal value between the two
+%    techniques. The dashed line shows the upper 15 per cent difference
+%    between two methods.
+%  \label{fig:comparison}}
+%\end{figure*}
 
@@
 
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.50\textwidth]{concentration.pdf}
-\end{center}
-\vspace{-0.5cm}
-\caption{Mass-concentration relationship for the three different
-  methods used on the same cosmological N-body data. 
-  All halos are used regardless of their relaxation state.
-  The lines correspond to the median concentration values in each mass bin.
-  The shaded region presents 10 and 90 per cent spread.
-  For clarity we only show the spread for the concentrations estimated
-  using the new method. The other two methods have a similar spread. The
-  dotted line corresponds to fits reported by \citep{Prada2012}.
-  \label{fig:concentration}}
-\end{figure}
-
 Figure \ref{fig:error} shows the behaviour of $\avg{|D|}$ as a function of
@@
 The dependence of $\avg{|D|}$ with the particle number $N$
-goes approximately as $\avg{|D|}\propto N^{-1/2}$.   
-This hints that the increasing accuracy of the method could be due to
-a decrease of Poisson noise.
+goes approximately as $\avg{|D|}\propto N^{-1}$.
 
@@
 
-\subsection{Halos from a cosmological simulation}
+We also find that the bias from different concentrations at fixed
+particle number is negligeable with respect to the effects induced by
+different particle numbers.
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.47\textwidth]{avg_foff_bolshoi.pdf}
+\end{center}
+\vspace{-0.5cm}
+\caption{Average value of the relative error in the concentration
+  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
+  the set of mock halos. Different symbols represent different
+  methods. The new method provides the most accurate estimate at fixed
+  particle number.  
+    \label{fig:downsampling}}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.45\textwidth]{error_conc_bolshoi.pdf}
+\end{center}
+\vspace{-0.5cm}
+\caption{Average value of the relative error in the concentration
+  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
+  the set of mock halos. Different symbols represent different
+  methods. The new method provides the most accurate estimate at fixed
+  particle number.  
+    \label{fig:downsampling}}
+\end{figure}
+
+\subsection{Measuring the concentration in halos from a cosmological simulation}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.45\textwidth]{concentration_bolshoi.pdf}
+  \includegraphics[width=0.45\textwidth]{concentration_bolshoi_corrected.pdf}
+\end{center}
+\vspace{-0.5cm}
+\caption{Mass-concentration relationship for the three different
+  methods used on the same cosmological N-body data. 
+  All halos are used regardless of their relaxation state.
+  The lines correspond to the median concentration values in each mass bin.
+  The shaded region presents 10 and 90 per cent spread.
+  For clarity we only show the spread for the concentrations estimated
+  using the new method. The other two methods have a similar spread. The
+  dotted line corresponds to fits reported by \citep{Prada2012}.
+  \label{fig:concentration}}
+\end{figure*}
 
@@
 
-We use data from the MultiDark cosmological simulation that follows
+We use data from the Bolshoi cosmological simulation that follows
 the non-linear evolution of a dark matter density field sampled with
-$2048^3$ particles over a cubic box of $1000\ \hMpc$ on a side.  
+$2048^3$ particles over a cubic box of $250\ \hMpc$ on a side.  
 The data is publicly available at \url{http://www.cosmosim.org/}.
@@
 We use a halo sample containing all the halos located in a cubic
-sub-volume of $100$ \hMpc\ on a side centered on the most massive halo
-in the simulation at $z=0$.
-This dataset corresponds to the \texttt{miniMDR1}
-table in the  database.  
+sub-volume of $100$ \hMpc\ on a side.
 From this sample we select all the halos at $z=0$ detected
-with a Friends-of-Friends (FoF) algorithm with masses in the interval
-$10^{12}\leq M_{\rm FoF}/\hMsun \leq 10^{14}$.  
+with a Friends-of-Friends (FoF) algorithm with more than 300
+particles, meaning that the masses are in the interval
+$4\times 10^{10}\leq M_{\rm FoF}/\hMsun \leq 10^{14}$.  
 The FoF algorithm used a linking length of $0.17$ times the mean
@@
 $\Delta_h\sim  400-700$ dependent on the halo concentration \citep{More2011}.
-Finally, we select from the database all the particles that belong to
-each FoF group.
 
@@
 On the interest of providing a fair comparison against the density method we
-only report results from overdensities with at least $200$ particles.
+only report results from overdensities with at least $200$ particles
+($2.6\times 10^{10}$\hMsun).
 
-Figure \ref{fig:comparison} shows the comparison between the
-concentration values obtained by the three different methods. 
-The diagonal line marks a one-to-one correspondence if all the values
-were equal.
-The three methods show a broad general agreement. 
-The largest difference is present at high concentration $c>5$ where
-the new method produces systematic lower values than the other two
-methods. Most of the differences are at the $20\%$ level, with some
-extreme cases for the highest concentration values with $50\%$
-differences.  The velocity and density methods produce consistent
-values within a $20\%$ scatter, only some halos with very high
-concentrations $c\sim 10$ have a $15\%$ lower concentration with the
-velocity method.
+\subsubsection{Convergence Test using Downsampling}
 
-We explored halo shape and relaxation as a source of this
-differences. We found that shape does not bias the concentration
-estimation; relaxation, quantified by the
-offset between the center of mass and minimum of the potential, can
-only offset at most $5\%$ the median results between methods.  
-We note that the highest concentration values correspond to the smallest halos
-with $\sim 200$ particles, a regime where both the density and
-velocity methods are reliable only the $5\%$ in a perfect spherical
-halo.
+We perform first a convergence test on the N-body data to find
+possible biases in the concentration estimates as a function of
+particle number. 
+We select $8$ halos from the simulation that have at least $3\times
+10^5$ particles. 
+We then downsample the total number of particles in each halo by
+factors of $10, 20, 45, 100, 215, 460, 1000$ to measure its
+concentration with both the integrated mass and the velocity method.
+each downsampling factor we repeat the operation $100$ times.
 
-The differences we find might signal a deviation from the NFW profile
-due to the low resolution of these halos. We suggest that asserting
-with confidence the systematic difference between the different
-methods should be confirmed  a higher resolution simulation and larger
-statistics. We leave this comparison for future work.
+The average concentration value for the largest number of particles, $c_{N_{max}}$,
+provides with a baseline to compare all the other results.
+We use the following statistic
+\begin{equation}
+f_{\rm off} = c_{N} / c_{N_{max}} - 1,
+\end{equation}
+to account for the offset between the concentration at a given
+downsampled particle number $c_{N}$ and the baseline $c_{N_{max}}$.
+
+Figure \ref{fig:downsampling} summarizes our results. 
+The plot shows the average value of $f_{\rm off}$ as a function
+of the particle number.
+As expected for large enough sample particle numbers, $N_{s}>5\times
+10^3$, the results of the two algorithms coincide and $\langle f_{\rm
+  off}\rangle\sim 0$.  
+For lower number of particles, the results of the two algorithms
+deviate from the expected concentration value.  
+The velocity method overestimates by a factor $\langle f_{\rm 
+  off}\rangle\sim 0.25$ the concentration values for the lowest
+sample particle numbers, $N_{s}\sim 100$. 
+Around the same sampling scale, the new algorithm shows a more stable
+behaviour with an understimate by a factor of $\langle f_{\rm 
+  off}\rangle \sim 0.02$.  
+This shows that in the more complex setup of a cosmological setup our
+algorithm continues to be stable below the $5\%$ level for low 
+particle numbers.
+
+The line on the same panel shows a fit to the data with the following
+functional form 
+\begin{equation}
+f_{\rm off} = \frac{A}{(1+\log_{10}N_s)^{B}}.
+\end{equation} 
+for the dataset shown in the panel we have $A=3385\pm 2065$, $B=7.99\pm0.48
+$ for the velocity method and $A=-110\pm 253$, $B=7.11\pm1.80$ for the
+new method, where the uncertainties are estimated from the covariance 
+matrix resulting from the non-linear optimization procedure. The lines
+on Figure \ref{fig:downsampling} are plotted using these best values.
+
+Figure \ref{fig:downsampling} summarizes different uncertainty
+results. 
+Large symbols show the standard deviation on $f_{\rm off}$
+from the downsampling experiment.
+Small dots show the uncertainty on each individual concentration value
+as estimated by the MCMC algorithm.
+The line shows the $\propto N^{-1}$  locus.
+The first thing to notice is that statistical uncertainties are at
+least one order of magnitude than the uncertainty associated to
+downsampling experiment.
+
+\subsubsection{Mass-Concentration Relationship}
 
@@
 can be fit by the following relationship
-\begin{equation} c_{200} = 5.62 \left(\frac{M_{200}}{10^{12}\hMsun}\right)^{-0.061}, 
-\end{equation}
+%\begin{equation} c_{200} = 5.62 \left(\frac{M_{200}}{10^{12}\hMsun}\right)^{-0.061}, 
+%\end{equation}
 %

### 2016-04-17 paper/paper.tex
lots of new text in the paper

@@
 outperforming the other two methods. 
+Convergence tests by downsampling halos with high number of particles in
+the N-body simulation show that the new method is robust with respect
+to changes in halo particle number.
+However the velocity method overpredicts concentration values by a
+factor of $25\%$ values for low particle numbers.
 We also measure the mass-concentration relationship on N-body
 data. 
-We find that in the probed mass range ($10^{12}\hMsun <
+We find that in the probed mass range ($10^{10}\hMsun < M_{h} <
 10^{14}\hMsun$) the three methods give consistent results within the
 statistical uncertainties.   
-We only find a small deviation at low masses, $M<10^{13}\hMsun$, where
-the new method yields lower median concentration values by $20\%-30\%$
-compared to the velocity and density methods. 
+We find a small deviation at low masses, $M<10^{12}\hMsun$, where
+the new method yields lower median concentration values by $25\%$
+compared to the velocity methods. 
+We find that accounting for the bias
+in the velocity method brings the results into agreement.
 From these results we believe that the new method is a promising tool
@@
 
-In this letter we present a third alternative based on fitting the
+In this paper we present a third alternative based on fitting the
 integrated mass profile.
@@
 
-In this letter we use $\Delta_h=740$, a number roughly corresponding to
+In this paper we use $\Delta_h=740$, a number roughly corresponding to
 200 times the critical density at redshift z=0.
@@
   particle number.  
-    \label{fig:downsampling}}
+    \label{fig:downsampling_err}}
 \end{figure}
@@
   dotted line corresponds to fits reported by \citep{Prada2012}.
-  \label{fig:concentration}}
+  \label{fig:concentration}. The left panel shows the raw results
+  comming from each algorithm. The right panel introduces a
+  correction on the velocity and integrated mass results. 
+  The corrections dependens on the number of particles following the
+  results of the downsampling experiments presented in Figure
+  \ref{fig:downsampling}.} 
 \end{figure*}
@@
 f_{\rm off} = \frac{A}{(1+\log_{10}N_s)^{B}}.
+\label{eq:f_off}
 \end{equation} 
@@
 The line shows the $\propto N^{-1}$  locus.
-The first thing to notice is that statistical uncertainties are at
+This figure demonstrates that the statistical uncertainties are at
 least one order of magnitude than the uncertainty associated to
@@
 
-Figure \ref{fig:concentration} summarizes the previous results in the
-mass-concentration relationship. 
-We find that the median concentration
-can be fit by the following relationship
-%\begin{equation} c_{200} = 5.62 \left(\frac{M_{200}}{10^{12}\hMsun}\right)^{-0.061}, 
-%\end{equation}
-%
-which has a similar power value compared to the $-0.075$ reported by
-\citep{Prada2012}, while the normalization is $\sim 20\%$ lower
-compared to the $7.28$ value reported by the same authors.
+Figure \ref{fig:concentration} shows the  mass-concentration
+relationship for the density, velocity and integrated mass method.  
+The left panel shows the results as they are produced by each of the
+algorithms, the thin dashed line marks the results by \citep{Prada2012}.
+
+We notice first that the results from the density method have a
+systematic $15\%$offset from the velocity methods.
+This offset was already presented by \citep{Prada2012} for some
+concentrations and halo masses, although a more organized study in
+terms of the mass-concentration relationship has not been presented in
+the literature.
+
+We then notice that our methods follows closely the results of the
+velocity method at higher masses, $M_h>10^{12}\hMsun$ or equivalently
+for $>5\times10^3$ particles. 
+For masses below that threshold our method saturates at a
+concentration value of $\sim 7$ while the velocity method continues to
+give higher concentration values.
+
+We hypothesize that the increase in the results for the velocity
+method below $5\times 10^{4}$ particles come from the systematic
+bias described in the previous subsection.  
+To test the general consistency of this hypothesis wwe correct the
+concentration values in the velocity and integrated mass methods by
+a factor of $1/(1+f_{\rm off})$, using the definition in Equation
+(\ref{eq:f_off}) and the parameters obtained from the data presented
+in Figure (\ref{fig:downsampling}).   
+The correction brings into perfect agreement the results between the
+velocity and the integrated mass method. 
+This suggests that the concentration at lower masses might very well
+reach a plateu in the halo mass range $10^{10}< M_{h}/\hMsun < 10^{12}$ .
 
@@
 
-In this letter we presented a new method to estimate the concentration
+In this paper we presented a new method to estimate the concentration
 of dark matter halos in N-body simulations.  
@@
 We also applied the method to halos extracted from a cosmological
-N-body simulation to estimate the impact on the mass concentration
-relationship. Although the three  methods are in broad agreement there
-are some noticeable differences in the mass concentration relationship
-at lower masses, $<10^{13}\hMsun$, at the $20-30\%$ level.
+N-body simulation.
+Using this data we showed that the new method is robust with respect to a
+decreasing number of particles in the halos. 
+On the other hand we showed that the velocity method has a
+systematic bias that overesimates the concentration for halos with a
+low particle number up to a factor of $25\%$.
 
-These are encouraging results. They show that using the integrated
-mass profile to find the DM halo concentration is a tool deserving
-deeper scrutiny. Further tests with larger simulated volumes, varying
-numerical resolution and different density profiles are
-the next natural step to explore the full potential of this
-new method.
+We also used the N-body simulation to estimate the impact on the mass
+concentration relationship. 
+Although the three methods are in broad agreement within their
+uncertainties there are some noticeable differences.
+The first difference is that the density method produces
+systematically higher concentrations by a factor of $15\%$ compared to
+the velocity mehod.
+The second difference is that the velocity and integrated mass methods
+start to differ for masses below $10^{12}\hMsun$. 
+We found that a correction of the results by the bias factor found
+using the same N-body data can bring these two methods into
+agreement.
 
-\vspace{0.5cm}
+These are encouraging results. 
+They show that using the integrated mass profile to find the DM halo
+concentration is a tool deserving deeper scrutiny. 
+Further tests with larger simulated volumes, varying numerical
+resolution and different density profiles are the next natural step to
+explore the full potential of this new method.
+
+\vspace{0.1cm}
 

### 2016-04-17 paper/paper.tex
paper full version

@@
 \begin{center}
-  \includegraphics[width=0.47\textwidth]{avg_foff_bolshoi.pdf}
+  \includegraphics[width=0.49\textwidth]{avg_foff_bolshoi.pdf}
 \end{center}
 \vspace{-0.5cm}
-\caption{Average value of the relative error in the concentration
-  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
-  the set of mock halos. Different symbols represent different
-  methods. The new method provides the most accurate estimate at fixed
-  particle number.  
+\caption{Average value of the fractional offset ($f_{\rm off}$Eq. \ref{eq:f_off})
+  between the concentration in a halo at high resolution versus its
+  downsampled  versions. 
+  Each point is the result of 100 downsampling iterations.
+  The velocity method noticeably overestimates the
+  concentration up to a factor of $0.25$, while the new method only
+  underestimates the concentrations by up to a factor of $0.05$.
     \label{fig:downsampling}}
@@
 \begin{center}
-  \includegraphics[width=0.45\textwidth]{error_conc_bolshoi.pdf}
+  \includegraphics[width=0.47\textwidth]{error_conc_bolshoi.pdf}
 \end{center}
 \vspace{-0.5cm}
-\caption{Average value of the relative error in the concentration
-  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
-  the set of mock halos. Different symbols represent different
-  methods. The new method provides the most accurate estimate at fixed
-  particle number.  
+\caption{Uncertainties on different concentration estimates.
+  The large symbols show the standard deviation of the fractional
+  offset ($f_{\rm off}$ Eq. \ref{eq:f_off}) from the downsampling
+  experiments.  
+  The small dots correspond to the $1-\sigma$ uncertainty on the
+  concentration for each halo as estimated by the MCMC algorithm in
+  used for the new method.
+  Uncertainties from fluctuations on the halo particle number are
+  larger than the statistical uncertainties from the fitting process. 
   \label{fig:downsampling_err}}

### 2016-04-17 paper/paper.tex
comentarios juan carlos

@@
 The internal DM distribution in a halo is usually parameterized
-through the density profile.  
-In a first approximation this profile is spherically symmetric; the
-density only depends on the radial coordinate.  
-One the most popular radial parameterizations is the
-Navarro-Frenk-White (NFW) profile 
-\citep{NFW}.   
-If one is not interested in the very central region of the
-dark matter halo (where galaxy formation takes place, and where the
-effects of baryon physics on dark matter distribution are still 
-unknown) one can also assume that this profile is universal.
-\citep{Navarro2010}.  
- This profile is a double power law in radius, where the transition
-break happens at the so-called scale radius, $r_s$.  
-The ratio between the scale radius and the halo virial radius $R_v$ is
-known as the concentration $c=R_v/r_s$.
+through the density profile.  In a first approximation this profile is
+spherically symmetric; the density only depends on the radial
+coordinate.  One {\bf of} the most popular radial parameterizations is
+the Navarro-Frenk-White (NFW) profile \citep{NFW}.  If one is not
+interested in the very central region of the dark matter halo (where
+galaxy formation takes place, and where the effects of baryon physics
+on dark matter distribution are still unknown) one can also assume
+that this profile is universal.  \citep{Navarro2010}.  This profile is
+a double power law in radius, where the transition break happens at
+the so-called scale radius, $r_s$.  The ratio between the scale radius
+and the halo virial radius $R_v$ is known as the concentration
+$c=R_v/r_s$.
 
-The concentration of the NFW profile provides a conceptual
-framework to study simulated dark matter halos as a function of
-redshift and cosmological parameters.
-In many numerical studies 
+The concentration of the NFW profile provides a conceptual framework
+to study simulated dark matter halos as a function of redshift and
+cosmological parameters.  In many numerical studies
 \citep{Neto2007,Maccio2008,Duffy2008,Munoz2011,Prada2012,Ludlow2014}
-the results are summarized through the
-mass-concentration relationship; that is the distribution of
-concentration values at a fixed halo mass and redshift.
-The success of such numerical experiments rests on a
-reliable algorithm to estimate the concentration. 
-Such an algorithm should provide unbiased results and must be robust
-when applied to simulations of different numerical resolution.
+the results are summarized through the mass-concentration
+relationship; that is the distribution of concentration values at a
+fixed halo mass and redshift.  The success of such numerical
+experiments rests on a reliable algorithm to estimate the
+concentration.  Such an algorithm should provide unbiased results and
+must be robust when applied to simulations of different numerical
+resolution.
 
-There are two stablished algorithms to estimate the concentration parameter
-of a N-body dark matter halo. 
-The first method takes the halo particles and bins them into
-logarithmic radii to estimate the density in each bin, then it 
-proceeds to fit the density as a function of the radius to the NFW
-profile.  
-A second method uses an analytic property of the NFW profile
-that relates the maximum of the ratio of the circular velocity to the
-virial velocity, $V_{\rm circ}$/$V_{\rm vir}$.  The concentration can
-be then found as the root of an algebraic equation dependent on this
-maximum value.
+There are two stablished algorithms to estimate the concentration
+parameter of a N-body dark matter halo.  The first method takes the
+halo particles and bins them into logarithmic radii to estimate the
+density in each bin, then it proceeds to fit the density as a function
+of the radius to the NFW profile.  A second method uses an analytic
+property of the NFW profile that relates the maximum of the ratio of
+the circular velocity to the virial velocity, $V_{\rm circ}$/$V_{\rm
+  vir}$.  The concentration can be then found as the root of an
+algebraic equation dependent on this maximum value.
 
 The first method is straightforward to apply but presents two
-disadvantages.  
-First, it requires a large number of particles in
-order to have a proper density estimate in each bin.  
-This makes the method robust only for halos with at least $10^3$ particles.  
-The second problem is that there is not a way to estimate the optimal
-radial bin size, different choices may produce different results for the
-concentration.
+disadvantages.  First, it requires a large number of particles in
+order to have a proper density estimate in each bin.  This makes the
+method robust only for halos with at least $10^3$ particles.  The
+second problem is that there is not a way to estimate the optimal
+radial bin size, different choices may produce different results for
+the concentration.
 
-The second method solves the two problems mentioned above.  
-It works with low particle numbers and does not involve data binning.  
-However, it effectively takes into account only a single data point and
+The second method solves the two problems mentioned above.  It works
+with low particle numbers and does not involve data binning.  However,
+it effectively takes into account only a single data point and
 discards the behavior of the ratio $V_{\rm circ}/V_{\rm vir}$ below
-and above its maxima.  
-Small fluctuations on the value of this maximum can yield large
-perturbations on the estimated concentration parameter.
+and above its maxima.  Small fluctuations on the value of this maximum
+can yield large perturbations on the estimated concentration
+parameter.
 
 In this paper we present a third alternative based on fitting the
-integrated mass profile.
-This approach has two advantages with respect to the above mentioned
-methods.  
-It does not involve any data binning and does not throw away data
-points. 
-This translates into a robust estimate even at low resolution/particle
-numbers.   
-Furthermore, since the method does not require any binning, there is
-no need to tune numerical parameters.
-This method provides a new independent method to estimate the
-concentration parameter.   
-Here we provide a detailed description of the method and a
-comparison against the two traditional techniques by measuring its
-performance both on mock and N-body halos.
+integrated mass profile.  This approach has two advantages with
+respect to the above mentioned methods.  It does not involve any data
+binning and does not throw away data points.  This translates into a
+robust estimate even at low resolution/particle numbers.  Furthermore,
+since the method does not require any binning, there is no need to
+tune numerical parameters.  This method provides a new independent
+method to estimate the concentration parameter.  Here we provide a
+detailed description of the method and a comparison against the two
+traditional techniques by measuring its performance both on mock and
+N-body halos.
 
@@
 $\delta_c$ is the halo dimensionless characteristic density and $r_s$
-is the scale radius. 
-This radius marks the point where the logarithmic slope of the density
-profile is equal to -2, the transition between the power law
-scaling $\rho\propto r^{-1}$ for $r<r_s$ and $\rho\propto r^{-3}$ for
-$r>r_s$.
+is the scale radius.  This radius marks the point where the
+logarithmic slope of the density profile is equal to -2, the
+transition between the power law scaling $\rho\propto r^{-1}$ for
+$r<r_s$ and $\rho\propto r^{-3}$ for $r>r_s$.
 
@@
 spherical volume that encloses a density of $\Delta_h$ times the mean
-density of the Universe.  
-The corresponding mass $M_{v}$, the virial mass, can be written as
-$M_{v} = \frac{4\pi}{3}\bar{\rho}\Delta_h r_v^3$.  
-From these virial quantities we define new dimensionless variables for
-the radius and mass $x\equiv r/r_v$ and $m\equiv M(<r)/M_v$.
+density of the Universe.  The corresponding mass $M_{v}$, the virial
+mass, can be written as $M_{v} = \frac{4\pi}{3}\bar{\rho}\Delta_h
+r_v^3$.  From these virial quantities we define new dimensionless
+variables for the radius and mass $x\equiv r/r_v$ and $m\equiv
+M(<r)/M_v$.
 
@@
 %
-and the parameter $c$ corresponds to the concentration $c\equiv r_v/r_s$.
+and the parameter $c$ corresponds to the concentration $c\equiv
+r_v/r_s$.
 
@@
 It is also customary to express the mass of the halo in terms of the
-circular velocity $V_{c}=\sqrt{GM(<r)/r}$.
-From this we can define a new dimensionless circular velocity $v(<x)\equiv
-V_{c}(<r)/V_{c}(<r_v)$, using the result in Eq. \ref{eq:profile}
-we have:
+circular velocity $V_{c}=\sqrt{GM(<r)/r}$.  From this we can define a
+new dimensionless circular velocity $v(<x)\equiv
+V_{c}(<r)/V_{c}(<r_v)$, using the result in Eq. \ref{eq:profile} we
+have:
 
@@
 This normalized profile always shows a maximum provided that the
-concentration is larger than $c>2$.
-It is possible to show that for the NFW profile the maximum is
-provided by
+concentration is larger than $c>2$.  It is possible to show that for
+the NFW profile the maximum is provided by
 
@@
 To date, there are two standard methods to estimate concentrations in
-dark matter halos extracted from N-body simulations. 
-The first method tries to directly estimate the density profile.  
-It takes all the particles in the halo and bins them in the logarithm of
-the radial coordinate from the halo center.  
-Then, it estimates the density in each logarithmic bin counting the
-particles and dividing by the corresponding shell volume.  
-At this point is possible to make a direct fit to the density as a
-function of the radial coordinate. 
+dark matter halos extracted from N-body simulations.  The first method
+tries to directly estimate the density profile.  It takes all the
+particles in the halo and bins them in the logarithm of the radial
+coordinate from the halo center.  Then, it estimates the density in
+each logarithmic bin counting the particles and dividing by the
+corresponding shell volume.  At this point is possible to make a
+direct fit to the density as a function of the radial coordinate.
 This method has been broadly used for more than two decades to study
@@
 
-A second method uses the circular velocity profile.  
-It finds the value of $x$ for which the normalized circular velocity
-$v(<x)$ shows a maximum.  
-Using this value it solves numerically for the corresponding value of
-the concentration using Eq. (\ref{eq:max_v}). 
+A second method uses the circular velocity profile.  It finds the
+value of $x$ for which the normalized circular velocity $v(<x)$ shows
+a maximum.  Using this value it solves numerically for the
+corresponding value of the concentration using Eq. (\ref{eq:max_v}).
 This method has been most recently used by \cite{Klypin2014} to study
@@
 The new method uses the integrated mass profile defined in
-Eq. (\ref{eq:profile}).
-We build it from N-body data following the next steps.
-First, we define the center of the halo to be at the position of the
-particle with the lowest gravitational potential.  
+Eq. (\ref{eq:profile}).  We build it from N-body data following the
+next steps.  First, we define the center of the halo to be at the
+position of the particle with the lowest gravitational potential.
 Then we rank the particles by their increasing radial distance from
+the center.  From this ranked list of $i=1,N$ particles, the total
+mass at a radius $r_i$ is $M_i=i\times m_p$, where $r_i$ is the
+position of the $i$-th particle and $m_p$ is the mass of a single
+computational particle.  In this process we discard the particle at
 the center.
-From this ranked list of $i=1,N$ particles, the total mass at a radius
-$r_i$ is $M_i=i\times m_p$, where $r_i$ is the position of the $i$-th
-particle and $m_p$ is the mass of a single computational particle. 
-In this process we discard the particle at the center.
 
@@
 Once the mass profile is expressed in dimensionless variables the
-concentration is the only free parameter. 
-We then use an Affine Invariant Markov Chain Monte Carlo implemented in the
-python module {\em emcee} \citep{emcee} to sample the likelihood
-function distribution defined by ${\cal L}(c)\propto
-\exp(-\chi^2(c)/2)$ where the $\chi^2(c)$ is 
-written as
+concentration is the only free parameter.  We then use an Affine
+Invariant Markov Chain Monte Carlo implemented in the python module
+{\em emcee} \citep{emcee} to sample the likelihood function
+distribution defined by ${\cal L}(c)\propto \exp(-\chi^2(c)/2)$ where
+the $\chi^2(c)$ is written as
 
@@
 We apply the three methods mentioned above on two different halo
-samples.
-The first sample is composed by mock halos generated to have known
-concentration values in perfect spherical symmetry following an NFW
-profile.    
-Using this sample we quantify the ability to recover the expected
-concentration as a function of particle number. 
-The second sample comes from a publicly available N-body cosmological
-simulation to test the new method on more realistic and complex data
-to show the impact on the mass-concentration relationship.
+samples.  The first sample is composed by mock halos generated to have
+known concentration values in perfect spherical symmetry following an
+NFW profile.  Using this sample we quantify the ability to recover the
+expected concentration as a function of particle number.  The second
+sample comes from a publicly available N-body cosmological simulation
+to test the new method on more realistic and complex data to show the
+impact on the mass-concentration relationship.
 
@@
 The method we use to generate the mock halos is based on the
-integrated mass profile.  
-We start by fixing the desired concentration $c$ and total number of
-particles $N$ in the mock halo.  
-With these values we define the mass element as $\delta m = 1/M$, corresponding
-to the mass of each particle such that the total mass is one.   
-Then for each particle, $i=1,\ldots,N$, we find the value of $r_i$
-such that the difference 
+integrated mass profile.  We start by fixing the desired concentration
+$c$ and total number of particles $N$ in the mock halo.  With these
+values we define the mass element as $\delta m = 1/M$, corresponding
+to the mass of each particle such that the total mass is one.  Then
+for each particle, $i=1,\ldots,N$, we find the value of $r_i$ such
+that the difference
 % 
@@
 The value of $r_i$ is the radius of the $i$-th particle of the mock
-halo.  
-Then we generate random polar and azimuthal angles $\theta$ and
-$\phi$ for each particle to ensure spherical symmetry.  
-Finally these three spherical coordinates are transformed into
-Cartesian coordinates $(r,\theta,\phi) \rightarrow (x,y,z)$.
+halo.  Then we generate random polar and azimuthal angles $\theta$ and
+$\phi$ for each particle to ensure spherical symmetry.  Finally these
+three spherical coordinates are transformed into Cartesian coordinates
+$(r,\theta,\phi) \rightarrow (x,y,z)$.
 
 We generate in total $400$ mock halos split into four different groups
-of $100$ halos each.  
-The four groups differ in the total number of particles for their
-halos: $20$, $200$, $2000$ and $20000$.   
-Inside each group the halos have random concentration values in the range
-$1<c<20$ with a uniform distribution.  
-We find the concentration values for all these halos using the
-density, velocity and integrated mass methods described in the
-previous section.
+of $100$ halos each.  The four groups differ in the total number of
+particles for their halos: $20$, $200$, $2000$ and $20000$.  Inside
+each group the halos have random concentration values in the range
+$1<c<20$ with a uniform distribution.  We find the concentration
+values for all these halos using the density, velocity and integrated
+mass methods described in the previous section.
 
@@
 where ${\cal{H}}$ corresponds to a set of mock halos, and
-$\left|{\cal{H}}\right|$ is the number of haloes in ${\cal{H}}$. 
-A large discrepancy between the estimated and input concentrations are
+$\left|{\cal{H}}\right|$ is the number of haloes in ${\cal{H}}$.  A
+large discrepancy between the estimated and input concentrations are
 quantified by a large $\avg{|D|}$.
 
-Figure \ref{fig:error} shows the behaviour of $\avg{|D|}$ as a function of
-halo particle number for the three different methods.
+Figure \ref{fig:error} shows the behaviour of $\avg{|D|}$ as a
+function of halo particle number for the three different methods.
 
 At fixed particle numbers the new method always shows the lowest
-$\avg{|D|}$ values compared to the other two.
-Its accuracy is on the order of $10\%$ for $20$ particles in the halo,
-decreasing to $0.01\%$ for halos with $20000$ particles.  
-The dependence of $\avg{|D|}$ with the particle number $N$
-goes approximately as $\avg{|D|}\propto N^{-1}$.
+$\avg{|D|}$ values compared to the other two.  Its accuracy is on the
+order of $10\%$ for $20$ particles in the halo, decreasing to $0.01\%$
+for halos with $20000$ particles.  The dependence of $\avg{|D|}$ with
+the particle number $N$ goes approximately as $\avg{|D|}\propto
+N^{-1}$.
 
 The method based on the maximum of the circular velocity shows a
-similar behaviour with $\avg{|D|}\propto N^{-1/3}$.  
-Its accuracy is $2-5$ times lower than in the new method, on the order of
-$20\%$ for $20$ particle halos and $0.5\%$ for $20000$ particle
-halos. 
-The method  based on the direct density fit shows the lowest accuracy for a low
-  particle number. 
-  As it is discussed in \citep{Munoz2011}, density binning for halos
-  with particle numbers below $\sim200$ leads to a biased estimation
-  of the mass density profile, and therefore to a biased estimation of
-  the concentration parameter. 
-This behaviour is evident in the large values of $\avg{|D|}$ for halos
-with number of particles below $\sim 200$ and an intermediate accuracy
-between the other two methods for a high particle number.
+similar behaviour with $\avg{|D|}\propto N^{-1/3}$.  Its accuracy is
+$2-5$ times lower than in the new method, on the order of $20\%$ for
+$20$ particle halos and $0.5\%$ for $20000$ particle halos.  The
+method based on the direct density fit shows the lowest accuracy for a
+low particle number.  As it is discussed in \citep{Munoz2011}, density
+binning for halos with particle numbers below $\sim200$ leads to a
+biased estimation of the mass density profile, and therefore to a
+biased estimation of the concentration parameter.  This behaviour is
+evident in the large values of $\avg{|D|}$ for halos with number of
+particles below $\sim 200$ and an intermediate accuracy between the
+other two methods for a high particle number.
 
@@
 \vspace{-0.5cm}
-\caption{Average value of the fractional offset ($f_{\rm off}$Eq. \ref{eq:f_off})
-  between the concentration in a halo at high resolution versus its
-  downsampled  versions. 
-  Each point is the result of 100 downsampling iterations.
-  The velocity method noticeably overestimates the
-  concentration up to a factor of $0.25$, while the new method only
-  underestimates the concentrations by up to a factor of $0.05$.
+\caption{Average value of the fractional offset ($f_{\rm
+    off}$Eq. \ref{eq:f_off}) between the concentration in a halo at
+  high resolution versus its downsampled versions.  Each point is the
+  result of 100 downsampling iterations.  The velocity method
+  noticeably overestimates the concentration up to a factor of $0.25$,
+  while the new method only underestimates the concentrations by up to
+  a factor of $0.05$.
     \label{fig:downsampling}}
@@
 \vspace{-0.5cm}
-\caption{Uncertainties on different concentration estimates.
-  The large symbols show the standard deviation of the fractional
-  offset ($f_{\rm off}$ Eq. \ref{eq:f_off}) from the downsampling
-  experiments.  
-  The small dots correspond to the $1-\sigma$ uncertainty on the
-  concentration for each halo as estimated by the MCMC algorithm in
-  used for the new method.
+\caption{Uncertainties on different concentration estimates.  The
+  large symbols show the standard deviation of the fractional offset
+  ($f_{\rm off}$ Eq. \ref{eq:f_off}) from the downsampling
+  experiments.  The small dots correspond to the $1-\sigma$
+  uncertainty on the concentration for each halo as estimated by the
+  MCMC algorithm {\bf delete ``in''} used for the new method.
   Uncertainties from fluctuations on the halo particle number are
-  larger than the statistical uncertainties from the fitting process. 
+  larger than the statistical uncertainties from the fitting
+  process. {\bf what is the solid line showing?}
   \label{fig:downsampling_err}}
@@
 \caption{Mass-concentration relationship for the three different
-  methods used on the same cosmological N-body data. 
-  All halos are used regardless of their relaxation state.
-  The lines correspond to the median concentration values in each mass bin.
-  The shaded region presents 10 and 90 per cent spread.
-  For clarity we only show the spread for the concentrations estimated
-  using the new method. The other two methods have a similar spread. The
-  dotted line corresponds to fits reported by \citep{Prada2012}.
+  methods used on the same cosmological N-body data.  All halos are
+  used regardless of their relaxation state.  The lines correspond to
+  the median concentration values in each mass bin.  The shaded region
+  presents 10 and 90 per cent spread.  For clarity we only show the
+  spread for the concentrations estimated using the new method. The
+  other two methods have a similar spread. The dotted line corresponds
+  to fits reported by \citep{Prada2012}.
   \label{fig:concentration}. The left panel shows the raw results
@@
 However, simulated dark matter halos in a cosmological context are
-complex. 
-They are not isolated, many of them  experience mergers that take them
-out of the equilibrium. 
-Halos may have also plenty of substructure. 
-All these effects disturb the mass density profile, taking it  away
-from the ideal NFW profile. 
-In order to explore the performance of the new method in this setting, we
-use it to estimate the  concentration parameter in dark matter halos
-obtained from a cosmological N-body simulation and compare it with the
-other two classical methods.
+complex.  They are not isolated, many of them experience mergers that
+take them out of the equilibrium.  Halos may have also plenty of
+substructure.  All these effects disturb the mass density profile,
+taking it away from the ideal NFW profile.  In order to explore the
+performance of the new method in this setting, we use it to estimate
+the concentration parameter in dark matter halos obtained from a
+cosmological N-body simulation and compare it with the other two
+classical methods.
 
-We use data from the Bolshoi cosmological simulation that follows
-the non-linear evolution of a dark matter density field sampled with
-$2048^3$ particles over a cubic box of $250\ \hMpc$ on a side.  
-The data is publicly available at \url{http://www.cosmosim.org/}.
-More details about the structure of the database and the simulation
-can be found in \citep{2013AN....334..691R}.
+We use data from the Bolshoi cosmological simulation that follows the
+non-linear evolution of a dark matter density field sampled with
+$2048^3$ particles over a cubic box of $250\ \hMpc$ on a side.  The
+data is publicly available at \url{http://www.cosmosim.org/}.  More
+details about the structure of the database and the simulation can be
+found in \citep{2013AN....334..691R}.
 
 We use a halo sample containing all the halos located in a cubic
-sub-volume of $100$ \hMpc\ on a side.
-From this sample we select all the halos at $z=0$ detected
-with a Friends-of-Friends (FoF) algorithm with more than 300
-particles, meaning that the masses are in the interval
-$4\times 10^{10}\leq M_{\rm FoF}/\hMsun \leq 10^{14}$.  
-The FoF algorithm used a linking length of $0.17$ times the mean
+sub-volume of $100$ \hMpc\ on a side.  From this sample we select all
+the halos at $z=0$ detected with a Friends-of-Friends (FoF) algorithm
+with more than 300 particles, meaning that the masses are in the
+interval $4\times 10^{10}\leq M_{\rm FoF}/\hMsun \leq 10^{14}$.  The
+FoF algorithm used a linking length of $0.17$ times the mean
 inter-particle distance. This choice translates into an overdensity
-$\Delta_h\sim  400-700$ dependent on the halo concentration \citep{More2011}.
+$\Delta_h\sim 400-700$ dependent on the halo concentration
+\citep{More2011}.
 
@@
 times the critical density) to select an spherical region that we
-redefine to be our halo.  
-This choice makes that the overdensities are fully included inside the
-original FoF particle group.   
-On the interest of providing a fair comparison against the density method we
+redefine to be our halo.  This choice makes that the overdensities are
+fully included inside the original FoF particle group.  On the
+interest of providing a fair comparison against the density method we
 only report results from overdensities with at least $200$ particles
@@
 possible biases in the concentration estimates as a function of
-particle number. 
-We select $8$ halos from the simulation that have at least $3\times
-10^5$ particles. 
-We then downsample the total number of particles in each halo by
-factors of $10, 20, 45, 100, 215, 460, 1000$ to measure its
-concentration with both the integrated mass and the velocity method.
-each downsampling factor we repeat the operation $100$ times.
+particle number.  We select $8$ halos from the simulation that have at
+least $3\times 10^5$ particles.  We then {\bf randomly} downsample the
+total number of particles in each halo by factors of $10, 20, 45, 100,
+215, 460, 1000$ to measure its concentration with both the integrated
+mass and the velocity method. {\bf For each} downsampling factor we
+repeat the operation $100$ times.
 
-The average concentration value for the largest number of particles, $c_{N_{max}}$,
-provides with a baseline to compare all the other results.
-We use the following statistic
+The average concentration value for the largest number of particles,
+$c_{N_{max}}$, provides with a baseline to compare all the other
+results.  We use the following statistic
 \begin{equation}
@@
 
-Figure \ref{fig:downsampling} summarizes our results. 
-The plot shows the average value of $f_{\rm off}$ as a function
-of the particle number.
-As expected for large enough sample particle numbers, $N_{s}>5\times
-10^3$, the results of the two algorithms coincide and $\langle f_{\rm
-  off}\rangle\sim 0$.  
-For lower number of particles, the results of the two algorithms
-deviate from the expected concentration value.  
-The velocity method overestimates by a factor $\langle f_{\rm 
-  off}\rangle\sim 0.25$ the concentration values for the lowest
-sample particle numbers, $N_{s}\sim 100$. 
-Around the same sampling scale, the new algorithm shows a more stable
-behaviour with an understimate by a factor of $\langle f_{\rm 
-  off}\rangle \sim 0.02$.  
-This shows that in the more complex setup of a cosmological setup our
-algorithm continues to be stable below the $5\%$ level for low 
-particle numbers.
+Figure \ref{fig:downsampling} summarizes our results.  The plot shows
+the average value of $f_{\rm off}$ as a function of the particle
+number.  As expected for large enough sample particle numbers,
+$N_{s}>5\times 10^3$, the results of the two algorithms coincide and
+$\langle f_{\rm off}\rangle\sim 0$.  For lower number of particles,
+the results of the two algorithms deviate from the expected
+concentration value.  The velocity method overestimates by a factor
+$\langle f_{\rm off}\rangle\sim 0.25$ the concentration values for the
+lowest sample particle numbers, $N_{s}\sim 100$.  Around the same
+sampling scale, the new algorithm shows a more stable behaviour with
+an understimate by a factor of $\langle f_{\rm off}\rangle \sim 0.02$.
+This shows that in the more complex setup of a cosmological {\bf
+  simulation} our algorithm continues to be stable below the $5\%$
+level for low particle numbers.
 
@@
 
-Figure \ref{fig:downsampling} summarizes different uncertainty
-results. 
-Large symbols show the standard deviation on $f_{\rm off}$
-from the downsampling experiment.
-Small dots show the uncertainty on each individual concentration value
-as estimated by the MCMC algorithm.
-The line shows the $\propto N^{-1}$  locus.
-This figure demonstrates that the statistical uncertainties are at
-least one order of magnitude than the uncertainty associated to
-downsampling experiment.
+Figure \ref{fig:downsampling} {\bf Aca no iría una referencia Fig 3 en
+  lugar de Fig 2?} summarizes different uncertainty results.  Large
+symbols show the standard deviation on $f_{\rm off}$ from the
+downsampling experiment.  Small dots show the uncertainty on each
+individual concentration value as estimated by the MCMC algorithm.
+The line shows the $\propto N^{-1}$ locus.  This figure demonstrates
+that the statistical uncertainties are at least one order of magnitude
+{\bf smaller} than the uncertainty associated to downsampling
+experiment.
 
@@
 The left panel shows the results as they are produced by each of the
-algorithms, the thin dashed line marks the results by \citep{Prada2012}.
+algorithms, the thin dashed line marks the results by
+\citep{Prada2012}.
 
 We notice first that the results from the density method have a
-systematic $15\%$offset from the velocity methods.
-This offset was already presented by \citep{Prada2012} for some
-concentrations and halo masses, although a more organized study in
-terms of the mass-concentration relationship has not been presented in
-the literature.
+systematic $15\%$offset from the velocity methods.  This offset was
+already presented by \citep{Prada2012} for some concentrations and
+halo masses, although a more organized study in terms of the
+mass-concentration relationship has not been presented in the
+literature.
 
-We then notice that our methods follows closely the results of the
-velocity method at higher masses, $M_h>10^{12}\hMsun$ or equivalently
-for $>5\times10^3$ particles. 
-For masses below that threshold our method saturates at a
-concentration value of $\sim 7$ while the velocity method continues to
-give higher concentration values.
+We then notice that our {\bf method} follows closely the results of
+the velocity method at higher masses, $M_h>10^{12}\hMsun$ or
+equivalently for $>5\times10^3$ particles.  For masses below that
+threshold our method saturates at a concentration value of $\sim 7$
+while the velocity method continues to give higher concentration
+values.
 
 We hypothesize that the increase in the results for the velocity
-method below $5\times 10^{4}$ particles come from the systematic
-bias described in the previous subsection.  
-To test the general consistency of this hypothesis wwe correct the
-concentration values in the velocity and integrated mass methods by
-a factor of $1/(1+f_{\rm off})$, using the definition in Equation
-(\ref{eq:f_off}) and the parameters obtained from the data presented
-in Figure (\ref{fig:downsampling}).   
-The correction brings into perfect agreement the results between the
-velocity and the integrated mass method. 
-This suggests that the concentration at lower masses might very well
-reach a plateu in the halo mass range $10^{10}< M_{h}/\hMsun < 10^{12}$ .
+method below $5\times 10^{4}$ particles come from the systematic bias
+described in the previous subsection.  To test the general consistency
+of this hypothesis {\bf we} correct the concentration values in the
+velocity and integrated mass methods by a factor of $1/(1+f_{\rm
+  off})$, using the definition in Equation (\ref{eq:f_off}) and the
+parameters obtained from the data presented in Figure
+(\ref{fig:downsampling}).  The correction brings into perfect
+agreement the results between the velocity and the integrated mass
+method.  This suggests that the concentration at lower masses might
+very well reach a plateu in the halo mass range $10^{10}< M_{h}/\hMsun
+< 10^{12}$ .
 
@@
 In this paper we presented a new method to estimate the concentration
-of dark matter halos in N-body simulations.  
-We tested the method on mock halo data to study the impact of total
-number of particles and input concentration on the retrieved values.  
-We compared these results against two other methods commonly used in
-the literature to estimate concentrations.  
-For all methods, the accuracy in retrieving the input concentration
-increases with the number of particles as summarized in Figure
-\ref{fig:error}.  The new method systematically outperforms the other two.
+of dark matter halos in N-body simulations.  We tested the method on
+mock halo data to study the impact of total number of particles and
+input concentration on the retrieved values.  We compared these
+results against two other methods commonly used in the literature to
+estimate concentrations.  For all methods, the accuracy in retrieving
+the input concentration increases with the number of particles as
+summarized in Figure \ref{fig:error}.  The new method systematically
+outperforms the other two.
 
 We also applied the method to halos extracted from a cosmological
-N-body simulation.
-Using this data we showed that the new method is robust with respect to a
-decreasing number of particles in the halos. 
-On the other hand we showed that the velocity method has a
-systematic bias that overesimates the concentration for halos with a
-low particle number up to a factor of $25\%$.
+N-body simulation.  Using this data we showed that the new method is
+robust with respect to a decreasing number of particles in the halos.
+On the other hand we showed that the velocity method has a systematic
+bias that overesimates the concentration for halos with a low particle
+number up to a factor of $25\%$.
+
+{\bf So far no procedure could provide a direct way to measure the
+  bias in the estimated halo concentration at low particle numbers and
+  a way to use it to make corrections on the estimates. In section 4.2
+  it was shown a simple method that can be used on any dataset to
+  estimate the errors and correct them when estimating the
+  concentration at low particle numbers.}
 
 We also used the N-body simulation to estimate the impact on the mass
-concentration relationship. 
-Although the three methods are in broad agreement within their
-uncertainties there are some noticeable differences.
-The first difference is that the density method produces
+concentration relationship.  Although the three methods are in broad
+agreement within their uncertainties there are some noticeable
+differences.  The first difference is that the density method produces
 systematically higher concentrations by a factor of $15\%$ compared to
-the velocity mehod.
-The second difference is that the velocity and integrated mass methods
-start to differ for masses below $10^{12}\hMsun$. 
-We found that a correction of the results by the bias factor found
-using the same N-body data can bring these two methods into
-agreement.
+the velocity mehod.  The second difference is that the velocity and
+integrated mass methods start to differ for masses below
+$10^{12}\hMsun$.  We found that a correction of the results by the
+bias factor found using the same N-body data can bring these two
+methods into agreement.
 
-These are encouraging results. 
-They show that using the integrated mass profile to find the DM halo
-concentration is a tool deserving deeper scrutiny. 
-Further tests with larger simulated volumes, varying numerical
-resolution and different density profiles are the next natural step to
-explore the full potential of this new method.
+These are encouraging results.  They show that using the integrated
+mass profile to find the DM halo concentration is a tool deserving
+deeper scrutiny.  Further tests with larger simulated volumes, varying
+numerical resolution and different density profiles are the next
+natural step to explore the full potential of this new method.
 

### 2016-04-17 paper/paper.tex
fixed typos

@@
 outperforming the other two methods. 
-Convergence tests by downsampling halos with high number of particles in
-the N-body simulation show that the new method is robust with respect
-to changes in halo particle number.
-However the velocity method overpredicts concentration values by a
+We design another simple test that can be used on any
+data-set to estimate and correct the biases when estimating the
+concentration at low particle numbers. 
+That test shows that the new method is robust with respect to changes
+in halo particle number. 
+However, the velocity method over-predicts concentration values by a
 factor of $25\%$ values for low particle numbers.
-We also measure the mass-concentration relationship on N-body
+Finally, we also measure the mass-concentration relationship on N-body
 data. 
@@
 statistical uncertainties.   
-We find a small deviation at low masses, $M<10^{12}\hMsun$, where
+There is a small deviation at low masses, $M<10^{12}\hMsun$, where
 the new method yields lower median concentration values by $25\%$
-compared to the velocity methods. 
-We find that accounting for the bias
-in the velocity method brings the results into agreement.
+compared to the velocity methods; accounting for the bias in the
+velocity method brings the results into agreement.  
 From these results we believe that the new method is a promising tool
@@
 
-There are two stablished algorithms to estimate the concentration
+There are two established algorithms to estimate the concentration
 parameter of a N-body dark matter halo.  The first method takes the
@@
 \end{equation}
-where $x_{\rm max}=2.163$ \citep{Klypin2014} and the function $f(x)$
+where $x_{\rm max}=2.163$ \citep{Klypin2016} and the function $f(x)$
 corresponds to the definition in Eq. (\ref{eq:f_NFW}).
@@
 corresponding value of the concentration using Eq. (\ref{eq:max_v}).
-This method has been most recently used by \cite{Klypin2014} to study
+This method has been most recently used by \cite{Klypin2016} to study
 the mass-concentration-redshift relation using the Multidark
@@
 \caption{Average value of the relative error in the concentration
-  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
+  estimate, $\avg{|D|}$, as a function of the particle number in
   the set of mock halos. Different symbols represent different
@@
 \end{figure}
-
-%\label{sec:data}
-%\begin{figure*}
-%  \begin{center}
-%    \includegraphics[width=0.32\textwidth]{conc_mass_vel.pdf}
-%    \includegraphics[width=0.32\textwidth]{conc_mass_dens.pdf}
-%    \includegraphics[width=0.32\textwidth]{conc_dens_vel.pdf}
-%  \end{center}
-%\vspace{-0.5cm}
-%  \caption{Comparison between the concentrations measured by the new 
-%    method and the maximum velocity (left) and density (middle)
-%    methods. The solid line indicates the equal value between the two
-%    techniques. The dashed line shows the upper 15 per cent difference
-%    between two methods.
-%  \label{fig:comparison}}
-%\end{figure*}
 
@@
 \begin{equation}
-D=(c_{in}-c_{out})/c_{in},
+D= c_{out}/c_{in}-1,
 \label{eq:D}
@@
 We also find that the bias from different concentrations at fixed
-particle number is negligeable with respect to the effects induced by
+particle number is negligible with respect to the effects induced by
 different particle numbers.
@@
   large symbols show the standard deviation of the fractional offset
-  ($f_{\rm off}$ Eq. \ref{eq:f_off}) from the downsampling
-  experiments.  The small dots correspond to the $1-\sigma$
+  ($f_{\rm off}$ as defined in Eq. \ref{eq:f_off}) from the downsampling
+  experiments.  The small dots correspond to the $1\sigma$
   uncertainty on the concentration for each halo as estimated by the
-  MCMC algorithm {\bf delete ``in''} used for the new method.
-  Uncertainties from fluctuations on the halo particle number are
-  larger than the statistical uncertainties from the fitting
-  process. {\bf what is the solid line showing?}
+  MCMC algorithm used for the new method.
+  The solid lines shows the $1/N$ tendency, which also corresponds
+  to the particle number dependence of the $\langle|D|\rangle$ statistic
+  (i.e. the accuracy to retrieve a known concentration in mock halos)
+  of the new method.
+  Uncertainties due to particle number fluctuations are always larger
+  than the statistical uncertainties from the fitting process. 
   \label{fig:downsampling_err}}
@@
 \subsection{Measuring the concentration in halos from a cosmological simulation}
+\label{subsec:cosmo}
 
@@
 \begin{center}
-  \includegraphics[width=0.45\textwidth]{concentration_bolshoi.pdf}
-  \includegraphics[width=0.45\textwidth]{concentration_bolshoi_corrected.pdf}
+  \includegraphics[width=0.49\textwidth]{concentration_bolshoi.pdf}
+  \includegraphics[width=0.49\textwidth]{concentration_bolshoi_corrected.pdf}
 \end{center}
@@
   \label{fig:concentration}. The left panel shows the raw results
-  comming from each algorithm. The right panel introduces a
+  coming from each algorithm. The right panel introduces a
   correction on the velocity and integrated mass results. 
-  The corrections dependens on the number of particles following the
+  The corrections depends on the number of particles following the
   results of the downsampling experiments presented in Figure
@@
 possible biases in the concentration estimates as a function of
-particle number.  We select $8$ halos from the simulation that have at
-least $3\times 10^5$ particles.  We then {\bf randomly} downsample the
-total number of particles in each halo by factors of $10, 20, 45, 100,
-215, 460, 1000$ to measure its concentration with both the integrated
-mass and the velocity method. {\bf For each} downsampling factor we
-repeat the operation $100$ times.
+particle number.  
+We select $8$ halos from the simulation that have at
+least $3\times 10^5$ particles.  
+We then randomly downsample the total number of particles in each halo
+by factors of $10, 20, 45, 100, 215, 460, 1000$ to measure its
+concentration with both the integrated mass and the velocity
+method. For each downsampling factor we repeat the operation $100$
+times.
 
@@
 $c_{N_{max}}$, provides with a baseline to compare all the other
-results.  We use the following statistic
+results.  
+We use the following statistic
 \begin{equation}
 f_{\rm off} = c_{N} / c_{N_{max}} - 1,
+\label{eq:f_off}
 \end{equation}
@@
 sampling scale, the new algorithm shows a more stable behaviour with
-an understimate by a factor of $\langle f_{\rm off}\rangle \sim 0.02$.
-This shows that in the more complex setup of a cosmological {\bf
-  simulation} our algorithm continues to be stable below the $5\%$
+an underestimate by a factor of $\langle f_{\rm off}\rangle \sim 0.02$.
+This shows that in the more complex setup of a cosmological 
+  simulation the new algorithm continues to be stable below the $5\%$
 level for low particle numbers.
@@
 f_{\rm off} = \frac{A}{(1+\log_{10}N_s)^{B}}.
-\label{eq:f_off}
+\label{eq:f_off_fit}
 \end{equation} 
@@
 
-Figure \ref{fig:downsampling} {\bf Aca no iría una referencia Fig 3 en
-  lugar de Fig 2?} summarizes different uncertainty results.  Large
-symbols show the standard deviation on $f_{\rm off}$ from the
-downsampling experiment.  Small dots show the uncertainty on each
-individual concentration value as estimated by the MCMC algorithm.
-The line shows the $\propto N^{-1}$ locus.  This figure demonstrates
-that the statistical uncertainties are at least one order of magnitude
-{\bf smaller} than the uncertainty associated to downsampling
-experiment.
+Figure \ref{fig:downsampling_err} summarizes different uncertainty
+results.  
+Large symbols show the standard deviation on $f_{\rm off}$ from the
+downsampling experiment.  
+Small dots show the uncertainty on each individual concentration value
+as estimated by the MCMC algorithm. 
+The line shows the $\propto N^{-1}$ locus.  
+This figure demonstrates that the statistical uncertainties are at
+least one order of magnitude smaller than the uncertainty associated
+to downsampling experiment.
 
@@
 We notice first that the results from the density method have a
-systematic $15\%$offset from the velocity methods.  This offset was
-already presented by \citep{Prada2012} for some concentrations and
-halo masses, although a more organized study in terms of the
-mass-concentration relationship has not been presented in the
-literature.
+systematic $15\%$offset from the velocity methods.  
+This offset was already presented by \citep{Prada2012} for low
+concentrations ($c<6$) and high ($M_h>10^{12}\hMsun$) halo masses.  
+Recently \citep{Klypin2016} summarized results for the
+mass-concentration relationship coming from different methods and
+datasets to show that similar systematic offsets are present.
+However, to the best of our knowledge, a systematic and modern study of
+the mass-concentration relationship spanning a wide range in mass,
+using a fixed dataset but different fitting methods has not been
+presented in the literature.
 
-We then notice that our {\bf method} follows closely the results of
+We then notice that the new method closely follows the results of
 the velocity method at higher masses, $M_h>10^{12}\hMsun$ or
-equivalently for $>5\times10^3$ particles.  For masses below that
-threshold our method saturates at a concentration value of $\sim 7$
-while the velocity method continues to give higher concentration
-values.
+equivalently for $>5\times10^3$ particles.  
+For masses below that threshold the new method saturates at a
+concentration value of $\sim 8$ while the velocity method continues to
+give higher concentration values.
 
@@
 described in the previous subsection.  To test the general consistency
-of this hypothesis {\bf we} correct the concentration values in the
+of this hypothesis we correct the concentration values in the
 velocity and integrated mass methods by a factor of $1/(1+f_{\rm
@@
 parameters obtained from the data presented in Figure
-(\ref{fig:downsampling}).  The correction brings into perfect
-agreement the results between the velocity and the integrated mass
-method.  This suggests that the concentration at lower masses might
-very well reach a plateu in the halo mass range $10^{10}< M_{h}/\hMsun
-< 10^{12}$ .
+(\ref{fig:downsampling}).  
+The correction brings into perfect agreement the results between the
+velocity and the integrated mass method.  
+This suggests that the concentration at lower masses might very well
+reach a plateau in the halo mass range $10^{10}< M_{h}/\hMsun <
+10^{12}$ .
 
@@
 On the other hand we showed that the velocity method has a systematic
-bias that overesimates the concentration for halos with a low particle
+bias that overestimates the concentration for halos with a low particle
 number up to a factor of $25\%$.
 
-{\bf So far no procedure could provide a direct way to measure the
-  bias in the estimated halo concentration at low particle numbers and
-  a way to use it to make corrections on the estimates. In section 4.2
-  it was shown a simple method that can be used on any dataset to
-  estimate the errors and correct them when estimating the
-  concentration at low particle numbers.}
+We provide for the first time in the literature a direct way to
+measure the bias in the estimated halo concentration at low particle numbers and
+a way to use it to make corrections on the estimates. 
+In Section \ref{subsec:cosmo} we presented a simple method that can be used on any
+dataset to estimate the errors and correct them when estimating the
+concentration at low particle numbers.
 
 We also used the N-body simulation to estimate the impact on the mass
-concentration relationship.  Although the three methods are in broad
-agreement within their uncertainties there are some noticeable
-differences.  The first difference is that the density method produces
+concentration relationship.  
+Although the three methods are in broad agreement within their
+uncertainties there are some noticeable differences.  
+The first difference is that the density method produces
 systematically higher concentrations by a factor of $15\%$ compared to
-the velocity mehod.  The second difference is that the velocity and
-integrated mass methods start to differ for masses below
-$10^{12}\hMsun$.  We found that a correction of the results by the
-bias factor found using the same N-body data can bring these two
-methods into agreement.
+the velocity method.
+This systematic offset has been reported in different datasets and
+techniques to measure concentrations, without any conclusive
+explanation for its origin \citep{Klypin2016}.
+The second difference is that the velocity and integrated mass methods
+start to differ for masses below $10^{12}\hMsun$.  
+We found that a correction of the results by the bias factor found
+using the same N-body data can bring these two methods into
+agreement.
 
-These are encouraging results.  They show that using the integrated
-mass profile to find the DM halo concentration is a tool deserving
-deeper scrutiny.  Further tests with larger simulated volumes, varying
-numerical resolution and different density profiles are the next
-natural step to explore the full potential of this new method.
+These are encouraging results.  
+They show that using the integrated mass profile to find the Dark
+Matter halo concentration is a tool deserving deeper scrutiny.  
+Further tests with larger simulated volumes, varying numerical
+resolution and different density profiles are the next natural step to
+explore the full potential of this new method.
 
@@
 \bibliographystyle{mn2e}
-%\bibliography{references}
+\bibliography{references}
+
 \begin{thebibliography}{}
@@
 
-\bibitem[\protect\citeauthoryear{{Klypin}, {Yepes}, {Gottlober}, {Prada} \&
-  {Hess}}{{Klypin} et~al.}{2014}]{Klypin2014}
-{Klypin} A.,  {Yepes} G.,  {Gottlober} S.,  {Prada} F.,    {Hess} S.,  2014,
-  ArXiv e-prints
+\bibitem[\protect\citeauthoryear{{Klypin}, {Yepes}, {Gottl{\"o}ber}, {Prada} \&
+  {He{\ss}}}{{Klypin} et~al.}{2016}]{Klypin2016}
+{Klypin} A.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Prada} F.,    {He{\ss}} S.,
+  2016, \mnras, 457, 4340
 

### 2016-04-26 paper/paper.tex
hello apj

@@
-\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
-%\documentclass{latex/emulateapj} 
-%External Packages and personalized macros
-%=========================================================================
-%		EXTERNAL PACKAGES
-%=========================================================================
-\usepackage{amsmath} 
-\usepackage{amssymb} 
-%\usepackage[section]{placeins}
+\documentclass{emulateapj}
+\submitted{{\it Submitted for publication in ApJ}}
+\usepackage{multirow,color,wrapfig,ulem}
 \usepackage {graphicx}
-%\usepackage{graphics}
+\usepackage{graphics}
 \usepackage[dvips]{epsfig}
-\usepackage{epsfig}  
-\usepackage{color}
-\usepackage[normalem]{ulem}
-\usepackage{hyperref}
-\usepackage{caption}
-%Non reposionated tables
-\usepackage{float}
-\restylefloat{table}
-%Multiple columns support for tables
-\usepackage{array}
-\usepackage{booktabs}
-\setlength{\heavyrulewidth}{1.5pt}
-\setlength{\abovetopsep}{4pt}
-\pdfminorversion=5
 
@@
 %=========================================================================
-\def\be{\begin{equation}}
-\def\ee{\end{equation}}
-\def\ba{\begin{eqnarray}}
-\def\ea{\end{eqnarray}}
 
-% To highlight comments 
-\definecolor{red}{rgb}{1,0.0,0.0}
-\newcommand{\red}{\color{red}}
-\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
-\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
-\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
-\newcommand{\before}[1]{\textcolor{red}{ #1}}
-\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}
+\newcommand{\avg}[1]{\langle{#1}\rangle}
 
@@
 \newcommand{\zz}{$z\sim 3$}
-\newcommand{\apj}{ApJ}  
-\newcommand{\jcap}{JCAP}  
-\newcommand{\apjs}{ApJS}  
-\newcommand{\apjl}{ApJL}  
-\newcommand{\aj}{AJ}  
-\newcommand{\mnras}{MNRAS}  
-\newcommand{\mnrassub}{MNRAS accepted}  
-\newcommand{\aap}{A\&A}  
-\newcommand{\aaps}{A\&AS}  
-\newcommand{\araa}{ARA\&A}  
-\newcommand{\nat}{Nature}  
-\newcommand{\physrep}{PhR}
-\newcommand{\pasp}{PASP}    
-\newcommand{\pasj}{PASJ}    
-\newcommand{\avg}[1]{\langle{#1}\rangle}  
+
 \newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
@@
 %=========================================================================
-\title[Halo concentration via the integrated mass profile]{Estimating dark matter  halo concentration using the integrated mass profile} 
-\author[C.N. Poveda-Ruiz, J.E. Forero-Romero, J.C. Mu\~noz-Cuartas]{
-\parbox[t]{\textwidth}{\raggedright 
+\title{A less biased dark matter halo concentration using the integrated mass profile} 
+\author{
   C. N. Poveda-Ruiz \thanks{cn.poveda542@uniandes.edu.co}$^{1}$
@@
 }
-\vspace*{6pt}\\
+
+\affil{
 $^1$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
@@
 }
-
-\maketitle
 
@@
 
-\begin{keywords}
-Cosmology: theory, large-scale structure of Universe --
-Methods: data analysis, numerical 
-\end{keywords}
+\keywords{
+Galaxies: halos --- Galaxies: high-redshift --- Galaxies: statistics
+--- Dark Matter --- Methods: numerical 
+}
 
@@
 
-\begin{thebibliography}{}
-
-\bibitem[\protect\citeauthoryear{{Duffy}, {Schaye}, {Kay} \& {Dalla
-  Vecchia}}{{Duffy} et~al.}{2008}]{Duffy2008}
-{Duffy} A.~R.,  {Schaye} J.,  {Kay} S.~T.,    {Dalla Vecchia} C.,  2008,
-  \mnras, 390, L64
-
-\bibitem[\protect\citeauthoryear{{Foreman-Mackey}, {Hogg}, {Lang} \&
-  {Goodman}}{{Foreman-Mackey} et~al.}{2013}]{emcee}
-{Foreman-Mackey} D.,  {Hogg} D.~W.,  {Lang} D.,    {Goodman} J.,  2013, \pasp,
-  125, 306
-
-\bibitem[\protect\citeauthoryear{{Klypin}, {Yepes}, {Gottl{\"o}ber}, {Prada} \&
-  {He{\ss}}}{{Klypin} et~al.}{2016}]{Klypin2016}
-{Klypin} A.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Prada} F.,    {He{\ss}} S.,
-  2016, \mnras, 457, 4340
-
-\bibitem[\protect\citeauthoryear{{Ludlow}, {Navarro}, {Angulo},
-  {Boylan-Kolchin}, {Springel}, {Frenk} \& {White}}{{Ludlow}
-  et~al.}{2014}]{Ludlow2014}
-{Ludlow} A.~D.,  {Navarro} J.~F.,  {Angulo} R.~E.,  {Boylan-Kolchin} M.,
-  {Springel} V.,  {Frenk} C.,    {White} S.~D.~M.,  2014, \mnras, 441, 378
-
-\bibitem[\protect\citeauthoryear{{Macci{\`o}}, {Dutton} \& {van den
-  Bosch}}{{Macci{\`o}} et~al.}{2008}]{Maccio2008}
-{Macci{\`o}} A.~V.,  {Dutton} A.~A.,    {van den Bosch} F.~C.,  2008, \mnras,
-  391, 1940
-
-\bibitem[\protect\citeauthoryear{{More}, {Kravtsov}, {Dalal} \&
-  {Gottl{\"o}ber}}{{More} et~al.}{2011}]{More2011}
-{More} S.,  {Kravtsov} A.~V.,  {Dalal} N.,    {Gottl{\"o}ber} S.,  2011, \apjs,
-  195, 4
-
-\bibitem[\protect\citeauthoryear{{Mu{\~n}oz-Cuartas}, {Macci{\`o}},
-  {Gottl{\"o}ber} \& {Dutton}}{{Mu{\~n}oz-Cuartas} et~al.}{2011}]{Munoz2011}
-{Mu{\~n}oz-Cuartas} J.~C.,  {Macci{\`o}} A.~V.,  {Gottl{\"o}ber} S.,
-  {Dutton} A.~A.,  2011, \mnras, 411, 584
-
-\bibitem[\protect\citeauthoryear{{Navarro}, {Frenk} \& {White}}{{Navarro}
-  et~al.}{1997}]{NFW}
-{Navarro} J.~F.,  {Frenk} C.~S.,    {White} S.~D.~M.,  1997, \apj, 490, 493
-
-\bibitem[\protect\citeauthoryear{{Navarro}, {Ludlow}, {Springel}, {Wang},
-  {Vogelsberger}, {White}, {Jenkins}, {Frenk} \& {Helmi}}{{Navarro}
-  et~al.}{2010}]{Navarro2010}
-{Navarro} J.~F.,  {Ludlow} A.,  {Springel} V.,  {Wang} J.,  {Vogelsberger} M.,
-  {White} S.~D.~M.,  {Jenkins} A.,  {Frenk} C.~S.,    {Helmi} A.,  2010,
-  \mnras, 402, 21
-
-\bibitem[\protect\citeauthoryear{{Neto}, {Gao}, {Bett}, {Cole}, {Navarro},
-  {Frenk}, {White}, {Springel} \& {Jenkins}}{{Neto} et~al.}{2007}]{Neto2007}
-{Neto} A.~F.,  {Gao} L.,  {Bett} P.,  {Cole} S.,  {Navarro} J.~F.,  {Frenk}
-  C.~S.,  {White} S.~D.~M.,  {Springel} V.,    {Jenkins} A.,  2007, \mnras,
-  381, 1450
-
-\bibitem[\protect\citeauthoryear{{Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo}
-  \& {Primack}}{{Prada} et~al.}{2012}]{Prada2012}
-{Prada} F.,  {Klypin} A.~A.,  {Cuesta} A.~J.,  {Betancort-Rijo} J.~E.,
-  {Primack} J.,  2012, \mnras, 423, 3018
-
-\bibitem[\protect\citeauthoryear{{Riebe}, {Partl}, {Enke}, {Forero-Romero},
-  {Gottl{\"o}ber}, {Klypin}, {Lemson}, {Prada}, {Primack}, {Steinmetz} \&
-  {Turchaninov}}{{Riebe} et~al.}{2013}]{2013AN....334..691R}
-{Riebe} K.,  {Partl} A.~M.,  {Enke} H.,  {Forero-Romero} J.,  {Gottl{\"o}ber}
-  S.,  {Klypin} A.,  {Lemson} G.,  {Prada} F.,  {Primack} J.~R.,  {Steinmetz}
-  M.,    {Turchaninov} V.,  2013, Astronomische Nachrichten, 334, 691
-
-\end{thebibliography}
-
 \end{document}

### 2016-06-28 paper/ms.tex
new name
shorter title
ms updated

--- 2016-04-26 paper/paper.tex
@@
 %=========================================================================
-\title{A less biased dark matter halo concentration using the integrated mass profile} 
+\title{A new method to estimate dark matter halo concentrations}
 \author{
@@
 limitation for other methods.   
-We test the performance of this method by estimating halo
-concentration both on mock and N-body halos. 
-We compare these results against two other methods:
+We compare the new algorithm against two other methods:
 maximum radial velocity measurements and radial particle binning.
-Tests on the mock halos show that the accuracy of the new method to
-recover known input concentrations varies with halo resolution,
-outperforming the other two methods. 
-We design another simple test that can be used on any
-data-set to estimate and correct the biases when estimating the
-concentration at low particle numbers. 
-That test shows that the new method is robust with respect to changes
-in halo particle number. 
-However, the velocity method over-predicts concentration values by a
-factor of $25\%$ values for low particle numbers.
-Finally, we also measure the mass-concentration relationship on N-body
-data. 
+Tests on mock and N-body halos show that the accuracy of the new method to
+measure concentrations varies with halo resolution, outperforming the
+other two methods.  
+We also esteimate the mass-concentration relationship on N-body data. 
 We find that in the probed mass range ($10^{10}\hMsun < M_{h} <
@@
 the new method yields lower median concentration values by $25\%$
-compared to the velocity methods; accounting for the bias in the
-velocity method brings the results into agreement.  
-From these results we believe that the new method is a promising tool
+compared to the velocity method; the difference is explained by the bias 
+that the velocity method introduces.
+From these results we believe that this new method is a promising tool
 to probe the internal structure of dark matter halos.
@@
 
-\bibliographystyle{mn2e}
-\bibliography{references}
+\bibliographystyle{apj}
+%\bibliography{references}
+\begin{thebibliography}{12}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Duffy} {et~al.}(2008){Duffy}, {Schaye}, {Kay}, \& {Dalla
+  Vecchia}}]{Duffy2008}
+{Duffy}, A.~R., {Schaye}, J., {Kay}, S.~T., \& {Dalla Vecchia}, C. 2008,
+  \mnras, 390, L64
+
+\bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
+  {Goodman}}]{emcee}
+{Foreman-Mackey}, D., {Hogg}, D.~W., {Lang}, D., \& {Goodman}, J. 2013, \pasp,
+  125, 306
+
+\bibitem[{{Klypin} {et~al.}(2016){Klypin}, {Yepes}, {Gottl{\"o}ber}, {Prada},
+  \& {He{\ss}}}]{Klypin2016}
+{Klypin}, A., {Yepes}, G., {Gottl{\"o}ber}, S., {Prada}, F., \& {He{\ss}}, S.
+  2016, \mnras, 457, 4340
+
+\bibitem[{{Ludlow} {et~al.}(2014){Ludlow}, {Navarro}, {Angulo},
+  {Boylan-Kolchin}, {Springel}, {Frenk}, \& {White}}]{Ludlow2014}
+{Ludlow}, A.~D., {Navarro}, J.~F., {Angulo}, R.~E., {Boylan-Kolchin}, M.,
+  {Springel}, V., {Frenk}, C., \& {White}, S.~D.~M. 2014, \mnras, 441, 378
+
+\bibitem[{{Macci{\`o}} {et~al.}(2008){Macci{\`o}}, {Dutton}, \& {van den
+  Bosch}}]{Maccio2008}
+{Macci{\`o}}, A.~V., {Dutton}, A.~A., \& {van den Bosch}, F.~C. 2008, \mnras,
+  391, 1940
+
+\bibitem[{{More} {et~al.}(2011){More}, {Kravtsov}, {Dalal}, \&
+  {Gottl{\"o}ber}}]{More2011}
+{More}, S., {Kravtsov}, A.~V., {Dalal}, N., \& {Gottl{\"o}ber}, S. 2011, \apjs,
+  195, 4
+
+\bibitem[{{Mu{\~n}oz-Cuartas} {et~al.}(2011){Mu{\~n}oz-Cuartas}, {Macci{\`o}},
+  {Gottl{\"o}ber}, \& {Dutton}}]{Munoz2011}
+{Mu{\~n}oz-Cuartas}, J.~C., {Macci{\`o}}, A.~V., {Gottl{\"o}ber}, S., \&
+  {Dutton}, A.~A. 2011, \mnras, 411, 584
+
+\bibitem[{{Navarro} {et~al.}(1997){Navarro}, {Frenk}, \& {White}}]{NFW}
+{Navarro}, J.~F., {Frenk}, C.~S., \& {White}, S.~D.~M. 1997, \apj, 490, 493
+
+\bibitem[{{Navarro} {et~al.}(2010){Navarro}, {Ludlow}, {Springel}, {Wang},
+  {Vogelsberger}, {White}, {Jenkins}, {Frenk}, \& {Helmi}}]{Navarro2010}
+{Navarro}, J.~F., {Ludlow}, A., {Springel}, V., {Wang}, J., {Vogelsberger}, M.,
+  {White}, S.~D.~M., {Jenkins}, A., {Frenk}, C.~S., \& {Helmi}, A. 2010,
+  \mnras, 402, 21
+
+\bibitem[{{Neto} {et~al.}(2007){Neto}, {Gao}, {Bett}, {Cole}, {Navarro},
+  {Frenk}, {White}, {Springel}, \& {Jenkins}}]{Neto2007}
+{Neto}, A.~F., {Gao}, L., {Bett}, P., {Cole}, S., {Navarro}, J.~F., {Frenk},
+  C.~S., {White}, S.~D.~M., {Springel}, V., \& {Jenkins}, A. 2007, \mnras, 381,
+  1450
+
+\bibitem[{{Prada} {et~al.}(2012){Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo},
+  \& {Primack}}]{Prada2012}
+{Prada}, F., {Klypin}, A.~A., {Cuesta}, A.~J., {Betancort-Rijo}, J.~E., \&
+  {Primack}, J. 2012, \mnras, 423, 3018
+
+\bibitem[{{Riebe} {et~al.}(2013){Riebe}, {Partl}, {Enke}, {Forero-Romero},
+  {Gottl{\"o}ber}, {Klypin}, {Lemson}, {Prada}, {Primack}, {Steinmetz}, \&
+  {Turchaninov}}]{2013AN....334..691R}
+{Riebe}, K., {Partl}, A.~M., {Enke}, H., {Forero-Romero}, J., {Gottl{\"o}ber},
+  S., {Klypin}, A., {Lemson}, G., {Prada}, F., {Primack}, J.~R., {Steinmetz},
+  M., \& {Turchaninov}, V. 2013, Astronomische Nachrichten, 334, 691
+
+\end{thebibliography}
 

### 2016-07-04 paper/ms.tex
new title new perspective
new plot in ms
new abstract

@@
 %=========================================================================
-\title{A new method to estimate dark matter halo concentrations}
+\title{Finding and controling biases in dark matter halo concentrations estimates}
 \author{
@@
 \begin{abstract}
-We present a new algorithm to estimate the concentration of N-body
-dark matter halos using the integrated mass profile.
+We present a jacknife method to estimate the bias on the estimated
+concentration values as a function of particle number in the halo. 
+We find that algorithms based on the maximum radial velocity
+and radial particle binning show similar biases,
+overestimating concentrations by a factor of $15\%-20\%$ for
+halos sampled with $200$ particles.  
+To overcome this bias we propose a new concentration estimation
+algorithm that uses the integrated mass profile.
 The method uses the full particle information without any binning,
 making it reliable in cases when low numerical resolution becomes a
-limitation for other methods.   
-We compare the new algorithm against two other methods:
-maximum radial velocity measurements and radial particle binning.
-Tests on mock and N-body halos show that the accuracy of the new method to
-measure concentrations varies with halo resolution, outperforming the
-other two methods.  
-We also esteimate the mass-concentration relationship on N-body data. 
-We find that in the probed mass range ($10^{10}\hMsun < M_{h} <
-10^{14}\hMsun$) the three methods give consistent results within the
-statistical uncertainties.   
-There is a small deviation at low masses, $M<10^{12}\hMsun$, where
-the new method yields lower median concentration values by $25\%$
-compared to the velocity method; the difference is explained by the bias 
-that the velocity method introduces.
-From these results we believe that this new method is a promising tool
-to probe the internal structure of dark matter halos.
+limitation for other methods, reducing the bias to $2\%-3\%$ for halos
+sampled with $200$ particles. 
+To keep the biases of the velocity and density methods to the same
+low levels, dark matter halos should be sampled with at least $\sim
+1000$ particles.
+We also find that the mass-concentration relationship could be
+shallower than expected from numerical experiments that do not take
+into account this bias. 
+From these results we believe that jacknife downsampling and the
+concentration estimate based on the integral mass densities are
+promising tools to probe the internal structure of dark matter halos
+in numerical simulations.
 \end{abstract}
@@
 
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{avg_foff_bolshoi.pdf}
+  \includegraphics[width=0.48\textwidth]{avg_foff_vialactea.pdf}
+\end{center}
+\vspace{-0.5cm}
+\caption{Average value of the fractional offset ($f_{\rm
+    off}$Eq. \ref{eq:f_off}) between the concentration in a halo at
+  high resolution versus its downsampled versions.  Each point is the
+  result of 100 downsampling iterations.  The velocity method
+  noticeably overestimates the concentration up to a factor of $0.25$,
+  while the new method only underestimates the concentrations by up to
+  a factor of $0.05$.
+    \label{fig:downsampling}}
+\end{figure*}
+
 \subsection{Our proposal: estimate from the integrated mass profile}
@@
 different particle numbers.
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.49\textwidth]{avg_foff_bolshoi.pdf}
-\end{center}
-\vspace{-0.5cm}
-\caption{Average value of the fractional offset ($f_{\rm
-    off}$Eq. \ref{eq:f_off}) between the concentration in a halo at
-  high resolution versus its downsampled versions.  Each point is the
-  result of 100 downsampling iterations.  The velocity method
-  noticeably overestimates the concentration up to a factor of $0.25$,
-  while the new method only underestimates the concentrations by up to
-  a factor of $0.05$.
-    \label{fig:downsampling}}
-\end{figure}
 

### 2016-07-04 paper/ms.tex
new references , new order

--- 2016-04-26 paper/paper.tex
@@
 %=========================================================================
-\title{A less biased dark matter halo concentration using the integrated mass profile} 
+\title{Finding and controling biases in dark matter halo concentrations estimates}
 \author{
@@
 \begin{abstract}
-We present a new algorithm to estimate the concentration of N-body
-dark matter halos using the integrated mass profile.
+We use bootstrapping to estimate the bias of concentration
+estimates on N-body dark matter halos as a function of particle
+number. 
+We find that algorithms based on the maximum radial velocity
+and radial particle binning have increaing biases with decreasing 
+particle numbers.
+For instance, these methods overestimate concentrations by 
+$15\%-20\%$ for halos sampled with $200$ particles.  
+To overcome this bias we propose a new algorithm based on the
+integrated mass profile. 
 The method uses the full particle information without any binning,
@@
 limitation for other methods.
-We test the performance of this method by estimating halo
-concentration both on mock and N-body halos. 
-We compare these results against two other methods:
-maximum radial velocity measurements and radial particle binning.
-Tests on the mock halos show that the accuracy of the new method to
-recover known input concentrations varies with halo resolution,
-outperforming the other two methods. 
-We design another simple test that can be used on any
-data-set to estimate and correct the biases when estimating the
-concentration at low particle numbers. 
-That test shows that the new method is robust with respect to changes
-in halo particle number. 
-However, the velocity method over-predicts concentration values by a
-factor of $25\%$ values for low particle numbers.
-Finally, we also measure the mass-concentration relationship on N-body
-data. 
-We find that in the probed mass range ($10^{10}\hMsun < M_{h} <
-10^{14}\hMsun$) the three methods give consistent results within the
-statistical uncertainties.   
-There is a small deviation at low masses, $M<10^{12}\hMsun$, where
-the new method yields lower median concentration values by $25\%$
-compared to the velocity methods; accounting for the bias in the
-velocity method brings the results into agreement.  
-From these results we believe that the new method is a promising tool
-to probe the internal structure of dark matter halos.
+This method reduces the bias to $2\%-3\%$ for halos sampled with
+$200$ particles.  
+To keep the biases of the velocity and density methods to the same
+low levels as in the new method, dark matter halos should be sampled
+with at least $\sim 2000$ particles. 
+We also show that the mass-concentration relationship could be
+shallower than expected from numerical experiments once the biases 
+of the different concentration measurements are taken into account.
+From these results we believe that bootstrapping and the
+concentration estimation based on the integrated mass are
+valuable tools to probe the internal structure of dark matter halos
+in numerical simulations.
 \end{abstract}
@@
 spherically symmetric; the density only depends on the radial
-coordinate.  One {\bf of} the most popular radial parameterizations is
-the Navarro-Frenk-White (NFW) profile \citep{NFW}.  If one is not
-interested in the very central region of the dark matter halo (where
+coordinate.  One of the most popular radial parameterizations is
+the Navarro-Frenk-White (NFW) profile \citep{NFW}.  
+This profile can be considered as universal \citep{Navarro2010}, assuming that 
+one is not interested in the very central region of the dark matter halo where
 galaxy formation takes place, and where the effects of baryon physics
-on dark matter distribution are still unknown) one can also assume
-that this profile is universal.  \citep{Navarro2010}.  This profile is
-a double power law in radius, where the transition break happens at
-the so-called scale radius, $r_s$.  The ratio between the scale radius
-and the halo virial radius $R_v$ is known as the concentration
-$c=R_v/r_s$.
+on dark matter distribution are still unknown.
+This profile is a double power law in radius, where the transition
+break happens at the so-called scale radius, $r_s$.  The ratio between
+the scale radius and the halo virial radius $R_v$ is known as the
+concentration $c=R_v/r_s$.
 
@@
 order to have a proper density estimate in each bin.  This makes the
-method robust only for halos with at least $10^3$ particles.  The
+method robust only for halos with at least $10^2$ particles.  The
 second problem is that there is not a way to estimate the optimal
@@
 
-The second method solves the two problems mentioned above.  It works
-with low particle numbers and does not involve data binning.  However,
+The second method solves the two problems mentioned above.  
+It works with low particle numbers and does not involve data binning.  
+However,
 it effectively takes into account only a single data point and
 discards the behavior of the ratio $V_{\rm circ}/V_{\rm vir}$ below
-and above its maxima.  Small fluctuations on the value of this maximum
+and above its maxima.  
+Small fluctuations on the value of this maximum
 can yield large perturbations on the estimated concentration
@@
 In this paper we present a third alternative based on fitting the
-integrated mass profile.  This approach has two advantages with
-respect to the above mentioned methods.  It does not involve any data
-binning and does not throw away data points.  This translates into a
-robust estimate even at low resolution/particle numbers.  Furthermore,
-since the method does not require any binning, there is no need to
-tune numerical parameters.  This method provides a new independent
-method to estimate the concentration parameter.  Here we provide a
-detailed description of the method and a comparison against the two
-traditional techniques by measuring its performance both on mock and
-N-body halos.
+integrated mass profile.  
+This approach has two advantages with respect to the above mentioned methods.  
+It does not involve any data binning and does not throw away data points.  
+This translates into a robust estimate even at low resolution/particle numbers.  
+Furthermore, since the method does not require any binning, there is no need to
+tune numerical parameters.   
+This method provides a new independent method to estimate the
+concentration parameter.
+
+In order to asses the quality of the three different methods we use
+bootstraping on halos that are sampled with $10^{5}$ particles.
+This allows us to estimate the bias and standard deviation on the
+concentration estimates as a function of particle number.
 
@@
 Simulation Suite.
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{avg_foff_bolshoi.pdf}
+  \includegraphics[width=0.48\textwidth]{avg_foff_vialactea.pdf}
+\end{center}
+\vspace{-0.5cm}
+\caption{Average value of the fractional offset ($f_{\rm
+    off}$Eq. \ref{eq:f_off}) between the concentration in a halo at
+  high resolution versus its downsampled versions.  Each point is the
+  result of 100 downsampling iterations.  The velocity method
+  noticeably overestimates the concentration up to a factor of $0.25$,
+  while the new method only underestimates the concentrations by up to
+  a factor of $0.05$.
+    \label{fig:downsampling}}
+\end{figure*}
 
@@
 \begin{center}
-  \includegraphics[width=0.49\textwidth]{avg_foff_bolshoi.pdf}
-\end{center}
-\vspace{-0.5cm}
-\caption{Average value of the fractional offset ($f_{\rm
-    off}$Eq. \ref{eq:f_off}) between the concentration in a halo at
-  high resolution versus its downsampled versions.  Each point is the
-  result of 100 downsampling iterations.  The velocity method
-  noticeably overestimates the concentration up to a factor of $0.25$,
-  while the new method only underestimates the concentrations by up to
-  a factor of $0.05$.
-    \label{fig:downsampling}}
-\end{figure}
-
-\begin{figure}
-\begin{center}
   \includegraphics[width=0.47\textwidth]{error_conc_bolshoi.pdf}
@@
 non-linear evolution of a dark matter density field sampled with
-$2048^3$ particles over a cubic box of $250\ \hMpc$ on a side.  The
+$2048^3$ particles over a cubic box of $250\ \hMpc$ on a side.  
+The cosmological parameters use a Hubble parameter $h=0.73$, a matter density
+$\Omega_m=0.3071$ and a normalization of the power spectrum
+$\sigma_8=0.82$. 
+The
 data is publicly available at \url{http://www.cosmosim.org/}.  More
@@
 
-\subsubsection{Convergence Test using Downsampling}
+We also use public data from the Via Lactea simulation project
+\citep{2008Natur.454..735D}.  
+This simulation was run for a single isolated halo with a virial mass
+of the order of $10^{12}$\hMsun using the parallel tree code PKDGRAV
+\citep{2001PhDT........21S}.  
+The simulation used $\sim 2\times 10^{8}$ particles to resolve this
+region.
+The cosmological parameters are diffferent from those in the Bolshoi
+simulation, with a Hubble parameter $h=0.73$, a matter density
+$\Omega_m=0.238$ and a normalization of the power spectrum
+$\sigma_8=0.74$. 
+The data available to the public corresponds to a downsampled set 
+of $10^5$ particles which corresponds to a particle mass of
+$2.24\times 10^{7}$\hMsun.
 
-We perform first a convergence test on the N-body data to find
-possible biases in the concentration estimates as a function of
-particle number.  
-We select $8$ halos from the simulation that have at
-least $3\times 10^5$ particles.  
-We then randomly downsample the total number of particles in each halo
-by factors of $10, 20, 45, 100, 215, 460, 1000$ to measure its
-concentration with both the integrated mass and the velocity
-method. For each downsampling factor we repeat the operation $100$
-times.
+We use a set of two very different simulations to demonstrate that the 
+results of our bootstraping tests are independent of the kind of
+parent simulation.
+
+\section{Bootstrapping to estimate biases}
+\label{sec:bootstrapping}
+
+Avoiding biases with varying simulation resolution is one of the most
+important goals of a robust method to estimate halo concentration. 
+We propose bootstraping individual high resolution halos to quantify these
+possible biases.
+In this experiment we take halos sampled with at least $10^{5}$
+particles and subsample each halo by factors of $2$ up to $10^{3}$ to
+measure the concentration every time the halo is resampled.
 
@@
 downsampled particle number $c_{N}$ and the baseline $c_{N_{max}}$.
+
+We select $8$ halos from the simulation that have at
+least $3\times 10^5$ particles.  
+We then randomly downsample the total number of particles in each halo
+by factors of $10, 20, 45, 100, 215, 460, 1000$ to measure its
+concentration with both the integrated mass and the velocity
+method. For each downsampling factor we repeat the operation $100$
+times.
 
@@
 
-\bibliographystyle{mn2e}
+\bibliographystyle{apj}
 \bibliography{references}

### 2016-07-05 data/results/mock/mock_100/error.py
removing unused code

@@ -1,104 +1,0 @@
-import numpy as np, pylab
-
-vlct = np.loadtxt('velocity/table.csv',delimiter=',')
-mass = np.loadtxt('newMass/table.csv',delimiter=',')
-dens = np.loadtxt('newDensity/table.csv',delimiter=',')
-
-orig = vlct[:,0]
-gtt = [int(x) for x in np.argwhere(orig >=3)]
-
-vlct = vlct[gtt]
-mass = mass[gtt]
-dens = dens[gtt]
-
-orig = vlct[:,0]
-def chi2(x_obs,x_org):
-    return np.sum(np.abs((x_obs-x_org)/x_org))/len(x_obs)
-
-def best_fit(original,results):
-    ans = np.empty(len(original))
-    for i in range(len(original)):
-        concentrations = results[i,:]
-        index = np.argmin(np.abs(original[i]-concentrations))
-        ans[i] = concentrations[index]
-    return ans
-
-pylab.title('$Velocity$')
-pylab.plot(orig,orig,'--k',label='$real$')
-#pylab.plot(orig,vlct[:,1],'.b',label='$n=20$')
-#pylab.plot(orig,vlct[:,2],'.r',label='$n=200$')
-#pylab.plot(orig,vlct[:,3],'.g',label='$n=2000$')
-#pylab.plot(orig,vlct[:,4],'.c',label='$n=20000$')
-pylab.plot(orig,best_fit(orig,vlct[:,1:5]),'-r',label='$best\ fit$')
-pylab.xlabel('$\mathrm{Original}$')
-pylab.ylabel('$\mathrm{Obtained}$')
-pylab.legend(loc=4, borderaxespad=0.5)
-pylab.savefig('vlct.png',dpi=300)
-pylab.close()
-
-
-chi_vlct = np.array([chi2(orig,vlct[:,1]),chi2(orig,vlct[:,2]),chi2(orig,vlct[:,3]),chi2(orig,vlct[:,4])])
-
-orig = mass[:,0]
-
-pylab.title('$Mass$')
-pylab.plot(orig,orig,'--k',label='$real$')
-#pylab.plot(orig,mass[:,1],'.',label='$n=20$',)
-#pylab.plot(orig,mass[:,2],'.',label='$n=200$')
-#pylab.plot(orig,mass[:,3],'.',label='$n=2000$',)
[…]

### 2016-07-05 data/results/jc/compare.py
removing unused data

@@ -1,116 +1,0 @@
-import numpy as np, pylab,sys
-
-dm =  3.41454E10
-
-def get_stats(log_mass,conc):
-
-    bins = np.arange(0,np.amax(log_mass)+0.5,0.25)
-    bins_index = np.digitize(log_mass,bins)
-    median = np.empty(len(bins))
-    quar1 = np.empty(len(bins))
-    quar2 = np.empty(len(bins))
-
-    for i in range(len(bins)):
-        tempo = []
-        for j in range(len(bins_index)):
-            if (i == bins_index[j]):
-                tempo.append(conc[j])
-        tempo = np.array(tempo)
-        if (tempo.size):
-            median[i] = np.median(tempo)
-            quar1[i],quar2[i] = np.percentile(tempo,[25,75])
-        else:
-            median[i],quar1[i],quar2[i]=0,0,0
-    return bins,median,quar1,quar2
-
-mcmc = np.genfromtxt(sys.argv[1],delimiter=',')
-vel = np.genfromtxt(sys.argv[2],delimiter=',')
-dens = np.genfromtxt(sys.argv[3],delimiter=',')
-
-index = [int(x) for x in np.argwhere(dens[:,1] > 100)]
-
-id_mcmc = mcmc[:,0][index]
-id_dens = dens[:,0][index]
-
-c_mcmc = mcmc[:,2][index]
-c_vel = vel[:,1][index]
-c_dens = (dens[:,3]/dens[:,4])[index]
-
-m_mcmc = dens[:,2][index]
-m_vel = dens[:,2][index]
-m_dens = dens[:,2][index]
-
-
-
-bins_mcmc,median_mcmc,quar1_mcmc,quar2_mcmc = get_stats(np.log10(m_mcmc),c_mcmc)
-bins_vel,median_vel,quar1_vel,quar2_vel = get_stats(np.log10(m_vel),c_vel)
-bins_dens,median_dens,quar1_dens,quar2_dens = get_stats(np.log10(m_dens),c_dens)
-
-
-fig, ax1 = pylab.subplots()
-
-ax1.plot(10**(bins_dens)*dm,median_dens,'-g',lw=2,label='$\mathrm{Density\ Method}$')
[…]

### 2016-07-05 paper/ms.tex
new structure

@@
 
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.49\textwidth]{avg_foff_bolshoi.pdf}
+  \includegraphics[width=0.48\textwidth]{sigma_foff_bolshoi.pdf}
+\end{center}
+\vspace{-0.5cm}
+\caption{Average value of the fractional offset ($f_{\rm
+    off}$Eq. \ref{eq:f_off}) between the concentration in a halo at
+  high resolution versus its downsampled versions.  Each point is the
+  result of 100 downsampling iterations.  The velocity method
+  noticeably overestimates the concentration up to a factor of $0.25$,
+  while the new method only underestimates the concentrations by up to
+  a factor of $0.05$.
+Uncertainties on different concentration estimates.  The
+  large symbols show the standard deviation of the fractional offset
+  ($f_{\rm off}$ as defined in Eq. \ref{eq:f_off}) from the downsampling
+  experiments.  The small dots correspond to the $1\sigma$
+  uncertainty on the concentration for each halo as estimated by the
+  MCMC algorithm used for the new method.
+  The solid lines shows the $1/N$ tendency, which also corresponds
+  to the particle number dependence of the $\langle|D|\rangle$ statistic
+  (i.e. the accuracy to retrieve a known concentration in mock halos)
+  of the new method.
+  Uncertainties due to particle number fluctuations are always larger
+  than the statistical uncertainties from the fitting process. 
+    \label{fig:downsampling}}
+\end{figure*}
+
 \section{Methods to estimate the concentration from N-body simulations}
@@
 
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{avg_foff_bolshoi.pdf}
-  \includegraphics[width=0.48\textwidth]{avg_foff_vialactea.pdf}
-\end{center}
-\vspace{-0.5cm}
-\caption{Average value of the fractional offset ($f_{\rm
-    off}$Eq. \ref{eq:f_off}) between the concentration in a halo at
-  high resolution versus its downsampled versions.  Each point is the
-  result of 100 downsampling iterations.  The velocity method
-  noticeably overestimates the concentration up to a factor of $0.25$,
-  while the new method only underestimates the concentrations by up to
-  a factor of $0.05$.
-    \label{fig:downsampling}}
-\end{figure*}
-
 \subsection{Our proposal: estimate from the integrated mass profile}
@@
 Invariant Markov Chain Monte Carlo implemented in the python module
-{\em emcee} \citep{emcee} to sample the likelihood function
+{\texttt{emcee}} \citep{emcee} to sample the likelihood function
 distribution defined by ${\cal L}(c)\propto \exp(-\chi^2(c)/2)$ where
@@
 
-\section{Results}
-\label{sec:results}
-
-We apply the three methods mentioned above on two different halo
-samples.  The first sample is composed by mock halos generated to have
-known concentration values in perfect spherical symmetry following an
-NFW profile.  Using this sample we quantify the ability to recover the
-expected concentration as a function of particle number.  The second
-sample comes from a publicly available N-body cosmological simulation
-to test the new method on more realistic and complex data to show the
-impact on the mass-concentration relationship.
-
-\subsection{Retrieving known concentrations from a mock halo sample}
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.50\textwidth]{error.pdf}
-\end{center}
-\vspace{-0.5cm}
-\caption{Average value of the relative error in the concentration
-  estimate, $\avg{|D|}$, as a function of the particle number in
-  the set of mock halos. Different symbols represent different
-  methods. The new method provides the most accurate estimate at fixed
-  particle number.
-    \label{fig:error}}
-\end{figure}
-
-The method we use to generate the mock halos is based on the
-integrated mass profile.  We start by fixing the desired concentration
-$c$ and total number of particles $N$ in the mock halo.  With these
-values we define the mass element as $\delta m = 1/M$, corresponding
-to the mass of each particle such that the total mass is one.  Then
-for each particle, $i=1,\ldots,N$, we find the value of $r_i$ such
-that the difference
-% 
-\begin{equation}
-m(<r_i;c) - i \cdot \delta m
-\end{equation}
-%
-is zero using Ridders' method.
-
-The value of $r_i$ is the radius of the $i$-th particle of the mock
-halo.  Then we generate random polar and azimuthal angles $\theta$ and
-$\phi$ for each particle to ensure spherical symmetry.  Finally these
-three spherical coordinates are transformed into Cartesian coordinates
-$(r,\theta,\phi) \rightarrow (x,y,z)$.
-
-We generate in total $400$ mock halos split into four different groups
-of $100$ halos each.  The four groups differ in the total number of
-particles for their halos: $20$, $200$, $2000$ and $20000$.  Inside
-each group the halos have random concentration values in the range
-$1<c<20$ with a uniform distribution.  We find the concentration
-values for all these halos using the density, velocity and integrated
-mass methods described in the previous section.
-
-We quantify the difference between the expected $c_{in}$ and measured
-$c_{out}$ values by
-%
-\begin{equation}
-D= c_{out}/c_{in}-1,
-\label{eq:D}
-\end{equation}
-%
-and
-%
-\begin{equation}
-\avg{|D|}=\frac{1}{\left|{\cal{H}}\right|}\sum_{{\cal{H}}} |D|,
-\end{equation}
-%
-where ${\cal{H}}$ corresponds to a set of mock halos, and
-$\left|{\cal{H}}\right|$ is the number of haloes in ${\cal{H}}$.  A
-large discrepancy between the estimated and input concentrations are
-quantified by a large $\avg{|D|}$.
-
-Figure \ref{fig:error} shows the behaviour of $\avg{|D|}$ as a
-function of halo particle number for the three different methods.
-
-At fixed particle numbers the new method always shows the lowest
-$\avg{|D|}$ values compared to the other two.  Its accuracy is on the
-order of $10\%$ for $20$ particles in the halo, decreasing to $0.01\%$
-for halos with $20000$ particles.  The dependence of $\avg{|D|}$ with
-the particle number $N$ goes approximately as $\avg{|D|}\propto
-N^{-1}$.
-
-The method based on the maximum of the circular velocity shows a
-similar behaviour with $\avg{|D|}\propto N^{-1/3}$.  Its accuracy is
-$2-5$ times lower than in the new method, on the order of $20\%$ for
-$20$ particle halos and $0.5\%$ for $20000$ particle halos.  The
-method based on the direct density fit shows the lowest accuracy for a
-low particle number.  As it is discussed in \citep{Munoz2011}, density
-binning for halos with particle numbers below $\sim200$ leads to a
-biased estimation of the mass density profile, and therefore to a
-biased estimation of the concentration parameter.  This behaviour is
-evident in the large values of $\avg{|D|}$ for halos with number of
-particles below $\sim 200$ and an intermediate accuracy between the
-other two methods for a high particle number.
-
-We also find that the bias from different concentrations at fixed
-particle number is negligible with respect to the effects induced by
-different particle numbers.
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.47\textwidth]{error_conc_bolshoi.pdf}
-\end{center}
-\vspace{-0.5cm}
-\caption{Uncertainties on different concentration estimates.  The
-  large symbols show the standard deviation of the fractional offset
-  ($f_{\rm off}$ as defined in Eq. \ref{eq:f_off}) from the downsampling
-  experiments.  The small dots correspond to the $1\sigma$
-  uncertainty on the concentration for each halo as estimated by the
-  MCMC algorithm used for the new method.
-  The solid lines shows the $1/N$ tendency, which also corresponds
-  to the particle number dependence of the $\langle|D|\rangle$ statistic
-  (i.e. the accuracy to retrieve a known concentration in mock halos)
-  of the new method.
-  Uncertainties due to particle number fluctuations are always larger
-  than the statistical uncertainties from the fitting process. 
-  \label{fig:downsampling_err}}
-\end{figure}
-
-\subsection{Measuring the concentration in halos from a cosmological simulation}
-\label{subsec:cosmo}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.49\textwidth]{concentration_bolshoi.pdf}
-  \includegraphics[width=0.49\textwidth]{concentration_bolshoi_corrected.pdf}
-\end{center}
-\vspace{-0.5cm}
-\caption{Mass-concentration relationship for the three different
-  methods used on the same cosmological N-body data.  All halos are
-  used regardless of their relaxation state.  The lines correspond to
-  the median concentration values in each mass bin.  The shaded region
-  presents 10 and 90 per cent spread.  For clarity we only show the
-  spread for the concentrations estimated using the new method. The
-  other two methods have a similar spread. The dotted line corresponds
-  to fits reported by \citep{Prada2012}.
-  \label{fig:concentration}. The left panel shows the raw results
-  coming from each algorithm. The right panel introduces a
-  correction on the velocity and integrated mass results. 
-  The corrections depends on the number of particles following the
-  results of the downsampling experiments presented in Figure
-  \ref{fig:downsampling}.} 
-\end{figure*}
-
-The results presented in the previous section show that in an
-idealized setup (pure NFW density profiles, perfect spherical halos in
-total isolation) the new method performs better than the other two
-methods commonly used in the literature.
-
-However, simulated dark matter halos in a cosmological context are
-complex.  They are not isolated, many of them experience mergers that
-take them out of the equilibrium.  Halos may have also plenty of
-substructure.  All these effects disturb the mass density profile,
-taking it away from the ideal NFW profile.  In order to explore the
-performance of the new method in this setting, we use it to estimate
-the concentration parameter in dark matter halos obtained from a
-cosmological N-body simulation and compare it with the other two
-classical methods.
+\section{Numerical Simulations and Halo Samples}
 
@@
 
-\section{Bootstrapping to estimate biases}
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.49\textwidth]{concentration_bolshoi.pdf}
+  \includegraphics[width=0.49\textwidth]{concentration_bolshoi_corrected.pdf}
+\end{center}
+\vspace{-0.5cm}
+\caption{Mass-concentration relationship for the three different
+  methods used on the same cosmological N-body data.  All halos are
+  used regardless of their relaxation state.  The lines correspond to
+  the median concentration values in each mass bin.  The shaded region
+  presents 10 and 90 per cent spread.  For clarity we only show the
+  spread for the concentrations estimated using the new method. The
+  other two methods have a similar spread. The dotted line corresponds
+  to fits reported by \citep{Prada2012}.
+  \label{fig:concentration}. The left panel shows the raw results
+  coming from each algorithm. The right panel introduces a
+  correction on the velocity and integrated mass results. 
+  The corrections depends on the number of particles following the
+  results of the downsampling experiments presented in Figure
+  \ref{fig:downsampling}.} 
+\end{figure*}
+
+\section{Results}
+\label{sec:results}
+
+\subsection{Bootstrapping to estimate biases}
 \label{sec:bootstrapping}
@@
 
-\subsubsection{Mass-Concentration Relationship}
+\subsection{Impact on the Mass-Concentration Relationship}
 

### 2016-07-05 paper/ms.tex
restructure conclusions

@@
 
-Avoiding biases with varying simulation resolution is one of the most
-important goals of a robust method to estimate halo concentration. 
-We propose bootstraping individual high resolution halos to quantify these
-possible biases.
+We use bootstraping of individual high resolution halos to quantify
+biases for different methods used to esteimate concentrations.
+
 In this experiment we take halos sampled with at least $10^{5}$
@@
 
-In this paper we presented a new method to estimate the concentration
-of dark matter halos in N-body simulations.  We tested the method on
-mock halo data to study the impact of total number of particles and
-input concentration on the retrieved values.  We compared these
-results against two other methods commonly used in the literature to
-estimate concentrations.  For all methods, the accuracy in retrieving
-the input concentration increases with the number of particles as
-summarized in Figure \ref{fig:error}.  The new method systematically
-outperforms the other two.
+In this paper we used bootstrapping on dark matter halos resolved with a
+large number of particles ($\sim 10^5$) in order to quantify biases on
+concentration estimates. 
+We found that methods commonly used in the literature present a large
+bias in the concentration by overestimating it by factors of
+$15\%-20\%$ for halos with $200$ particles. 
+The scaling of the bias as a function of particle number was found in
+two very different kinds of simulations, one cosmological and the
+other of an individual high resolution halo, suggesting its universal
+nature.
 
-We also applied the method to halos extracted from a cosmological
-N-body simulation.  Using this data we showed that the new method is
-robust with respect to a decreasing number of particles in the halos.
-On the other hand we showed that the velocity method has a systematic
-bias that overestimates the concentration for halos with a low particle
-number up to a factor of $25\%$.
+This provided a motivation to introduce a new method to estimate the
+concentration that shows a lower bias.
+The method is based on the integrated mass profile. 
+We also implemented a fitting procedure based on a Markov Chain Monte Carlo
+algorithm.
+In the bootstrapping experiment this method showed a bias on the order
+of $2\%-3\%$ for halos with $200$ particles.
 
@@
 a way to use it to make corrections on the estimates.
-In Section \ref{subsec:cosmo} we presented a simple method that can be used on any
-dataset to estimate the errors and correct them when estimating the
-concentration at low particle numbers.
 

### 2016-07-06 paper/ms.tex
rewriting the conclusions

@@
 
-In this paper we used bootstrapping on dark matter halos resolved with a
-large number of particles ($\sim 10^5$) in order to quantify biases on
-concentration estimates. 
+In this paper we quantified biases on concentration numerical estimates by
+bootstrapping dark matter halos resolved with a  large number of
+particles ($\sim 10^5$).
 We found that methods commonly used in the literature present a large
 bias in the concentration by overestimating it by factors of
-$15\%-20\%$ for halos with $200$ particles. 
-The scaling of the bias as a function of particle number was found in
+$15\%$-$20\%$ for halos with $200$ particles, or $6\%$-$8\%$ for halos
+with $500$ particles. 
+This procedure is a new way to quantify the bias in concentration
+estimates.
+
+The scaling of the bias as a function of particle number was found using
 two very different kinds of simulations, one cosmological and the
-other of an individual high resolution halo, suggesting its universal
-nature.
+other of an individual high resolution halo.
 
-This provided a motivation to introduce a new method to estimate the
-concentration that shows a lower bias.
-The method is based on the integrated mass profile. 
-We also implemented a fitting procedure based on a Markov Chain Monte Carlo
-algorithm.
+This results motivated the introduction of a new method to estimate the
+concentration with a lower bias at low particle numbers.
+The method we presented is based on the integrated mass profile. 
+To show its performance on simulation data Ww also implemented a
+fitting procedure based on a Markov Chain Monte Carlo algorithm.
 In the bootstrapping experiment this method showed a bias on the order
-of $2\%-3\%$ for halos with $200$ particles.
-
-We provide for the first time in the literature a direct way to
-measure the bias in the estimated halo concentration at low particle numbers and
-a way to use it to make corrections on the estimates.
+of $2\%-3\%$ for halos with $200$ particles and less than $1\%$ for
+halos with $500$ particles or more.
 
 We also used the N-body simulation to estimate the impact on the mass
-concentration relationship.  
+concentration relationship of the new method to estimate
+concentration.   
 Although the three methods are in broad agreement within their

### 2016-07-06 paper/ms.tex
reformulando conclusiones

@@
 datasets to show that similar systematic offsets are present.
-However, to the best of our knowledge, a systematic and modern study of
-the mass-concentration relationship spanning a wide range in mass,
-using a fixed dataset but different fitting methods has not been
-presented in the literature.
+\citep{2014MNRAS.441.3359D} studied the mass-concentration
+relationship using the maximum velocity and density methods and did
+not report any significant difference. However, they implemented a
+modified version of the velocity algorithm that uses the data binning
+obtained for the density algorithm.
 
@@
 We found that methods commonly used in the literature present a large
-bias in the concentration by overestimating it by factors of
-$15\%$-$20\%$ for halos with $200$ particles, or $6\%$-$8\%$ for halos
-with $500$ particles. 
+bias by overestimating concentrations by factors of $13\%$-$20\%$ for
+halos with $200$ particles, or $7\%$-$10\%$ for halos with $500$
+particles.  
 This procedure is a new way to quantify the bias in concentration
-estimates.
+estimates with the advantage that it works without having to run new
+simulations.
 
-The scaling of the bias as a function of particle number was found using
-two very different kinds of simulations, one cosmological and the
-other of an individual high resolution halo.
+These results motivated us to introduction a method with a robust
+performace at low particle numbers.
+This method is based on the integrated mass profile. 
+The results of the algorithm on the same data sample showed a bias  of
+$2\%-3\%$ for halos with $200$ particles and less than $1\%$ for halos
+with $500$ particles or more.
 
-This results motivated the introduction of a new method to estimate the
-concentration with a lower bias at low particle numbers.
-The method we presented is based on the integrated mass profile. 
-To show its performance on simulation data Ww also implemented a
-fitting procedure based on a Markov Chain Monte Carlo algorithm.
-In the bootstrapping experiment this method showed a bias on the order
-of $2\%-3\%$ for halos with $200$ particles and less than $1\%$ for
-halos with $500$ particles or more.
-
-We also used the N-body simulation to estimate the impact on the mass
-concentration relationship of the new method to estimate
-concentration.   
-Although the three methods are in broad agreement within their
-uncertainties there are some noticeable differences.  
+We also measured the mass concentration relationship. 
+The three methods are in broad agreement within the statistical
+uncertainties, although there are some noticeable differences.
 The first difference is that the density method produces
@@
 the velocity method.
-This systematic offset has been reported in different datasets and
-techniques to measure concentrations, without any conclusive
-explanation for its origin \citep{Klypin2016}.
+This systematic offset has been reported before with the same dataset 
+\citep{Prada2012} and with different simulations \citep{Klypin2016}
+without any conclusive explanation for its origin. 
 The second difference is that the velocity and integrated mass methods
 start to differ for masses below $10^{12}\hMsun$.  
-We found that a correction of the results by the bias factor found
-using the same N-body data can bring these two methods into
-agreement.
+We found that correcting the mean concentration by the mean bias
+factor brings these two techniques into agreement
 
-These are encouraging results.  
-They show that using the integrated mass profile to find the Dark
-Matter halo concentration is a tool deserving deeper scrutiny.  
+These results show that using the integrated mass profile to find the
+Dark Matter halo concentration is a tool deserving deeper scrutiny.   
 Further tests with larger simulated volumes, varying numerical
@@
 \bibliographystyle{apj}
-\bibliography{references}
+%\bibliography{references}
+\begin{thebibliography}{15}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Diemand} {et~al.}(2008){Diemand}, {Kuhlen}, {Madau}, {Zemp},
+  {Moore}, {Potter}, \& {Stadel}}]{2008Natur.454..735D}
+{Diemand}, J., {Kuhlen}, M., {Madau}, P., {Zemp}, M., {Moore}, B., {Potter},
+  D., \& {Stadel}, J. 2008, \nat, 454, 735
+
+\bibitem[{{Duffy} {et~al.}(2008){Duffy}, {Schaye}, {Kay}, \& {Dalla
+  Vecchia}}]{Duffy2008}
+{Duffy}, A.~R., {Schaye}, J., {Kay}, S.~T., \& {Dalla Vecchia}, C. 2008,
+  \mnras, 390, L64
+
+\bibitem[{{Dutton} \& {Macci{\`o}}(2014)}]{2014MNRAS.441.3359D}
+{Dutton}, A.~A., \& {Macci{\`o}}, A.~V. 2014, \mnras, 441, 3359
+
+\bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
+  {Goodman}}]{emcee}
+{Foreman-Mackey}, D., {Hogg}, D.~W., {Lang}, D., \& {Goodman}, J. 2013, \pasp,
+  125, 306
+
+\bibitem[{{Klypin} {et~al.}(2016){Klypin}, {Yepes}, {Gottl{\"o}ber}, {Prada},
+  \& {He{\ss}}}]{Klypin2016}
+{Klypin}, A., {Yepes}, G., {Gottl{\"o}ber}, S., {Prada}, F., \& {He{\ss}}, S.
+  2016, \mnras, 457, 4340
+
+\bibitem[{{Ludlow} {et~al.}(2014){Ludlow}, {Navarro}, {Angulo},
+  {Boylan-Kolchin}, {Springel}, {Frenk}, \& {White}}]{Ludlow2014}
+{Ludlow}, A.~D., {Navarro}, J.~F., {Angulo}, R.~E., {Boylan-Kolchin}, M.,
+  {Springel}, V., {Frenk}, C., \& {White}, S.~D.~M. 2014, \mnras, 441, 378
+
+\bibitem[{{Macci{\`o}} {et~al.}(2008){Macci{\`o}}, {Dutton}, \& {van den
+  Bosch}}]{Maccio2008}
+{Macci{\`o}}, A.~V., {Dutton}, A.~A., \& {van den Bosch}, F.~C. 2008, \mnras,
+  391, 1940
+
+\bibitem[{{More} {et~al.}(2011){More}, {Kravtsov}, {Dalal}, \&
+  {Gottl{\"o}ber}}]{More2011}
+{More}, S., {Kravtsov}, A.~V., {Dalal}, N., \& {Gottl{\"o}ber}, S. 2011, \apjs,
+  195, 4
+
+\bibitem[{{Mu{\~n}oz-Cuartas} {et~al.}(2011){Mu{\~n}oz-Cuartas}, {Macci{\`o}},
+  {Gottl{\"o}ber}, \& {Dutton}}]{Munoz2011}
+{Mu{\~n}oz-Cuartas}, J.~C., {Macci{\`o}}, A.~V., {Gottl{\"o}ber}, S., \&
+  {Dutton}, A.~A. 2011, \mnras, 411, 584
+
+\bibitem[{{Navarro} {et~al.}(1997){Navarro}, {Frenk}, \& {White}}]{NFW}
+{Navarro}, J.~F., {Frenk}, C.~S., \& {White}, S.~D.~M. 1997, \apj, 490, 493
+
+\bibitem[{{Navarro} {et~al.}(2010){Navarro}, {Ludlow}, {Springel}, {Wang},
+  {Vogelsberger}, {White}, {Jenkins}, {Frenk}, \& {Helmi}}]{Navarro2010}
+{Navarro}, J.~F., {Ludlow}, A., {Springel}, V., {Wang}, J., {Vogelsberger}, M.,
+  {White}, S.~D.~M., {Jenkins}, A., {Frenk}, C.~S., \& {Helmi}, A. 2010,
+  \mnras, 402, 21
+
+\bibitem[{{Neto} {et~al.}(2007){Neto}, {Gao}, {Bett}, {Cole}, {Navarro},
+  {Frenk}, {White}, {Springel}, \& {Jenkins}}]{Neto2007}
+{Neto}, A.~F., {Gao}, L., {Bett}, P., {Cole}, S., {Navarro}, J.~F., {Frenk},
+  C.~S., {White}, S.~D.~M., {Springel}, V., \& {Jenkins}, A. 2007, \mnras, 381,
+  1450
+
+\bibitem[{{Prada} {et~al.}(2012){Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo},
+  \& {Primack}}]{Prada2012}
+{Prada}, F., {Klypin}, A.~A., {Cuesta}, A.~J., {Betancort-Rijo}, J.~E., \&
+  {Primack}, J. 2012, \mnras, 423, 3018
+
+\bibitem[{{Riebe} {et~al.}(2013){Riebe}, {Partl}, {Enke}, {Forero-Romero},
+  {Gottl{\"o}ber}, {Klypin}, {Lemson}, {Prada}, {Primack}, {Steinmetz}, \&
+  {Turchaninov}}]{2013AN....334..691R}
+{Riebe}, K., {Partl}, A.~M., {Enke}, H., {Forero-Romero}, J., {Gottl{\"o}ber},
+  S., {Klypin}, A., {Lemson}, G., {Prada}, F., {Primack}, J.~R., {Steinmetz},
+  M., \& {Turchaninov}, V. 2013, Astronomische Nachrichten, 334, 691
+
+\bibitem[{{Stadel}(2001)}]{2001PhDT........21S}
+{Stadel}, J.~G. 2001, PhD thesis, UNIVERSITY OF WASHINGTON
+
+\end{thebibliography}
 

### 2016-07-07 paper/ms.tex
conclusions edit

@@
 low levels as in the new method, dark matter halos should be sampled
-with at least $\sim 2000$ particles. 
+with at least $\sim 4000$ particles. 
 We also show that the mass-concentration relationship could be
@@
 
-We then notice that the new method closely follows the results of
+The new method closely follows the results of
 the velocity method at higher masses, $M_h>10^{12}\hMsun$ or
@@
 with $500$ particles or more.  
+To keep the bias of the velocity and density methods below $2\%$ only halos
+with at least $\sim 4000$ particles should be taken into account.
 
-We also measured the mass concentration relationship. 
-The three methods are in broad agreement within the statistical
-uncertainties, although there are some noticeable differences.
-The first difference is that the density method produces
-systematically higher concentrations by a factor of $15\%$ compared to
-the velocity method.
+Measuring the mass concentration relationship the three methods are in
+broad agreement within the statistical  uncertainties, although there
+are some noticeable differences. 
+For instance, the density method produces systematically higher
+concentrations by a factor of $15\%$ compared to the velocity method.
 This systematic offset has been reported before with the same dataset 
@@
 without any conclusive explanation for its origin. 
-The second difference is that the velocity and integrated mass methods
+A second difference is that the velocity and integrated mass methods
 start to differ for masses below $10^{12}\hMsun$.  
 We found that correcting the mean concentration by the mean bias
-factor brings these two techniques into agreement
+factor brings these two techniques into agreement.
 

### 2016-07-08 paper/ms.tex
y

@@
 %=========================================================================
-\title{Finding and controling biases in dark matter halo concentrations estimates}
+\title{Finding and controling biases in dark matter halo concentration estimates}
 \author{
@@
 particle numbers.
-For instance, these methods overestimate concentrations by 
-$15\%-20\%$ for halos sampled with $200$ particles.  
-To overcome this bias we propose a new algorithm based on the
+These methods overestimate the concentration by 
+$15\%-20\%$ for halos sampled with $200$ particles, and $7\%$-$8\%$
+for halos sampled with $500$ particles. 
+To control this bias level we propose a new algorithm based on the
 integrated mass profile. 
@@
 This method reduces the bias to $2\%-3\%$ for halos sampled with
-$200$ particles.  
+$200$-$500$ particles.
 To keep the biases of the velocity and density methods to the same
-low levels as in the new method, dark matter halos should be sampled
-with at least $\sim 4000$ particles. 
+low levels as in the new method, only halos sampled
+with at least $\sim 4000$ particles should be used.
 We also show that the mass-concentration relationship could be
@@
 
-In this paper we present a third alternative based on fitting the
+In this paper we use bootstraping to estimate the bias and standard
+deviation on the concentration estimates as a function of particle
+number. 
+We show that the two standard methods to estimate concentrations have
+increasing biases for decreasing particle numbers.
+
+This motivates us to present a third alternative based on fitting the
 integrated mass profile.  
@@
 concentration parameter.
-
-In order to asses the quality of the three different methods we use
-bootstraping on halos that are sampled with $10^{5}$ particles.
-This allows us to estimate the bias and standard deviation on the
-concentration estimates as a function of particle number.
 
@@
 \vspace{-0.5cm}
-\caption{Average value of the fractional offset ($f_{\rm
-    off}$Eq. \ref{eq:f_off}) between the concentration in a halo at
-  high resolution versus its downsampled versions.  Each point is the
-  result of 100 downsampling iterations.  The velocity method
-  noticeably overestimates the concentration up to a factor of $0.25$,
+\caption{\emph{Left panel}. Average value of the fractional offset ($f_{\rm
+    off}$ in Eq. \ref{eq:f_off}) between the concentration in a halo at
+  high resolution versus its downsampled versions. 
+  Thick lines
+  correspond to massive halos in the Bolshoi simulation, thin lines to
+  the Via Lactea simulation.
+  For each case close to $10000$ bootstrapping samples are used.
+  The velocity method noticeably overestimates the concentration up to
+  a factor of $0.20$, 
   while the new method only underestimates the concentrations by up to
-  a factor of $0.05$.
-Uncertainties on different concentration estimates.  The
-  large symbols show the standard deviation of the fractional offset
-  ($f_{\rm off}$ as defined in Eq. \ref{eq:f_off}) from the downsampling
-  experiments.  The small dots correspond to the $1\sigma$
-  uncertainty on the concentration for each halo as estimated by the
-  MCMC algorithm used for the new method.
-  The solid lines shows the $1/N$ tendency, which also corresponds
-  to the particle number dependence of the $\langle|D|\rangle$ statistic
-  (i.e. the accuracy to retrieve a known concentration in mock halos)
-  of the new method.
-  Uncertainties due to particle number fluctuations are always larger
-  than the statistical uncertainties from the fitting process. 
+  a factor of $0.04$.
+  \emph{Right panel.}
+  1$\sigma$ uncertainties on the offset and the concentration
+  estimates from the integrated mass method.  
+  Lines show the width between the 14 and 86 percentiles
+  of the $f_{\rm off}$ distribution at fixed particle number. 
+  The lines include the results for the three methods: maximum
+  velocity, density and integrated mass.
+  Grey symbols correspond to the $1\sigma$ uncertainty on each of
+  the halos in the Bolshoi Simulation as a result of the MCMC
+  sampling. 
+  To allow a fair comparison with $f_{\rm off}$, this uncertainty has
+  been normalized by the preferred concentration value for each halo. 
+  In both cases (bootstrapping for individul halos and MCMC fit of a
+  halo population) the $1\sigma$ is of the same order with a
+  decreasing behaviour as $1/\sqrt{N_s}$.
   \label{fig:downsampling}}
@@
 
-The new method uses the integrated mass profile defined in
+Here we propose a new method to estimate the concentration. 
+It uses the integrated mass profile defined in
 Eq. (\ref{eq:profile}).  We build it from N-body data following the
@@
 position of the $i$-th particle and $m_p$ is the mass of a single
-computational particle.  In this process we discard the particle at
-the center.
+computational particle.
 
@@
 Once the mass profile is expressed in dimensionless variables the
-concentration is the only free parameter.  We then use an Affine
-Invariant Markov Chain Monte Carlo implemented in the python module
-{\texttt{emcee}} \citep{emcee} to sample the likelihood function
-distribution defined by ${\cal L}(c)\propto \exp(-\chi^2(c)/2)$ where
-the $\chi^2(c)$ is written as
+concentration is the only free parameter.  
+We then use an Affine Invariant Markov Chain Monte Carlo implemented
+in the python module {\texttt{emcee}} \citep{emcee} to sample the
+likelihood function distribution defined by ${\cal L}(c)\propto
+\exp(-\chi^2(c)/2)$ where the $\chi^2(c)$ is written as
 
 \begin{equation}
-\chi^2(c)= \sum_{i=1}^{N}[\log m_i - \log m(< x_i;c)]^2,
+\chi^2(c)= \frac{1}{N}\sum_{i=1}^{N}[\log m_i - \log m(< x_i;c)]^2,
 \end{equation}
@@
 
+We use two very different simulations to be sure that the results (bias,
+uncertainty on the bias) measured using bootstraping tests are
+independent of the kind of parent simulation.
+
 We use data from the Bolshoi cosmological simulation that follows the
@@
 $\sigma_8=0.82$. 
-The
-data is publicly available at \url{http://www.cosmosim.org/}.  More
-details about the structure of the database and the simulation can be
+The data is publicly available at \url{http://www.cosmosim.org/}.  
+Details about the structure of the database and the simulation can be
 found in \citep{2013AN....334..691R}.
@@
 We use a halo sample containing all the halos located in a cubic
-sub-volume of $100$ \hMpc\ on a side.  From this sample we select all
-the halos at $z=0$ detected with a Friends-of-Friends (FoF) algorithm
-with more than 300 particles, meaning that the masses are in the
-interval $4\times 10^{10}\leq M_{\rm FoF}/\hMsun \leq 10^{14}$.  The
-FoF algorithm used a linking length of $0.17$ times the mean
-inter-particle distance. This choice translates into an overdensity
-$\Delta_h\sim 400-700$ dependent on the halo concentration
-\citep{More2011}.
+sub-volume of $100$ \hMpc\ on a side.  
+From this sample we select all the halos at $z=0$ detected with a
+Friends-of-Friends (FoF) algorithm with more than 300 particles,
+meaning that the masses are in the interval $4\times 10^{10}\leq
+M_{\rm FoF}/\hMsun \leq 10^{14}$.  The FoF algorithm used a linking
+length of $0.17$ times the mean inter-particle distance. 
+This choice translates into an overdensity $\Delta_h\sim 400-700$
+dependent on the halo concentration \citep{More2011}.
 
@@
 times the critical density) to select an spherical region that we
-redefine to be our halo.  This choice makes that the overdensities are
-fully included inside the original FoF particle group.  On the
-interest of providing a fair comparison against the density method we
-only report results from overdensities with at least $200$ particles
-($2.6\times 10^{10}$\hMsun).
+redefine to be our halo.  
+This choice makes that the overdensities are fully included inside the
+original FoF particle group.   
+On the interest of providing a fair comparison against the density
+method we only report results from overdensities with at least $200$
+particles ($2.6\times 10^{10}$\hMsun).
 
@@
 
-We use a set of two very different simulations to demonstrate that the 
-results of our bootstraping tests are independent of the kind of
-parent simulation.
-
 \begin{figure*}
@@
 \caption{Mass-concentration relationship for the three different
-  methods used on the same cosmological N-body data.  All halos are
-  used regardless of their relaxation state.  The lines correspond to
-  the median concentration values in each mass bin.  The shaded region
-  presents 10 and 90 per cent spread.  For clarity we only show the
-  spread for the concentrations estimated using the new method. The
-  other two methods have a similar spread. The dotted line corresponds
-  to fits reported by \citep{Prada2012}.
-  \label{fig:concentration}. The left panel shows the raw results
-  coming from each algorithm. The right panel introduces a
-  correction on the velocity and integrated mass results. 
-  The corrections depends on the number of particles following the
-  results of the downsampling experiments presented in Figure
+  methods used on the same cosmological N-body data.  
+  We only used relaxed halos.
+  All halos are
+  The lines correspond to the median concentration values in each mass
+  bin.  
+  The shaded region presents 10 and 90 per cent spread. 
+  For clarity we only show the spread for the concentrations estimated
+  using the new method.  
+  The other two methods have a similar spread. 
+  The dotted line corresponds to fits reported by \citep{Prada2012}.
+  \label{fig:concentration}. 
+  The left panel shows the raw results coming from each algorithm. 
+  The right panel introduces a correction on the velocity and
+  integrated mass results following the results of the downsampling
+  experiments presented in Figure 
   \ref{fig:downsampling}.} 
@@
 
-We use bootstraping of individual high resolution halos to quantify
-biases for different methods used to esteimate concentrations.
-
-In this experiment we take halos sampled with at least $10^{5}$
-particles and subsample each halo by factors of $2$ up to $10^{3}$ to
-measure the concentration every time the halo is resampled.
+In our bootstrapping experiments we take halos sampled with at least
+$10^{5}$ particles and subsample each halo by factors of $2$ up to
+$10^{3}$ to measure the concentration every time the halo is
+resampled. 
+Every time we keep fixed the virial radius and the center found for
+the high resolution halo.
+We extract in total 10000 bootstrapping samples for the Bolshoi
+and the Via Lactea simulations.
+In the case of the Bolshoi simulation we select 14 massive halos and
+create 700 subsamples for each one. 
+For the Via Lactea simulation only one halo is subsampled 10000
+times.
 
@@
 downsampled particle number $c_{N}$ and the baseline $c_{N_{max}}$.
+For each method we keep its corresponding concentration $c_{N_{max}}$
+value at high resolution.
 
-We select $8$ halos from the simulation that have at
-least $3\times 10^5$ particles.  
-We then randomly downsample the total number of particles in each halo
-by factors of $10, 20, 45, 100, 215, 460, 1000$ to measure its
-concentration with both the integrated mass and the velocity
-method. For each downsampling factor we repeat the operation $100$
-times.
-
-Figure \ref{fig:downsampling} summarizes our results.  The plot shows
-the average value of $f_{\rm off}$ as a function of the particle
-number.  As expected for large enough sample particle numbers,
-$N_{s}>5\times 10^3$, the results of the two algorithms coincide and
-$\langle f_{\rm off}\rangle\sim 0$.  For lower number of particles,
-the results of the two algorithms deviate from the expected
-concentration value.  The velocity method overestimates by a factor
-$\langle f_{\rm off}\rangle\sim 0.25$ the concentration values for the
-lowest sample particle numbers, $N_{s}\sim 100$.  Around the same
-sampling scale, the new algorithm shows a more stable behaviour with
-an underestimate by a factor of $\langle f_{\rm off}\rangle \sim 0.02$.
-This shows that in the more complex setup of a cosmological 
-  simulation the new algorithm continues to be stable below the $5\%$
-level for low particle numbers.
+Figure \ref{fig:downsampling} summarizes our results.  
+The plot on the left shows the average value of $f_{\rm off}$ as a
+function of the particle number.  
+As expected, for large enough sample particle numbers,
+$N_{s}>4\times 10^3$, the results of the three algorithms coincide
+below the $1\%$ level.
+For a lower number of particles, the results deviate from the expected
+concentration value.  
+For $200$ particles the velocity method overestimates by a factor
+$14\%$ while the density method overestimates it by $20\%$.
+Around the same sampling scale, the new algorithm shows a more stable
+behaviour underestimating the concentration only by a factor of
+$1\%$-$2\%$
 
@@
 
-Figure \ref{fig:downsampling_err} summarizes different uncertainty
+The right panel in \ref{fig:downsampling} shows different uncertainty
 results. 
-Large symbols show the standard deviation on $f_{\rm off}$ from the
-downsampling experiment.  
-Small dots show the uncertainty on each individual concentration value
-as estimated by the MCMC algorithm. 
-The line shows the $\propto N^{-1}$ locus.  
-This figure demonstrates that the statistical uncertainties are at
-least one order of magnitude smaller than the uncertainty associated
-to downsampling experiment.
+The lines show the difference between the 14 and 86 percentiles in the
+$f_{\rm off}$ distribution at fixed mass.
+Each line corresponds to the three different methods to estimate the
+concentration and the two simulations.
+This shows that the bootstraping technique can help us to assign a
+$1\sigma$ uncertainty to the concentration values at a fixed $N_s$. 
+This uncertainty is shown as normalized by the preferred value of the
+concentration, which in this case corresponds to $c_{N_{max}}$.  
+The circles in the same figure show the $1\sigma$ uncertainty as
+estimated from the MCMC chains using the integrated mass method on all
+the relaxed halos in the Bolshoi simulation sample. 
+To allow for a fair comparison with the bootstrapping results, this
+uncertainty was normalized by the preferred concentration.
+The MCMC uncertainties follow the same trend as the bootstraping
+results. {\bf Hay algun significado profundo de esto o es lo que
+  deberiamos esperar?}.
+
+From these results we defined a universal $1\sigma$ fractional
+uncertainty for the concentration as a function of the number of
+particles $N_s$ as  
+%
+\begin{equation}
+\sigma_{c} = \frac{0.40}{\sqrt{N_s/200}}.
+\end{equation}
+%
+An interesting application of this result is that $\sigma_c=1$ for
+$N_s=32$ particles, independent of the method used to estimate the
+concentration.
 

### 2016-07-08 paper/ms.tex
nueva version completa

@@
 These methods overestimate the concentration by 
-$15\%-20\%$ for halos sampled with $200$ particles, and $7\%$-$8\%$
+$15\%-20\%$ for halos sampled with $200$ particles, and $7\%$-$10\%$
 for halos sampled with $500$ particles. 
@@
 
+We now turn to the question of quantifying the concentration results
+of the new algorithm and possible applications of the biases found.
+
 Figure \ref{fig:concentration} shows the mass-concentration
@@
 
-We notice first that the results from the density method have a
+We notice first that the results from the new algorithm follow very
+closely the velocity algorithm at high masses ($M_h>10^{12}\hMsun$ or
+equivalently for $>8\times10^3$ particles). 
+For lower masses there is a difference between the median of the two
+methods, but they are still consistent within the statistical
+uncertainties.
+
+We also notice that the results from the density method have a
 systematic $15\%$offset from the velocity methods.  
-This offset was already presented by \citep{Prada2012} for low
+This offset was already presented by \cite{Prada2012} for low
 concentrations ($c<6$) and high ($M_h>10^{12}\hMsun$) halo masses.  
@@
 relationship using the maximum velocity and density methods and did
-not report any significant difference. However, they implemented a
-modified version of the velocity algorithm that uses the data binning
-obtained for the density algorithm.
-
-The new method closely follows the results of
-the velocity method at higher masses, $M_h>10^{12}\hMsun$ or
-equivalently for $>5\times10^3$ particles.  
-For masses below that threshold the new method saturates at a
-concentration value of $\sim 8$ while the velocity method continues to
-give higher concentration values.
+not report any significant difference. 
+However, they implemented a modified version of the velocity algorithm
+that uses the data binning obtained for the density algorithm.
 
 We hypothesize that the increase in the results for the velocity
-method below $5\times 10^{4}$ particles come from the systematic bias
-described in the previous subsection.  To test the general consistency
-of this hypothesis we correct the concentration values in the
-velocity and integrated mass methods by a factor of $1/(1+f_{\rm
-  off})$, using the definition in Equation (\ref{eq:f_off}) and the 
+and density methods below $8\times 10^{3}$ particles come from the
+systematic bias described in the previous section.  
+To test the general consistency of this hypothesis we correct the
+concentration values in the velocity and integrated mass methods by a
+factor of $1/(1+f_{\rm  off})$, using the definition in Equation
+(\ref{eq:f_off}) and the  
 parameters obtained from the data presented in Figure
@@
 The correction brings into perfect agreement the results between the
-velocity and the integrated mass method.  
-This suggests that the concentration at lower masses might very well
-reach a plateau in the halo mass range $10^{10}< M_{h}/\hMsun <
-10^{12}$ .
+velocity/density methods and the new algorithm.
 
@@
 We found that methods commonly used in the literature present a large
-bias by overestimating concentrations by factors of $13\%$-$20\%$ for
+bias by overestimating concentrations by factors of $15\%$-$20\%$ for
 halos with $200$ particles, or $7\%$-$10\%$ for halos with $500$

### 2016-07-09 paper/ms.tex
minor updates in abstract

@@
 for halos sampled with $500$ particles. 
-To control this bias level we propose a new algorithm based on the
-integrated mass profile. 
+To control this bias level we propose a new algorithm to estimate halo
+concentrations based on the integrated mass profile. 
 The method uses the full particle information without any binning,
@@
 To keep the biases of the velocity and density methods to the same
-low levels as in the new method, only halos sampled
+low levels as in the integrated mass method, we find that only halos sampled
 with at least $\sim 4000$ particles should be used.
@@
 From these results we believe that bootstrapping and the
-concentration estimation based on the integrated mass are
+concentration estimation based on the integrated mass profile are
 valuable tools to probe the internal structure of dark matter halos

### 2016-07-10 paper/ms.tex
mass-conc intro

@@
 
-We now turn to the question of quantifying the concentration results
-of the new algorithm and possible applications of the biases found.
+We now compare the esults for the mass-concentration
+relationship obtained with the three different algorithms.
+This helps to compare the concentration results
+of the new algorithm and, more importantly, showcase a probable
+consequence of the biases detected through bootstrapping.
 

### 2016-07-12 paper/ms.tex
minor caption edit

@@
 \caption{\emph{Left panel}. Average value of the fractional offset ($f_{\rm
-    off}$ in Eq. \ref{eq:f_off}) between the concentration in a halo at 
-  high resolution versus its downsampled versions. 
-  Thick lines
-  correspond to massive halos in the Bolshoi simulation, thin lines to
-  the Via Lactea simulation.
+    off}$ (Eq. \ref{eq:f_off}) between the concentration in a halo at 
+  high resolution and its bootstrapped versions. 
+  Thick (thin) lines correspond to massive halos in the Bolshoi (Via
+  Lactea) simulation.
   For each case close to $10000$ bootstrapping samples are used.

### 2016-07-13 paper/ms.tex
latest version

@@
 \documentclass{emulateapj}
-\submitted{{\it Submitted for publication in ApJ}}
+\submitted{{\it Submitted for publication in ApJL}}
 \usepackage{multirow,color,wrapfig,ulem}
@@
 %=========================================================================
-\title{Finding and controling biases in dark matter halo concentration estimates}
+\title{Quantifying and controlling biases in dark matter halo concentration estimates}
 \author{
@@
 We find that algorithms based on the maximum radial velocity
-and radial particle binning have increaing biases with decreasing 
-particle numbers.
-These methods overestimate the concentration by 
-$15\%-20\%$ for halos sampled with $200$ particles, and $7\%$-$10\%$
+and radial particle binning tend to overestimate the concentration by 
+$15\%-20\%$ for halos sampled with $200$ particles and by $7\%$-$10\%$
 for halos sampled with $500$ particles. 
-To control this bias level we propose a new algorithm to estimate halo
-concentrations based on the integrated mass profile. 
+To control this bias at low particle numbers we propose a new
+algorithm to estimate halo concentrations based on the integrated mass
+profile.   
 The method uses the full particle information without any binning,
@@
 limitation for other methods.
-This method reduces the bias to $2\%-3\%$ for halos sampled with
+This method reduces the bias to $1\%-3\%$ for halos sampled with
 $200$-$500$ particles.
-To keep the biases of the velocity and density methods to the same
-low levels as in the integrated mass method, we find that only halos sampled
-with at least $\sim 4000$ particles should be used.
+The velocity and density methods have to use halos with least $\sim
+4000$ particles in order to keep the biases down to the same low
+level. 
 We also show that the mass-concentration relationship could be
@@
 of the different concentration measurements are taken into account.
-From these results we believe that bootstrapping and the
-concentration estimation based on the integrated mass profile are
+These results show that bootstrapping and the
+concentration estimates based on the integrated mass profile are
 valuable tools to probe the internal structure of dark matter halos
@@
 
-In this paper we use bootstraping to estimate the bias and standard
+In this letter we use bootstrapping to estimate the bias and standard
 deviation on the concentration estimates as a function of particle
@@
   been normalized by the preferred concentration value for each halo. 
-  In both cases (bootstrapping for individul halos and MCMC fit of a
+  In both cases (bootstrapping for individual halos and MCMC fit of a
   halo population) the $1\sigma$ is of the same order with a
-  decreasing behaviour as $1/\sqrt{N_s}$.
+  decreasing behavior as $1/\sqrt{N_s}$.
   \label{fig:downsampling}}
@@
 We use two very different simulations to be sure that the results (bias,
-uncertainty on the bias) measured using bootstraping tests are
+uncertainty on the bias) measured using bootstrapping tests are
 independent of the kind of parent simulation.
@@
 region.
-The cosmological parameters are diffferent from those in the Bolshoi
+The cosmological parameters are different from those in the Bolshoi
 simulation, with a Hubble parameter $h=0.73$, a matter density
@@
 \caption{Mass-concentration relationship for the three different
-  methods used on the same cosmological N-body data.  
-  We only used relaxed halos.
-  All halos are
+  methods on the Bolshoi data using only relaxed halos.
   The lines correspond to the median concentration values in each mass
@@
   The shaded region presents 10 and 90 per cent spread. 
-  For clarity we only show the spread for the concentrations estimated
-  using the new method.  
-  The other two methods have a similar spread. 
+  The three methods have a similar spread but for clarity we only show
+  the spread for the concentrations estimated using the new method.   
   The dotted line corresponds to fits reported by \citep{Prada2012}.
@@
 the high resolution halo.
+We tested that leaving the virial radius and center free in each
+bootstrapping iteration has an effect lower than $1\%$ in the
+concentration. 
 We extract in total 10000 bootstrapping samples for the Bolshoi
@@
 In the case of the Bolshoi simulation we select 14 massive halos and
-create 700 subsamples for each one. 
+create 700 subsamples for each halo. 
 For the Via Lactea simulation only one halo is subsampled 10000
@@
 \end{equation} 
-for the dataset shown in the panel we have $A=3385\pm 2065$, $B=7.99\pm0.48
-$ for the velocity method and $A=-110\pm 253$, $B=7.11\pm1.80$ for the
-new method, where the uncertainties are estimated from the covariance 
-matrix resulting from the non-linear optimization procedure. The lines
-on Figure \ref{fig:downsampling} are plotted using these best values.
+for the dataset shown in the panel we have $A=2842\pm 1900$,
+$B=7.96\pm 0.54$ for the density method; $A=239\pm 131$,
+$B=6.23\pm 0.43$ for the velocity method; $A=-3.66\pm 5.22$,
+$B=4.65\pm 1.12$ for the integrated mass method.
+The uncertainties are estimated from the covariance  matrix resulting
+from the non-linear optimization procedure. The lines on Figure
+\ref{fig:downsampling} are plotted using these best values.
 
@@
 concentration and the two simulations.
-This shows that the bootstraping technique can help us to assign a
+This shows that the bootstrapping technique can help us to assign a
 $1\sigma$ uncertainty to the concentration values at a fixed $N_s$. 
@@
 uncertainty was normalized by the preferred concentration.
-The MCMC uncertainties follow the same trend as the bootstraping
-results. {\bf Hay algun significado profundo de esto o es lo que
-  deberiamos esperar?}.
+The MCMC uncertainties follow the same trend as the bootstrapping
+results.
 
@@
 %
-An interesting application of this result is that $\sigma_c=1$ for
+An interesting consequence of this result is that $\sigma_c=1$ for
 $N_s=32$ particles, independent of the method used to estimate the
@@
 
-We now compare the esults for the mass-concentration
+We now compare the results for the mass-concentration
 relationship obtained with the three different algorithms.
@@
 We also notice that the results from the density method have a
-systematic $15\%$offset from the velocity methods.  
+systematic $15\%$ offset from the velocity methods.  
 This offset was already presented by \cite{Prada2012} for low
@@
 
-In this paper we quantified biases on concentration numerical estimates by
-bootstrapping dark matter halos resolved with a  large number of
-particles ($\sim 10^5$).
+In this letter we used bootstrapping to quantify the biases on
+concentration estimates. 
 We found that methods commonly used in the literature present a large
@@
 particles.  
-This procedure is a new way to quantify the bias in concentration
-estimates with the advantage that it works without having to run new
-simulations.
+This procedure provides a robust technique to quantify the bias in
+concentration estimates with the advantage that it works without
+having to run new simulations.
 
-These results motivated us to introduction a method with a robust
-performace at low particle numbers.
+These results motivated us to introduce a method with a robust
+performance at low particle numbers.
 This method is based on the integrated mass profile. 
@@
 A second difference is that the velocity and integrated mass methods
-start to differ for masses below $10^{12}\hMsun$.  
+start to differ for masses below $10^{12}\hMsun$ ($\sim 4000$
+particles).   
 We found that correcting the mean concentration by the mean bias
-factor brings these two techniques into agreement.
+factor found through bootstrapping brings these two techniques into
+agreement.
 

### 2016-07-14 paper/ms.tex
notes on the approximated covariance matrix

@@
 concentration is the only free parameter.
-We then use an Affine Invariant Markov Chain Monte Carlo implemented
-in the python module {\texttt{emcee}} \citep{emcee} to sample the
-likelihood function distribution defined by ${\cal L}(c)\propto
-\exp(-\chi^2(c)/2)$ where the $\chi^2(c)$ is written as
+
+Using the bootstrapping data we find that at a given normalized
+radius, $x$, the logarithm of the normalized integrated mass, $m$, follows a 
+distribution that can approximated by a gaussian with variance
+\begin{equation}
+\sigma_x^2 = \frac{1-x}{x}\frac{1}{6N}.
+\label{eq:sigma}
+\end{equation}
+
+If the integrated mass values at different radii were independent from
+each other, this could be used as the basis to develop a simple
+bayesian likelihood to be sampled with Markov Chain Monte Carlo techniques where
+the likelihood could be then defined to be ${\cal L}(c)\propto
+\exp(-\chi^2(c)/2)$ with a $\chi^2(c)$ written as
 
 \begin{equation}
-\chi^2(c)= \frac{1}{N}\sum_{i=1}^{N}[\log m_i - \log m(< x_i;c)]^2,
+\chi^2(c)= \sum_{i=2}^{N-1}\frac{[\log m_i - \log m(< x_i;c)]^2}{\sigma_i^2},
 \end{equation}
 %
-where $m(<x_i;c)$ corresponds to the values in Eq.(\ref{eq:profile})
-at $x=x_i$ for a given value of the concentration parameter $c$ and
-the $i$ index sums over all the particles in the numerical profile.
+where $\sigma_i^2=\sigma_x^2$, $m(<x_i;c)$ corresponds to the
+values in Eq.(\ref{eq:profile}) at $x=x_i$ for a given value of the
+concentration parameter $c$, and the $i$ index sums over all the
+particles in the numerical profile. 
+In this computation the particles $i=1$ and $i=N$ are discarded to
+avoid divergent terms in the sum.
+
+However, tests on the bootstrapping data show that the covariance
+matrix is not diagonal and using $\sigma_i^2=\sigma_x^2$ would grossly
+overestimate $\chi^2(c)$ providing too optimistic error bars.
+
+Given the high expense of computing a full covariance matrix for
+each desired number of particles $N$, we have calibrated an effective
+$\sigma_{\rm eff}^2$ such that it keeps the dependence on $x$ that we have
+discovered for the diagonal elements and also gives similar curves of
+$\chi^{2}(c)$-$c$ around the minimum as the full covariance matrix
+computation.
+
+We found that this effective $\sigma_{\rm eff}^2$ can be approximated as
+
+\begin{equation}
+\sigma_{\rm eff}^2 = \frac{1-x}{x}\frac{N^{1.15}}{4.5\times 10^3}.
+\end{equation}
+
+We then use $\sigma_i^2=\sigma_{\rm eff}^2$ to feed an Affine
+Invariant Markov Chain Monte Carlo implemented in the python module
+{\texttt{emcee}} \citep{emcee} to sample the likelihood function
+distribution.
 From the $\chi^2$ distribution we find the optimal value of the

### 2016-07-14 src/old/AnotherPaperPlots.py
removing old code

@@ -1,64 +1,0 @@
-import pylab, numpy as np, nfw, matplotlib
-
-r = np.linspace(0,1,1000)
-C = [1,2,6,12,20]
-
-for c in C:
-    c = int(c)
-    pylab.plot(r,nfw.mass_norm(r,c),color='black',lw = .2*c+1,label="$c="+str(c)+"$")
-pylab.legend(loc=0, scatterpoints=1, prop={'size':20})
-filename = 'nfw_normalized'
-matplotlib.rcParams.update({'font.size': 18})
-pylab.xlabel('$x$',fontsize=20)
-pylab.ylabel('$m(<x)$',fontsize=20)
-pylab.savefig(filename+'.eps',transparent=True)
-pylab.savefig(filename+'.pdf',transparent=True)
-pylab.savefig(filename+'.png',transparent=True)
-pylab.close()
-
-
-for c in C:
-    c = int(c)
-    pylab.plot(r,nfw.velocity_norm(r,c),color='black',lw = .2*c+1,label="$c="+str(c)+"$")
-pylab.legend(loc=0, scatterpoints=1, prop={'size':20})
-filename = 'vel_normalized'
-matplotlib.rcParams.update({'font.size': 18})
-pylab.xlabel('$x$',fontsize=20)
-pylab.ylabel('$v(<x)$',fontsize=20)
-pylab.savefig(filename+'.eps',transparent=True)
-pylab.savefig(filename+'.pdf',transparent=True)
-pylab.savefig(filename+'.png',transparent=True)
-pylab.close()
-
-for c in C:
-    c = int(c)
-    dv_dx = (nfw.velocity_norm(np.delete(r,0),c)-nfw.velocity_norm(np.delete(r,-1),c))/(r[1]-r[0])
-    pylab.plot(np.delete(r,0),dv_dx,color='black',lw = .2*c+1,label="$c="+str(c)+"$")
-pylab.legend(loc=0, scatterpoints=1, prop={'size':20})
-filename = 'dv_dx'
-matplotlib.rcParams.update({'font.size': 18})
-pylab.xlabel('$x$',fontsize=20)
-pylab.ylabel('$dv/dx$',fontsize=20)
-pylab.yscale('log')
-pylab.ylim(ymin=1E-2)
-pylab.savefig(filename+'.eps',transparent=True)
-pylab.savefig(filename+'.pdf',transparent=True)
[…]

### 2016-07-14 src/old/compile.sh

@@ -1,3 +1,0 @@
-cython -a mcmc.pyx
-gcc -shared -pthread -fPIC -fwrapv -O2 -Wall -fno-strict-aliasing \
-      -I/usr/include/python2.7 -o mcmc.so mcmc.c

### 2016-07-14 src/old/configure.py

@@ -1,64 +1,0 @@
-import Tkinter as tk, tkFileDialog, tkMessageBox
-
-root = tk.Tk()
-root.title('Configure')
-
-directory = tk.StringVar()
-x = tk.StringVar()
-y = tk.StringVar()
-z = tk.StringVar()
-skip = tk.StringVar()
-proc = tk.StringVar()
-step = tk.StringVar()
-plot = tk.BooleanVar()
-test = tk.BooleanVar()
-
-tk.Entry(root,textvariable=directory).grid(row=0,column=1)
-tk.Entry(root,textvariable=x).grid(row=1,column=1)
-tk.Entry(root,textvariable=y).grid(row=2,column=1)
-tk.Entry(root,textvariable=z).grid(row=3,column=1)
-tk.Entry(root,textvariable=skip).grid(row=4,column=1)
-tk.Entry(root,textvariable=proc).grid(row=5,column=1)
-tk.Entry(root,textvariable=step).grid(row=6,column=1)
-
-try:
-    params = open('config.div','r').readline().split(',')
-    directory.set(params[0])
-    x.set(params[1])
-    y.set(params[2])
-    z.set(params[3])
-    skip.set(params[4])
-    proc.set(params[5])
-    step.set(params[6])
-    plot.set((params[7] == '1'))
-    test.set((params[8] == '1'))
-except:
-    print '',
-tk.Label(root, text='Path').grid(row=0)
-tk.Label(root, text='X Column').grid(row=1)
-tk.Label(root, text='Y Column').grid(row=2)
-tk.Label(root, text='Z Column').grid(row=3)
-tk.Label(root, text='Lines to Skip').grid(row=4)
-tk.Label(root, text='Processes').grid(row=5)
-tk.Label(root, text='MCMC Steps').grid(row=6)
-tk.Label(root, text='Plotting Mode').grid(row=7)
-tk.Label(root, text='Test Mode').grid(row=8)
-
-def change_path():
-    directory.set(tkFileDialog.askdirectory())
-
-def save():
-    export = open('config.div','w')
-    line =  directory.get()+','+x.get()+','+y.get()+','+z.get()+','+skip.get()+','+proc.get()+','+step.get()+','+('%r' % (plot.get()))+','+('%r' % (test.get()))
-    export.write(line)
-    export.close()
-    tkMessageBox.showinfo('Saving...', 'Configuration file was saved successfully')
-
-
[…]

### 2016-07-14 src/old/density.py

@@ -1,173 +1,0 @@
-import numpy as np, pylab, math, sys, timeit, os, random, datetime, nfw, mcmc,fit , plotter, multiprocessing, time
-from scipy.optimize import fsolve
-
-# Gets the concentration and virial radius for several haloes
-
-config = open('config.div','r').readline().split(',')
-config[-1] = config[-1].replace('\n','')
-
-processes = int(config[5])
-now = datetime.datetime.now().strftime("%Y-%m-%d-%H:%M:%S")
-mass_element = 1.0   
-plt = 1
-total_list = os.listdir(str(config[0]))
-len_list = len(total_list)
-lists = [total_list[i*len_list // processes: (i+1)*len_list //processes] for i in range(processes)]
-jobs = []
-
-if (config[7]=='0'):
-    print 'Plotting mode disabled'
-    plt = 0
-else:
-    print 'Plotting mode enabled'
-    plt = 1
-    
-if config[8]=='0':
-    print 'Test mode disabled'
-else:
-    print 'Test mode enabled'
- 
-os.system('mkdir dens_'+now)
-sys.stdout.write('\rCompiling the code used to calculate the center of each halo... ')
-sys.stdout.flush()
-os.system('cc potential.c -lm -o  potential.out')
-sys.stdout.write('Done\n')
-
-def run(directories,process_number):
-
-    process_number+=1
-    count = 0
-    filename_export = './dens_'+now+'/results_'+str(process_number)+'.csv'
-    os.system('touch '+filename_export)
-
-    for filename in directories:
-
-        count = count + 1
-        print '\rWorking with file '+str(count)+' of '+str(len(directories))+' in process '+str(process_number)
-
-    # Creates the "data" array with the information from the file in "path"
-        path = os.path.expanduser(str(config[0])+'/'+filename)
-        data = np.loadtxt(open(path, 'r'), delimiter=",",skiprows=int(config[4]))
-
-    # Gets the cartesian coordinates for each particle in the halo and the number of particles
-        x = data[:,int(config[1])]
-        y = data[:,int(config[2])]
-        z = data[:,int(config[3])]
-        n_points = len(x)
-
-    # Exports a file with the cartesian coordinates of each particle
-        file_id = int(filename.split('_')[1])
-        positions_name ='positions_'+str(file_id)+'.dat'
-        potential_name ='potential_'+str(file_id)+'.dat'
[…]

### 2016-07-14 src/old/diff.py

@@ -1,37 +1,0 @@
-import numpy as np, pylab,sys
-
-data = np.loadtxt(sys.argv[1],delimiter=',')
-v = data[:,-3:]
-print v
-r = np.empty(len(v))
-
-for i in range(len(r)):
-    r[i] = np.sum(v[i]*np.ones(3))/(np.sqrt(3*np.sum(v[i]*v[i])))
-
-r -= (3)**(-.5)
-r /= 1-(3)**(-.5)
-
-pylab.plot(data[:,8]/data[:,9],r,'.k')
-pylab.plot([0,1],[1,1],'--',label='$\mathrm{Bun\~uelo}$')
-pylab.plot([0,1],[0.93689,0.93689],'--',label='$\mathrm{Empanada}$')
-pylab.plot([0,1],[2/(3*(np.sqrt(3)-1)),2/(3*(np.sqrt(3)-1))],'--',label='$\mathrm{Arepa}$')
-pylab.plot([0,1],[(np.sqrt(2)-1)/(np.sqrt(3)-1),(np.sqrt(2)-1)/(np.sqrt(3)-1)],'--',label='$\mathrm{Palito\ de\ queso}$')
-pylab.ylabel('$\mathrm{Coeficiente\ de\ bu\~nuelidad}$',fontsize=16)
-pylab.xlabel('$n_{vir}/n_{tot}$',fontsize=16)
-pylab.xlim([0,1])
-pylab.ylim([0,1.1])
-pylab.legend(loc=4)
-pylab.savefig('plot.png',dpi=200)
-pylab.show()
-
-pylab.hist(r,bins=100)
-pylab.plot([1,1],[0,len(r)],'--',label='$\mathrm{Bu\~nuelo}$')
-pylab.plot([0.93689,0.93689],[0,len(r)],'--',label='$\mathrm{Empanada}$')
-pylab.plot([2/(3*(np.sqrt(3)-1)),2/(3*(np.sqrt(3)-1))],[0,len(r)],'--',label='$\mathrm{Arepa}$')
-pylab.plot([(np.sqrt(2)-1)/(np.sqrt(3)-1),(np.sqrt(2)-1)/(np.sqrt(3)-1)],[0,len(r)],'--',label='$\mathrm{Palito\ de\ queso}$')
-pylab.xlim([0,1.1])
-pylab.ylim([0,len(r)])
[…]

### 2016-07-14 src/old/fit.py

@@ -1,163 +1,0 @@
-import numpy as np, sys, os, nfw
-from scipy.optimize import curve_fit
-
-# Returns the chi squared estimate given a prediction and the real data
-# Requires:
-#     obs: observed data
-#     mod: expected data from the model
-# Returns:
-#     The chi squared estimate
-
-def chi2(obs,mod):
-    return np.sum((obs-mod)**2)
-
-# Does a maximum-likelihood estimate using the Metropolis-Hastings algorithm for a model with one parameters.
-# Requires:
-#     data: free variable data
-#     obs: observed data
-#     mod: expected data from the model
-#     n_iterations: number of steps for the random walk
-# Returns:
-#     best parameter, the random walk for the parameter and the chi squared for each step
-
-def metropolis_one(data,obs,mod,n_iterations):
-
-    guess = [np.log(10)]
-    
-    a_walk = np.empty((n_iterations+1))
-    chisq = np.empty((n_iterations+1))
-
-    a_walk[0] = guess[0]
-    chisq[0] = chi2(obs,mod(data,guess[0]))
-
-    step_a = np.abs(np.log(1.01))    
-
-    for i in range(n_iterations):
-        
-        a_prime = np.random.normal(a_walk[i],step_a)
-
-        while a_prime < 0 :            
-            a_prime = np.random.normal(a_walk[i],step_a)
-        
-        chi2_init = chi2(obs,mod(data,a_walk[i]))
-        chi2_prime = chi2(obs,mod(data,a_prime))
-        ratio = (chi2_init - chi2_prime)
-
-        if (ratio > 0.0):
-            a_walk[i+1] = a_prime
-            chisq[i+1] = chi2_prime
-        else:
-            beta = np.random.random()
-            if (ratio > np.log(beta)):
-                a_walk[i+1] = a_prime
-                chisq[i+1] = chi2_prime
-            else:
-                a_walk[i+1] = a_walk[i]
-                chisq[i+1] = chisq[i]
-
-    n = np.argmin(chisq)
-
-    best_a = a_walk[n]
-
-    return best_a,a_walk,chisq
-
-# Does a maximum-likelihood estimate using the Metropolis-Hastings algorithm for a model with two parameters.
-# Requires:
-#     data: free variable data
-#     obs: observed data
-#     mod: expected data from the model
[…]

### 2016-07-14 src/old/glue.py

@@ -1,26 +1,0 @@
-import sys, os, numpy as np
-
-directory = str(sys.argv[1])
-total_list = os.listdir(directory)
-filenames = sorted([directory+'/'+element for element in total_list if 'result' in element])
-
-export = open(directory+'/results.csv', 'w')
-for fname in filenames:
-    with open(fname) as infile:
-        for line in infile:
-            export.write(line)   
-
-export.close()
-
-data = np.loadtxt(directory+'/results.csv',delimiter=',')
-data = data[data[:,0].argsort()]
-
-if len(data[0,:]) == 10:
-    head = 'Id,x_center,y_center,z_center,c,c_max,c_min,r_vir,n_vir,n_tot'
-    np.savetxt(directory+'/results.csv',data,fmt='%d,%f,%f,%f,%f,%f,%f,%f,%d,%d',header=head)
-if len(data[0,:]) == 13:
-    head = 'Id,x_center,y_center,z_center,c,c_max,c_min,r_vir,n_vir,n_tot,e_x,e_y,e_z'
-    np.savetxt(directory+'/results.csv',data,fmt='%d,%f,%f,%f,%f,%f,%f,%f,%d,%d,%f,%f,%f',header=head)
-else:
-    head = 'Id,x_center,y_center,z_center,c,f(c),r_vir,n_vir,n_tot'
-    np.savetxt(directory+'/results.csv',data,fmt='%d,%f,%f,%f,%f,%f,%f,%d,%d',header=head)

### 2016-07-14 src/old/main.py

@@ -1,169 +1,0 @@
-import numpy as np, pylab, sys, os, datetime, nfw, mcmc, plotter, multiprocessing, time, fit
-
-# Gets the concentration and virial radius for several haloes
-
-config = open('config.div','r').readline().split(',')
-config[-1] = config[-1].replace('\n','')
-
-processes = int(config[5])
-now = datetime.datetime.now().strftime("%Y-%m-%d-%H:%M:%S")
-mass_element = 1.0
-plt = 1
-total_list = os.listdir(str(config[0]))
-len_list = len(total_list)
-lists = [total_list[i*len_list // processes: (i+1)*len_list //processes] for i in range(processes)]
-jobs = []
-
-if (config[7]=='0'):
-    print 'Plotting mode disabled'
-    plt = 0
-else:
-    print 'Plotting mode enabled'
-    plt = 1
-
-if config[8]=='0':
-    print 'Test mode disabled'
-else:
-    print 'Test mode enabled'
-
-os.system('mkdir mass_'+now)
-sys.stdout.write('\rCompiling the code used to calculate the center of each halo... ')
-sys.stdout.flush()
-os.system('cc potential.c -lm -o  potential.out')
-sys.stdout.write('Done\n')
-
-def run(directories,process_number):
-
-    process_number+=1
-    count = 0
-    filename_export = './mass_'+now+'/results_'+str(process_number)+'.csv'
-    os.system('touch '+filename_export)
-
-    for filename in directories:
-
-        count = count + 1
-        print '\rWorking with file '+str(count)+' of '+str(len(directories))+' in process '+str(process_number)
-
-    # Creates the "data" array with the information from the file in "path"
-        path = os.path.expanduser(str(config[0])+'/'+filename)
-        data = np.loadtxt(open(path, 'r'), delimiter=",",skiprows=int(config[4]))
-
-    # Gets the cartesian coordinates for each particle in the halo and the number of particles
-        x = data[:,int(config[1])]
-        y = data[:,int(config[2])]
-        z = data[:,int(config[3])]
-        n_points = len(x)
-
-    # Exports a file with the cartesian coordinates of each particle
-        file_id = int(filename.split('_')[1])
-        positions_name ='positions_'+str(file_id)+'.dat'
-        potential_name ='potential_'+str(file_id)+'.dat'
-        results_folder ='./mass_'+now+'/'+str(file_id)
[…]

### 2016-07-14 src/old/mcmc.pyx

@@ -1,54 +1,0 @@
-STUFF = "Hi"
-
-import numpy as np
-cimport numpy as np
-
-def chi2(np.ndarray p,model,np.ndarray x_obs,np.ndarray y_obs,np.ndarray sigma):
-    cdef float chi_sq = np.sum(((model(x_obs,p) - y_obs)/sigma)**2)
-    return chi_sq
-
-def walker(dist,np.ndarray state_0,np.ndarray step_size,n_iterations,reestrictions = None):
-
-    cdef int dims = len(state_0)
-    cdef np.ndarray walk = np.empty((dims,n_iterations))
-    cdef np.ndarray prob = np.empty(n_iterations)
-    cdef np.ndarray t_init
-    cdef np.ndarray t_prime
-    cdef float P_init
-    cdef float P_prime
-    cdef float a
-    cdef float b
-    walk[:,0] = state_0
-    prob[0] = dist(state_0)
-
-    if reestrictions == None:
-        reestrictions = [lambda x: True for i in range(dims)]
-        
-    for i in range(1,n_iterations):
-        
-        t_init = walk[:,i-1]
-        t_prime = np.empty(dims)
-        
-        for n in range(dims):
-            t_prime[n] = np.random.normal(t_init[n],step_size[n])
-            while reestrictions[n](t_prime[n]) == False:
-                t_prime[n] = np.random.normal(t_init[n],step_size[n])
-
-        P_init = dist(t_init)
-        P_prime = dist(t_prime)
-
-        a = -(P_prime-P_init)
-
-        if a > 0:
-            walk[:,i] = t_prime
-            prob[i] = P_prime
-        else:
-            b = np.log(np.random.random())
-            if a > b:
-                walk[:,i] = t_prime
-                prob[i] = P_prime
-            else:
-                walk[:,i] = t_init
-                prob[i] = P_init
-                
-    return walk,prob

### 2016-07-14 src/old/nfw.py

@@ -1,61 +1,0 @@
-import numpy as np
-
-# Profiles in normal scale
-# Parameters:
-#     r: numpy array with the radial distances from the center of the halo
-#     rho0: mean density
-#     rs: scale radius
-# Returns:
-#     a numpy array with the mass/density profile
-
-def mass(r,a,b):
-    return 4*np.pi*a*(b**3)*(np.log(1+r/b)-(1+(b/r))**(-1))
-
-def density(r,a,b):
-    return a*((r/b)*(1+(r/b))**2)**(-1)
-
-def mass_norm(r_norm,c):
-    return (np.log(1.0+r_norm*c)-r_norm*c/(1.0+r_norm*c))/(np.log(1.0+c)-c/(1.0+c))
-
-def density_norm(r_norm,c):
-    return ((1+c)**2/(r_norm*(1+r_norm*c)**2))
-
-def velocity_norm(r_norm,c):
-    return np.sqrt(mass_norm(r_norm,c)/r_norm)
-
-# Profiles in logarithmic scale
-# Parameters:
-#     logr: numpy array with the logarithm of the radial distances from the center of the halo
-#     a: mean density
-#     b: scale radius
-# Returns:
-#     a numpy array with the logarithm of the mass/density profile
-
-def logmass(logr,a,b):
-    return np.log(4*np.pi)+ np.log(a)+3*np.log(b)+np.log(np.log(1+np.exp(logr)/b)-(1+b/np.exp(logr))**(-1))
-
-def logdensity(logr,a,b):
-    return np.log(a)+np.log(b)-logr-2*np.log(1+np.exp(logr)/b)
-
-def logdensity_norm(logr_norm,c):
-    return (2.0*(np.log(1+c)-np.log(1+c*np.exp(logr_norm)))-np.log(logr_norm))
-
-# Profiles in logarithmic scale with logarithmic parameters
-# Parameters:
-#     logr: numpy array with the logarithm of the radial distances from the center of the halo
-#     loga: logarithm of the mean density
-#     logb: logarithm of the scale radius
-# Returns:
-#     a numpy array with the logarithm of the mass/density profile
-
-def loglogmass(logr,loga,logb):
-    return np.log(4*np.pi)+ loga+3*logb+np.log(np.log(1+np.exp(logr-logb))-(1+np.exp(logb-logr))**(-1))
-
[…]

### 2016-07-14 src/old/old_catalog.py

@@ -1,143 +1,0 @@
-import numpy as np, pylab, sys, matplotlib, plotter
-from matplotlib.mlab import griddata
-from scipy.optimize import curve_fit
-
-def distance(x1,y1,z1,x2,y2,z2):
-    return np.sqrt(((x1-x2)**2.0)+((y1-y2)**2.0)+((z1-z2)**2.0))
-
-mcmc = np.loadtxt(sys.argv[1],delimiter=',')
-bdmv = np.loadtxt(sys.argv[2],delimiter=',')
-
-mcmc_id = mcmc[:,0]
-mcmc_x = mcmc[:,1]
-mcmc_y = mcmc[:,2]
-mcmc_z = mcmc[:,3]
-mcmc_rho0 = mcmc[:,4]
-mcmc_rho0_max = mcmc[:,5]
-mcmc_rho0_min = mcmc[:,6]
-mcmc_rs = mcmc[:,7]
-mcmc_rs_max = mcmc[:,8]
-mcmc_rs_min = mcmc[:,9]
-mcmc_rvir = mcmc[:,10]
-mcmc_c = mcmc[:,11]
-
-bdmv_id = bdmv[:,0]
-bdmv_x = bdmv[:,1]
-bdmv_y = bdmv[:,2]
-bdmv_z = bdmv[:,3]
-bdmv_rvir = bdmv[:,7]
-bdmv_c = bdmv[:,8]
-bdmv_rs = bdmv_rvir/bdmv_c
-
-used_id = np.empty((0))
-used_x = np.empty((0))
-used_y = np.empty((0))
-used_z = np.empty((0))
-used_rho0 = np.empty((0))
-used_rho0_max = np.empty((0))
-used_rho0_min = np.empty((0))
-used_rs = np.empty((0))
-used_rs_max = np.empty((0))
-used_rs_min = np.empty((0))
-used_rvir = np.empty((0))
-used_c = np.empty((0))
-
-FA = 0
-NV = 0
-
-for i in range(len(bdmv_x)):
-    d = distance(bdmv_x[i],bdmv_y[i],bdmv_z[i],mcmc_x,mcmc_y,mcmc_z)
-    j = np.argmin(d)
-    d_min = d[j]
-
-    if (d_min <= (mcmc_rvir[j] + bdmv_rvir[i]) and mcmc_rvir[j] > 0):
-        used_id = np.append(used_id , mcmc_id[j])
-        used_x = np.append(used_x , mcmc_x[j])
[…]

### 2016-07-14 src/old/old_main.py

@@ -1,136 +1,0 @@
-import numpy as np, pylab, math, sys, timeit, os, random, datetime, nfw, fit, plotter
-from scipy.optimize import fsolve
-
-# Gets the mean-density, scale radius and virial radius for several haloes
-# It must be executed with the following command line:
-#
-#      python main.py directory #x #y #x noplot*
-#
-# Where:
-#      directory: is the path of the directory with the files with the positions of the haloes
-#      #x, #y, #z: are the column position of each coordinate in the files (for Multidark is 2 3 4)
-#      noplot: is an optional parameter, if it is added the code will not make any graphics
-#
-# Have fun! 
-#
-# Done by: Christian Poveda (cn.poveda542@uniandes.edu.co)
-
-totaltime = 0.0
-now = datetime.datetime.now().strftime("%Y-%m-%d-%H:%M:%S")
-
-plt = 1
-try:
-    if (sys.argv[5]=='noplot'):
-        print 'No Plotting mode enabled'
-        plt = 0
-except:
-    plt = 1
-
-os.system('mkdir results_'+now)
-
-sys.stdout.write('\rCompiling the code used to calculate the center of each halo... ')
-sys.stdout.flush()
-os.system('cc potential.c -lm -o  potential.out')
-sys.stdout.write('Done\n')
-
-export = open('./results_'+now+'/results_'+now+'.csv', 'w')
-export.write('#Id,x,y,z,rho0,rho0_max,rho0_min,rs,rs_max,rs_min,r_max,r_vir,c\n')
-export.close()
-
-fit.compile_c_metropolis()
-
-count = 1
-for filename in os.listdir('./'+str(sys.argv[1])):
-
-    start = timeit.default_timer()
-    print ''
-    sys.stdout.write('\rLoading data from "'+str(filename)+'" (file '+str(count)+' of '+str(len(os.listdir('./'+str(sys.argv[1]))))+') ... ')
-    count = count + 1
-    sys.stdout.flush()
-
-    path = os.path.expanduser('./'+str(sys.argv[1])+'/'+filename)
-    data = np.loadtxt(open(path, 'r'), delimiter=",",skiprows=16)
-
-    x = data[:,int(sys.argv[2])]
-    y = data[:,int(sys.argv[3])]
-    z = data[:,int(sys.argv[4])]
-    sys.stdout.write('Done\n')
[…]

### 2016-07-14 src/old/plotter.py

@@ -1,218 +1,0 @@
-import numpy as np, pylab,sys, nfw
-from matplotlib.mlab import griddata
-
-angle = np.arange(0,2*np.pi,0.01)
-
-# Plots a halo
-# Requires:
-#     x,y,z: arrays with the positions for each particle
-#     x_center,y_center,z_center: position of the halo center
-# Returns:
-#     Three files with graphics in the planes x-y, y-z and z-x of the halo
-
-def halo(x,y,z,x_center,y_center,z_center,r_vir):
-    
-    pylab.plot(x , y, 'k.')
-    pylab.plot(x_center , y_center, 'ko')
-    pylab.plot(r_vir*np.cos(angle)+x_center,r_vir*np.sin(angle)+y_center,'--b')
-    
-    pylab.xlabel('x (Mpc/H)')
-    pylab.ylabel('y (Mpc/H)')
-    pylab.title('Halo x-y')
-    pylab.savefig('halo_xy.pdf',format='pdf',dpi=300)
-    pylab.close()
-
-    pylab.plot(y , z, 'k.')
-    pylab.plot(y_center , z_center, 'ko')
-    pylab.plot(r_vir*np.cos(angle)+y_center,r_vir*np.sin(angle)+z_center,'--b')
-    pylab.xlabel('y (Mpc/H)')
-    pylab.ylabel('z (Mpc/H)')
-    pylab.title('Halo y-z')
-    pylab.savefig('halo_yz.pdf',format='pdf',dpi=300)
-    pylab.close()
-
-    pylab.plot(z , x, 'k.')
-    pylab.plot(z_center , x_center, 'ko')
-    pylab.plot(r_vir*np.cos(angle)+z_center,r_vir*np.sin(angle)+x_center,'--b')
-    pylab.xlabel('z (Mpc/H)')
-    pylab.ylabel('x (Mpc/H)')
-    pylab.title('Halo z-x')
-    pylab.savefig('halo_zx.pdf',format='pdf',dpi=300)
-    pylab.close()
-   
-# Plots the NFW mass profile 
-# Requires:
-#     radius: array with the radial distances
-#     mass: array with the mass values
-#     parameters: an array with the parameters of the NFW profile (mean density and scale radius)
-# Returns:
-#     A file with agraphic of the mass profile
-
-def mass(radius, mass, parameters):
-    
-    pylab.plot(radius , mass,'.r',label="Real Mass")
[…]

### 2016-07-14 src/old/potential.c

@@ -1,77 +1,0 @@
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-
-int count_lines(char *filename);
-
-// Gives an array with the gravitational potential for each particle
-// Requires:
-//    argv[1]: name of the file with the positions of each particle in x,y and z
-//    argv[2]: name of the file to export the potential of each particle
-// Returns:
-//    a file with the potential for each particle
-
-int main(int argc, char** argv){
-
- int i,j,n_points;
- double count;
- double* x;
- double* y;
- double* z;
- double* k;
- FILE *rfile;
- FILE *cfile;
-
- n_points = count_lines(argv[1]);
-
- rfile = fopen(argv[1], "r");
- cfile = fopen(argv[2], "w");
-
- x = malloc(n_points*sizeof(double));
- y = malloc(n_points*sizeof(double));
- z = malloc(n_points*sizeof(double));
- k = malloc(n_points*sizeof(double));
-
- for (i = 0; i < n_points; i ++){
-   fscanf(rfile,"%lf,%lf,%lf\n",&(x[i]),&(y[i]),&(z[i]));
-   k[i] = 0;
- }
-
-for (i = 0; i < n_points; i ++){
-   for (j = i+1; j < n_points; j ++){
-     count = 1.0/sqrt(pow(x[i]-x[j],2.0) + pow(y[i]-y[j],2.0) + pow(z[i]-z[j],2.0));
-     k[i] += count;
-     k[j] += count;    
-   }
- }
- for (i = 0; i < n_points; i ++){
-   fprintf(cfile,"%lf\n",k[i]);
- }
-}
-
-// Counts lines of a file, copied from github.com/forero/ComputationalPhysicsUniandes repository
-// Requires
-//    filename: a string with the name of the file
-// Returns:
-//    number of lines in the file
-int count_lines(char *filename){
-  FILE *in;
-  int n_lines;
-  int c;
-  if(!(in=fopen(filename, "r"))){
-    printf("problem opening file %s\n", filename);
-    exit(1);
-  }
-
-  n_lines = 0;
-  do{
-    c = fgetc(in);
-    if(c=='\n'){
-      n_lines++;
-    }
-  }while(c!=EOF);
-
-  rewind(in);
-  fclose(in);
-  return n_lines;
-}

### 2016-07-14 src/old/table.py

@@ -1,18 +1,0 @@
-import numpy as np
-
-data = np.loadtxt('results.csv',delimiter=',')
-orig = np.loadtxt('parameters.csv',delimiter=',')
-
-conc = orig[:,0]
-
-n = int(len(conc)/4)
-print n
-conc = conc[0:n]
-c_20 = data[0:n,4]
-c_200 = data[n:2*n,4]
-c_2000 = data[2*n:3*n,4]
-c_20000 = data[3*n:4*n,4]
-print len(conc),len(c_20),len(c_200),len(c_2000),len(c_20000)
-export = np.dstack((conc,c_20,c_200,c_2000,c_20000))[0]
-head = 'c,c_20,c_200,c_2000,c_20000'
-np.savetxt('table.csv',export,fmt='%f,%f,%f,%f,%f',header=head)

### 2016-07-14 src/old/velocity.py

@@ -1,143 +1,0 @@
-import numpy as np, pylab, math, sys, timeit, os, random, datetime, nfw, mcmc,fit , plotter, multiprocessing, time
-from scipy.optimize import fsolve
-
-# Gets the concentration and virial radius for several haloes
-
-config = open('config.div','r').readline().split(',')
-config[-1] = config[-1].replace('\n','')
-
-processes = int(config[5])
-now = datetime.datetime.now().strftime("%Y-%m-%d-%H:%M:%S")
-mass_element = 1.0   
-plt = 1
-total_list = os.listdir(str(config[0]))
-len_list = len(total_list)
-lists = [total_list[i*len_list // processes: (i+1)*len_list //processes] for i in range(processes)]
-jobs = []
-
-if (config[7]=='0'):
-    print 'Plotting mode disabled'
-    plt = 0
-else:
-    print 'Plotting mode enabled'
-    plt = 1
-
-if config[8]=='0':
-    print 'Test mode disabled'
-else:
-    print 'Test mode enabled'
-
-os.system('mkdir vlct_'+now)
-sys.stdout.write('\rCompiling the code used to calculate the center of each halo... ')
-sys.stdout.flush()
-os.system('cc potential.c -lm -o  potential.out')
-sys.stdout.write('Done\n')
-
-def run(directories,process_number):
-
-    process_number+=1
-    count = 0
-    filename_export = './vlct_'+now+'/results_'+str(process_number)+'.csv'
-    os.system('touch '+filename_export)
-
-    for filename in directories:
-
-        count = count + 1
-        print '\rWorking with file '+str(count)+' of '+str(len(directories))+' in process '+str(process_number)
-
-    # Creates the "data" array with the information from the file in "path"
-        path = os.path.expanduser(str(config[0])+'/'+filename)
-        data = np.loadtxt(open(path, 'r'), delimiter=",",skiprows=int(config[4]))
-
-    # Gets the cartesian coordinates for each particle in the halo and the number of particles
-        x = data[:,int(config[1])]
-        y = data[:,int(config[2])]
-        z = data[:,int(config[3])]
-        n_points = len(x)
-
-    # Exports a file with the cartesian coordinates of each particle
-        file_id = int(filename.split('_')[1])
-        positions_name ='positions_'+str(file_id)+'.dat'
-        potential_name ='potential_'+str(file_id)+'.dat'
-        results_folder ='./vlct_'+now+'/'+str(file_id)
[…]

### 2016-07-14 src/run_mass_bolshoi_all.sh
scripts on erebos

@@ -1,0 +1,1 @@
+nohup python mass.py --dir /scratch/jforero/Bolshoi/allhalos/largest/ -o full_bolshoi/results.csv -v -csv &

### 2016-07-14 src/run_mass_bolshoi_downsample.sh

@@ -1,0 +1,14 @@
+nohup python mass.py --dir /scratch/jforero/Bolshoi/jcdownsample/halos/003438/ -o downsample_bolshoi/results_mass_003438.csv -v -r 5.78735232e-01 &
+nohup python mass.py --dir /scratch/jforero/Bolshoi/jcdownsample/halos/004497/ -o downsample_bolshoi/results_mass_004497.csv -v -r 6.89785719e-01 &
+nohup python mass.py --dir /scratch/jforero/Bolshoi/jcdownsample/halos/014976/ -o downsample_bolshoi/results_mass_014976.csv -v -r 5.75412631e-01 &
+nohup python mass.py --dir /scratch/jforero/Bolshoi/jcdownsample/halos/019876/ -o downsample_bolshoi/results_mass_019876.csv -v -r 5.88606954e-01 &
+nohup python mass.py --dir /scratch/jforero/Bolshoi/jcdownsample/halos/026975/ -o downsample_bolshoi/results_mass_026975.csv -v -r 6.02686644e-01 &
+nohup python mass.py --dir /scratch/jforero/Bolshoi/jcdownsample/halos/030491/ -o downsample_bolshoi/results_mass_30491.csv -v -r 6.16504192e-01 &
+nohup python mass.py --dir /scratch/jforero/Bolshoi/jcdownsample/halos/036320/ -o downsample_bolshoi/results_mass_036320.csv -v -r 5.77344954e-01 &
+nohup python mass.py --dir /scratch/jforero/Bolshoi/jcdownsample/halos/055806/ -o downsample_bolshoi/results_mass_055806.csv -v -r 5.66279829e-01 &
+nohup python mass.py --dir /scratch/jforero/Bolshoi/jcdownsample/halos/059095/ -o downsample_bolshoi/results_mass_059095.csv -v -r 5.77222586e-01 &
+nohup python mass.py --dir /scratch/jforero/Bolshoi/jcdownsample/halos/059875/ -o downsample_bolshoi/results_mass_059875.csv -v -r 6.73682272e-01 &
+nohup python mass.py --dir /scratch/jforero/Bolshoi/jcdownsample/halos/060662/ -o downsample_bolshoi/results_mass_060662.csv -v -r 6.18945062e-01 &
[…]

### 2016-07-14 src/run_mass_vialactea_downsample.sh

@@ -1,0 +1,1 @@
+nohup python mass.py --dir /scratch/jforero/ViaLactea/downsample/ -o downsample_vialactea/results_mass_vialactea.csv -v -r 207.11499608 &

### 2016-07-14 src/mass.py
mass.py

@@ -40,9 +40,11 @@ def nfw_log_mass(log_r,log_c):
 # Loglikelihood using the chi squared. If the concentration is less than one it
 # returns -inf.
 def log_likelihood(log_c,log_r,log_m):
+    n = 1.0*len(log_m)
     if log_c >= 0:
         s = np.sum(log_m-nfw_log_mass(log_r,log_c))
-        return -.5*s*s
+        sigma2 = (1.0 - np.exp(log_r))/(np.exp(log_r)) * (n **1.15)/4500.0
+        return -0.5*s*s/sigma2
     return -np.inf
 
 def main():
@@ -88,6 +90,9 @@ def main():
             else:
                 virial_radius = args.radius
             r = r/virial_radius
+
+            r = np.delete(r,-1)
+
             del x,y,z
 
             n_particles = len(r)

### 2016-07-14 src/mass.py
fixes edge case

@@ -43,8 +43,11 @@ def log_likelihood(log_c,log_r,log_m):
     n = 1.0*len(log_m)
     if log_c >= 0:
         s = np.sum(log_m-nfw_log_mass(log_r,log_c))
-        sigma2 = (1.0 - np.exp(log_r))/(np.exp(log_r)) * (n **1.15)/4500.0
-        return -0.5*s*s/sigma2
+        sigma2 = (1.0 - np.exp(log_r))/(np.exp(log_r)) * (n**1.15)/4500.0
+        if(np.any(sigma2<0.0)):
+            return -np.inf
+        else:
+            return -0.5*s*s/sigma2
     return -np.inf
 
 def main():
@@ -84,15 +87,16 @@ def main():
 
             r = np.sqrt(x*x+y*y+z*z)
             r = np.sort(r)
-            r = np.delete(r,0)
+            ii = r<1E-8
+            r  = np.delete(r,np.int_(ii))
             if args.radius == None:
                 virial_radius = r[-1]
             else:
                 virial_radius = args.radius
             r = r/virial_radius
 
-            r = np.delete(r,-1)
 
+            r = np.delete(r,-1)
             del x,y,z
 
             n_particles = len(r)

### 2016-07-17 paper/ms.tex
drop 6
notation

@@
 \begin{equation}
-\sigma_x^2 = \frac{1-x}{x}\frac{1}{6N}.
+\sigma_x^2 = \frac{1-x}{x}\frac{1}{N}.
 \label{eq:sigma}
@@
 %
-where $\sigma_i^2=\sigma_x^2$, $m(<x_i;c)$ corresponds to the
+where $\sigma_i^2=\sigma_x^2(x_i)$, $m(<x_i;c)$ corresponds to the
 values in Eq.(\ref{eq:profile}) at $x=x_i$ for a given value of the
@@
 However, tests on the bootstrapping data show that the covariance
-matrix is not diagonal and using $\sigma_i^2=\sigma_x^2$ would grossly
+matrix is not diagonal and using $\sigma_i^2=\sigma_x^2(x_i)$ would grossly
 overestimate $\chi^2(c)$ providing too optimistic error bars.
@@
 
-We then use $\sigma_i^2=\sigma_{\rm eff}^2$ to feed an Affine
+We then use $\sigma_i^2=\sigma_{\rm eff}^2(x_i)$ to feed an Affine
 Invariant Markov Chain Monte Carlo implemented in the python module

### 2016-07-18 paper/ms.tex
ready to submit

--- 2016-07-13 paper/ms.tex
@@
 To control this bias at low particle numbers we propose a new
-algorithm to estimate halo concentrations based on the integrated mass
-profile.   
+algorithm that estimates halo concentrations based on the integrated
+mass profile.
 The method uses the full particle information without any binning,
@@
 limitation for other methods.
-This method reduces the bias to $1\%-3\%$ for halos sampled with
+This method reduces the bias to $< 3\%$ for halos sampled with
 $200$-$500$ particles.
@@
 We also show that the mass-concentration relationship could be
-shallower than expected from numerical experiments once the biases 
-of the different concentration measurements are taken into account.
-These results show that bootstrapping and the
-concentration estimates based on the integrated mass profile are
-valuable tools to probe the internal structure of dark matter halos
-in numerical simulations.
+shallower than expected once the biases  of the different
+concentration measurements are taken into account. 
+These results show that bootstrapping and the concentration estimates
+based on the integrated mass profile are valuable tools to probe the
+internal structure of dark matter halos in numerical simulations. 
 \end{abstract}
@@
 \keywords{
-Galaxies: halos --- Galaxies: high-redshift --- Galaxies: statistics
---- Dark Matter --- Methods: numerical 
+Galaxies: halos --- Dark matter --- Methods: numerical 
 }
@@
 tune numerical parameters.   
-This method provides a new independent method to estimate the
+This is a new independent method to estimate the
 concentration parameter.
@@
   For each case close to $10000$ bootstrapping samples are used.
-  The velocity method noticeably overestimates the concentration up to
-  a factor of $0.20$, 
-  while the new method only underestimates the concentrations by up to
-  a factor of $0.04$.
+  The density method noticeably overestimates the concentration up to
+  a factor of $20\%$, 
+  while the new method only underestimates the concentrations by less
+  than $3\%$.
   \emph{Right panel.}
@@
   been normalized by the preferred concentration value for each halo. 
-  In both cases (bootstrapping for individual halos and MCMC fit of a
-  halo population) the $1\sigma$ is of the same order with a
-  decreasing behavior as $1/\sqrt{N_s}$.
+  The $1\sigma$ bootstrapping uncertainty follow a $1/\sqrt{N_s}$
+  behaviour. 
   \label{fig:downsampling}}
@@
 
-\subsection{Our proposal: estimate from the integrated mass profile}
+\subsection{Estimate from the integrated mass profile}
 
@@
 
-We divide the enclosed mass mass $M_i$ and the radii $r_i$ by their
+We divide the enclosed mass $M_i$ and the radii $r_i$ by their
 virial values to obtain the dimensionless variables $m_i$ and $x_i$.
@@
 concentration is the only free parameter.
-We then use an Affine Invariant Markov Chain Monte Carlo implemented
-in the python module {\texttt{emcee}} \citep{emcee} to sample the
-likelihood function distribution defined by ${\cal L}(c)\propto
-\exp(-\chi^2(c)/2)$ where the $\chi^2(c)$ is written as
+
+Using bootstrapping data (\S \ref{sec:bootstrapping}) we find that at
+a given normalized radius, $x$, the logarithm of the normalized
+integrated mass, $m$, approximately follows a gaussian distribution
+with variance
 
 \begin{equation}
-\chi^2(c)= \frac{1}{N}\sum_{i=1}^{N}[\log m_i - \log m(< x_i;c)]^2,
+\sigma_x^2 = \frac{1-x}{x}\frac{1}{N}.
+\label{eq:sigma}
+\end{equation}
+
+If the integrated mass values at different radii were independent from
+each other we could write a likelihood distribution as ${\cal
+  L}(c)\propto \exp(-\chi^2(c)/2)$ with
+
+\begin{equation}
+\chi^2(c)= \sum_{i=2}^{N-1}\frac{[\log m_i - \log m(< x_i;c)]^2}{\sigma_i^2},
 \end{equation}
 %
-where $m(<x_i;c)$ corresponds to the values in Eq.(\ref{eq:profile})
-at $x=x_i$ for a given value of the concentration parameter $c$ and
-the $i$ index sums over all the particles in the numerical profile.
+where $\sigma_i^2=\sigma_x^2(x_i)$, $m(<x_i;c)$ corresponds to the
+values in Eq.(\ref{eq:profile}) at $x=x_i$ for a given value of the
+concentration parameter $c$, and the $i$ index sums over all the
+particles in the numerical profile. 
+In this computation the particles $i=1$ and $i=N$ are discarded to
+avoid divergent terms in the sum.
+
+However, tests on the bootstrapping data show that using
+$\sigma_i^2=\sigma_x^2(x_i)$, instead of the full inverse covariance
+matrix, grossly overestimates $\chi^2(c)$,
+providing small uncertainties around the best concentration value. 
+To avoid the expensive computation and inversion of a full covariance
+matrix we use the bootsrapping data to calibrate an effective
+$\sigma_i^2\approx \sigma_{\rm eff}^2(x_i)$.
+
+We impose two conditions on the approximate $\sigma_{\rm eff}^{2}$. It
+must keep the dependence on $x$ that we have discovered for the
+diagonal elements and must give similar curves of $\chi^{2}(c)$-$c$
+around the minimum as the full covariance matrix.
+We found that this effective $\sigma_{\rm eff}^2$ can be approximated
+as
+
+\begin{equation}
+\sigma_{\rm eff}^2 = \frac{1-x}{x}\frac{N^{1.15}}{4.5\times 10^3}.
+\end{equation}
+
+We then use an Affine Invariant Markov Chain Monte Carlo (MCMC)
+implemented in the python module {\texttt{emcee}} \citep{emcee} to sample the
+likelihood function distribution.
 From the $\chi^2$ distribution we find the optimal value of the
-concentration and its associated uncertainty.
+concentration and its associated uncertainty. Different choices for
+$\sigma^2_{\rm eff}$ do not affect the optimal concentration value,
+only its uncertainty.
 
@@
 
-We use two very different simulations to be sure that the results (bias,
-uncertainty on the bias) measured using bootstrapping tests are
-independent of the kind of parent simulation.
-
-We use data from the Bolshoi cosmological simulation that follows the
-non-linear evolution of a dark matter density field sampled with
-$2048^3$ particles over a cubic box of $250\ \hMpc$ on a side.  
+We use two very different simulations to test our methods.
+The first data sample comes from the Bolshoi run, a cosmological
+simulation that follows the non-linear evolution of a dark matter density field
+sampled with $2048^3$ particles over a cubic box of $250\ \hMpc$ on a side.  
 The cosmological parameters use a Hubble parameter $h=0.73$, a matter density
@@
 We use a halo sample containing all the halos located in a cubic
-sub-volume of $100$ \hMpc\ on a side.  
+sub-volume of $100$ \hMpc\ on a side containing a total of $64531$
+halos. 
 From this sample we select all the halos at $z=0$ detected with a
@@
   The dotted line corresponds to fits reported by \citep{Prada2012}.
-  \label{fig:concentration}. 
   The left panel shows the raw results coming from each algorithm. 
@@
   experiments presented in Figure 
-  \ref{fig:downsampling}.} 
+  \ref{fig:downsampling}.
+  \label{fig:concentration}} 
 \end{figure*}
@@
 We tested that leaving the virial radius and center free in each
-bootstrapping iteration has an effect lower than $1\%$ in the
+bootstrapping iteration has an effect smaller than $1\%$ in the
 concentration. 
@@
 and the Via Lactea simulations.
-In the case of the Bolshoi simulation we select 14 massive halos and
-create 700 subsamples for each halo. 
-For the Via Lactea simulation only one halo is subsampled 10000
+In the Bolshoi simulation we select 14 massive halos and create 700
+subsamples for each one.  
+For the Via Lactea simulation the same halo is subsampled 10000
 times.
@@
 The average concentration value for the largest number of particles,
-$c_{N_{max}}$, provides with a baseline to compare all the other
-results.  
+$c_{N_{max}}$, provides a baseline to compare all the other results.  
 We use the following statistic
@@
 downsampled particle number $c_{N}$ and the baseline $c_{N_{max}}$.
-For each method we keep its corresponding concentration $c_{N_{max}}$
-value at high resolution.
 
@@
 The plot on the left shows the average value of $f_{\rm off}$ as a
-function of the particle number.  
-As expected, for large enough sample particle numbers,
-$N_{s}>4\times 10^3$, the results of the three algorithms coincide
-below the $1\%$ level.
-For a lower number of particles, the results deviate from the expected
-concentration value.  
-For $200$ particles the velocity method overestimates by a factor
-$14\%$ while the density method overestimates it by $20\%$.
+function of particle number.  
+As expected, for a large enough particle number, $N_{s}>4\times 10^3$,
+the results of the three algorithms coincide below the $1\%$ level.
+For a lower number of particles the results start to deviate.
+At $200$ particles the velocity method overestimates the concentration
+by a factor $14\%$ while the density method overestimates it by $20\%$.
 Around the same sampling scale, the new algorithm shows a more stable
 behaviour underestimating the concentration only by a factor of
-$1\%$-$2\%$
+$1\%$-$3\%$
 
-The line on the same panel shows a fit to the data with the following
-functional form 
+The thin continous lines on the same panel shows a fit to the data
+with the following functional form 
 \begin{equation}
@@
 \end{equation} 
-for the dataset shown in the panel we have $A=2842\pm 1900$,
+for the dataset shown in the panel we find $A=2842\pm 1900$,
 $B=7.96\pm 0.54$ for the density method; $A=239\pm 131$,
@@
 
-The right panel in \ref{fig:downsampling} shows different uncertainty
+The right panel in Figure \ref{fig:downsampling} shows different uncertainty
 results.  
@@
 This shows that the bootstrapping technique can help us to assign a
-$1\sigma$ uncertainty to the concentration values at a fixed $N_s$. 
-This uncertainty is shown as normalized by the preferred value of the
-concentration, which in this case corresponds to $c_{N_{max}}$.  
-The circles in the same figure show the $1\sigma$ uncertainty as
-estimated from the MCMC chains using the integrated mass method on all
-the relaxed halos in the Bolshoi simulation sample. 
-To allow for a fair comparison with the bootstrapping results, this
-uncertainty was normalized by the preferred concentration.
-The MCMC uncertainties follow the same trend as the bootstrapping
-results.
-
-From these results we defined a universal $1\sigma$ fractional
-uncertainty for the concentration as a function of the number of
-particles $N_s$ as  
+$1\sigma$ uncertainty to the concentration values at a fixed $N_s$as 
 %
@@
 
+The circles in the same Figure show the $1\sigma$ uncertainty as
+estimated from the MCMC chains using the integrated mass method on all
+the relaxed halos in the Bolshoi simulation sample. 
+To allow for a fair comparison with the bootstrapping results, this
+uncertainty was normalized by the concentration value.
+Below the range $N_{s}<10^5$ the MCMC uncertainty is lower than the
+bootstrapping estimate, with a weak dependence on the particle
+number.
+
 \subsection{Impact on the Mass-Concentration Relationship}
@@
 relationship obtained with the three different algorithms.
-This helps to compare the concentration results
-of the new algorithm and, more importantly, showcase a probable
+This helps us to study the concentration results
+for the new algorithm and, more importantly, showcase a probable
 consequence of the biases detected through bootstrapping.
@@
 The left panel shows the results as they are produced by each of the
-algorithms, the thin dashed line marks the results by
-\citep{Prada2012}.
+algorithms. The thin dashed line marks the trend reported by
+\citep{Prada2012} using the velocity method.
 
@@
 closely the velocity algorithm at high masses ($M_h>10^{12}\hMsun$ or
-equivalently for $>8\times10^3$ particles). 
+equivalently for $>4\times10^3$ particles). 
 For lower masses there is a difference between the median of the two
@@
 However, they implemented a modified version of the velocity algorithm
-that uses the data binning obtained for the density algorithm.
+that bins the particle data, which might explain why they the offset
+was not reported.
 
 We hypothesize that the increase in the results for the velocity
-and density methods below $8\times 10^{3}$ particles come from the
+and density methods below $4\times 10^{3}$ particles comes from the
 systematic bias described in the previous section.  
-To test the general consistency of this hypothesis we correct the
+To test the general consistency of this hypothesis, we correct the
 concentration values in the velocity and integrated mass methods by a
@@
 (\ref{fig:downsampling}).  
-The correction brings into perfect agreement the results between the
+The correction brings into good agreement the results between the
 velocity/density methods and the new algorithm.
@@
 The results of the algorithm on the same data sample showed a bias  of
-$2\%-3\%$ for halos with $200$ particles and less than $1\%$ for halos
+$< 3\%$ for halos with $200$ particles and less than $1\%$ for halos
 with $500$ particles or more.  
@@
  The authors acknowledge the technical support from the new
- high-performance computing facility at Uniandes. JEF-R acknowledges
+ high-performance computing facility at Uniandes. JEFR acknowledges
  financial support from Vicerrector\'ia de Investigaciones at Uniandes

### 2016-08-11 paper/ms.tex

@@
 $B=7.96\pm 0.54$ for the density method; $A=239\pm 131$,
-$B=6.23\pm 0.43$ for the velocity method; $A=-3.66\pm 5.22$,
-$B=4.65\pm 1.12$ for the integrated mass method.
+$B=6.23\pm 0.43$ for the velocity method; $A=-0.46\pm 3.49$,
+$B=0.79\pm 1.31$ for the integrated mass method.
 The uncertainties are estimated from the covariance  matrix resulting

### 2016-08-11 src/ks_test.py
ks test to check good randomization

@@ -1,0 +1,31 @@
+import numpy as np
+from scipy import stats
+
+
+
+def make_ks_test(halo_id=0):
+    n_samples = 700
+    fileout = open('ks_test_p_values_{:06d}.dat'.format(halo_id), 'w')
+    fileout.write("#id_i id_j n_part_i n_part_j ks_test_value pvalue\n")
+    print(fileout)
+
+    filename = '/scratch/jforero/Bolshoi/allhalos/largest/halo_{:06}.dat'.format(halo_id)
+    data = np.loadtxt(filename, delimiter=',')
+    r = np.sqrt(data[:,0]**2 + data[:,1]**2+ data[:,2]**2)
+    for j in range(n_samples):
+        print halo_id, j
+        filename_j = '//scratch/jforero/Bolshoi/jcdownsample/halos/{:06d}/sample_{:03d}.dat'.format(halo_id,j)
+        data_j = np.loadtxt(filename_j)
+        r_j = np.sqrt(data_j[:,0]**2 + data_j[:,1]**2+ data_j[:,2]**2)
+
+        ks_value, p_value = stats.ks_2samp(r, r_j)
+        fileout.write("{} {} {} {}\n".format(j, len(r_j), ks_value, p_value))
+
+    fileout.close()
+
+
+
+halo_id_list = [3438, 4497, 14976, 19876, 26975, 30491, 36320, 55806, 59095, 59875, 60662, 69962, 73222, 78002]
+
+for halo_id in halo_id_list:
+    make_ks_test(halo_id=halo_id)

### 2016-08-12 src/ks_test.py
test

@@ -1,8 +1,6 @@
 import numpy as np
 from scipy import stats
 
-
-
 def make_ks_test(halo_id=0):
     n_samples = 700
     fileout = open('ks_test_p_values_{:06d}.dat'.format(halo_id), 'w')

### 2016-08-25 paper/ms.tex
KS test. Mencionado en el paper y en el reply

@@
 \submitted{{\it Submitted for publication in ApJL}}
-\usepackage{multirow,color,wrapfig,ulem}
+\usepackage{multirow,color,wrapfig}
 \usepackage {graphicx}
@@
 resampled. 
-Every time we keep fixed the virial radius and the center found for
-the high resolution halo.
-We tested that leaving the virial radius and center free in each
-bootstrapping iteration has an effect smaller than $1\%$ in the
-concentration. 
+We use a two-sample Kolmogorov-Smirnov (KS) test to check that the
+bootstrapped sets are a fair subsample of the parent halo.
+Using the KS test we compare the list of radial distances from each
+subsample against that of its parent halo.
+We find that the resulting p-value distribution is flat.
+This confirms that the radial distribution of particles in the
+bootraped halo is consistent with coming from the distribution given
+by the parent halo.
+
+For every subsample we keep fixed the virial radius and the center
+found for the high resolution halo.
+Leaving the virial radius and center free in each bootstrapping
+iteration has an effect smaller than $1\%$ in the concentration. 
 We extract in total 10000 bootstrapping samples for the Bolshoi
@@
  ``Estrategia de  sostenibilidad 2014-2015, Universidad de
- Antioquia''.
+ Antioquia''. The authors also thank Tom\'as Verdugo, Stefan
+ Gottloeber and Nelson Padilla for their comments on earlier version
+ of this work.
 

### 2016-08-25 paper/ms.tex
new references and impact on recent work

@@
 cosmological parameters.  In many numerical studies
-\citep{Neto2007,Maccio2008,Duffy2008,Munoz2011,Prada2012,Ludlow2014}
+\citep{Neto2007,Maccio2008,Duffy2008,Munoz2011,Prada2012,Ludlow2014,Ludlow2016,Klypin2016}
 the results are summarized through the mass-concentration
@@
 This method has been broadly used for more than two decades to study
-the mass-concentration-redshift relation of dark matter halos.
+the mass-concentration-redshift relation of dark matter halos. A
+recent example is \citep{Ludlow2016}
 
@@
 corresponding value of the concentration using Eq. (\ref{eq:max_v}).
-This method has been most recently used by \cite{Klypin2016} to study
-the mass-concentration-redshift relation using the Multidark
-Simulation Suite.
+A recent example of this methodology in cosmological simulation is
+given by \cite{Klypin2016}.
 
@@
 
-In our bootstrapping experiments we take halos sampled with at least
-$10^{5}$ particles and subsample each halo by factors of $2$ up to
-$10^{3}$ to measure the concentration every time the halo is
-resampled. 
+In our bootstrapping experiments we take halos with at least
+$10^{5}$ particles and subsample them by factors of $2$ up to
+$10^{3}$ to measure the concentration in every resampling.
 We use a two-sample Kolmogorov-Smirnov (KS) test to check that the
-bootstrapped sets are a fair subsample of the parent halo.
+bootstrapped sets are a fair subsample of its parent.
 Using the KS test we compare the list of radial distances from each
@@
 
+How does this impact the most recent mass-concentration estimates? 
+\cite{Ludlow2016} and \cite{Klypin2016} estimated the mass-concentration
+relation over a suite of cosmological N-body simulations using the
+density and velocity methods, respectively. 
+Both used halos that had at least $5\times 10^{3}$ particles,
+so their results should not be affected by the bias we report here.
+However, Figure 16 in \cite{Klypin2016} seems to push the results
+below this particle limit for redshifts larger than $z=2.5$ where
+their simulations should not be able to reach the mass range
+$5\times 10^{10}$\hMsun - $5\times 10^{12}$\hMsun that they claim. 
+Consistent with this limitation \cite{Ludlow2016} only report results
+up to a redshift of $z=3$.
+
 \section{Conclusions}
@@
  Antioquia''. The authors also thank Tom\'as Verdugo, Stefan
- Gottloeber and Nelson Padilla for their comments on earlier version
+ Gottloeber and Nelson Padilla for their comments on earlier versions
  of this work.
@@
 %\bibliography{references}
-\begin{thebibliography}{15}
+\begin{thebibliography}{16}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
   2016, \mnras, 457, 4340
+
+\bibitem[{{Ludlow} {et~al.}(2016){Ludlow}, {Bose}, {Angulo}, {Wang},
+  {Hellwing}, {Navarro}, {Cole}, \& {Frenk}}]{Ludlow2016}
+{Ludlow}, A.~D., {Bose}, S., {Angulo}, R.~E., {Wang}, L., {Hellwing}, W.~A.,
+  {Navarro}, J.~F., {Cole}, S., \& {Frenk}, C.~S. 2016, \mnras, 460, 1214
 

### 2016-08-25 paper/ms.tex
muchos edits, casi listo

--- 2016-08-25 paper/ms.tex
@@
 In this paradigm the sizes and dynamics of galaxies are driven by
-the DM distribution inside a halo. This has motivated the detailed study
-a DM halo internal structure in the last three decades.
+the halo internal DM distribution.
 
 The internal DM distribution in a halo is usually parameterized
-through the density profile.  In a first approximation this profile is
-spherically symmetric; the density only depends on the radial
-coordinate.  One of the most popular radial parameterizations is
-the Navarro-Frenk-White (NFW) profile \citep{NFW}.  
+through the density profile.  
+In a first approximation this profile is spherically symmetric; the
+density only depends on the radial coordinate.  
+One of the most popular radial parameterizations is the
+Navarro-Frenk-White (NFW) profile \citep{NFW}.   
 This profile can be considered as universal \citep{Navarro2010}, assuming that 
-one is not interested in the very central region of the dark matter halo where
-galaxy formation takes place, and where the effects of baryon physics
-on dark matter distribution are still unknown.
+one is not interested in the very central region where galaxy
+formation takes place, and where the effects of baryon physics on the
+dark matter distribution are still unknown. 
 This profile is a double power law in radius, where the transition
-break happens at the so-called scale radius, $r_s$.  The ratio between
-the scale radius and the halo virial radius $R_v$ is known as the
-concentration $c=R_v/r_s$.
+break happens at the so-called scale radius, $r_s$.  
+The ratio between the scale radius and the halo virial radius $R_v$ is
+known as the concentration $c=R_v/r_s$.
 
@@
 to study simulated dark matter halos as a function of redshift and
-cosmological parameters.  In many numerical studies
-\citep{Neto2007,Maccio2008,Duffy2008,Munoz2011,Prada2012,Ludlow2014}
-the results are summarized through the mass-concentration
-relationship; that is the distribution of concentration values at a
-fixed halo mass and redshift.  The success of such numerical
-experiments rests on a reliable algorithm to estimate the
-concentration.  Such an algorithm should provide unbiased results and
-must be robust when applied to simulations of different numerical
-resolution.
+cosmological parameters.  
+Numerical studies
+\citep{Neto2007,Maccio2008,Duffy2008,Munoz2011,Prada2012,Ludlow2014,Ludlow2016,Klypin2016}
+summarized their results through the mass-concentration
+relationship; that is, the distribution of concentration values at a
+fixed halo mass and redshift.  
+The success of such numerical experiments rests on a reliable
+algorithm to estimate the concentration.  
+Such an algorithm should provide unbiased results and must be robust
+when applied at varying numerical resolution.
 
 There are two established algorithms to estimate the concentration
-parameter of a N-body dark matter halo.  The first method takes the
-halo particles and bins them into logarithmic radii to estimate the
-density in each bin, then it proceeds to fit the density as a function
-of the radius to the NFW profile.  A second method uses an analytic
-property of the NFW profile that relates the maximum of the ratio of
-the circular velocity to the virial velocity, $V_{\rm circ}$/$V_{\rm
-  vir}$.  The concentration can be then found as the root of an
-algebraic equation dependent on this maximum value.
+parameter.
+The first method takes the halo particles and bins them into
+logarithmic radii to estimate the density in each bin, then it
+proceeds to fit the density as a function of the radius.  
+A second method uses an analytic property of the NFW profile that
+relates the maximum of the ratio of the circular velocity to the
+virial velocity, $V_{\rm circ}$/$V_{\rm   vir}$.  The concentration
+can be then found as the root of an algebraic equation dependent on
+this maximum value.
 
@@
 order to have a proper density estimate in each bin.  This makes the
-method robust only for halos with at least $10^2$ particles.  The
+method robust only for halos with at least $10^3$ particles.  The
 second problem is that there is not a way to estimate the optimal
@@
 It works with low particle numbers and does not involve data binning.  
-However,
-it effectively takes into account only a single data point and
-discards the behavior of the ratio $V_{\rm circ}/V_{\rm vir}$ below
-and above its maxima.  
-Small fluctuations on the value of this maximum
-can yield large perturbations on the estimated concentration
-parameter.
+However, it effectively takes into account only a single data point
+and discards the rest of the data.
+Small fluctuations on the maximum can yield large perturbations on the
+estimated concentration parameter.
 
@@
 It does not involve any data binning and does not throw away data points.  
-This translates into a robust estimate even at low resolution/particle numbers.  
+This translates into a robust estimate even at low resolution/particle
+numbers.   
 Furthermore, since the method does not require any binning, there is no need to
@@
   Lactea) simulation.
-  For each case close to $10000$ bootstrapping samples are used.
   The density method noticeably overestimates the concentration up to
@@
   been normalized by the preferred concentration value for each halo. 
-  The $1\sigma$ bootstrapping uncertainty follow a $1/\sqrt{N_s}$
-  behaviour. 
   \label{fig:downsampling}}
@@
 dark matter halos extracted from N-body simulations.  The first method
-tries to directly estimate the density profile.  It takes all the
-particles in the halo and bins them in the logarithm of the radial
-coordinate from the halo center.  Then, it estimates the density in
-each logarithmic bin counting the particles and dividing by the
-corresponding shell volume.  At this point is possible to make a
+takes all the particles in the halo and bins them in the logarithm of
+the radial coordinate from the halo center.  Then, it estimates the
+density in each logarithmic bin.  At this point is possible to make a
 direct fit to the density as a function of the radial coordinate.
@@
 the mass-concentration-redshift relation of dark matter halos. 
-
 A second method uses the circular velocity profile.  It finds the
@@
 corresponding value of the concentration using Eq. (\ref{eq:max_v}).
-This method has been most recently used by \cite{Klypin2016} to study
-the mass-concentration-redshift relation using the Multidark
-Simulation Suite.
 
@@
 It uses the integrated mass profile defined in
-Eq. (\ref{eq:profile}).  We build it from N-body data following the
-next steps.  First, we define the center of the halo to be at the
-position of the particle with the lowest gravitational potential.
-Then we rank the particles by their increasing radial distance from
-the center.  From this ranked list of $i=1,N$ particles, the total
-mass at a radius $r_i$ is $M_i=i\times m_p$, where $r_i$ is the
-position of the $i$-th particle and $m_p$ is the mass of a single
-computational particle.
-
-We divide the enclosed mass $M_i$ and the radii $r_i$ by their
-virial values to obtain the dimensionless variables $m_i$ and $x_i$.
-Once the mass profile is expressed in dimensionless variables the
-concentration is the only free parameter.
+Eq. (\ref{eq:profile}).  We build it from N-body data as follows.
+First, we define the center of the halo to be at the position of the
+particle with the lowest gravitational potential. Then we rank the
+particles by their increasing radial distance from the center.  From
+this ranked list of $i=1,N$ particles, the total mass at a radius
+$r_i$ is $M_i=i\times m_p$, where $r_i$ is the position of the $i$-th
+particle and $m_p$ is the mass of a single computational particle. 
+We then divide the enclosed mass $M_i$ and the radii $r_i$ by their
+virial values to finally obtain the dimensionless variables $m_i$ and
+$x_i$.
 
@@
 each other we could write a likelihood distribution as ${\cal
-  L}(c)\propto \exp(-\chi^2(c)/2)$ with
+  L}(c|x_i)\propto \exp(-\chi^2(c,x_i)/2)$ with
 
 \begin{equation}
-\chi^2(c)= \sum_{i=2}^{N-1}\frac{[\log m_i - \log m(< x_i;c)]^2}{\sigma_i^2},
+\chi^2(c,x_i)= \sum_{i=2}^{N-1}\frac{[\log m_i - \log m(< x_i;c)]^2}{\sigma_i^2},
 \end{equation}
@@
 $\sigma_i^2=\sigma_x^2(x_i)$, instead of the full inverse covariance
-matrix, grossly overestimates $\chi^2(c)$,
+matrix, grossly overestimates $\chi^2(c,x_i)$,
 providing small uncertainties around the best concentration value. 
@@
 must keep the dependence on $x$ that we have discovered for the
-diagonal elements and must give similar curves of $\chi^{2}(c)$-$c$
+diagonal elements and must give similar curves of $\chi^{2}(c,x_i)$-$c$
 around the minimum as the full covariance matrix.
@@
 From the $\chi^2$ distribution we find the optimal value of the
-concentration and its associated uncertainty. Different choices for
-$\sigma^2_{\rm eff}$ do not affect the optimal concentration value,
-only its uncertainty.
+concentration and its associated uncertainty. 
+We stress that different choices for $\sigma^2_{\rm eff}$ do not
+affect the optimal concentration value, only its uncertainty.
 
@@
 
-We use two very different simulations to test our methods.
-The first data sample comes from the Bolshoi run, a cosmological
-simulation that follows the non-linear evolution of a dark matter density field
-sampled with $2048^3$ particles over a cubic box of $250\ \hMpc$ on a side.  
-The cosmological parameters use a Hubble parameter $h=0.73$, a matter density
-$\Omega_m=0.3071$ and a normalization of the power spectrum
+We use two different simulations to test our methods.
+The first is the Bolshoi run, a cosmological simulation that follows
+the non-linear evolution of a dark matter density field sampled with
+$2048^3$ particles over a cubic box of $250\ \hMpc$ on a side.   The
+cosmological parameters use a Hubble parameter $h=0.73$, a matter
+density $\Omega_m=0.3071$ and a normalization of the power spectrum
 $\sigma_8=0.82$. 
@@
 Details about the structure of the database and the simulation can be
-found in \citep{2013AN....334..691R}.
+found in \citep{2011ApJ...740..102K,2013AN....334..691R}.
 
-We use a halo sample containing all the halos located in a cubic
-sub-volume of $100$ \hMpc\ on a side containing a total of $64531$
-halos. 
+We use the halos located in a cubic sub-volume of $100$ \hMpc\ on a
+side containing a total of $64531$ objects.
 From this sample we select all the halos at $z=0$ detected with a
@@
 From this set of particles we follow the procedure spelled out in
-Section \ref{sec:method} with $\Delta_h=740$ (corresponding to $200$
-times the critical density) to select an spherical region that we
-redefine to be our halo.  
+Section \ref{sec:method} with $\Delta_h=740$ to select an spherical
+region that we redefine to be our halo.  
 This choice makes that the overdensities are fully included inside the
@@
 \citep{2008Natur.454..735D}.  
-This simulation was run for a single isolated halo with a virial mass
-of the order of $10^{12}$\hMsun using the parallel tree code PKDGRAV
+This simulation contains a single isolated halo with a virial mass
+of the order of $10^{12}$\hMsun simulated using the tree code PKDGRAV
 \citep{2001PhDT........21S}.  
-The simulation used $\sim 2\times 10^{8}$ particles to resolve this
+The simulation had $\sim 2\times 10^{8}$ particles to resolve this
 region.
@@
 The data available to the public corresponds to a downsampled set 
-of $10^5$ particles which corresponds to a particle mass of
+of $10^5$ particles, which corresponds to a particle mass of
 $2.24\times 10^{7}$\hMsun.
@@
 
-In our bootstrapping experiments we take halos sampled with at least
-$10^{5}$ particles and subsample each halo by factors of $2$ up to
-$10^{3}$ to measure the concentration every time the halo is
-resampled. 
-We use a two-sample Kolmogorov-Smirnov (KS) test to check that the
-bootstrapped sets are a fair subsample of the parent halo.
-Using the KS test we compare the list of radial distances from each
-subsample against that of its parent halo.
+We take halos with at least $10^{5}$ particles and subsample them by
+factors of $2$ up to $10^{3}$. 
+We measure the concentration at every resampling.
+We use a two-sample Kolmogorov-Smirnov (KS) test to  compare the list
+of radial distances from each subsample against that of its parent halo.
 We find that the resulting p-value distribution is flat.
-This confirms that the radial distribution of particles in the
-bootraped halo is consistent with coming from the distribution given
-by the parent halo.
+This confirms that the radial particle distribution in the bootraped
+halo is consistent with coming from the distribution given by the
+parent halo.
 
@@
 iteration has an effect smaller than $1\%$ in the concentration. 
-We extract in total 10000 bootstrapping samples for the Bolshoi
-and the Via Lactea simulations.
 In the Bolshoi simulation we select 14 massive halos and create 700
@@
 function of particle number.  
-As expected, for a large enough particle number, $N_{s}>4\times 10^3$,
-the results of the three algorithms coincide below the $1\%$ level.
+This can be interpreted as the statistical bias on the concentration
+estimate. 
+For large enough particle numbers, $N_{s}>4\times 10^3$ the results of
+the three algorithms show a bias below the $1\%$ level.
 For a lower number of particles the results start to deviate.
@@
 behaviour underestimating the concentration only by a factor of
-$1\%$-$3\%$
+$1\%$-$3\%$.
+Work  that studied the effect of
+lowering numerical resolution on the same individual halos
+\citep{2008MNRAS.391.1685S} yielded similar values for the
+concentration across resolutions.  That work  explored a particle
+number range $>5\times 10^5$, completely consistent with our result that the
+bias can only be evident for particle numbers $<4\times 10^4$.
 
-The thin continous lines on the same panel shows a fit to the data
-with the following functional form 
+The thin lines on the same panel show a fit to the function 
 \begin{equation}
-f_{\rm off} = \frac{A}{(1+\log_{10}N_s)^{B}}.
+f_{\rm off} = \frac{A}{(1+\log_{10}N_s)^{B}},
 \label{eq:f_off_fit}
 \end{equation} 
-for the dataset shown in the panel we find $A=2842\pm 1900$,
-$B=7.96\pm 0.54$ for the density method; $A=239\pm 131$,
-$B=6.23\pm 0.43$ for the velocity method; $A=-0.46\pm 3.49$,
-$B=0.79\pm 1.31$ for the integrated mass method.
-The uncertainties are estimated from the covariance  matrix resulting
-from the non-linear optimization procedure. The lines on Figure
-\ref{fig:downsampling} are plotted using these best values.
+%
+with $A=2842\pm 1900$, $B=7.96\pm 0.54$; $A=239\pm 131$, $B=6.23\pm
+0.43$ and $A=-0.46\pm 3.49$, $B=0.79\pm 1.31$ for the density,
+velocity and mass method, respectively.
 
@@
 %
-An interesting consequence of this result is that $\sigma_c=1$ for
-$N_s=32$ particles, independent of the method used to estimate the
-concentration.
 
-The circles in the same Figure show the $1\sigma$ uncertainty as
-estimated from the MCMC chains using the integrated mass method on all
-the relaxed halos in the Bolshoi simulation sample. 
+The circles in the same Figure show the $1\sigma$ uncertainty on all
+the relaxed halos in the Bolshoi simulation sample using the MCMC
+results.  
 To allow for a fair comparison with the bootstrapping results, this
-uncertainty was normalized by the concentration value.
-Below the range $N_{s}<10^5$ the MCMC uncertainty is lower than the
-bootstrapping estimate, with a weak dependence on the particle
-number.
+uncertainty is normalized to the concentration value.
+The uncerainty from the bootstrapping experiment provides an upper
+bound uncertainty on the concentration estimate for individual halos.
 
@@
 
-We now compare the results for the mass-concentration
-relationship obtained with the three different algorithms.
-This helps us to study the concentration results
-for the new algorithm and, more importantly, showcase a probable
-consequence of the biases detected through bootstrapping.
+We now inspect the mass-concentration relationship 
+results with the three different algorithms.
+This can help us to identify possible consequences of the 
+biases detected through the bootstrapping experiments.
 
@@
 algorithms. The thin dashed line marks the trend reported by
-\citep{Prada2012} using the velocity method.
+\citep{Prada2012} using the velocity method, showing that our
+velocity method implementation can reproduce their results.
 
-We notice first that the results from the new algorithm follow very
+The results from the new algorithm follow very
 closely the velocity algorithm at high masses ($M_h>10^{12}\hMsun$ or
@@
 uncertainties.
+
+We hypothesize that the increase in the results for the velocity
+and density methods below $4\times 10^{3}$ particles comes from the
+systematic bias described in the previous section.  
+To test the general consistency of this hypothesis, we correct the
+concentration values in the velocity and integrated mass methods by a
+factor of $1/(1+f_{\rm  off})$, using the definition in Equation
+(\ref{eq:f_off}) and the  
+parameters obtained from the data presented in Figure
+(\ref{fig:downsampling}).  
+The correction brings into good agreement the results between the
+velocity/density methods and the new algorithm.
 
@@
 
-We hypothesize that the increase in the results for the velocity
-and density methods below $4\times 10^{3}$ particles comes from the
-systematic bias described in the previous section.  
-To test the general consistency of this hypothesis, we correct the
-concentration values in the velocity and integrated mass methods by a
-factor of $1/(1+f_{\rm  off})$, using the definition in Equation
-(\ref{eq:f_off}) and the  
-parameters obtained from the data presented in Figure
-(\ref{fig:downsampling}).  
-The correction brings into good agreement the results between the
-velocity/density methods and the new algorithm.
+How do these results impact the most recent mass-concentration estimates? 
+\cite{Ludlow2016} and \cite{Klypin2016} estimated the mass-concentration
+relation over different suites of cosmological N-body simulations using the
+density and velocity methods, respectively. 
+Both used halos with at least $5\times 10^{3}$ particles.
+This imposes a lower halo mass limit of $\sim 10^{12}$\hMsun (Figure 8
+in \cite{Ludlow2016}, Figure 17 in \cite{Klypin2016}) to have robust
+estimates. 
+This means that their results for individual halos should not be
+affected by the bias we report here.
+However, this also leaves open the question about what other methods
+can robustly say about the flattening we report below $10^{12}$\Msun
+using the new method.
 
@@
 concentration estimates. 
-We found that methods commonly used in the literature present a large
-bias by overestimating concentrations by factors of $15\%$-$20\%$ for
-halos with $200$ particles, or $7\%$-$10\%$ for halos with $500$
-particles.  
+We found that methods commonly used in the literature can overestimate
+the concentrations by factors of $15\%$-$20\%$ for halos with $200$
+particles, or $7\%$-$10\%$ for halos with $500$ particles.  
 This procedure provides a robust technique to quantify the bias in
@@
 
-These results motivated us to introduce a method with a robust
-performance at low particle numbers.
-This method is based on the integrated mass profile. 
-The results of the algorithm on the same data sample showed a bias  of
-$< 3\%$ for halos with $200$ particles and less than $1\%$ for halos
-with $500$ particles or more.  
+These results motivated us to introduce a new method based on the
+integrated mass profile that show a robust performance at low particle
+numbers. 
+The new algorithm showed a bias  of $< 3\%$ for halos with $200$
+particles and less than $1\%$ for halos with $500$ particles or more.  
 To keep the bias of the velocity and density methods below $2\%$ only halos
-with at least $\sim 4000$ particles should be taken into account.
+with at least $\sim 4000$ particles should be considered.
 
-Measuring the mass concentration relationship the three methods are in
-broad agreement within the statistical  uncertainties, although there
-are some noticeable differences. 
-For instance, the density method produces systematically higher
-concentrations by a factor of $15\%$ compared to the velocity method.
+The three methods are in broad agreement, within the statistical
+uncertainties, concerning their estimates of the  mass-concentration
+relationship. 
+Some noticeable differences include a $15\%$ systematically higher 
+concentrations in the density method compared to the velocity method.
 This systematic offset has been reported before with the same dataset 
@@
 without any conclusive explanation for its origin. 
-A second difference is that the velocity and integrated mass methods
+Another difference is that the velocity and integrated mass methods
 start to differ for masses below $10^{12}\hMsun$ ($\sim 4000$
@@
 
-These results show that using the integrated mass profile to find the
-Dark Matter halo concentration is a tool deserving deeper scrutiny.   
+These results show that using the integrated mass profile to estimate the
+DM halo concentrations is a tool deserving deeper scrutiny.   
 Further tests with larger simulated volumes, varying numerical
-resolution and different density profiles are the next natural step to
-explore the full potential of this new method.
+resolution, stacked data and different density profiles are the next
+natural step to explore the full potential of this new method.
 
@@
 
- The authors acknowledge the technical support from the new
- high-performance computing facility at Uniandes. JEFR acknowledges
- financial support from Vicerrector\'ia de Investigaciones at Uniandes
- through a FAPA project. JCMC acknowledges financial support from
- ``Estrategia de  sostenibilidad 2014-2015, Universidad de
- Antioquia''. The authors also thank Tom\'as Verdugo, Stefan
- Gottloeber and Nelson Padilla for their comments on earlier version
- of this work.
+ We acknowledge technical and financial support from Uniandes
+ and Universidad de Antioquia.
+ We acknowledge discussions with Tom\'as Verdugo, Stefan Gottloeber and Nelson
+ Padilla.
+ We thank the anonymous referee for comments that helped us improve
+ the presentation of these results.
 
@@
 %\bibliography{references}
-\begin{thebibliography}{15}
+
+\begin{thebibliography}{18}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
   2016, \mnras, 457, 4340
+
+\bibitem[{{Klypin} {et~al.}(2011){Klypin}, {Trujillo-Gomez}, \&
+  {Primack}}]{2011ApJ...740..102K}
+{Klypin}, A.~A., {Trujillo-Gomez}, S., \& {Primack}, J. 2011, \apj, 740, 102
+
+\bibitem[{{Ludlow} {et~al.}(2016){Ludlow}, {Bose}, {Angulo}, {Wang},
+  {Hellwing}, {Navarro}, {Cole}, \& {Frenk}}]{Ludlow2016}
+{Ludlow}, A.~D., {Bose}, S., {Angulo}, R.~E., {Wang}, L., {Hellwing}, W.~A.,
+  {Navarro}, J.~F., {Cole}, S., \& {Frenk}, C.~S. 2016, \mnras, 460, 1214
 
@@
 
+\bibitem[{{Springel} {et~al.}(2008){Springel}, {Wang}, {Vogelsberger},
+  {Ludlow}, {Jenkins}, {Helmi}, {Navarro}, {Frenk}, \&
+  {White}}]{2008MNRAS.391.1685S}
+{Springel}, V., {Wang}, J., {Vogelsberger}, M., {Ludlow}, A., {Jenkins}, A.,
+  {Helmi}, A., {Navarro}, J.~F., {Frenk}, C.~S., \& {White}, S.~D.~M. 2008,
+  \mnras, 391, 1685
+
 \bibitem[{{Stadel}(2001)}]{2001PhDT........21S}

### 2016-08-25 paper/ms.tex
nailed the word count

@@
 likelihood function distribution.
+This runs roughly proportional to $N$. Using a single 2.3Ghz CPU core with two
+walkers over 500 steps takes approximatly $0.5$ miliseconds per halo per
+particle in the halo, i.e. a halo with $N=2\times 10^{3}$ can be fit
+in one second approximately.
+
 From the $\chi^2$ distribution we find the optimal value of the
@@
 number range $>5\times 10^5$, completely consistent with our result that the
-bias can only be evident for particle numbers $<4\times 10^4$.
+bias can only be evident for particle numbers $<4\times 10^3$.
 

### 2016-08-25 paper/ms.tex
agradecimientos

@@
 likelihood function distribution.
-This runs roughly proportional to $N$. Using a single 2.3Ghz CPU core with two
-walkers over 500 steps takes approximatly $0.5$ miliseconds per halo per
-particle in the halo, i.e. a halo with $N=2\times 10^{3}$ can be fit
-in one second approximately.
-
-From the $\chi^2$ distribution we find the optimal value of the
-concentration and its associated uncertainty. 
+From the $\chi^2$ distribution we find the optimal concentration value
+and its associated uncertainty.   
 We stress that different choices for $\sigma^2_{\rm eff}$ do not
 affect the optimal concentration value, only its uncertainty.
+
+Runtime is roughly proportional to $N$. Using a single 2.3Ghz CPU core with two
+walkers over 500 steps takes $\sim 0.5$ miliseconds per halo per
+particle in the halo, i.e. a halo with $N=2\times 10^{3}$ can be fit
+in one second.
 
@@
 Further tests with larger simulated volumes, varying numerical
-resolution, stacked data and different density profiles are the next
-natural step to explore the full potential of this new method.
+resolution, higher redshifts, stacked data and different density
+profiles are the next natural step to explore the full potential of
+this new method.
 
@@
 
- We acknowledge technical and financial support from Uniandes
+ We acknowledge financial support from Uniandes
  and Universidad de Antioquia. 
- We acknowledge discussions with Tom\'as Verdugo, Stefan Gottloeber and Nelson
- Padilla.
- We thank the anonymous referee for comments that helped us improve
+ We thank Tom\'as Verdugo, Stefan Gottloeber and Nelson  Padilla for
+their feedback.
+We thank the anonymous referee for comments that improved
 the presentation of these results.

### 2016-08-25 paper/ms.tex
updated caption

@@
 \vspace{-0.5cm}
-\caption{\emph{Left panel}. Average value of the fractional offset ($f_{\rm
-    off}$ (Eq. \ref{eq:f_off}) between the concentration in a halo at 
-  high resolution and its bootstrapped versions. 
+\caption{\emph{Left panel}. Bias estimated via bootstrapping on the
+  concentration as a function of particle number.
   Thick (thin) lines correspond to massive halos in the Bolshoi (Via
@@
   \emph{Right panel.}
-  1$\sigma$ uncertainties on the offset and the concentration
-  estimates from the integrated mass method.  
+  1$\sigma$ uncertainties on the bootrsapped halos (lines) and the MCMC
+  uncertainties on the concentration estimates for each halo using the
+  integrated mass method (circles).   
   Lines show the width between the 14 and 86 percentiles
   of the $f_{\rm off}$ distribution at fixed particle number. 
-  The lines include the results for the three methods: maximum
-  velocity, density and integrated mass.
-  Grey symbols correspond to the $1\sigma$ uncertainty on each of
-  the halos in the Bolshoi Simulation as a result of the MCMC
-  sampling. 
-  To allow a fair comparison with $f_{\rm off}$, this uncertainty has
+  The lines include the results for the three methods using Bolshoi data.
+  To allow a fair comparison agains $f_{\rm off}$, the MCMC uncertainty has
   been normalized by the preferred concentration value for each halo. 
@@
 a given normalized radius, $x$, the logarithm of the normalized
-integrated mass, $m$, approximately follows a gaussian distribution
+integrated mass, $m$, approximately follows a Gaussian distribution
 with variance
@@
 To avoid the expensive computation and inversion of a full covariance
-matrix we use the bootsrapping data to calibrate an effective
+matrix we use the bootstrapping data to calibrate an effective
 $\sigma_i^2\approx \sigma_{\rm eff}^2(x_i)$.
@@
 
-Runtime is roughly proportional to $N$. Using a single 2.3Ghz CPU core with two
-walkers over 500 steps takes $\sim 0.5$ miliseconds per halo per
+Run-time is roughly proportional to $N$. Using a single 2.3Ghz CPU core with two
+walkers over 500 steps takes $\sim 0.5$ milliseconds per halo per
 particle in the halo, i.e. a halo with $N=2\times 10^{3}$ can be fit
@@
 uncertainty is normalized to the concentration value.
-The uncerainty from the bootstrapping experiment provides an upper
+The uncertainty from the bootstrapping experiment provides an upper
 bound uncertainty on the concentration estimate for individual halos.

### 2016-08-25 paper/ms.tex
all files updated

@@
 must keep the dependence on $x$ that we have discovered for the
-diagonal elements and must give similar curves of $\chi^{2}(c,x_i)$-$c$
-around the minimum as the full covariance matrix.
-We found that this effective $\sigma_{\rm eff}^2$ can be approximated
+diagonal elements and must give similar curves of $\chi^{2}(c,x_i)$
+vs. $c$ around the minimum as the full covariance matrix.
+We found that the effective $\sigma_{\rm eff}^2$ can be approximated
 as

### 2016-08-25 paper/ms.tex
prada

@@
   The three methods have a similar spread but for clarity we only show
-  the spread for the concentrations estimated using the new method.   
+  the spread for the new method.   
   The dotted line corresponds to fits reported by \citep{Prada2012}.
@@
 affected by the bias we report here.
-However, this also leaves open the question about what other methods
+This also leaves open the question about what other methods
 can robustly say about the flattening we report below $10^{12}$\Msun
 using the new method. 
+However, there are other results at lower masses and higher redshifts
+\citep[i.e.][]{Prada2012} that should be reconfirmed using higher resolution
+simulations as they use halos with only $500$ particles.
 
@@
 their feedback.
-We thank the anonymous referee for comments that improved
+We thank the anonymous referees for comments that improved
 the presentation of these results.

### 2016-09-01 paper/ms.tex
shorter caption
updated draft

@@
   The left panel shows the raw results coming from each algorithm. 
-  The right panel introduces a correction on the velocity and
-  integrated mass results following the results of the downsampling
-  experiments presented in Figure 
-  \ref{fig:downsampling}.
+  The right panel introduces a correction following the results on the
+  bias as a function of particle number.
   \label{fig:concentration}} 
@@
 parent halo.  
+Why not using different simulations with the same initial conditions
+and lower resolutions \citep[i.e.][]{2008MNRAS.391.1685S}?. 
+Because we want to be sure that we are only measuring the bias of a
+given method as a function of particle number for statistically
+identical halos, and not a possible simulation artifact that changes
+the halo structure.
 
@@
 $1\%$-$3\%$.
-Work  that studied the effect of
-lowering numerical resolution on the same individual halos
-\citep{2008MNRAS.391.1685S} yielded similar values for the
-concentration across resolutions.  That work  explored a particle
-number range $>5\times 10^5$, completely consistent with our result that the
-bias can only be evident for particle numbers $<4\times 10^3$.
 

### 2016-09-07 paper/ms.tex
Correcciones de revision listas

@@
 \begin{abstract}
-We use bootstrapping to estimate the bias of concentration
-estimates on N-body dark matter halos as a function of particle
-number. 
-We find that algorithms based on the maximum radial velocity
-and radial particle binning tend to overestimate the concentration by 
-$15\%-20\%$ for halos sampled with $200$ particles and by $7\%$-$10\%$
-for halos sampled with $500$ particles. 
-To control this bias at low particle numbers we propose a new
-algorithm that estimates halo concentrations based on the integrated
-mass profile.
-The method uses the full particle information without any binning,
-making it reliable in cases when low numerical resolution becomes a
-limitation for other methods.
+We use bootstrapping to estimate the bias of concentration estimates
+on N-body dark matter halos as a function of particle number.  We find
+that algorithms based on the maximum radial velocity and radial
+particle binning tend to overestimate the concentration by $15\%-20\%$
+for halos sampled with $200$ particles and by $7\%$-$10\%$ for halos
+sampled with $500$ particles.  To control this bias at low particle
+numbers we propose a new algorithm that estimates halo concentrations
+based on the integrated mass profile.  The method uses the full
+particle information without any binning, making it reliable in cases
+when low numerical resolution becomes a limitation for other methods.
 This method reduces the bias to $< 3\%$ for halos sampled with
-$200$-$500$ particles.
-The velocity and density methods have to use halos with least $\sim
-4000$ particles in order to keep the biases down to the same low
-level. 
-We also show that the mass-concentration relationship could be
-shallower than expected once the biases  of the different
-concentration measurements are taken into account. 
-These results show that bootstrapping and the concentration estimates
-based on the integrated mass profile are valuable tools to probe the
+$200$-$500$ particles.  The velocity and density methods have to use
+halos with at least $\sim 4000$ particles in order to keep the biases
+down to the same low level.  We also show that the mass-concentration
+relationship could be shallower than expected once the biases of the
+different concentration measurements are taken into account.  These
+results show that bootstrapping and the concentration estimates based
+on the integrated mass profile are valuable tools to probe the
 internal structure of dark matter halos in numerical simulations.
@@
 formation takes place, and where the effects of baryon physics on the
-dark matter distribution are still unknown. 
+DM distribution are still unknown. 
 This profile is a double power law in radius, where the transition
@@
 The concentration of the NFW profile provides a conceptual framework
-to study simulated dark matter halos as a function of redshift and
+to study simulated DM halos as a function of redshift and
 cosmological parameters.  
@@
 where $\rho_c\equiv 3H^2/8\pi G$ is the Universe critical density, $H$
-is the Hubble constant, $G$ and the universal gravitational constant,
+is the Hubble constant, $G$ the universal gravitational constant,
 $\delta_c$ is the halo dimensionless characteristic density and $r_s$
@@
 To date, there are two standard methods to estimate concentrations in
-dark matter halos extracted from N-body simulations.  The first method
+DM halos extracted from N-body simulations.  The first method
 takes all the particles in the halo and bins them in the logarithm of
@@
 This method has been broadly used for more than two decades to study
-the mass-concentration-redshift relation of dark matter halos. 
+the mass-concentration-redshift relation of DM halos. 
 A second method uses the circular velocity profile.  It finds the
@@
 The first is the Bolshoi run, a cosmological simulation that follows
-the non-linear evolution of a dark matter density field sampled with
+the non-linear evolution of a DM density field sampled with
 $2048^3$ particles over a cubic box of $250\ \hMpc$ on a side.   The
@@
 
-The right panel in Figure \ref{fig:downsampling} shows different uncertainty
-results.
-The lines show the difference between the 14 and 86 percentiles in the
-$f_{\rm off}$ distribution at fixed mass. 
-Each line corresponds to the three different methods to estimate the
-concentration and the two simulations.
-This shows that the bootstrapping technique can help us to assign a
-$1\sigma$ uncertainty to the concentration values at a fixed $N_s$as 
+The right panel in Figure \ref{fig:downsampling} shows different
+uncertainty results.  The lines show the difference between the 14 and
+86 percentiles in the $f_{\rm off}$ distribution at fixed mass.  Each
+line corresponds to the three different methods to estimate the
+concentration applied to both simulations.  This shows that the
+bootstrapping technique can help us to assign a $1\sigma$ uncertainty
+to the concentration values at a fixed $N_s$as
 %
@@
 
- We acknowledge financial support from Uniandes
- and Universidad de Antioquia. 
- We thank Tom\'as Verdugo, Stefan Gottloeber and Nelson  Padilla for
-their feedback.
-We thank the anonymous referees for comments that improved
-the presentation of these results.
+ We acknowledge financial support from Uniandes and Estrategia de
+ Sostenibilidad 2014-2015 Universidad de Antioquia.  We thank Tom\'as
+ Verdugo, Stefan Gottloeber and Nelson Padilla for their feedback.  We
+ thank the anonymous referees for comments that improved the
+ presentation of these results.
 
